### 2023-08-01 paper.tex
update journal

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
\documentclass[journal]{IEEEtran}  % Comment this line out

\IEEEoverridecommandlockouts                       % This command is only
% needed if you want to
% use the \thanks command
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org

\input{preamble/common}
\usepackage{cleveref}
\graphicspath{{Figs/}}

\pagenumbering{arabic}

\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}

\title{\LARGE \bf
 %Distributed Task Assignment for Cyber-Physical Security in Multi-Agent Systems
 Multi-agent cross-trajectory planning using graph theory}
 %with Applications to Cyber-Physical Security}
% with Applications to Introspection Monitoring}
\author{Ziqi Yang and Roberto Tron\thanks{This project is supported by the National Science Foundation grant "CPS: Medium: Collaborative Research: Multiagent Physical Cognition and Control Synthesis Against Cyber Attacks" (Award number 1932162).}}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control. Such compromises could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission. To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots as an additional security measure. Our approach guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations. We achieve this by introducing \emph{reachability} constraints into the previously developed continuous trajectory planning algorithm. These constraints ensure an empty intersection between the sets of locations that the agents could potentially reach and the forbidden regions. Furthermore, to enhance system resilience, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments. This redundancy enables robots to deviate from their assigned sub-teams and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories simultaneously. To efficiently plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories. We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
\end{abstract}

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. The use of MRS offers numerous advantages, but it also introduces new cybersecurity challenges, including unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. Given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats. In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.

These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience} \zyang{add most recent articles}. The work of \cite{wardega2019resilience} provide exact solution for grid-world configuration. Using the onboard sensing capabilities, robots can perform inter-robot observations as an additional security measure. Each robot' self-report includes not only its own status, but also additional observations of other robots' status. For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''. Similarly, robot $j$ also reports its observations of robot $i$ to the CE. This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.

When transforming the solution to continuous configuration spaces, additional analysis is needed on the reachability of robots in order for the security of co-observation schedule to hold. More broadly, the problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.  This constraint is formulated using an ellipsoidal bound of the reachability region, and the idea of using an ellipsoidal bound to limit the search space is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm.

We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.  The idea is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm; in that case, an ellipsoidal bound is used to limit the search space with the initial and goal states fixed. In our case, we use a similar bound to optimize the location of the two states to exclude the forbidden region from the ellipsoidal region. We propose a mathematical formulation of reachability regions that is compatible with the solver from \zyang{cite ADMM} as a spatio-temporal constraint.

However, two main challenges have been identified in \cite{wardega2023hola} \zyang{previous works}. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path. Agent 3 in the Figure \zyang{ref fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas. Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \zyang{ref fig:trajectories-more-constraint} and \zyang{ref fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots. This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. These challenges are addressed in Chapter \ref{chapter:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.

We propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams. Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
In this chapter, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in Chapter \ref{chapter:task-assignment}), making it more difficult for attackers to successfully plan and execute attacks. Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.

\begin{figure}
	\centering
    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.45\linewidth]{co-observ}}
    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.45\linewidth]{cross-traj}}

    \caption{\ref{fig:example-co-observation} Limited by the co-observation requirement, both red and blue robot follow the co-observation secured routes (solid lines) and abandon the optimal ones (dashed line). \ref{fig:example-cross-traj} Through cross-trajectory co-observations, the blue team sends one robot to follow the red team (solid blue line) and performs co-observation while having the rest of the robots following the optimal trajectory.}\label{fig:cross-traj-comparison-set}
\end{figure}

\paragraph{Paper contributions} In this paper, we formulate a way to enforce an empty intersection between forbidden region and reachability regions, such that if an attacker takes control of the robots, they cannot perform an undetected attack by entering forbidden regions and meeting co-observation schedules at the same time. The constraints are formulated using an ellipsoidal bound of the reachability region.

We propose to incorporate redundancy in the form of \emph{sub-team}s of multiple robots in place of individual robots along each route. This allows robots to deviate from their assigned sub-team, and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories. We propose a formulation of the multi-flow problem on unsecured MRS trajectories to plan the cross-trajectory co-observations that can preserve the security against plan-deviation attacks.

\section{Preliminaries}
In this section, we review various mathematical concepts that will provide the foundations and context for our novel constraint.
\subsection{Ellipsoidal reachability constraints}\label{Chapter:ProblemFormulation}
  The reachability region is defined as the set of locations $x(t)$ that a robot can reach between two given fixed positions:

  \begin{definition}
    The \emph{reachability region} for two waypoints $x(t_1)=x_1$, $x(t_2)=x_2$ is defined as the sets of points $x'$ in the workspace such that there exist a trajectory $x(t)$ where $x(t')=x'$, $t_1\leq t' \leq t_2$ and $x(t)$ satisfies the velocity constraint $d(x(t),x(t+1))\leq v_{max}$.
  \end{definition}
  This region can be analytically bound via an ellipsoid:
  \begin{definition}\label{Def_Reachability}
    The \emph{reachability ellipsoid} is the region  $\mathcal{E}(x_1,x_2)=\{\tilde{x}\in\mathbb{R}^n: d(x_1,\tilde{x})+d(\tilde{x}+x_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
  \end{definition}
  % The reachability ellipsoid for a robot during time $[t_1,t_2]$ is the locations it could visit if only the planning at time $t_1$ and $t_2$ is obeyed.
  The region $\cE(x_1,x_2)$ is an ellipsoid with foci at $x_1,x_2$, center $o_{\cE} = \frac{1}{2}(x_1+x_2)$, and the major radius equal to $a$. Let $c_\cE=\frac{1}{2}\norm{x_1-x_2}=\norm{o_\cE-x_1}$ be the distance from the center to a foci.

  The reachability ellipsoid is an over-approximation of the exact reachability region; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.

\subsection{Rapidly-exploring Random Trees}
We use RRT* as a component of the solution \cite{karaman2010incremental}, which is an optimized variant of the rapidly-exploring Random Trees (RRT). As a optimal path planning algorithm, RRT* returns the shortest paths between an initial location and multiple potential goals. We assume that the generated paths can be travelled in both directions (this is used later in our analysis). The basic RRT* algorithm is shown in Algorithm \ref{alg:rrt}. For a given tree $G=(V,E)$, key functions called by the algorithm are
\begin{description}
\item[$\texttt{Sample}(i)$] This function returns independent identically distributed samples from the free configuration space.
\item[$\texttt{Nearest}(x)$] This function returns the vertex $v\in V$ that is closest in Euclidean distance to the input point $x$.
\item[$\texttt{Steer}(x,y)$] This function returns a point $z$ that minimize $\norm{z-y}$ subject to $\norm{z-x}\leq \eta$ for a prespecified $\eta>0$.
\item[$\texttt{ObstacleFree}(x,y)$] This function returns whether the line segment between $x$ and $y$ is free of collision.
\item[$\texttt{Cost}(v)$] This function assigns a non-negative cost (total travel distance in our application) to the unique path from the initial position to $v$ . 
\item[$\texttt{Parent}(v)$] This is a function that maps the vertex $v$ to $v'\in V$ such that $(v',v)\in E$
\end{description}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.8\linewidth]{RRT_example_new}
\caption{RRT* used to find trajectory from a point to different trajectories}
\label{fig:RRT*}
\end{center}
\end{figure}

	\begin{algorithm} 
		\caption{RRT*($x_{init}, \{x_{goal}\}$)} \label{alg:rrt}
		\begin{algorithmic}[1]
			\State $V_{goal}\gets\{x_{goal}\}$
			\State $V\gets x_{init} \union V_{goal} $, $E\gets 0$
			\State $i\leftarrow 0$
			\While{$i<N$}
			\State $G\leftarrow (V,E)$
			\State $x_{rand}\leftarrow \texttt{Sample}(i)$; $i=i+1$;
			\State $x_{nearest}\leftarrow \texttt{Nearest}(G=(V,E),x_{rand})$;
			\State $x_{new}\leftarrow\texttt{Steer}(x_{nearest},x_{rand})$;
			\If{$\texttt{ObstacleFree}(x_{nearest},x_{new})$}
			\State $V\leftarrow V\cup \{x_{new}\}$;
			\State $x_{min}\leftarrow x_{nearest}$;
			\ForAll{ $x_{near}\in X_{near}$}
				\If{$\texttt{ObstacleFree}(x_{near},x_{new})$}
					\State $c'\leftarrow \texttt{Cost}(x_{near})+c(\texttt{Line}(x_{near}, x_{new}))$;
					\If{$c'<\texttt{Cost}(x_{new})$}
						\State $x_{min}\leftarrow x_{near}$;
					\EndIf			
				\EndIf
			\EndFor

			\ForAll{$ x_{near}\in X_{near}\backslash {x_{min}} $}
				\If{$\texttt{ObstacleFree}(x_{new},x_{near})$ and $\texttt{Cost}(x_{near})>\texttt{Cost}(x_{new}+c(\texttt{Line}({x_{new},x_{near}})))$}
					\State $x_{parent}\leftarrow \texttt{Parent}(x_{near})$;
					\State $E' \leftarrow E' \backslash \{ (x_{parent}, x_{near})\}$;
					\State $E' \leftarrow E' \union  \{ (x_{new}, x_{near})\} $
				\EndIf
			\EndFor
			\EndIf
			\EndWhile
			\State \Return $V_{goal}$;
		\end{algorithmic}
	\end{algorithm}

\section{Problem overview}

Assume we have a total of $N$ robots in the system. We define a partition $\cI=\union_p \cI_p$ of the robots such that robots in \emph{sub-team} $\cI_p$ have the same nominal trajectory. We use the planner introduced in Chapter \ref{chapter:Multi-agent-ADMM} to generate multi-robot trajectories with $N_{p}<N$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{0,\ldots,N_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, t_{e}\}$. Within each sub-team, at least one robot is required to follow the reference trajectory to fulfill the required tasks. Meanwhile, the additional robots can switch from one reference trajectory to another in order to perform co-observation with different sub-teams. We refer to the new type of co-observations as \emph{cross-trajectory co-observation}s. The goal is to find the cross trajectory co-observation plan to secure an unsecured MRS trajectory as with a minimal number of additional robots.

To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. Vertices $V_{q}$ are a key locations in $\{q_p\}$ that are used to perform co-observations. Part of these vertices are \emph{checkpoints} which are selected to guarantee that, if robots deviate and reach forbidden regions, they will miss the scheduled co-observations. Other vertices are selected to connect checkpoints on different trajectories. The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges of two types, trajectory edges $E_{t}$ and cross-trajectory edges $E_{c}$, representing paths which robots can take. The trajectory edges $E_{t}$ represent the reference trajectories, where each edge connects two waypoints on the trajectory of the same sub-team. The cross-trajectory edges $E_{c}$ connect vertices on different reference trajectories, with at least one of the vertices being a checkpoint. These edges represent the potential paths that robots can take to travel and perform co-observations between trajectories of different sub-teams. Similar to the work done by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.

In this chapter, we present a solution to the cross-trajectory co-observation planning problem. This approach consists of two components: constructing the checkpoint graph based on unsecured multi-robot trajectories, which includes the location of security checkpoints and cross-trajectory paths, and the formulation of the network flow problem to solve for the co-observation plan.
\section{Checkpoint graph construction}

In this section, we describe in detail how we define and search for security checkpoints and use the checkpoints to find cross-trajectory edges and construct a directed security graph $G_{q}=(V_{q},E_{q})$.

\subsection{Checkpoints}\label{sec:security-checkpoint}
Let $q\in\real{nmT}$ be the MRS trajectory found in Chapter \ref{chapter:Multi-agent-ADMM} for $m$ sub-teams with time horizon $T=t_{e}$, with $q_{p}(t)$ be the reference trajectory waypoint for sub-team $p$ at time $t$. A checkpoint $v_i=(q_{i},t_{i})$ is a pair composed of a location $q_{i}=q_{p}(t_{i})$ and a time $t_{i}$ representing a co-observation between a sub-team $\cI_p$'s member and robots either from the same sub-team or different ones. For convenience, let $\cI_{v_{i}}$ represent the corresponding sub-team $v_{i}$ belongs to.

Similar to the requirements of co-observations introduced in Chapter \ref{chapter:Reachability_Constraints}, checkpoints $V_{p}=\{ v_{p_{1}}, \dots ,v_{p_{e}}\} \subset V_{q}$ for a reference trajectory $\{q_{p}(t)\}$ of sub-team $p$ need to guarantee that the reachability region between consecutive checkpoints $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}})$ does not intersect with any of the forbidden areas. For convenience, we denote the union of all forbidden areas as $F$; then the requirement can be written as $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}}) \intersect F = \emptyset$, for every $i$.

We provide a heuristic approach to locate the checkpoints on given trajectories; an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose. We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon. Then, we search for the waypoint $q_{p}(t_{1})$ with the largest $t_{1} \in \{t_{0}, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1}, \dots ,t_{2}\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. $q_{p}(t_{1})$ and $q_{p}(t_{3})$ are then added to $V_{q}$. Afterwards, we set $t_{0}=t_{1}$, $t_{2}=t_{3}$ and repeat the same process. The search is stopped when $t_{0}>t_{2}$, or when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$. A toy example is shown in Figure \ref{fig:checkpoint-generate}.

\begin{figure}
	\centering
    \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_1}}
    \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_2}}
    \caption{Checkpoint generation example}\label{fig:checkpoint-generate}
\end{figure}

\subsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
After locating checkpoints $\union_p V_p$ for all sub-teams, we can search for cross-trajectory edges to connected all checkpoints to trajectories. Cross-trajectory edges represents feasible paths between two references trajectories that allow robots to reach a different reference trajectories and perform co-observations with the corresponding sub-teams. Thus, at least one end of the edges must be a security checkpoint $v_{p} \in \union_p V_p$. Additionally, assuming that only one robot is sent at a time between trajectories, the cross-trajectory edges must satisfy the reachability constraints from Chapter~\ref{chapter:Reachability_Constraints} to ensure that no deviation to forbidden areas can be performed while switching trajectories.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth]{two_edges}
\caption{For checkpoints of the red trajectory, latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.}
\label{fig:two-edges}
\end{center}
\end{figure}

To find cross-trajectory edges, we base our approach on RRT*. First, we search for feasible paths between each security checkpoint in each reference trajectory and all other trajectories, as shown in Figure \ref{fig:RRT*}. Since paths returned by RRT* are optimal and bidirectional, we can analyze the travel time and reachability for each candidate cross-trajectories, and  add these edges to the checkpoint graph if they are feasible.

More vigorously, After a fixed iterations of RRT*, we find all possible and close to optimal paths between one security checkpoint $v_{p}=(q_{p},t_{p}) \in V_{p}$ for sub-team $\cI_p$, and $V_{r} = \{ (q_{{r}_{i}}, t_{{r}_{i}}) \}$ where  $q_{{r}_{i}} = q_{r}(t_{{r}_{i}})$ are the entire waypoints on a reference trajectories for a different sub-team $\cI_{r}$ for a fixed number of RRT* iterations. We can calculate the minimal travel time $t=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path. We call all nodes $v_{{r}_{i}} \in V_{r}$ \emph{arrival node}s if there exist a path between $v_{{r}_{i}}$ and $v_{p}$ with $t_{p}+t<t_{{r}_{i}}$, and the reachability ellipsoid $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$. Similarly, \emph{departure node}s are defined for $v_{{r}_{i}}$ with $t_{p}>t_{{r}_{i}}+t$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$. Given a point $v_{p} \in V_{p}$, we define the \emph{latest departure node} $q_{r}(t^{d}_r)$, and the \emph{earliest arrival node} $q_{r}(t^{a}_r)$ as follows:

\begin{description}
\item[Latest departure node $q_{r}(t^{d}_r)$]: is the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
\item[Earliest arrival node $q_{r}(t^{a}_r)$]: is waypoint with the earliest time $t^{a}_r$ such that a robot from sub-team $\cI_p$ deviating from $v_{p}$ can meet with sub-team $\cI_r$.
\end{description}

For $v_{p} \in V_{p}$, latest departure node $v_{d}=(q_{r}(t^{d}_r),t^{d}_r)$ and earliest arrival node $v_{a}= (q_{r}(t^{a}_r),t^{a}_r)$, if feasible, are added to $V_{q}$. Cross-trajectory edges $(v_{p} \to v_{a})$ and $(v_{d} \to v_{p})$ are added to $E_{q}$. Examples are shown in Figure \ref{fig:two-edges}. Full algorithm is shown in Algorithm \ref{alg:cross-trajectory-edges}.

\begin{algorithm}
\caption{Cross-trajectory edges generation}\label{alg:cross-trajectory-edges}
\begin{algorithmic}
\Procedure{CrossTrajectoryEdges}{$V$}
\State $V_{q} \gets V$; $E_{q}\gets 0$;
\ForAll {$v\in V$}
	\ForAll{$\vq_{r}$ that $\cI_{r} \neq \cI_{v}$}
		\State $V_{q},E_{q} \gets \textsc{AddEdges} (q_{v}, \vq_{r}, V_{q}, E_{q}) $;
	\EndFor
\EndFor
\State \Return $V_{q}, E_{q}$
\EndProcedure
\Procedure{AddEdges}{$q_{v}, \vq_{r}, V_{q},E_{q}$}
\State $t^{d}_r \gets -\infty $; $t^{a}_r \gets \infty$;
\State $\cV_{goal}=RRT^*(q_{v}, \vq_{r})$;
    \ForAll{$ q \in \cV_{goal} $ that $\texttt{Parent}(q)\neq \emptyset $}
        \If{$\texttt{Cost}(q)/ v_{max} < t_{q}-t_{v}$ and $\cE(q, v_{p},t_{q}, t_{v_{p}})\union F = \emptyset$}
        		\If{$t_{q}<t^{a}_r$}
			\State $t^{a}_r \gets t_{q}$;
		\EndIf
        \ElsIf{$\texttt{Cost}(q)/ v_{max} < t_{v} - t_{q}$ and $\cE(q, v_{p},t_{q},t_{v_{p}})\union F = \emptyset$}
        		\If{$t_{q}>t^{d}_r$}
			\State $t^{d}_r \gets t_{q}$;
		\EndIf
        \EndIf
    \EndFor
    \If{$t^{d}_r \neq -\infty $ and $t^{a}_r \neq \infty$}
    \State $v_{a} \gets (q(t^{a}_r),t^{a}_r)$; $v_{d} \gets(q(t^{d}_r), t^{d}_r)$;
    \State $V_{q}\gets V_{q} \union v_{a}$; $V_{q}\gets V_{q} \union v_{d}$;
    \State $E_{q}\gets E_{q} \union (v_{p} \rightarrow v_{a})$; $E_{q}\gets E_{q} \union (v_{d} \rightarrow v_{p})$
    \EndIf
    \State \Return $V_{q},E_{q}$
    \EndProcedure
   \end{algorithmic}
\end{algorithm}

\subsection{In-trajectory edges}\label{sec:Graph-intro}

%With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
All checkpoints $V_{q}$ found in Section~\ref{sec:security-checkpoint} and \ref{sec:cross-traj-edges}, can be divided by the corresponding sub-team and sorted in ascending order of time into $N_{p}$ subsets $V_{p}=\{v^{p}_{0}, v^{p}_{1}, \dots , v^{p}_{T}\}$ where $p\in \{1,\dots, N_{p}\}$. Consecutive edges in the same subset are added to $E_{q}$ as in-trajectory edges $(v^{p}_{i}\rightarrow v^{p}_{i+1} )$. Example are shown in Figure \ref{fig:security-graph-generate}.
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth]{security_graph}
\caption{Example of a two trajectory security graph. Round vertices are checkpoint generated through the heuristic search and triangle vertices are added with the cross-trajectory edges. Additional virtual source $v^{+}$ and sink $v^{-}$ is used later in planning problem.}
\label{fig:security-graph-generate}
\end{center}
\end{figure}

%For convenience, we use $|V_{q}|$ and $|E_{q}|$ to denote the cardinality of the sets $V_{q}$ and $E_{q}$

\section{Co-observation planning problem}
In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network flow problem, and solve it using mixed-integer linear programs (MILP). We assume that there are always \emph{reference robot}s in each sub-team following the reference trajectory.  We want to plan the routes for additional \emph{cross-trajectory robots} to perform co-observation with the reference robots.

To formulate the planning problem as a network multi flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$. The vertices of the new graph are defined as $V= V_{q} \union \{v^{+},v^{-}\}$,  a \emph{virtual source} $v^{+}$ and a \emph{virtual sink} node $v^{-}$ are added to $V$. The edges of the new graph are defined as $ E = E_{q} \union \{( v^{e}_{p},v_{-})\}_{p} \union \{(v_{+},v^{0}_{p})\}_{p}$, where directed edges are added to $E$ from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^e_p$ representing the start and end vertices of sub-team $\cI_p$.

Assume that all the robots starting from the virtual source $v^{+}$ and end in the virtual sink $v^{-}$. Each robot may move from vertex $v_{i}$ to $v_{j}$ if $(v_{i},v_{j})\in E_{q}$. The path of a robot $k$ can be represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $(v_{i},v_{j})$. As required by the security guarantee, reference robots must be seen by at least one surveillance robot at every checkpoint. Thus, the planning problem can then be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $V_{p}$ is included in at least one path in $F$. Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations are preferred compared to co-observation within the same team. This is achieved with the weights for edges $(v_{i},v_{j})\in E$ defined as:
\begin{equation}
	w_{i,j}=\begin{cases}
	-w_{t} & \cI_{v_{i}}=\cI_{v_{j}}, (v_{i},v_{j})\in E_{q}\\
	w_{c} & \cI_{v_{i}} \neq \cI_{v_{j}}, (v_{i},v_{j})\in E_{q}\\
	0 &  (v_{i},v_{j})\in E / E_{q} 
	\end{cases}
\end{equation}
where $w_{c} > w_{t}$.

With the formulation above, the planning problem can be written as an optimization problem, where we want to balance between the co-observation performance and total number of flows (cross-trajectory robots) needed. For convenience, we use $(ij)$ to represent the edge $(v_{i},v_{j})$, and $(+i)$ to represent the edge $(v^{+},v_{i})$.

 \begin{subequations} \label{eq:flow-coverage-problem}
     \begin{align}
        \min &\quad \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} &\label{eq:flow-cost}\\
        \subjectto & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij}, & \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1 & \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
        & f^k_{ij} \in \{0,1\} &  \forall (ij)\in E\label{eq:SingleFLowCapacity}
     \end{align}
 \end{subequations}

The first term in \ref{eq:flow-cost} is total outgoing flow from the source $v^{+}$ while the second term is the total cost of all flows which represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges). The constant $\rho$ is a penalty parameter manually elected to balance between two terms in the cost function. The constraint \eqref{eq:FlowBalanceConstraint} is the flow conservation constraint, which ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$). The constratin \eqref{eq:FlowCoverage} is the flow coverage constraints, which ensures that all security checkpoints $ \{V^{s}_{p}\}$ have been visited by at least one flow (robot). Since the security graph $G_{q}$ is acyclic, this problem is in complexity class $P$, and can be solved in polynominal time \cite{ntafos1979path}.

\section{Co-observation performance}
Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{\cE} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{\cE}$, these flow will not increase the cost and will not have any impact on the solution.  
The trade-off between the number of surveillance robots used, and the overall security performance is a critical consideration in this case. Increasing the number of robots generally contributes to improved security by enabling more cross-trajectory co-observations. However, adding more robots can lead to diminishing returns, as the benefits gained from additional robots may be counterbalanced by increased complexity and coordination challenges. To capture this trade-off, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} allows us to fine-tune the balance between the number of robots employed and the desired task performance. By optimizing this parameter, we can strike a suitable equilibrium between security enhancement and operational efficiency.

To find such tradeoff, we employ an iterative approach. We start with $\cK=1$ and gradually increase it until $F$ contains a empty flow. This indicates that the performance can no longer be improved by adding more robots. To ensure that the value of $\cK$ does not grow unbounded, penalty parameter $\rho$ need to ensure that the second term for a single flow in \eqref{eq:flow-cost} $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}$ is always smaller than $1$.

\section{Result and simulation}
In this section, we test the proposed method starting from the results in Figure \ref{fig:trajectories-more-constraint}, where three trajectories are provided for the map exploration task with no security related constraints (co-observation schedule and reachability). We use the same environment and dynamic setup, where we have a $10m\times10m$ task space, two forbidden regions (two rectangles in  \ref{fig:trajectories-more-constraint}) and robots with a max velocity of $0.5m/dt$.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.4\linewidth]{graph_flow_result_3}
\caption{Security Graph and result for 3 flows}
\label{fig:security-graph-3-flow}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth]{3_flow_result}
\caption{Result of 3 surveillance agents' plan in workspace}
\label{fig:workspace-3-flow}
\end{center}
\end{figure}

We start by adding a total of $\cK=3$ surveillance robots into the workspace using the parameters $w_{c}=10$, $w_{t}=1$ and $\rho = 0.01$. The three trajectories are transformed into the graph $G$ shown in Figure \ref{fig:security-graph-3-flow}, where the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$. Vertices in each column belong to the same trajectory, and edges across different columns are cross-trajectory edges.

The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph. The planning result in the workspace is shown in \ref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \ref{fig:security-graph-3-flow}. Notice that flows represent the robot co-observation plan instead of actual robots, such that the red flow, for example, shows that the sub-team 2 is expecting a robot from sub-team 1, departing at $t=0$ and arriving at $t=10$, and needs to send a robot (not necessarily the same one received from sub-team 1) to sub-team 3, departing at $t=67$ and arriving at $t=79$. This plan is not ideal in terms of our security criteria since co-observations happens between the same pair of surveillance robot and sub-team for the majority of the time with only three cross-trajectory edges that are covered.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.4\linewidth]{graph_flow_result_4}
\caption{Security Graph and result for 4 flows.}
\label{fig:security-graph-4-flow}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth]{4_flow_result}
\caption{Result of 3 surveillance agents' plan in work space.}
\label{fig:workspace-4-flow}
\end{center}
\end{figure}

For the case where $\cK=4$, the results are shown in Figure \ref{fig:security-graph-4-flow}-\ref{fig:workspace-4-flow}. With one additional robot added, there are significant increase in the total cross-trajectory edges covered, and sub-teams performs co-observation with different robots during the task period.

If we further increase $\cK>4$, we do not get a better result; instead, the planner will generate 4 flows with the rest $\cK-4$ flows empty.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\linewidth]{nflow_vs_cost}
\caption{Plan reach optimality when $\cK=4$, further increase of $\cK$ does not increase the cost of objectives.}
\label{fig:flow-n-vs-cost}
\end{center}
\end{figure}

\section{Summary}
In this chapter, we provide a method to enhance the security of a multi-robot system without sacrificing the performance. This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories. We model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories. We have shown that the co-observation planning problem across different trajectories can be transformed into a multi flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.

{\small
\bibliographystyle{unsrt}
\bibliography{ADMM_planning,ACC}
}

\end{document}

### 2023-08-01 preamble/preambleHelp.tex
update journal

\section*{Markup and commenting commands}
Use the command \var{\textbackslash newcommenter\{cname\}\{color\}} to enable the following commands (substitute \var{cname} with your pseudonim of choice, e.g., \var{rtron}, and \var{color} with a color name supported by the \var{xcolor} package):
\begin{itemize}
\item \var{\textbackslash cname\{comment\}}: typeset a colored comment labeled with the pseudonim.
\item \var{\textbackslash atcname}: use this to refer to another commenter.
\item \var{\textbackslash cnamehl\{comment\}\{text\}}: use this to highligth a portion of the text and comment on it.
\end{itemize}
Examples after using \var{\textbackslash newcommenter\{rtron\}\{Green3\}}:
\begin{itemize}
\item \var{\textbackslash rtron\{Ignore this comment\}} produces \rtron{Ignore this comment}.
\item \var{\textbackslash atrtron} produces \atrtron.
\item \var{\textbackslash rtronhl\{Sentence is obvious\}\{The sky is blue\}} produces \rtronhl{Sentence is obvious}{The sky is blue}
\end{itemize}

Use the command \var{\textbackslash sout} to strike out text.

### 2023-08-01 paper/1.py

@@ -1,0 +1,368 @@
+import math
+import pygame as pg
+import numpy as np
+from pygame.math import Vector2
+import time
+import quadprog
+import cvxopt
+from cvxopt import matrix
+import matplotlib.pyplot as plt
+
+#r0 is the radius of the task region
+#(x0, y0) is the position of the center of the task region
+r0=50
+x0=250
+y0=250
+
+# 1,2 represents the obstalces
+r1=25
+x1=250
+y1=320
+
+r2=30
+x2=180
+y2=325
+
+r4=40
+x4=320
+y4=350
+
+r5=40
+x5=120
+y5=200
+
+#3 represent the connectivity circle
+r3=400
+x3=250
+y3=350
+
+#t_max is the deadline
+#v_max is the maximum velocity
+t_max=20
+v_max=15
+
+#w1, w2 are weights, see equation (14) in the paper
+w1=0.1
+w2=0.5
+w3=0.01
+
+# beta is a weight, see equation (12)
+beta=0.06
+
+#lamda is a weight for adjusting the angle speed
+lamda=0.3
+
+def theta_fi(theta,fi):
+    if abs(theta-fi)<=180:
+        result=theta-fi
+    elif theta>fi:
+        result=theta-fi-360
+    else:
+        result=theta-fi+360
+    return result
+
+#convex optimization solver
+def cvxopt_solve_qp(P, q, G=None, h=None, A=None, b=None):
+    P = .5 * (P + P.T)  # make sure P is symmetric
+    args = [matrix(P), matrix(q)]
+    if G is not None:
+        args.extend([matrix(G), matrix(h)])
+        if A is not None:
+            args.extend([matrix(A), matrix(b)])
+    sol = cvxopt.solvers.qp(*args)
+    if 'optimal' not in sol['status']:
+        return None
+    return numpy.array(sol['x']).reshape((P.shape[1],))
+
+#quadratic program solver
+def quadprog_solve_qp(P, q, G=None, h=None, A=None, b=None):
+    qp_G = .5 * (P + P.T)   # make sure P is symmetric
+    qp_a = -q
+    if A is not None:
+        qp_C = -numpy.vstack([A, G]).T
+        qp_b = -numpy.hstack([b, h])
+        meq = A.shape[0]
+    else:  # no equality constraint
+        qp_C = -G.T
+        qp_b = -h
+        meq = 0
[…]

### 2023-08-01 paper/move.py

@@ -1,0 +1,292 @@
+import math
+import pygame as pg
+import numpy as np
+from pygame.math import Vector2
+import time
+import quadprog
+import cvxopt
+from cvxopt import matrix
+import matplotlib.pyplot as plt
+
+#r0 is the radius of the task region
+#(x0, y0) is the position of the center of the task region
+r0=50
+x0=250
+y0=250
+
+#t_max is the deadline
+#v_max is the maximum velocity
+t_max=15
+v_max=15
+
+#w1, w2 are weights, see equation (14) in the paper
+w1=0.5
+w2=10
+
+# beta is a weight, see equation (12)
+beta=0.03
+
+#lamda is a weight for adjusting the angle speed
+lamda=0.3
+
+def theta_fi(theta,fi):
+    if abs(theta-fi)<=180:
+        result=theta-fi
+    elif theta>fi:
+        result=theta-fi-360
+    else:
+        result=theta-fi+360
+    return result
+
+#convex optimization solver
+def cvxopt_solve_qp(P, q, G=None, h=None, A=None, b=None):
+    P = .5 * (P + P.T)  # make sure P is symmetric
+    args = [matrix(P), matrix(q)]
+    if G is not None:
+        args.extend([matrix(G), matrix(h)])
+        if A is not None:
+            args.extend([matrix(A), matrix(b)])
+    sol = cvxopt.solvers.qp(*args)
+    if 'optimal' not in sol['status']:
+        return None
+    return numpy.array(sol['x']).reshape((P.shape[1],))
+
+#quadratic program solver
+def quadprog_solve_qp(P, q, G=None, h=None, A=None, b=None):
+    qp_G = .5 * (P + P.T)   # make sure P is symmetric
+    qp_a = -q
+    if A is not None:
+        qp_C = -numpy.vstack([A, G]).T
+        qp_b = -numpy.hstack([b, h])
+        meq = A.shape[0]
+    else:  # no equality constraint
+        qp_C = -G.T
+        qp_b = -h
+        meq = 0
+    return quadprog.solve_qp(qp_G, qp_a, qp_C, qp_b, meq)[0]
+
+def distance(x):
+    return ((x[0]-x0)**2+(x[1]-y0)**2)**0.5-r0
+
+class Player(pg.sprite.Sprite):
+    # initialize the robot as a circle
+    def __init__(self, pos=(420, 420), rgb=(50,120,180),width=0):
+        super(Player, self).__init__()
[…]

### 2023-08-01 paper/obstacle.py

@@ -1,0 +1,302 @@
+import math
+import pygame as pg
+import numpy as np
+from pygame.math import Vector2
+import time
+import quadprog
+import matplotlib.pyplot as plt
+import random
+
+r0=50
+x0=250
+y0=250
+
+r_d=30
+x_d=220
+y_d=350
+
+t_max=23
+v_max=15
+d=40
+deta=2
+
+w1=0.2
+w2=8
+w3=0.01
+
+w_alpha=0.03
+
+labda=1.5
+
+def theta_fi(theta,fi):
+    if abs(theta-fi)<=180:
+        result=theta-fi
+    elif theta>fi:
+        result=theta-fi-360
+    else:
+        result=theta-fi+360
+    return result
+
+def quadprog_solve_qp(P, q, G=None, h=None, A=None, b=None):
+    qp_G = .5 * (P + P.T)   # make sure P is symmetric
+    qp_a = -q
+    if A is not None:
+        qp_C = -numpy.vstack([A, G]).T
+        qp_b = -numpy.hstack([b, h])
+        meq = A.shape[0]
+    else:  # no equality constraint
+        qp_C = -G.T
+        qp_b = -h
+        meq = 0
+    return quadprog.solve_qp(qp_G, qp_a, qp_C, qp_b, meq)[0]
+
+def distance(x):
+    return ((x[0]-x0)**2+(x[1]-y0)**2)**0.5-r0
+
+class Player(pg.sprite.Sprite):
+
+    def __init__(self, pos=(420, 420), rgb=(50,120,180),width=0, radius=15, obs=False):
+        super(Player, self).__init__()
+        self.image = pg.Surface((radius*2, radius*2), pg.SRCALPHA)
+        pg.draw.circle(self.image, rgb, (radius,radius),radius,width)
+        if obs==False:
+            pg.draw.circle(self.image,(150,30,30),(26,15),4,width)
+        self.original_image = self.image
+        self.rect = self.image.get_rect(center=pos)
+        self.position = Vector2(pos)
+        self.direction = Vector2(1, 0)  # A unit vector pointing rightward.
+        self.speed = 0
+        self.angle_speed = 0
+        self.angle = 0
+        self.alpha=0
+        self.weight=0
+        self.alphadot=0
+
+    def h_c(self,t):
+        return t_max-t-distance(self.position)/v_max  
+    
+    def h_d(self, pos):
+        return ((self.position[0]- pos[0])**2+(self.position[1]- pos[1])**2)**0.5-r_d
+
[…]

### 2023-08-02 paper.tex
update from tron

@@
 \title{\LARGE \bf
- %Distributed Task Assignment for Cyber-Physical Security in Multi-Agent Systems
- Multi-agent cross-trajectory planning using graph theory}
- %with Applications to Cyber-Physical Security}
-% with Applications to Introspection Monitoring}
+
+Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories}
+
 \author{Ziqi Yang and Roberto Tron\thanks{This project is supported by the National Science Foundation grant "CPS: Medium: Collaborative Research: Multiagent Physical Cognition and Control Synthesis Against Cyber Attacks" (Award number 1932162).}}
@@
 Our approach guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations.
-We achieve this by introducing \emph{reachability} constraints into the previously developed continuous trajectory planning algorithm.
+We achieve this by introducing \emph{reachability} constraints into continuous trajectory planning algorithm.
 These constraints ensure an empty intersection between the sets of locations that the agents could potentially reach and the forbidden regions.
-Furthermore, to enhance system resilience, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments.
+\rtron{The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.}
+Furthermore, to enhance system resilience and feasibility of the planning problem, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments.
 This redundancy enables robots to deviate from their assigned sub-teams and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories simultaneously.
 To efficiently plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories.
+\rtron{This second part fixes the feasiblity problems of the first one, and uses the same reacheability constraints to build inter-team trajectories.}
 We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.

### 2023-08-02 paper.tex
Updates from Overleaf

@@
 In this section, we review various mathematical concepts that will provide the foundations and context for our novel constraint.
+
+In this section, we review various mathematical concepts that will provide the foundations and context for our novel constraints.
+
+\subsection{Differentials}
+We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
+\begin{equation}\label{equ:dt_to_dx}
+  \left.\dert f\bigl(x(t)\bigr)\right|_{t=0}=\partial_x f\bigl(x(0)\bigr) \dot{x}(0)
+\end{equation}
+where $t\mapsto x(t)\in\real{n}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$.
+For later part of this paper, we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
+The differentials $\partial_x f$ is derived through (\ref{equ:dt_to_dx}) having $\dot f$ divided by $\dot x$.
+
+With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{R}\to\real{m\times n}$  Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although semantically different.
+
+\subsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
+In this section, we briefly review the path planning algorithm based on ADMM constraints discussed in \cite{yangmulti}.
+This algorithm can deal with a variety of types of non-convex and non-smooth optimization constraints that are commonly encountered in trajectory optimization tasks once they are formulated in a certain format.
+The goal of the section is to lay the groundwork for proposing our novel constraint in the following sections.
+
+Let $x_{ij}\in\real{m}$ denote the position of agent $i\in\{1,\ldots,n\}$ at the discrete-time index $j\in[0,\ldots,T]$, with $m$ being the dimension of the workspace, $n$ the number of agents, and $T$ the planning time horizon.
+Let $\vx=\stack(\{x_{ij}\})$ denote the aggregated vector of all the agents' trajectories over the entire time interval.
+The goal of the algorithm is to optimize an objective function $\varPhi(\vx)$ on a set $\Omega$ defined by nonlinear constraints.
+To solve the problem using ADMM, we introduce a new set of variables $\vz=D(\vx)$ to translate the constraints $\Omega$ on $x$ to (typically lower-dimensional) sets of constraints on $\vz$, such that the projection operator on $\zeta$ can be easily implemented (e.g., a constrained distance between two agents is translated into their difference constrained to an origin-centered sphere).
+The new set of constraints $\zeta$ on $z$ is incorporated using an indicator function $\varTheta_\zeta$. The main problem is written as:
+\begin{equation}\label{eq:ADMMSetConstraint_general}
+		\begin{array}{r@{\quad}c}
+    	\min&\varPhi(\vx)+\varTheta_\zeta(\vz) \\
+        s.t.& D(\vx)-\vz=0,
+      \end{array}
+  \end{equation}
+  where $D(\vx)= [D_1(\vx)^T,\dots,D_l(\vx)^T]^T$ is a vertical concatenation of different functions for different constraints.
+
+  And having the update steps shown as:
+  \begin{subequations}\label{eq:ADMMupdate}
+    \begin{align}
+      \label{eq:admm-mod-update-q}\vx^{k+1}&:=\argmin_\vx(\varPhi(\vx^k) +\frac{\rho}{2}\norm{D(\vx)-\vz^k+\vu^k}_2^2)\\
+      \vz^{k+1}&:=\Pi_\zeta(D(\vx^{k+1})+\vu^k) \label{eq:ADMM_constraint_update}\\
+      \vu^{k+1}&:=\vu^k+D(\vx^{k+1})-\vz^{k+1},
+    \end{align}
+  \end{subequations}
+  Previous work in \cite{yangmulti} considered the following types of constraints:
+  \begin{lenumerate}{C}
+  \item \emph{Velocity constraints}: The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
+This constraint could be adapted also to enforce more refined dynamical models.
+  \item \emph{Convex obstacles}: We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
+Obstacles with non-convex shapes can be modeled using unions of the convex sets.
+  \item \emph{Waypoints with flexible deadlines}: We give locations that the agents need to visit at any point in a given time window (which can potentially contain a single time).
+These constraints can also be interpreted as static, trusted cameras that can complement the introspection constraints.
+  \item\label{it:introspection} \emph{Introspection constraints}: In a given time window, agents are asked to remain at a certain distance from each other to detect each other's presence.
+  \end{lenumerate}
+  Constraint~\ref{it:introspection} is the main mechanism that was provided in~\cite{yangmulti} for forcing agents to stay away from the forbidden region.
+However, this mechanism alone cannot provide strong guarantees in this regard.
+This motivates the introduction of our novel \emph{ellipsoidal constraints} in Sections~\ref{sec:ellipsoid-point},~\ref{sec:ellipsoide-plane}.
+This novel constraint is defined with the assumption that the velocity constraints still hold under attack.
+
+  \subsection{Householder rotations}\label{sec:householder}
+
+  To formulate the operator $\Pi_\zeta$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
+This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
+With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection).
+We call our version of the operator a \emph{Householder rotation}.
+In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.
+
+  \begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u$ as
+    \begin{equation}
+      u'=\nu_\cF+\nu_\cE,\quad u =\frac{u'}{\norm{u'}}.
+    \end{equation}
+    The \emph{Householder rotation} $H(\nu_\cF,\nu_\cE)$ is defined as
+    \begin{equation}\label{eq:H definition}
+      H(\nu_\cF,\nu_\cE) = 2 u u\transpose-I.
+    \end{equation}
+  \end{definition}
+  The main property of interest for our application is the fact that $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
+  \begin{proposition}
+    The matrix $H$ has the following properties:
+    \begin{enumerate}
+    \item It is a rotation, i.e.
+      \begin{enumerate}
+      \item\label{it:orthonormality} $H\transpose H=I$;
+      \item\label{it:determinant} $\det(H)=1$.
+      \end{enumerate}
+    \item\label{it:transformation} $\nu_\cE=H \nu_\cF$.
+    \end{enumerate}
+  \end{proposition}
+
+  We compute the differential of $H$ implicitly using the relation \eqref{equ:dt_to_dx}.
+We will use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
+  \begin{equation}
+    \bmat{v_1\\v_2\\v_3}\mapsto \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
+  \end{equation}
+  such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. One can verify by direct computation the following property:
+  \begin{equation}\label{eq:asymmetric to cross}
+    wv\transpose-vw\transpose=\cross{\cross{v}w}.
+  \end{equation}
+  \begin{proposition}
+    Let $\nu_\cF(t)$ represent a parametric curve. Then we have
+    \begin{equation}
+      \dot{H}=H\cross{-2M\dot{\nu}_{\cF}}
+    \end{equation}
+    where the matrix $M\in\real{3\times3}$ is given by
+    \begin{equation}
+      M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\norm{u'} \norm{\nu_\cF}}.
+    \end{equation}
+  \end{proposition}
+
 \subsection{Ellipsoidal reachability constraints}\label{Chapter:ProblemFormulation}
@@
 
+\appendix
+
+\section{Proof of proposition 1 }
+  \begin{proof}
+    For subclaim~\ref{it:orthonormality}:
+    \begin{equation}
+      H\transpose H=H^2=4uu\transpose u u\transpose - 4uu\transpose +I^2=I,
+    \end{equation}
+    since $u\transpose u=1$.
+
+    For subclaim~\ref{it:determinant}, let $U=\bmat{u & u^\bot_{1},u^\bot_{2}}$, where $u^\bot_{1},u^\bot_{2}$ are two orthonormal vectors such that $I=UU\transpose=uu\transpose + u^\bot_{1}(u^\bot_{1})\transpose+u^\bot_{2}(u^\bot_{2})\transpose$; then, substituting $I$ in \eqref{eq:H definition}, we have that the eigenvalue decomposition of $H$ is given by
+    \begin{equation}
+      H=U\diag(1,-1,-1) U\transpose.
+    \end{equation}
+    Since the determinant of a matrix is equal to the product of the eigenvalues, $\det(H)=1$.
+
+    For subclaim~\ref{it:transformation}, first note that $Hu=2uu\transpose u - u=u$.
+    It follows that the sum of $\nu_\cF$ and $\nu_\cE$ is invariant under $H$:
+    \begin{equation}\label{equ:H(u1+u2)}
+      H(\nu_\cF+\nu_\cE)=H u \norm{\nu_\cF+\nu_\cE}
+      = u\norm{\nu_\cF+\nu_\cE} =\nu_\cF+\nu_\cE,
+    \end{equation}
+    and that their difference is flipped under $H$:
+    \begin{equation}\label{equ:H(u1-u2)}
+      H(\nu_\cF-\nu_\cE) = 2uu\transpose (\nu_\cF-\nu_\cE) - (\nu_\cF-\nu_\cE)^2 = -(\nu_\cF-\nu_\cE).
+    \end{equation}
+    Combining (\ref{equ:H(u1+u2)}) and (\ref{equ:H(u1-u2)}) we obtain
+    \begin{equation}
+      H\nu_\cF = \frac{1}{2}\bigl(H(\nu_\cF+\nu_\cE)+H(\nu_\cF-\nu_\cE)\bigr)
+      = \nu_\cE
+    \end{equation}
+  \end{proof}
+
+\section{Proof or proposition 2}
+\begin{proof}
+    From the definition of $H$ in \eqref{eq:H definition}, we have
+    \begin{equation} \label{equ:H_dot original}
+      \dot H =   2(\dot u u\transpose + u \dot u\transpose)
+    \end{equation}
+
+    Recall that $\dot{u}=\frac{1}{\norm{u'}}(I-uu\transpose)\dot{u}'$ (see, for instance, \cite{Tron:Arxiv14}), which implies $(I-uu\transpose)\dot{u}'=\dot{u}'$.
+It follows that $\dot{u}$ flips sign under the action of $H\transpose$:
+    \begin{multline}
+      H\transpose \dot u = (2u u\transpose-I)\frac{ \left( I - u u\transpose \right) } {\left\|u'\right\|} \dot u' \\
+      =\frac{1}{\norm{u'}} (2u u\transpose-I-2u u\transpose u u\transpose+u u\transpose)\dot{u}'\\
+      = -\frac{1}{\norm{u'}} (I-u u\transpose)\dot u'
+      = -\dot u
+    \end{multline}
+
+    Inserting $HH\transpose=I$ in (\ref{equ:H_dot original}), and using \ref{eq:asymmetric to cross}, we finally have
+    \begin{equation}
+      \begin{split}
+        \dot H =  &  2H H\transpose(\dot u u\transpose + u \dot u\transpose)
+        =  2 H (-\dot u u\transpose + u \dot u\transpose)\\
+        =  &  -2H [[u]_{\times} \dot u]_{\times} \\
+        = &  -2 H \left[ [u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\left\|u'\right\| \left\|\nu_\cF\right\|} \dot{\nu}_\cF\right]_{\times}\\
+        = & -2 H \cross{M \dot{\nu}_\cF},
+      \end{split}
+    \end{equation}
+    which is equivalent to the claim.
+  \end{proof}
 {\small

### 2023-08-08 paper.tex
updates

@@
 
-However, two main challenges have been identified in \cite{wardega2023hola} \zyang{previous works}.
+A preliminary version of the paper was presented at conferences \zyang{cite CDC IROS}.
+This paper extend the previous works by fixing two main challenges identified in \cite{wardega2023hola} \zyang{previous works}.
 Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other.
@@
 Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
-In this chapter, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in Chapter \ref{chapter:task-assignment}), making it more difficult for attackers to successfully plan and execute attacks.
+In this paper, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in Chapter \ref{chapter:task-assignment}), making it more difficult for attackers to successfully plan and execute attacks.
 Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
@@
 \section{Preliminaries}
-In this section, we review various mathematical concepts that will provide the foundations and context for our novel constraint.
-
 In this section, we review various mathematical concepts that will provide the foundations and context for our novel constraints.
@@
   \end{subequations}
-  Previous work in \cite{yangmulti} considered the following types of constraints:
-  \begin{lenumerate}{C}
-  \item \emph{Velocity constraints}: The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
+
+  Since $D(\vx)$ is the vertical concatenation of $D_l(\vx)$, the projection of each set $\zeta_l$ is independent for each constraint and can be computed separately.
+The advantage of this formulation is that we can choose $D(\vx)$ such that the new constraint set~$\zeta$ becomes simple to compute; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vx$ in \eqref{eq:admm-mod-update-q}.
+Additionally, the function~$D(\vx)$ can be used to select only the subset of the variables on which a constraint depends.
+
+We consider the following types of traditional path planning constraints:
+  \subsubsection{Velocity constraints}
+  The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
+We then define the function $D(\vx)$ to return the velocity vectors for the $i$-th agent at time step $j$:
+\begin{equation}
+     D_{ij}(\vx) = x_{ij}-x_{i(j-1)}, \quad j\in\{1,\ldots, T\}
+\end{equation}
+and the constraint set is:
+\begin{equation}\label{eq:velocity_constraint}
+   \zeta_{ij} =\bigl\{z \mid \norm{z} \leq v_{max}\bigr\}.
+\end{equation}
+The projection operator $\Pi_\zeta(z)$ for this constraint implies that the projection of the vector $z$ is inside a sphere with a radius of $v_{max}$ which can then be written as:
+\begin{equation}\label{eq:velocity_constraint_update}
+    \Pi_{\zeta}(z) = \begin{cases}
+ v_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > v_{max},\\
+z	& otherwise.
+\end{cases}
+\end{equation}
+
 This constraint could be adapted also to enforce more refined dynamical models.
-  \item \emph{Convex obstacles}: We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
+
+  \subsubsection{Convex obstacles}: We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
 Obstacles with non-convex shapes can be modeled using unions of the convex sets.
-  \item \emph{Waypoints with flexible deadlines}: We give locations that the agents need to visit at any point in a given time window (which can potentially contain a single time).
-These constraints can also be interpreted as static, trusted cameras that can complement the introspection constraints.
-  \item\label{it:introspection} \emph{Introspection constraints}: In a given time window, agents are asked to remain at a certain distance from each other to detect each other's presence.
-  \end{lenumerate}
-  Constraint~\ref{it:introspection} is the main mechanism that was provided in~\cite{yangmulti} for forcing agents to stay away from the forbidden region.
-However, this mechanism alone cannot provide strong guarantees in this regard.
-This motivates the introduction of our novel \emph{ellipsoidal constraints} in Sections~\ref{sec:ellipsoid-point},~\ref{sec:ellipsoide-plane}.
-This novel constraint is defined with the assumption that the velocity constraints still hold under attack.
+
+  We enforce the constraints at each discrete time step $x_{ij}$ (enforcement of the constraints between these points can be achieved by making the obstacles sightly bigger than its actual size).
+For a convex area, waypoints stays unchanged it they are outside the zone, and if the waypoints are inside the zone, the constraint function $D(\vx)$ returns the least negative distance from the waypoints to the zone defined by hyperplanes which is represented as:
+\begin{equation}\label{eq:zoneConstraintMap}
+D_i(\vx) = \bmat{d_{11} \\\vdots\\ d_{nm}}
+\end{equation}
+where 
+\begin{align}
+    d_{ij}&= \max(\min(d_{ijk},0)),\\
+   d_{ijk} &= p_{ij}\transpose n_k - m_k,
+\end{align}
+and $n_k$ is the normal vector and $m_k$ is the scalar offset defining the $k$-th hyperplane.
+The corresponding constraint set is simply
+\begin{equation}
+    \zeta= \{z \mid z = 0 \},
+\end{equation}
+with a projection function:
+\begin{equation}\label{eq:zoneConstraintProjection}
+    \Pi_\zeta(z) = 0.
+\end{equation}
+The motivating idea for \eqref{eq:zoneConstraintMap} and \eqref{eq:zoneConstraintProjection} is to find waypoints inside the zone and project them to the closest boundary.
+As mentioned before, non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
+\subsubsection{Waypoints with flexible deadlines}
+In this type of constraint, we assume that an agent needs to go through a spherical ball around a given point $p$ with a radius of $d_{max}$ at some time instant $j$ belonging to a given time window $[t_1,t_2]$.
+In this case, we define the function $D(\vq)$ to return the smallest distance from the point $p$ to any point on the trajectory restricted to the relevant time window.
+This can be expressed precisely in the following form:
+\begin{equation}\label{eq:waypoint_constraint_D}
+D_i(\vq) = \min_{i\in\{1\dots,n\}, j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),
+\end{equation}
+with the constraint set:
+\begin{equation}\label{eq:waypoint_constraint}
+\zeta= \{z \mid z < z_{max} \},
+\end{equation}
+where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
+Note that this function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
+The projection $\Pi_\zeta(z)$ for this constraint can be written as:
+\begin{equation}\label{eq:waypoint_constraint_update}
+\Pi_\zeta(z) = \min(z,z_{max}).
+\end{equation}
+Note that \eqref{eq:waypoint_constraint} and \eqref{eq:waypoint_constraint_update} are equivalent to \eqref{eq:velocity_constraint} and \eqref{eq:velocity_constraint_update}, except for the fact that the quantity in \eqref{eq:waypoint_constraint_D} is always a positive scalar.
 
@@
   The main property of interest for our application is the fact that $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
-  \begin{proposition}
+  \begin{proposition}\label{prop:HProperidy}
     The matrix $H$ has the following properties:
@@
   \end{equation}
-  \begin{proposition}
+  \begin{proposition}\label{prop:Hderivitive}
     Let $\nu_\cF(t)$ represent a parametric curve. Then we have
@@
   \end{proposition}
-
-\subsection{Ellipsoidal reachability constraints}\label{Chapter:ProblemFormulation}
-  The reachability region is defined as the set of locations $x(t)$ that a robot can reach between two given fixed positions:
-
-  \begin{definition}
-    The \emph{reachability region} for two waypoints $x(t_1)=x_1$, $x(t_2)=x_2$ is defined as the sets of points $x'$ in the workspace such that there exist a trajectory $x(t)$ where $x(t')=x'$, $t_1\leq t' \leq t_2$ and $x(t)$ satisfies the velocity constraint $d(x(t),x(t+1))\leq v_{max}$.
-  \end{definition}
-  This region can be analytically bound via an ellipsoid:
-  \begin{definition}\label{Def_Reachability}
-    The \emph{reachability ellipsoid} is the region  $\mathcal{E}(x_1,x_2)=\{\tilde{x}\in\mathbb{R}^n: d(x_1,\tilde{x})+d(\tilde{x}+x_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
-  \end{definition}
-  % The reachability ellipsoid for a robot during time $[t_1,t_2]$ is the locations it could visit if only the planning at time $t_1$ and $t_2$ is obeyed.
-  The region $\cE(x_1,x_2)$ is an ellipsoid with foci at $x_1,x_2$, center $o_{\cE} = \frac{1}{2}(x_1+x_2)$, and the major radius equal to $a$.
-Let $c_\cE=\frac{1}{2}\norm{x_1-x_2}=\norm{o_\cE-x_1}$ be the distance from the center to a foci.
-
-  The reachability ellipsoid is an over-approximation of the exact reachability region; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
 
@@
 
+\section{Secure Multi-robot path planning using co-observation and reachability constraints}
+
+Besides traditional path planning constraints, additional security constraints need to be incorporated into the path planning problem to prevent cases where an attacker changes a robot's path between two observations to reach a forbidden region without being detected.
+The work of \cite{wardega2019resilience} provide exact solution for grid-world configuration.
+Using the onboard sensing capabilities, robots can perform inter-robot observations as an additional security measure.
+Each robot' self-report includes not only its own status, but also additional observations of other robots' status.
+For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''.
+Similarly, robot $j$ also reports its observations of robot $i$ to the CE.
+This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.
+
+When transforming the solution to continuous configuration spaces, additional analysis is needed on the reachability of robots in order for the security of co-observation schedule to hold.
+More broadly, the problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.
+This constraint is formulated using an ellipsoidal bound of the reachability region, and the idea of using an ellipsoidal bound to limit the search space is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm.
+
+We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.
+To the best of our knowledge, our path planning algorithm is the only one flexible enough to handle the safety related spatio-temporal constraints introduced by co-observations and reachability.
+
+\subsection{Co-observation schedule}
+The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
+The co-observation constraint is modeled as a relative distance constraint between two robots at some time instant $j$ (i.e., to require two agents see each other within a certain radius to inspect each other, or to exchange data).
+The location of the co-observation location should make sure that the ellipsoidal reachability region between each co-observation, considered in later sections \ref{sec:reachability}, has an empty intersection with all forbidden regions.
+ We write the function for the constraint as:
+\begin{align}
+D(\vq) = \overrightarrow{q_{aj}q_{bj}},
+\end{align}
+where $a,b$ are the indices of the pair of agents required for a mutual inspection. The corresponding constraint set is simply
+\begin{equation}
+\zeta= \{z \mid z \leq d_{max} \},
+\end{equation}
+with a projection function:
+\begin{equation}\label{eq:co-observation_constraint_update}
+\Pi_{\zeta}(z) = \begin{cases}
+d_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > d_{max},\\
+z	& otherwise.
+\end{cases}
+\end{equation}
+The locations $q_{aj}$ and $q_{bj}$ where the co-observation performed are computed as part of the optimization.
+
+\subsection{Reachability constraints}\label{sec:reachability}
+  In this section, we first provide the definition of an \emph{ellipsoidal reachability region}.
+We then provide a differentiable map to transform such region in a canonical axis-aligned form where the operator $\Pi_\zeta$ and its differential can be obtained; these operators are then extended to the general case via the aforementioned transform.
+The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be used in the ADMM formulation in Chapter \ref{chapter:Multi-agent-ADMM}.
+
+\subsection{Definition of reachability constraint}\label{sec:ellipsoidal definition}
+The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
+
+\begin{definition}
+	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the workspace such that there exist a trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$.
+\end{definition}
+This region can be analytically bounded via an ellipsoid:
+\begin{definition}\label{def:Reachability}
+	The \emph{reachability ellipsoid} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{maq}}{2}(t_2-t_1)$.
+\end{definition}
+
+ \begin{figure}
+    \centering
+    \includegraphics[width=0.6\linewidth]{Reachability}
+    \caption{The ellipse showcases the reachability region.
+The black line is the planned trajectory of a robot, $q_1$ and $q_2$ are two locations this robot are expected at given time $t_1$ and $t_2$, blue and red line are possible trajectories if the robot is compromised in after reaching $q_1$.
+Robot that goes outside the reachability region to forbidden region can only reach $q_{2}'$ instead of $q_{2}$ at time $t_{2}$, even if it drives directly toward $q_{2}$ at full speed $v_{max}$ after the intrusion into forbidden region.}
+    \label{fig:EllipseConstraintExample}
+  \end{figure}
+
+The region $\cE(q_1,q_2)$ is an ellipsoid with foci at $q_1,q_2$, center $o_{\cE} = \frac{1}{2}(q_1+q_2)$, and the major radius equal to $a$.
+Let $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ be the distance from the center to a foci.
+
+The reachability ellipsoid is an over-approximation of the exact reachability region; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
+\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
+  To simplify the problem, a canonical rigid body transformation is used to transform the ellipse $\cE$ from a global frame $\cF$ to a canonical frame $\cF_\cE$.
+The latter is defined such that the center of the ellipsoid is located at the origin and the foci are aligned with the first axis of $\cF_\cE$.
+Since the transformation depends on the two foci, i.e., two waypoints of an agent, the challenge here is to construct the transformation in a differentiable way.
+  For the convenience of derivation, we define the coordinate transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, from now on we simply refer to as $R$ and $o$, respectively.
+The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the formulation:
+  \begin{equation}
+    \Fframe{q}=R\Eframe{q}+o,\label{eq:E to F transform}\quad
+    \Eframe{q}=R\transpose(\Fframe{q}-o).
+  \end{equation}
+  The reverse transformation is $\Eframe{q}=R\transpose( \Fframe{q}-o)$.
+
+  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
+  \begin{align}
+    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
+  \end{align}
+  see Fig.\ref{fig:EllipseConstraintExample} for an illustration.
+Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$.
+We then define the rotation $R$ using a Householder rotation, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
+  \begin{align}
+    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
+  \end{align}
+  To simplify the notation, in the following we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$.
+
+\subsection{Reachability constraints via ellipsoids}\label{sec:ellipoid constraints}
+In later sections, we define constraint formulation of the ellipsoid regions against different types of forbidden regions: a point, a plane, a segment, and a convex polygon.
+For each one, our goal is to define the function $D(q)$, the set $\zeta$ and the projection $\Pi_\zeta$ that can be incorporated in the ADMM optimization (\ref{eq:ADMMSetConstraint_modified}); we also include derivations for the differential $\partial_qD(q)$, which can be used to significantly speed up the optimization.
+
+\subsection{Point-ellipsoid constraint}\label{sec:ellipsoid-point}
+As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
+The goal is to design the trajectory $q(t)$ such that $q_{avoid}\notin\mathcal{E}(q_1,q_2)$.
+We first define a projection function $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$, which returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
+
+\begin{equation}\label{eq:ellipse-point-projection}
+\begin{split}
+\argmin_{q_p} &\quad \norm{q_{avoid}-q_p}^2 \\
+s.t. &\quad q_p\in \cE^{c}.
+\end{split}
+\end{equation}
+where $\cE^{c}$ is the set complement of the region $\cE$.
+
 \begin{figure}[htbp]
 \begin{center}
-\includegraphics[width=0.8\linewidth]{RRT_example_new}
-\caption{RRT* used to find trajectory from a point to different trajectories}
-\label{fig:RRT*}
+\includegraphics[width=0.6\linewidth]{Ellipse2point}
+\caption{Point-ellipsoid constraint, a point $f$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$.}
+\label{fig:Ellipse-to-point}
 \end{center}
@@
 
-	\begin{algorithm} 
-		\caption{RRT*($x_{init}, \{x_{goal}\}$)} \label{alg:rrt}
-		\begin{algorithmic}[1]
-			\State $V_{goal}\gets\{x_{goal}\}$
-			\State $V\gets x_{init} \union V_{goal} $, $E\gets 0$
-			\State $i\leftarrow 0$
-			\While{$i<N$}
-			\State $G\leftarrow (V,E)$
-			\State $x_{rand}\leftarrow \texttt{Sample}(i)$; $i=i+1$;
-			\State $x_{nearest}\leftarrow \texttt{Nearest}(G=(V,E),x_{rand})$;
-			\State $x_{new}\leftarrow\texttt{Steer}(x_{nearest},x_{rand})$;
-			\If{$\texttt{ObstacleFree}(x_{nearest},x_{new})$}
-			\State $V\leftarrow V\cup \{x_{new}\}$;
-			\State $x_{min}\leftarrow x_{nearest}$;
-			\ForAll{ $x_{near}\in X_{near}$}
-				\If{$\texttt{ObstacleFree}(x_{near},x_{new})$}
-					\State $c'\leftarrow \texttt{Cost}(x_{near})+c(\texttt{Line}(x_{near}, x_{new}))$;
-					\If{$c'<\texttt{Cost}(x_{new})$}
-						\State $x_{min}\leftarrow x_{near}$;
-					\EndIf			
-				\EndIf
-			\EndFor
+  Then, the constraint $q_{avoid}\notin\mathcal{E}(q(t_1),q(t_2))$ can be written as:
+  \begin{equation}
+    D(q) = \pi_{p\cE}(q_{avoid};q(t_1),q(t_2),r)-q_{avoid} = 0
+  \end{equation}
 
-			\ForAll{$ x_{near}\in X_{near}\backslash {x_{min}} $}
-				\If{$\texttt{ObstacleFree}(x_{new},x_{near})$ and $\texttt{Cost}(x_{near})>\texttt{Cost}(x_{new}+c(\texttt{Line}({x_{new},x_{near}})))$}
-					\State $x_{parent}\leftarrow \texttt{Parent}(x_{near})$;
-					\State $E' \leftarrow E' \backslash \{ (x_{parent}, x_{near})\}$;
-					\State $E' \leftarrow E' \union  \{ (x_{new}, x_{near})\} $
-				\EndIf
-			\EndFor
-			\EndIf
-			\EndWhile
-			\State \Return $V_{goal}$;
-		\end{algorithmic}
-	\end{algorithm}
+  For cases where $q_{avoid} \notin \cE(q(t_2),q(t_1),r)$, $\pi_{p\cE}(q_{avoid}) = q_{avoid}$.
+And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse, which is discussed below.
 
-\section{Problem overview}
+  \subsubsection{Projection to the standard ellipse}
+  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
+  \begin{align}
+    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
+  \end{align}
+  with $c=\frac{\norm{q_2-q_1}}{2}$.
+
+  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
+  \begin{equation}\label{equ:standard-ellipse}
+    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
+  \end{equation}
+  where
+  \begin{equation}
+    Q = \diag(a^{-2},b^{-2},b^{-2}),
+  \end{equation}
+  and $b = \sqrt{a^2-c^2}$.
+  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
+
+  % Using the transformation defined in Section~\ref{sec:rotation2Standard}, the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
+  % \begin{equation}
+  %   \Fframe{E}(\Fframe{x}) = (\Fframe{x}-o_\cE)\transpose H\transpose Q H (\Fframe{x}-o_\cE) - 1
+  % \end{equation}
+
+  The point to project, $q_{avoid}$, can be likewise expressed in $\cF_\cE$ as $\Eframe{q}_{avoid} =  H (\Fframe q_{avoid}-o)$.
+
+  We now turn our attention to the problem of projecting $\Eframe{q}_{avoid}$ on the zero level set of $E^\cE$ (i.e., the reachability ellipsoid in the canonical frame).
+The derivations below are loosely inspired by \cite{eberly}.
+
+  Let $q^\cE_p$ be the point on the surface of the ellipsoid, i.e., $\Eframe E(q^\cE_p) = 0$, corresponding to the projection of the point $q^\cE_{avoid}$.
+Using Lagrange multipliers applied to the constrained optimization problem \eqref{eq:ellipse-point-projection} (after transforming it in the canonical frame), one can show that the vector from a point to its projection, $q^\cE_{avoid}- q^\cE_p$, must be collinear with the gradient of $\Eframe \cE$, i.e.
+  \begin{equation}
+    q^\cE_p- q^\cE_{avoid} = s \partial_q \Eframe E(q^\cE_p)\transpose = s Q q^\cE_p
+  \end{equation}
+  for some scale $s\in\real{}$;
+  thus $q^\cE_p$ can be written as:
+  \begin{equation}\label{eq:qp from S}
+    q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid}
+    % \bmat{\frac{a^{2}}{s+a^{2}}& 0 & 0 \\
+    % 0 & \frac{b^{2}}{s+b^{2}}&0 \\
+    % 0&0&\frac{b^{2}}{s+b^{2}}} q^\cE_{avoid} =
+  \end{equation}
+  where $S=(I+sQ)\inverse$.
+  Using the fact that since $q^\cE_p$ is a point on the ellipse, $s$ can be solved as the root of the equation obtained by substituting \eqref{eq:qp from S} in $\Eframe E(\Eframe q)$:
+  \begin{equation}
+    0=F(s)={q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1,
+  \end{equation}
+  where
+  \begin{equation}
+    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right)
+  \end{equation}
+ Detailed methods for computing $s$ can be found in \cite{eberly}.
+
+  Then the point-to-ellipse projection function can be represented as:
+  \begin{multline}\label{equ:Point2EllipseProjection}
+    \pi_{p\cE}(q)= R^{-1}(q(t_1),q(t_2))q^\cE_p+o \\
+    = R^{-1}(q(t_1),q(t_2))Sq^\cE_{avoid}+o\\
+    = R^{-1}S R ( q_{avoid}- o)+o
+  \end{multline}
+  In our derivations, we consider only the 3-D case ($m=3$); for the 2-D case, let $P=\bmat{I & 0}\in\real{2\times 3}$: then $\pi_{p\cE}^{\textrm{2D}}=P\pi_{p\cE}^{\textrm{3D}}(P\transpose q_{avoid}; P\transpose q_1, P\transpose q_2,a)$.
+
+  \subsubsection{ADMM constraints}
+  The corresponding constraint is written as
+  \begin{equation}
+    D_{p}(q) = \begin{cases}
+      \pi_{p\cE}(q) - q_{avoid} & q_{avoid} \in \cE, \\
+      {0} & \textrm{otherwise}.
+    \end{cases}
+  \end{equation}
+  and feasible set and projection function as:
+  \begin{equation}
+    \zeta = \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\quad \Pi(D_p(q)) = {0}
+  \end{equation}
+
+  \begin{proposition}\label{prop:Ellipse2PointDiff}
+    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (where we use $q$ as a shorthand notation for $q^\cE_{avoid}$)
+    \begin{multline}
+      \partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} \pi_{p\cE}=-2 H [ SH(q-o)]_{\times}U   \\
+      + \left( (q\transpose \partial_sQ' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q - o]_\times U \right. \\
+      \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
+      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o
+    \end{multline}
+  \end{proposition}
+  The differential of $D_p$ is the same as the one for $\pi_{p\cE}$.
+
+\subsection{Plane-ellipsoid constraint}\label{sec:ellipsoide-plane}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=0.6\linewidth]{Ellipse2line_V2}
+\caption{Plane-ellipse constraint.
+Projected a ellipsoid to one side of a plane.
+The projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.}
+\label{fig:Ellipse-to-plane}
+\end{center}
+\end{figure}
+
+For a intermediate step to get the relationship between a polygon shaped forbidden region, we first consider a forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
+The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+  Using the transformation introduced in (\ref{sec:rotation2Standard}), the ellipse can be transferred into a standard one with the new hyperplane in the form of $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
+  \begin{equation}
+    n_\cE = H(q_1,q_2)n
+\end{equation}
+\begin{equation} 
+	d_\cE =-\vn\transpose o + d
+  \end{equation}
+\subsubsection{Projection via the tangent interpolation point}
+  For each $\cL_\cE$, there exist two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse, where
+  \begin{equation}
+    d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}.
+  \end{equation}
+  The corresponding tangent points are given as 
+  \begin{equation}
+    p^\cE_{1} = \frac{  d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},
+  \end{equation}
+  \begin{equation}
+   p^\cE_{2} = -  p^\cE_{1}.
+  \end{equation}
+  We use these two tangent points to define a novel measure of displacement between a plane and an ellipse.
+  \begin{definition}
+    The \emph{tangent interpolation point} is defined as 
+    \begin{equation}\label{equ:ProjectPoint}
+      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}
+    \end{equation}
+  \end{definition}
+  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively. 
+  % it is easy to see that $\Eframe p_{\cL} \in \mathcal{L}$, and $p_{\mathcal{L}}$ can be used to indicate the relationship between the $\mathcal{L}$ and $\mathcal{E}$, which is shown below.
+\zyang{how to emphaise this?
+maybe a graph here?}
+  %The reason such that a specific point is used is for the convenience of evaluating ellipse-plane-segment relationship in Section~\ref{chapter:ellipse to segment}.
+  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
+Using this fact, we define the following projection operator:
+  \begin{equation}\label{equ:plane2ellipse}
+    \pi^\cE_{\vn \cE}(q) =\begin{cases}
+      p^\cE_{t1}-p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
+      p^\cE_{t2}-p^\cE_{\cL} &  d_\cE \in [- d_{\cE t},0), \\
+      {0} & \textrm{otherwise}.
+    \end{cases}
+  \end{equation}
+  \subsubsection{ADMM constraints}
+  Transforming the projection $\pi^\cE$ back to $\cF$ we have:
+  \begin{equation}\label{equ:constraint plane to ellipse}
+    D_{\vn}(q)= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o,
+  \end{equation}
+  with the corresponding constraint written as
+  \begin{equation}
+    \zeta_\vn = \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \}
+  \end{equation}
+  \begin{equation}
+   \quad\Pi_\vn(D_{\vn}(q)) = {0}
+  \end{equation}
+
+  \subsubsection{Gradients for the projection function}
+  \begin{proposition}\label{prop:dpi_ne dt}
+    The differential of the projection function $\Eframe \Pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
+    \begin{equation}
+      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
+        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
+        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
+        {0} & otherwise.
+      \end{cases}
+    \end{equation}
+    where
+    \begin{multline}
+      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
+      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
+    \end{multline}
+    \begin{equation}
+      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
+      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
+    \end{equation}
+  \end{proposition}
+  Based on the previous proposition, the differential of (\ref{equ:constraint plane to ellipse}) can be written as:
+  \begin{equation}
+    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
+  \end{equation}
+
+\subsection{Line-segment-ellipse constraint}\label{chapter:ellipse to segment}
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=0.6\linewidth]{Ellipse2safezone_V2}
+\caption{Polygen-ellipse constraint. This constraint is simplified to either a plane-ellipse constraint or a point-ellipse constraint.}
+\label{fig:Ellipse-to-safezone}
+\end{center}
+\end{figure}
+
+To avoid (or stay in) a region defined by several hyperplanes, the relative position between the ellipse and segment of the hyperplane needs to be studied instead of the whole plane.
+Assume the segment has endpoints $p_1$ and $p_2$, the segment can be defined as:
+\begin{equation}
+\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
+\end{equation}
+And using the $p_{\cL}$ defined in (\ref{equ:ProjectPoint}), we define
+\begin{equation}
+D_{seg}(q) = \begin{cases}
+D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
+D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
+D_2(p_{\cL}) & otherwise
+\end{cases}
+\end{equation}
+where $D_{p\cE}$ and $D_{\vn\cE}$ are corresponding constraint function introduced in section \ref{sec:ellipsoid-point} and \ref{sec:ellipsoide-plane}
+with the constraint set and projection written as:
+\begin{equation}
+\zeta_{seg} = \{q\in\mathbb{R}^{nm}:\norm{D_{seg}(q)} = 0 \}
+\end{equation}
+\begin{equation}
+\Pi_{seg}(D_{seg}(q)) = {0}
+\end{equation}
+\subsection{Convex-polygon-ellipse constraint}\label{sec:ellipse-region-constraint} 
+To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse.
+And a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) is also added to prevent cases where the ellipse is a subset of the region.
+Similar to \eqref{equ:ProjectPoint}, we define
+\begin{equation}
+D_{cp}(q) = \bmat{D_{seg1}\\D_{seg2}\\ \vdots}
+\end{equation}
+with the constraint set and projection written as:
+\begin{equation}
+\zeta_{cp} = \{q\in\mathbb{R}^{nm}:\norm{D_{cp}(q)} = 0 \}
+\end{equation}
+\begin{equation}
+\Pi_{cp}(D_{cp}(q)) = {0}
+\end{equation}
+
+\section{Cross-trajectory co-observation planning}
+
+We propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
+Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
+In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.
+Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
+
+\subsection{Problem overview}
 
@@
 
-\section{Proof of proposition 1 }
+\subsection{Proof of proposition \ref{prop:HProperidy}}
 \begin{proof}
@@
 
-\section{Proof or proposition 2}
+\subsection{Proof or proposition \ref{prop:Hderivitive}}
 \begin{proof}
@@
   \end{proof}
+
+  \subsection{Proof of proposition \ref{prop:Ellipse2PointDiff}}
+  \begin{proof}
+    To make the notation more compact, we will use $\partial_q f$ instead of $\partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} f$ for the remainder of the proof.
+    The differential of \eqref{equ:Point2EllipseProjection} can be represented as:
+    \begin{equation}\label{equ:dPi_dt}
+      \begin{split}
+        \dot \pi_{p\cE} = &  \dot H^{-1}SH (q_{avoid} - o)  + H^{-1}\dot S H (q_{avoid} - o) \\
+        &+ H^{-1}S \dot H (q_{avoid} - o) + (H^{-1}SH -I)\dot o\\
+      \end{split}
+    \end{equation}
+
+    where
+    \begin{equation}\label{equ:S_dot}
+      \begin{split}
+        \dot S  =& - S^2 (Q \dot s + s \dot Q)\\
+        =& - S^2 (Q \partial_q s \dot q - \partial_b Q \partial_q b \dot q)
+      \end{split}
+    \end{equation}
+    where
+    \begin{equation}
+      \partial_b Q = 2\frac{s}{b^3} \diag\{0,1,1\}
+    \end{equation}
+    To compute the derivative $\partial_q \pi$, we need the expression of $\partial_q b$, $\partial_q o$ and $\partial_q s$; the first two can be easily derived using the equations above:
+    \begin{align}
+      \partial_q b &= \frac{1}{4b}\bmat{q_1-q_2,q_2-q_1}\transpose\\
+      \partial_q o &= \bmat{I/2,I/2}\transpose
+    \end{align}
+
+    In order to get $\partial_q s$, we use the fact that $F\bigl(s(q)\bigr)=0$ for all $q$; hence $F\bigl(\tilde{q}(t)\bigr)\equiv 0$, and $\partial_q F = 0$. We then have:
+
+    \begin{equation}
+      0=\dot F =  2q\transpose Q' \dot q + q\transpose \partial_s Q' q \dot s + q\transpose \partial_bQ' q \dot b
+    \end{equation}
+    where
+    \begin{equation}
+      \partial_s Q'= -\diag\left(\frac{2a^2}{(s+a^2)^3},\frac{2b^2}{(s+b^2)^3},\frac{2b^2}{(s+b^2)^3}\right).
+    \end{equation}
+    By moving term $\dot s$ to the left-hand side we can obtain:
+    \begin{multline}\label{equ:s_dot}
+      \dot s =  (q\transpose \partial_s Q' q)^{-1} (2q\transpose Q' \dot q + q\transpose \partial_b Q' q \dot b)\\
+      =  (q\transpose \partial_s Q' q)^{-1} (-4q\transpose Q' H[U\dot q]_\times (q_{avoid} - o) \\
+      -2q\transpose Q'H\dot o + q\transpose \partial_b Q' q \dot b)\\
+      =  (q\transpose \partial_s Q' q)^{-1} (-4q\transpose Q' H[q_{avoid} - o]_\times U\dot q \\
+      -2q\transpose Q'H\dot o + q\transpose \partial_b Q' q \dot b)
+    \end{multline}
+
+    The second term of equation (\ref{equ:dPi_dt}) turns into:
+    \begin{multline}
+      H^{-1}\dot S H (q_{avoid} - o)
+      = - H^{-1} Q' q \dot s - s H^{-1} S^2 \partial_b Q q \dot b\\
+      =   \big( (q\transpose \partial_s Q' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q_{avoid} - o]_\times U  \\
+      + 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\big) \dot q\\
+    \end{multline}
+
+    Thus equation \eqref{equ:dPi_dt} could be written as:
+    \begin{multline}
+      \dot \pi_{p\cE} = \big(-2 H [ SH(q_{avoid}-o)]_{\times}U   \\
+      + \left( (q\transpose \partial_s Q' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q_{avoid} - o]_\times U \right. \\
+      \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
+      -2H^{-1} S H[q_{avoid}-o]_{\times} U  \\
+      + (H^{-1}SH -I)\partial_q o \big) \dot q,
+    \end{multline}
+    from which the claim follows.
+  \end{proof}
+
+  \subsection{Proof of proposition \ref{prop:dpi_ne dt}}
+  \begin{proof}
+    We first need to derive $\dot{d}_\cE$ and $\dot{d}_{\cE t}$
+
+    \begin{equation}
+      \dot d_\cE = -n\transpose \partial_q o \dot q
+    \end{equation}
+    \begin{equation}\label{equ:dot det}
+      \begin{split}
+        \dot d_{\cE t} =&  (\dot n_\cE\transpose Q^{-1} n_\cE + n_\cE\transpose \dot Q^{-1} n_\cE + n_\cE\transpose Q^{-1} \dot n_\cE) /\sqrt{n_\cE\transpose Q^{-1} n_\cE}\\
+        = & (\sqrt{n_\cE\transpose Q^{-1} n_\cE})^{-1}\left(-2n\transpose H[Q^{-1}n_\cE]_\times U \right.\\
+        &\left. + n_\cE \transpose \partial_b Q^{-1} n_\cE \partial_q b  -2 n_\cE Q^{-1}H[n]_\times U \right) \dot q
+      \end{split}
+    \end{equation}
+    Next, we need to derive  $\dot p_{t1}$, $\dot p_{t2} $ and $\dot p_\cL$. Since $p_\cL$ could be written as
+    \begin{equation}
+      p_\cL = \frac{d_\cE Q^{-1} n_\cE}{ d_{\cE t} ^2},
+    \end{equation}
+    we have
+    \begin{multline}\label{equ:dpl_dt}
+        \dot p_\cL =  \left( (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \right.\\
+        \left .+ \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2}\right) \dot q
+    \end{multline}
+    \begin{multline}\label{equ:dplt_dt}
+        \dot p_{1} =  \left(-\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} \right.\\
+         \left. + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}} \right) \dot q
+    \end{multline}
+    subtracting $\dot q$ from (\ref{equ:dpl_dt}) and (\ref{equ:dplt_dt}), we can derive the result shown in (\ref{equ:ProjectPoint})
+  \end{proof}
+
 {\small

### 2023-08-09 paper.tex
Updates from Overleaf

@@
 \input{preamble/common}
+\newcommand{\rrtstar}{$\texttt{RRT}^\texttt{*}$}
+
 \usepackage{cleveref}
@@
 The goal of the section is to lay the groundwork for proposing our novel constraint in the following sections.
+\rtron{Do a literature review of other trajectory optimization algorithms, and state if they could be applicable}
 
@@
 The goal of the algorithm is to optimize an objective function $\varPhi(\vx)$ on a set $\Omega$ defined by nonlinear constraints.
-To solve the problem using ADMM, we introduce a new set of variables $\vz=D(\vx)$ to translate the constraints $\Omega$ on $x$ to (typically lower-dimensional) sets of constraints on $\vz$, such that the projection operator on $\zeta$ can be easily implemented (e.g., a constrained distance between two agents is translated into their difference constrained to an origin-centered sphere).
+To solve the problem using ADMM, we introduce a new set of variables \rtronhl{$D$ is not well defined}{$\vz=D(\vx)$} to translate the constraints $\Omega$ on $x$ to (typically lower-dimensional) sets of constraints on $\vz$ \rtron{(leaving $x$ unconstrained, except for the equality constraints with $z$)}, such that the projection operator on $\zeta$ can be easily implemented (e.g., a constrained distance between two agents is translated into their difference constrained to an origin-centered sphere).\zyang{Clearify the notations and use capital zeta}
 The new set of constraints $\zeta$ on $z$ is incorporated using an indicator function $\varTheta_\zeta$. The main problem is written as:
@@
 
-  And having the update steps shown as:
+  Applying the ADMM iterations \rtron{ref ADMM paper}, the update steps can be derived as:
   \begin{subequations}\label{eq:ADMMupdate}
@@
   \end{subequations}
-
+  \rtron{where $u$ is...}
   Since $D(\vx)$ is the vertical concatenation of $D_l(\vx)$, the projection of each set $\zeta_l$ is independent for each constraint and can be computed separately.
@@
 
-We consider the following types of traditional path planning constraints:
+We consider the following types of traditional path planning constraints:\zyang{notation using x or q}
   \subsubsection{Velocity constraints}
@@
 \end{equation}
-The projection operator $\Pi_\zeta(z)$ for this constraint implies that the projection of the vector $z$ is inside a sphere with a radius of $v_{max}$ which can then be written as:
-\begin{equation}\label{eq:velocity_constraint_update}
-    \Pi_{\zeta}(z) = \begin{cases}
- v_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > v_{max},\\
-z	& otherwise.
-\end{cases}
-\end{equation}
-
-This constraint could be adapted also to enforce more refined dynamical models.
-
-  \subsubsection{Convex obstacles}: We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
+The projection operator $\Pi_\zeta(z)$ for this constraint  is simply a projection of $z$ to the interior of a sphere centered at the origin and having radius $v_{max}$
+%implies that the projection of the vector $z$ is inside a sphere with a radius of $v_{max}$ which can then be written as:
+%\begin{equation}\label{eq:velocity_constraint_update}
+%    \Pi_{\zeta}(z) = \begin{cases}
+% v_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > v_{max},\\
+%z	& otherwise.
+%\end{cases}
+\%end{equation}
+
+This constraint could be adapted to enforce more refined dynamical models.
+
+\subsubsection{Convex obstacles} We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
 Obstacles with non-convex shapes can be modeled using unions of the convex sets.
 
-  We enforce the constraints at each discrete time step $x_{ij}$ (enforcement of the constraints between these points can be achieved by making the obstacles sightly bigger than its actual size).
+\rtron{Define for a single $x_{ij}$, then just say that we add constraints for all $ij$.
+Instead of using $min(d_{ijk})$, use $dist(x_{ij},\cP)$, where $\cP$ is the cvx polygon} We enforce the constraints at each discrete time step $x_{ij}$ (enforcement of the constraints between these points can be achieved by making the obstacles sightly bigger than its actual size).
 For a convex area, waypoints stays unchanged it they are outside the zone, and if the waypoints are inside the zone, the constraint function $D(\vx)$ returns the least negative distance from the waypoints to the zone defined by hyperplanes which is represented as:
@@
 Note that \eqref{eq:waypoint_constraint} and \eqref{eq:waypoint_constraint_update} are equivalent to \eqref{eq:velocity_constraint} and \eqref{eq:velocity_constraint_update}, except for the fact that the quantity in \eqref{eq:waypoint_constraint_D} is always a positive scalar.
+
+\rtron{Give example application here, and include application of ADMM without the security constraints, but highlighting a path that would break the security}
 
@@
   \end{equation}
-  such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. One can verify by direct computation the following property:
-  \begin{equation}\label{eq:asymmetric to cross}
-    wv\transpose-vw\transpose=\cross{\cross{v}w}.
-  \end{equation}
+  such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. %One can verify by direct computation the following property:
+  %\begin{equation}\label{eq:asymmetric to cross}
+  %  wv\transpose-vw\transpose=\cross{\cross{v}w}.
+  %\end{equation}
   \begin{proposition}\label{prop:Hderivitive}
@@
 \subsection{Rapidly-exploring Random Trees}
-We use RRT* as a component of the solution \cite{karaman2010incremental}, which is an optimized variant of the rapidly-exploring Random Trees (RRT).
+\rtron{consider moving this section to part II}
+\rtron{Mention that one could theoretically use the ADMM solver, but RRT* is more appropriate to find one start-many destination paths, and is more efficient, although it can only minimize path length (or simial additive cost) with obstacle constraints (not the other spatio-temporal constraints).}
+We use \rrtstar{} \cite{karaman2010incremental} as a component of \rtronhl{mention that is used only in part II}{the solution}, which is an optimized variant of the rapidly-exploring Random Trees (RRT).
 As a optimal path planning algorithm, RRT* returns the shortest paths between an initial location and multiple potential goals.
 We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
-The basic RRT* algorithm is shown in Algorithm \ref{alg:rrt}.
-For a given tree $G=(V,E)$, key functions called by the algorithm are
+%The basic RRT* algorithm is shown in Algorithm \ref{alg:rrt}.
+For a given tree $G=(V,E)$, key functions called by the algorithm are \zyang{Check with cross-trajectory algorithm, leave the functions used in later algorithm}
 \begin{description}
@@
 \end{description}
+\rtron{You do not need to put the full pseudocode, but either mention how the functions above are used, or do not mention them}
+\rtron{More importantly, emphasize that we use it to solve the single-to-many path planning problem.}
 
@@
 
-Besides traditional path planning constraints, additional security constraints need to be incorporated into the path planning problem to prevent cases where an attacker changes a robot's path between two observations to reach a forbidden region without being detected.
+\rtron{Streamline this introductory paragraphs.
+The point is to point out again the problem (use the figure from the example application), give an overview of the solution (co-observations, ellipsoidal constraints, then ADMM), and say that [5] solved this for grid worlds, but not optimizing $\Phi(x)$.}
+Beside traditional path planning constraints, additional security constraints need to be incorporated into the path planning problem to prevent cases where an attacker changes a robot's path between two observations to reach a forbidden region without being detected.
 The work of \cite{wardega2019resilience} provide exact solution for grid-world configuration.
@@
 For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''.
-Similarly, robot $j$ also reports its observations of robot $i$ to the CE.
+Similarly, robot $j$ also reports its observations of robot $i$ to the \rtronhl{defined?}{CE}.
 This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.
@@
 
-\subsection{Co-observation schedule}
+\rtron{Include overview of how the rest of the section is organized}
+
+\subsection{Co-observation schedule constraint}
 The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
@@
 
-\subsection{Reachability constraints}\label{sec:reachability}
+\rtron{First a subsection "Definition of ellipsoidal constraints and their differential", and then another one "Reachability constraints using ellipsoidal constraints" with the three cases}
+\subsection{Reachability constraint}\label{sec:reachability}
   In this section, we first provide the definition of an \emph{ellipsoidal reachability region}.

### 2023-08-31 paper.tex
finish ADMM section

--- 2023-08-08 paper.tex
@@
 \DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
-
+\def\sZ{\mathcal{Z}}
 \title{\LARGE \bf
@@
 
-\section{Preliminaries}
-In this section, we review various mathematical concepts that will provide the foundations and context for our novel constraints.
-
-\subsection{Differentials}
+\section{Multi-robot trajectory planning with co-observation}
+
+In this section, we aims to enhance the security of MRSs against malicious takeovers and deviations by attackers.
+Specifically, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
+This achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions.
+In this way, the plan ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\cite{wardega2019resilience} solved this problem in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but was unable to optimizing over arbitrary smooth cost functions.
+
+We formulate the planning problem into an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
+The security constraints including co-observation schedule and reachability analysis, alongside with traditional path planning constraints, are transformed into different types of spatio-temporal constraints in the optimization problem.
+We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space.
+For a team of $n$ agents, and a task time horizon of $T$, the overall trajectory of the multi-agent system can be represented as an aggregated vector $\vq\in \real{n m T}$.
+The goal of our path planning problem is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, formally:
+\begin{equation}\label{eq:general-problem}
+	\begin{split}
+		\min/\max & \quad \varPhi(\vq)\\
+		\textrm{subject to} &\quad \vq \in \Omega.
+	\end{split}
+\end{equation}
+
+As an example application, we assume that there exists an underlying slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
+To explore unknown spatially-distributed fields, autonomous agents are usually required to traverse the entire unknown environment while collecting sensory data to estimate a corresponding map (Figure~\ref{fig:ADMM-example-application}).
+We model the map as a set of locations of interests arranged on a regular grid, where at each location, we assume that there is a corresponding slowly-time-varying quantity.
+For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.
+We define the cost function $\varPhi(\vq)$ to be an approximation of the uncertainty at any of the given points, and we aim to minimize such maximum uncertainty.
+We focus on a particular choice of objective function $\varPhi(\vq)$, in the context of a mapping and estimation applications, for the optimization problem \eqref{eq:general-problem}.
+\zyang{Do we need detail of the problem formulations?}
+
+\begin{figure}
+     \centering
+     \subfloat[Continuous world trajectory \label{fig:ADMM-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{Example_application}}
+     \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+     \caption{Trajectory design of an example map exploration task for a three-robot system with start locations and destinations fixed.
+Task are planned in a $8 \times 8$ grid world.
+Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones.
+Fig~\ref{fig:Grid-example-application} shows the planned trajectory with co-observation schedule in grid-world.
+Fig~\ref{fig:ADMM-example-application} shows the trajectory design in continuous world optimized with respect to a map exploration task}
+     \label{fig:example-application}
+ \end{figure}
+
+ This section is organized as follows.
+We begin by presenting the foundational mathematical concepts, notably the basic ADMM optimal trajectory solver.
+Subsequently, we seamlessly integrate security constraints, encompassing co-observation schedule and reachability constraints, into our proposed solver.
+Concluding this section, we present the obtained results alongside identifying limitations that will be addressed in the upcoming section.
+
+\subsection{Preliminary}
+In this section, we review various mathematical concepts that will provide the foundations and context for the solver.
+
+\subsubsection{Differentials}
 We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
@@
 
-\subsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
-In this section, we briefly review the path planning algorithm based on ADMM constraints discussed in \cite{yangmulti}.
-This algorithm can deal with a variety of types of non-convex and non-smooth optimization constraints that are commonly encountered in trajectory optimization tasks once they are formulated in a certain format.
-The goal of the section is to lay the groundwork for proposing our novel constraint in the following sections.
-
-Let $x_{ij}\in\real{m}$ denote the position of agent $i\in\{1,\ldots,n\}$ at the discrete-time index $j\in[0,\ldots,T]$, with $m$ being the dimension of the workspace, $n$ the number of agents, and $T$ the planning time horizon.
-Let $\vx=\stack(\{x_{ij}\})$ denote the aggregated vector of all the agents' trajectories over the entire time interval.
-The goal of the algorithm is to optimize an objective function $\varPhi(\vx)$ on a set $\Omega$ defined by nonlinear constraints.
-To solve the problem using ADMM, we introduce a new set of variables $\vz=D(\vx)$ to translate the constraints $\Omega$ on $x$ to (typically lower-dimensional) sets of constraints on $\vz$, such that the projection operator on $\zeta$ can be easily implemented (e.g., a constrained distance between two agents is translated into their difference constrained to an origin-centered sphere).
-The new set of constraints $\zeta$ on $z$ is incorporated using an indicator function $\varTheta_\zeta$. The main problem is written as:
-\begin{equation}\label{eq:ADMMSetConstraint_general}
-		\begin{array}{r@{\quad}c}
-    	\min&\varPhi(\vx)+\varTheta_\zeta(\vz) \\
-        s.t.& D(\vx)-\vz=0,
+\subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
+The basic idea behind ADMM based solver \cite{zyang} is to split the constraints from the objective function using a different set of variables $\vz$, and then solve an Augmented Lagrangian formulation of the optimization problem in \eqref{eq:general-problem}.
+More specifically, we can rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function.
+However, in the traditional application of ADMM, the duplicated variables $\vz$ are solved through a projection to the constraint set $\Omega$.
+However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
+To deal with this problem, we propose a minor generalization of the ADMM formulation~\eqref{equ:ADMMSetConstraint} where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy):
+\begin{equation}\label{eq:ADMMSetConstraint_modified}
+	\begin{aligned}
+		&\max\quad \varPhi(\vq)+\varTheta(\vz) \\
+		& \begin{array}{r@{\quad}c}
+			s.t.& D(\vq)-\vz=0
 		\end{array} 
-  \end{equation}
-  where $D(\vx)= [D_1(\vx)^T,\dots,D_l(\vx)^T]^T$ is a vertical concatenation of different functions for different constraints.
-
-  And having the update steps shown as:
+	\end{aligned}
+\end{equation}
+where $D(\vq)= [D_1(\vq)^T,\dots,D_l(\vq)^T]^T$ is a vertical concatenation of different functions for different constraints.
+
+The update steps of the ADMM algorithm can be then denoted as \cite{Boyd2011}:
 \begin{subequations}\label{eq:ADMMupdate}
 	\begin{align}
-      \label{eq:admm-mod-update-q}\vx^{k+1}&:=\argmin_\vx(\varPhi(\vx^k) +\frac{\rho}{2}\norm{D(\vx)-\vz^k+\vu^k}_2^2)\\
-      \vz^{k+1}&:=\Pi_\zeta(D(\vx^{k+1})+\vu^k) \label{eq:ADMM_constraint_update}\\
-      \vu^{k+1}&:=\vu^k+D(\vx^{k+1})-\vz^{k+1},
+		\label{eq:admm-mod-update-q}\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2)\\
+		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k) \\
+		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1},
 	\end{align}
 \end{subequations}
-
-  Since $D(\vx)$ is the vertical concatenation of $D_l(\vx)$, the projection of each set $\zeta_l$ is independent for each constraint and can be computed separately.
-The advantage of this formulation is that we can choose $D(\vx)$ such that the new constraint set~$\zeta$ becomes simple to compute; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vx$ in \eqref{eq:admm-mod-update-q}.
-Additionally, the function~$D(\vx)$ can be used to select only the subset of the variables on which a constraint depends.
-
-We consider the following types of traditional path planning constraints:
-  \subsubsection{Velocity constraints}
+where $\Pi_\mathcal{Z}$ is the new projection to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that intuitively accumulates the sum of primal residuals
+\begin{equation}\label{eq:primal-residual}
+	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
+\end{equation}
+Checking the primal residuals alongside with the dual residuals 
+\begin{equation}\label{eq:dual-residual}
+	\vs^{k}=-\rho(z^{k}-z^{k-1}),
+\end{equation}
+after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed large number of iterations.
+Since $D(\vq)$ is the vertical concatenation of $D_i(\vq)$, the projection of each set $\mathcal{Z}_i$ is independent for each constraint and can be computed separately.
+The advantage of this formulation is that we can choose $D(\vq)$ such that the new constraint set~$Z$ becomes simple to compute; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vq$ in \eqref{eq:admm-mod-update-q}.
+Additionally, the function~$D(\vq)$ can be used to select only the subset of the variables on which a constraint depends.
+
+We consider the following types of traditional path planning constraints in the ADMM constraints:
+\subsubsection*{Velocity constraints}
   The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
-We then define the function $D(\vx)$ to return the velocity vectors for the $i$-th agent at time step $j$:
-\begin{equation}
-     D_{ij}(\vx) = x_{ij}-x_{i(j-1)}, \quad j\in\{1,\ldots, T\}
+We then define the function $D(\vq)$ to return the velocity vectors for the $i$-th agent at time step $j$:
+\begin{equation}
+     D_{ij}(\vq) = q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\}
 \end{equation}
@@
 \begin{equation}\label{eq:velocity_constraint}
-   \zeta_{ij} =\bigl\{z \mid \norm{z} \leq v_{max}\bigr\}.
-\end{equation}
-The projection operator $\Pi_\zeta(z)$ for this constraint implies that the projection of the vector $z$ is inside a sphere with a radius of $v_{max}$ which can then be written as:
-\begin{equation}\label{eq:velocity_constraint_update}
-    \Pi_{\zeta}(z) = \begin{cases}
- v_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > v_{max},\\
-z	& otherwise.
-\end{cases}
-\end{equation}
-
-This constraint could be adapted also to enforce more refined dynamical models.
-
-  \subsubsection{Convex obstacles}: We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
+   \sZ_{ij} =\bigl\{z \mid \norm{z} \leq v_{max}\bigr\}.
+\end{equation}
+The projection operator $\Pi_\zeta(z)$ for this constraint  is simply a projection of $z$ to the interior of a sphere centered at the origin and having radius $v_{max}$.
+This constraint could be adapted to enforce more refined dynamical models.
+
+%implies that the projection of the vector $z$ is inside a sphere with a radius of $v_{max}$ which can then be written as:
+%\begin{equation}\label{eq:velocity_constraint_update}
+%    \Pi_{\zeta}(z) = \begin{cases}
+% v_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > v_{max},\\
+%z	& otherwise.
+%\end{cases}
+%\end{equation}
+
+\subsubsection*{Convex obstacles}
+
+We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
 Obstacles with non-convex shapes can be modeled using unions of the convex sets.
 
-  We enforce the constraints at each discrete time step $x_{ij}$ (enforcement of the constraints between these points can be achieved by making the obstacles sightly bigger than its actual size).
-For a convex area, waypoints stays unchanged it they are outside the zone, and if the waypoints are inside the zone, the constraint function $D(\vx)$ returns the least negative distance from the waypoints to the zone defined by hyperplanes which is represented as:
+The convex region $\cP$ is defined using a collection of $l$ hyperplanes $n_{k} q = m_{k}$, where $n_k$ is the normal vector (outward pointing for obstacle boundaries and inward pointing for workspace boundaries) and $m_k$ is the scalar offset defining the $k$-th hyperplane.
+The distance between a single waypoint $q_{ij}$ and the $k$th hyperplane $d_{k}(q_{ij},\cP)$ is defined as:
+\begin{equation}
+    d_{k}(q_{ij},\cP)= p_{ij}\transpose n_k - m_k.
+\end{equation}
+
+The constraint function $D(q_{ij})$ returns the least negative distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, defined as:
 \begin{equation}\label{eq:zoneConstraintMap}
-D_i(\vx) = \bmat{d_{11} \\\vdots\\ d_{nm}}
-\end{equation}
-where 
-\begin{align}
-    d_{ij}&= \max(\min(d_{ijk},0)),\\
-   d_{ijk} &= p_{ij}\transpose n_k - m_k,
-\end{align}
-and $n_k$ is the normal vector and $m_k$ is the scalar offset defining the $k$-th hyperplane.
+	D(q_{ij}) = \max_{k=1,\dots,l} (\min(d_{k}(q_{ij},\cP),0))
+\end{equation}
+
+%\rtron{Define for a single $x_{ij}$, then just say that we add constraints for all $ij$.
+Instead of using $min(d_{ijk})$, use $dist(x_{ij},\cP)$, where $\cP$ is the cvx polygon} We enforce the constraints for all $ij$ (enforcement of the constraints between these points can be achieved by making the obstacles sightly bigger than its actual size).
+
 The corresponding constraint set is simply
 \begin{equation}
-    \zeta= \{z \mid z = 0 \},
+    \sZ= \{z \mid z = 0 \},
 \end{equation}
@@
 \begin{equation}\label{eq:zoneConstraintProjection}
-    \Pi_\zeta(z) = 0.
+    \Pi_\sZ(z) = 0.
 \end{equation}
@@
 As mentioned before, non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
-\subsubsection{Waypoints with flexible deadlines}
-In this type of constraint, we assume that an agent needs to go through a spherical ball around a given point $p$ with a radius of $d_{max}$ at some time instant $j$ belonging to a given time window $[t_1,t_2]$.
-In this case, we define the function $D(\vq)$ to return the smallest distance from the point $p$ to any point on the trajectory restricted to the relevant time window.
+
+\subsubsection*{Waypoints with flexible deadlines}
+We assume that an robot $i$ needs to reach a given point $p$ within a radius of $d_{max}$ at some time instant $j$ belonging to a given time window $[t_1,t_2]$.
+The constraint function $D(\vq)$ to return the smallest distance from the point $p$ to waypoint on the trajectory restricted to the relevant time window.
 This can be expressed precisely in the following form:
 \begin{equation}\label{eq:waypoint_constraint_D}
-D_i(\vq) = \min_{i\in\{1\dots,n\}, j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),
+D(\vq) = \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),
 \end{equation}
@@
 \begin{equation}\label{eq:waypoint_constraint}
-\zeta= \{z \mid z < z_{max} \},
+\sZ= \{z \mid z < z_{max} \},
 \end{equation}
@@
 Note that this function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
-The projection $\Pi_\zeta(z)$ for this constraint can be written as:
+The projection $\Pi_\sZ(z)$ for this constraint can be written as:
 \begin{equation}\label{eq:waypoint_constraint_update}
-\Pi_\zeta(z) = \min(z,z_{max}).
-\end{equation}
-Note that \eqref{eq:waypoint_constraint} and \eqref{eq:waypoint_constraint_update} are equivalent to \eqref{eq:velocity_constraint} and \eqref{eq:velocity_constraint_update}, except for the fact that the quantity in \eqref{eq:waypoint_constraint_D} is always a positive scalar.
-
-  \subsection{Householder rotations}\label{sec:householder}
-
-  To formulate the operator $\Pi_\zeta$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
+\Pi_\sZ(z) = \min(z,z_{max}).
+\end{equation}
+%Note that \eqref{eq:waypoint_constraint} and \eqref{eq:waypoint_constraint_update} are equivalent to \eqref{eq:velocity_constraint} and \eqref{eq:velocity_constraint_update}, except for the fact that the quantity in \eqref{eq:waypoint_constraint_D} is always a positive scalar.
+
+\rtron{Give example application here, and include application of ADMM without the security constraints, but highlighting a path that would break the security}
+\zyang{plot new simpler example, add collision avoidance}
+
+ \subsubsection{Householder rotations}\label{sec:householder}
+
+  To formulate the operator $\Pi_\sZ$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
 This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
@@
 
-\subsection{Rapidly-exploring Random Trees}
-We use RRT* as a component of the solution \cite{karaman2010incremental}, which is an optimized variant of the rapidly-exploring Random Trees (RRT).
-As a optimal path planning algorithm, RRT* returns the shortest paths between an initial location and multiple potential goals.
-We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
-The basic RRT* algorithm is shown in Algorithm \ref{alg:rrt}.
-For a given tree $G=(V,E)$, key functions called by the algorithm are
-\begin{description}
-\item[$\texttt{Sample}(i)$] This function returns independent identically distributed samples from the free configuration space.
-\item[$\texttt{Nearest}(x)$] This function returns the vertex $v\in V$ that is closest in Euclidean distance to the input point $x$.
-\item[$\texttt{Steer}(x,y)$] This function returns a point $z$ that minimize $\norm{z-y}$ subject to $\norm{z-x}\leq \eta$ for a prespecified $\eta>0$.
-\item[$\texttt{ObstacleFree}(x,y)$] This function returns whether the line segment between $x$ and $y$ is free of collision.
-\item[$\texttt{Cost}(v)$] This function assigns a non-negative cost (total travel distance in our application) to the unique path from the initial position to $v$ . 
-\item[$\texttt{Parent}(v)$] This is a function that maps the vertex $v$ to $v'\in V$ such that $(v',v)\in E$
-\end{description}
-
-\section{Secure Multi-robot path planning using co-observation and reachability constraints}
-
-Besides traditional path planning constraints, additional security constraints need to be incorporated into the path planning problem to prevent cases where an attacker changes a robot's path between two observations to reach a forbidden region without being detected.
-The work of \cite{wardega2019resilience} provide exact solution for grid-world configuration.
-Using the onboard sensing capabilities, robots can perform inter-robot observations as an additional security measure.
-Each robot' self-report includes not only its own status, but also additional observations of other robots' status.
-For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''.
-Similarly, robot $j$ also reports its observations of robot $i$ to the CE.
-This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.
-
-When transforming the solution to continuous configuration spaces, additional analysis is needed on the reachability of robots in order for the security of co-observation schedule to hold.
-More broadly, the problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.
-This constraint is formulated using an ellipsoidal bound of the reachability region, and the idea of using an ellipsoidal bound to limit the search space is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm.
-
-We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.
-To the best of our knowledge, our path planning algorithm is the only one flexible enough to handle the safety related spatio-temporal constraints introduced by co-observations and reachability.
-
-\subsection{Co-observation schedule}
+%\subsection{Secure Multi-robot path planning using co-observation and reachability constraints}
+\subsection{Co-observation schedule constraint}
 The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
-The co-observation constraint is modeled as a relative distance constraint between two robots at some time instant $j$ (i.e., to require two agents see each other within a certain radius to inspect each other, or to exchange data).
+This constraint is modeled as a relative distance constraint between two robots at some time instant $j$ (i.e., to require two agents see each other within a certain radius to inspect each other, or to exchange data).
 The location of the co-observation location should make sure that the ellipsoidal reachability region between each co-observation, considered in later sections \ref{sec:reachability}, has an empty intersection with all forbidden regions.
@@
 \begin{equation}
-\zeta= \{z \mid z \leq d_{max} \},
+\sZ= \{z \mid z \leq d_{max} \},
 \end{equation}
@@
 \begin{equation}\label{eq:co-observation_constraint_update}
-\Pi_{\zeta}(z) = \begin{cases}
+\Pi_{\sZ}(z) = \begin{cases}
 d_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > d_{max},\\
@@
 
-\subsection{Reachability constraints}\label{sec:reachability}
+\subsection{Definition of reachability constraint}\label{sec:reachability}
   In this section, we first provide the definition of an \emph{ellipsoidal reachability region}.
 We then provide a differentiable map to transform such region in a canonical axis-aligned form where the operator $\Pi_\zeta$ and its differential can be obtained; these operators are then extended to the general case via the aforementioned transform.
-The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be used in the ADMM formulation in Chapter \ref{chapter:Multi-agent-ADMM}.
-
-\subsection{Definition of reachability constraint}\label{sec:ellipsoidal definition}
+The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be used in the ADMM formulation in section \ref{chapter:ADMM review}.
+
 The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
 
-\begin{definition}
+\begin{definition}\label{sec:ellipsoidal definition}
 	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the workspace such that there exist a trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$.
@@
 The reachability ellipsoid is an over-approximation of the exact reachability region; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
-\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
+\subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
   To simplify the problem, a canonical rigid body transformation is used to transform the ellipse $\cE$ from a global frame $\cF$ to a canonical frame $\cF_\cE$.
@@
 
-\subsection{Reachability constraints via ellipsoids}\label{sec:ellipoid constraints}
+\subsection{Reachability constraints using ellipsoidal constraints and their differential}\label{sec:ellipoid constraints}
 In later sections, we define constraint formulation of the ellipsoid regions against different types of forbidden regions: a point, a plane, a segment, and a convex polygon.
@@
 
+\subsection{Secured planning results and limitation}
+In this section, we apply our ADMM path planning algorithm to an instance of a map exploration problem (Figure~\ref{fig:ADMM-example-application}), and test the algorithm in both simulations and an experimental testbed.
+The environment to be explored, with three agents, is a $10m\times10m$ region and two forbidden regions \emph{Zone 2, 3} which is shown in Fig.\ref{fig:Grid-example-application}.We assume that the robots can meaningfully collect information on the underlying vector field for data locations no further than $3m$.
+The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.
+
+We utilize the APMAPF solver introduced in \cite{wardega2019resilience} to generate a MAPF plan with co-observation schedule on a grid-world application (Fig.\ref{fig:Grid-example-application}) and transform the result to a continuous configuration space, under the map exploration tasks.
+All robots have the task of collecting sensor information on the underlying vector field, with agent 3 having an additional task to visit the \emph{checkpoint} at time $8$.
+Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:trajectories-base}).
+We first set up an co-observation schedules considering two forbidden regions using the APMAPF algorithm, and add reachability constraints ensure a empty intersection between all robots' reachability regions between co-observations and forbidden regions.
+
+As shown in Fig.\ref{fig:Grid-example-application}, no task has been assigned to the agent besides the start and goal location.
+Agent 1 and 2 need to meet at time 8 and 14, whereas agent 2 and 3 need to meet at time 18.
+This result is also used as the initial trajectory input for the ADMM solver.
+
+Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained.
+Notice that additional checkpoint (i.e.
+stationary security camera) need to be incorporated in order to generated an attack-proof solution.
+Additional solutions to avoid these checkpoints will be discussed in Chapter \ref{chapter:cross-trajectory}.
+
+The result of the simulation is shown in Fig.\ref{fig:ReachabilitySimulation}.
+The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3.
+Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles.
+Therefore, the intersections between obstacles and ellipsoids, i.e.
+the case here between agent 3 and zone 1, are tolerable.
+All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=0.6\linewidth]{FinalResult}
+\caption{Simulation result for map exploration task. Reachability regions are shown as black ellipses in the result. Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones}
+\label{fig:ReachabilitySimulation}
+\end{center}
+\end{figure}
+
+\subsubsection{Limitations}\label{sec:reachability-discussion}
+Our solution shows that planning with reachability and co-observation is a promising approach to enhance the security of multi-agent systems.
+However, two main challenges have been identified in \cite{wardega2023hola}.
+Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other.
+In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path.
+Agent 3 in the Figure \ref{fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas.
+Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:trajectories-more-constraint} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
+This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
+These challenges are addressed in Chapter \ref{chapter:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
+
 \section{Cross-trajectory co-observation planning}
 
-We propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
+To address the feasibility challenge and performance trade-off of the ADMM problem discussed in Section \ref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
 Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
+
 In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.
@@
 This approach consists of two components: constructing the checkpoint graph based on unsecured multi-robot trajectories, which includes the location of security checkpoints and cross-trajectory paths, and the formulation of the network flow problem to solve for the co-observation plan.
+
+\subsection{Rapidly-exploring Random Trees}
+In this section, we utilize the \rrtstar{} \cite{karaman2010incremental} algorithm to address the task of determining path feasibility from a single starting location to multiple destination points (reference trajectories of other robots in this application).
+Our objective here is not to optimize specific constraints but to ascertain the existence of feasible paths.
+While the ADMM based solver \ref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
+RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for our specific task.
+
+As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and multiple potential goals.
+We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
+Key functions from \rrtstar{} that are called by the algorithm in this section are
+\begin{description}
+\item[$\texttt{Cost}(v)$] This function assigns a non-negative cost (total travel distance in our application) to the unique path from the initial position to $v$ . 
+\item[$\texttt{Parent}(v)$] This is a function that maps the vertex $v$ to $v'\in V$ such that $(v',v)\in E$
+\end{description}
+
 \section{Checkpoint graph construction}

### 2023-08-31 paper.tex
update

@@
 
-\section{Checkpoint graph construction}
+\subsection{Checkpoint graph construction}
 
@@
 
-\subsection{Checkpoints}\label{sec:security-checkpoint}
+\subsubsection{Checkpoints}\label{sec:security-checkpoint}
 Let $q\in\real{nmT}$ be the MRS trajectory found in Chapter \ref{chapter:Multi-agent-ADMM} for $m$ sub-teams with time horizon $T=t_{e}$, with $q_{p}(t)$ be the reference trajectory waypoint for sub-team $p$ at time $t$.
@@
 
-\subsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
+\subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
 After locating checkpoints $\union_p V_p$ for all sub-teams, we can search for cross-trajectory edges to connected all checkpoints to trajectories.
@@
 
-\subsection{In-trajectory edges}\label{sec:Graph-intro}
+\subsubsection{In-trajectory edges}\label{sec:Graph-intro}
 
@@
 
-\section{Co-observation planning problem}
+\subsection{Co-observation planning problem}
 In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network flow problem, and solve it using mixed-integer linear programs (MILP).
@@
      \begin{align}
-        \min &\quad \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} &\label{eq:flow-cost}\\
-        \subjectto & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij}, & \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
-        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1 & \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
-        & f^k_{ij} \in \{0,1\} &  \forall (ij)\in E\label{eq:SingleFLowCapacity}
+        \min & \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
+        s.t. & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij},  \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
+        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1, \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
+        & f^k_{ij} \in \{0,1\} ,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
      \end{align}
@@
 
-\section{Co-observation performance}
+\subsection{Co-observation performance}
 Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
@@
 
-\section{Result and simulation}
+\subsection{Result and simulation}
 In this section, we test the proposed method starting from the results in Figure \ref{fig:trajectories-more-constraint}, where three trajectories are provided for the map exploration task with no security related constraints (co-observation schedule and reachability).
@@
 \section{Summary}
-In this chapter, we provide a method to enhance the security of a multi-robot system without sacrificing the performance.
+In this paper, we provide a method to enhance the security of a multi-robot system without sacrificing the performance.
 This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories.

### 2023-09-01 paper.tex
Updates from Overleaf

@@
 \newcommand{\rrtstar}{$\texttt{RRT}^\texttt{*}$}
+\newtheorem{constraint}{ADMM constraint}
+\newtheoreom{example}{Example}
 
@@
 We formulate the planning problem into an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
-The security constraints including co-observation schedule and reachability analysis, alongside with traditional path planning constraints, are transformed into different types of spatio-temporal constraints in the optimization problem.
+The security constraints, including those from the co-observation schedule, reachability analysis, and the traditional path planning constraints, are transformed into different types of spatio-temporal sets in the optimization problem.
 We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space.
@@
 
-As an example application, we assume that there exists an underlying slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
+To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.
+\begin{example} Assume that there exists an underlying slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
 To explore unknown spatially-distributed fields, autonomous agents are usually required to traverse the entire unknown environment while collecting sensory data to estimate a corresponding map (Figure~\ref{fig:ADMM-example-application}).
@@
 For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.
-We define the cost function $\varPhi(\vq)$ to be an approximation of the uncertainty at any of the given points, and we aim to minimize such maximum uncertainty.
+\rtron{Define $\varPhi$ and $\Omega$ in words but briefly}
+%We define the cost function $\varPhi(\vq)$ to be an approximation of the uncertainty at any of the given points, and we aim to minimize such maximum uncertainty.
 We focus on a particular choice of objective function $\varPhi(\vq)$, in the context of a mapping and estimation applications, for the optimization problem \eqref{eq:general-problem}.
 \zyang{Do we need detail of the problem formulations?}
+\end{example}
 
@@
 
-\subsection{Preliminary}
+\subsection{Preliminaries}
 In this section, we review various mathematical concepts that will provide the foundations and context for the solver.
@@
   The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
-We then define the function $D(\vq)$ to return the velocity vectors for the $i$-th agent at time step $j$:
-\begin{equation}
-     D_{ij}(\vq) = q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\}
-\end{equation}
-and the constraint set is:
-\begin{equation}\label{eq:velocity_constraint}
-   \sZ_{ij} =\bigl\{z \mid \norm{z} \leq v_{max}\bigr\}.
-\end{equation}
-The projection operator $\Pi_\zeta(z)$ for this constraint  is simply a projection of $z$ to the interior of a sphere centered at the origin and having radius $v_{max}$.
+We then define the function $D(\vq)$ to return the velocity vectors for the $i$-th agent at time step $j$; its result then needs to be constrained to a sphere.
+
+  \begin{constraint}[Velocity constraint]
+\begin{align}
+     D_{ij}(\vq) &= q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\}\\
+\label{eq:velocity_constraint}
+   \sZ_{ij} &=\bigl\{z \mid \norm{z} \leq v_{max}\bigr\}\\
+   \Pi_{\sZ_{ij}}(z)&=\begin{cases}
+   v_{\max}\frac{z}{\norm{z}} \textrm{ if } \norm{z}>v_{\max}\\
+   z\textrm{ otherwise}
+   \end{cases}
+\end{align}
+\end{constraint}
+\rtron{Put all the constraints using this $\LaTeX$ environment.}
+\rtron{Make sure notation for $\sZ$ is consistent}
+%The projection operator $\Pi_\zeta(z)$ for this constraint  is simply a projection of $z$ to the interior of a sphere centered at the origin and having radius $v_{max}$.
 This constraint could be adapted to enforce more refined dynamical models.
@@
  \subsubsection{Householder rotations}\label{sec:householder}
-
+ \rtron{Move to right after the definition of differential}
   To formulate the operator $\Pi_\sZ$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
@@
 
-\subsection{Definition of reachability constraint}\label{sec:reachability}
-  In this section, we first provide the definition of an \emph{ellipsoidal reachability region}.
-We then provide a differentiable map to transform such region in a canonical axis-aligned form where the operator $\Pi_\zeta$ and its differential can be obtained; these operators are then extended to the general case via the aforementioned transform.
-The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be used in the ADMM formulation in section \ref{chapter:ADMM review}.
-
-The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
+\subsection{Definition of ellipsoidal reachability regions}\label{sec:reachability}
+  In this section, we define  \emph{ellipsoidal reachability regions} based on pairs of locations on a trajectory, and a transformation of such region in axis-aligned form.
+These definitions will be used to define different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon), their projections, and differentials in subsequent sections.
+  %differentiable map to transform such region in a canonical axis-aligned form where the operator $\Pi_\zeta$ and its differential can be obtained; these operators are then extended to the general case via the aforementioned transform.
+The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be
+  These will be used in the ADMM formulation in section \ref{chapter:ADMM review}.
+
+%The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
 
@@
     \includegraphics[width=0.6\linewidth]{Reachability}
+\rtron{Extend the figure to give a graphical representation of the canonical transformation}
     \caption{The ellipse showcases the reachability region.
@@
 
-\subsection{Reachability constraints using ellipsoidal constraints and their differential}\label{sec:ellipoid constraints}
-In later sections, we define constraint formulation of the ellipsoid regions against different types of forbidden regions: a point, a plane, a segment, and a convex polygon.
-For each one, our goal is to define the function $D(q)$, the set $\zeta$ and the projection $\Pi_\zeta$ that can be incorporated in the ADMM optimization (\ref{eq:ADMMSetConstraint_modified}); we also include derivations for the differential $\partial_qD(q)$, which can be used to significantly speed up the optimization.
+%\subsection{Reachability constraints using ellipsoidal constraints and their differential}\label{sec:ellipoid constraints}
+\rtron{Make sure that, throughout the paper, we use reachability ellipsoid instead of ellipsoidal regions}
+We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon.
+For each one, our goal is to define the function $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$ that can be incorporated in the ADMM optimization (\ref{eq:ADMMSetConstraint_modified}).
 
@@
 
+\rtron{For these constraints, add $\pi$ inside the constraint environment, then follow that environment with the proposition with the differential of $\pi$.}
+
 \begin{equation}\label{eq:ellipse-point-projection}
-\begin{split}
-\argmin_{q_p} &\quad \norm{q_{avoid}-q_p}^2 \\
-s.t. &\quad q_p\in \cE^{c}.
-\end{split}
+\pi_{p\cE}=\argmin_{q_p\in\cE^c} &\quad \norm{q_{avoid}-q_p}^2 
 \end{equation}
@@
 
-  \subsubsection{Projection to the standard ellipse}
+  \subsubsection{Projection to the standard ellipse}\rtron{Move to the appendix or refer to the conference paper}
   The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
@@
   \end{equation}
+  \rtron{Refer to figure}
   We use these two tangent points to define a novel measure of displacement between a plane and an ellipse.
@@
 \includegraphics[width=0.6\linewidth]{Ellipse2safezone_V2}
-\caption{Polygen-ellipse constraint. This constraint is simplified to either a plane-ellipse constraint or a point-ellipse constraint.}
+\caption{Polygon-ellipse constraint. This constraint is simplified to either a plane-ellipse constraint or a point-ellipse constraint.}
 \label{fig:Ellipse-to-safezone}

### 2023-09-06 paper.tex
update

@@
 \newtheorem{constraint}{ADMM constraint}
-\newtheoreom{example}{Example}
+\newtheorem{example}{Example}
 
@@
 For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.
-\rtron{Define $\varPhi$ and $\Omega$ in words but briefly}
-%We define the cost function $\varPhi(\vq)$ to be an approximation of the uncertainty at any of the given points, and we aim to minimize such maximum uncertainty.
-We focus on a particular choice of objective function $\varPhi(\vq)$, in the context of a mapping and estimation applications, for the optimization problem \eqref{eq:general-problem}.
-\zyang{Do we need detail of the problem formulations?}
+
+We address the estimation problem using Kalman Filters (KFs)(cf.
+\cite{anderson2012optimal}), with a focus on the estimated covariance $P_j$, to calculate the map model uncertainty.
+We assume the robot provides field measurements at waypoints~$q$, with Gaussian radial basis function modeling radius and quality.
+Our cost function $\varPhi(\vq)$ measures the maximum uncertainty $P_{j}$ among map locations of interest along the entire trajectory $\vq$, and our objective is to minimize this maximum uncertainty.
+Constraints $\Omega$ includes traditional constraints like velocity constraints, convex obstacles, waypoints to reach with deadlines, and security constraints including co-observation constraints and reachability constraints.
 \end{example}
@@
 With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{R}\to\real{m\times n}$  Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although semantically different.
+
+ \subsubsection{Householder rotations}\label{sec:householder}
+  To formulate the operator $\Pi_\sZ$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
+This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
+With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection).
+We call our version of the operator a \emph{Householder rotation}.
+In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.
+
+  \begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u$ as
+    \begin{equation}
+      u'=\nu_\cF+\nu_\cE,\quad u =\frac{u'}{\norm{u'}}.
+    \end{equation}
+    The \emph{Householder rotation} $H(\nu_\cF,\nu_\cE)$ is defined as
+    \begin{equation}\label{eq:H definition}
+      H(\nu_\cF,\nu_\cE) = 2 u u\transpose-I.
+    \end{equation}
+  \end{definition}
+  The main property of interest for our application is the fact that $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
+  \begin{proposition}\label{prop:HProperidy}
+    The matrix $H$ has the following properties:
+    \begin{enumerate}
+    \item It is a rotation, i.e.
+      \begin{enumerate}
+      \item\label{it:orthonormality} $H\transpose H=I$;
+      \item\label{it:determinant} $\det(H)=1$.
+      \end{enumerate}
+    \item\label{it:transformation} $\nu_\cE=H \nu_\cF$.
+    \end{enumerate}
+  \end{proposition}
+
+  We compute the differential of $H$ implicitly using the relation \eqref{equ:dt_to_dx}.
+We will use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
+  \begin{equation}
+    \bmat{v_1\\v_2\\v_3}\mapsto \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
+  \end{equation}
+  such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. %One can verify by direct computation the following property:
+  %\begin{equation}\label{eq:asymmetric to cross}
+  %  wv\transpose-vw\transpose=\cross{\cross{v}w}.
+  %\end{equation}
+  \begin{proposition}\label{prop:Hderivitive}
+    Let $\nu_\cF(t)$ represent a parametric curve. Then we have
+    \begin{equation}
+      \dot{H}=H\cross{-2M\dot{\nu}_{\cF}}
+    \end{equation}
+    where the matrix $M\in\real{3\times3}$ is given by
+    \begin{equation}
+      M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\norm{u'} \norm{\nu_\cF}}.
+    \end{equation}
+  \end{proposition}
 
@@
 \end{constraint}
-\rtron{Put all the constraints using this $\LaTeX$ environment.}
+\rtron{Put all the constraints using this \LaTeX environment.}
 \rtron{Make sure notation for $\sZ$ is consistent}
@@
 
-We use convex polygons to model regions defining the boundary of the workspace, as well as solid obstacles that cannot be entered by agents (note that the latter represent a non-convex constraint set from the point of view of the optimization problem).
-Obstacles with non-convex shapes can be modeled using unions of the convex sets.
-
-The convex region $\cP$ is defined using a collection of $l$ hyperplanes $n_{k} q = m_{k}$, where $n_k$ is the normal vector (outward pointing for obstacle boundaries and inward pointing for workspace boundaries) and $m_k$ is the scalar offset defining the $k$-th hyperplane.
+We use convex polygons to model regions defining solid obstacles and forbidden regions that cannot be entered by agents.
+The convex region $\cP$ is defined using a collection of $l$ hyperplanes $n_{k} q = m_{k}$, where $n_k$ is the normal vector pointing toward the outside of the obstacle and $m_k$ is the scalar offset defining the $k$-th hyperplane.
 The distance between a single waypoint $q_{ij}$ and the $k$th hyperplane $d_{k}(q_{ij},\cP)$ is defined as:
@@
 \end{equation}
-
-The constraint function $D(q_{ij})$ returns the least negative distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, defined as:
-\begin{equation}\label{eq:zoneConstraintMap}
-	D(q_{ij}) = \max_{k=1,\dots,l} (\min(d_{k}(q_{ij},\cP),0))
-\end{equation}
-
-%\rtron{Define for a single $x_{ij}$, then just say that we add constraints for all $ij$.
-Instead of using $min(d_{ijk})$, use $dist(x_{ij},\cP)$, where $\cP$ is the cvx polygon} We enforce the constraints for all $ij$ (enforcement of the constraints between these points can be achieved by making the obstacles sightly bigger than its actual size).
-
-The corresponding constraint set is simply
-\begin{equation}
-    \sZ= \{z \mid z = 0 \},
-\end{equation}
-with a projection function:
-\begin{equation}\label{eq:zoneConstraintProjection}
-    \Pi_\sZ(z) = 0.
-\end{equation}
-The motivating idea for \eqref{eq:zoneConstraintMap} and \eqref{eq:zoneConstraintProjection} is to find waypoints inside the zone and project them to the closest boundary.
-As mentioned before, non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
+We then defined function $D(\vq)$ to return the maximum distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, and set constraint on $z$ that it is a non-negative scalar.
+This constraint is applied to all $q_{ij} \in \vq$.
+
+\begin{constraint}[Obstacle constraint]
+\begin{align}
+     	D(q_{ij}) &= \max_{k=1,\dots,l} (d_{k}(q_{ij},\cP))\\
+\label{eq:obstacle_constraint}
+  \sZ &= \{z \mid z \geq 0 \},\\
+   \Pi_\sZ(z) & = \begin{cases}
+   0 & \textrm{if} \quad z < 0\\
+   z  & \textrm{otherwise}
+   \end{cases}
+\end{align}
+\end{constraint}
+
+The motivating idea for \eqref{eq:zoneConstraintMap} and \eqref{eq:zoneConstraintProjection} is to identify waypoints within a specific region and project them to the closest boundary.
+Non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
+By setting the normal vector pointing toward the inside of the region, this method can also serve to constrain the robots within the designated workspace region.
 
 \subsubsection*{Waypoints with flexible deadlines}
-We assume that an robot $i$ needs to reach a given point $p$ within a radius of $d_{max}$ at some time instant $j$ belonging to a given time window $[t_1,t_2]$.
+It is common for security related constraints to require robot reach a specific location at specific time.
+We assume robot $i$ is required to reach a given point $p$ within a radius of $d_{max}$ at some time instant $j$ belonging to a given time window $[t_1,t_2]$.
 The constraint function $D(\vq)$ to return the smallest distance from the point $p$ to waypoint on the trajectory restricted to the relevant time window.
-This can be expressed precisely in the following form:
-\begin{equation}\label{eq:waypoint_constraint_D}
-D(\vq) = \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),
-\end{equation}
-with the constraint set:
-\begin{equation}\label{eq:waypoint_constraint}
-\sZ= \{z \mid z < z_{max} \},
-\end{equation}
+\begin{constraint}[Waypoint constraint]
+\begin{align}
+     	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr)\\
+\label{eq:obstacle_constraint}
+  \sZ &= \{z \mid z < z_{max} \},\\
+   \Pi_\sZ(z) & = \min(z, d_{max}).
+\end{align}
+\end{constraint}
+
 where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
 Note that this function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
-The projection $\Pi_\sZ(z)$ for this constraint can be written as:
-\begin{equation}\label{eq:waypoint_constraint_update}
-\Pi_\sZ(z) = \min(z,z_{max}).
-\end{equation}
+
 %Note that \eqref{eq:waypoint_constraint} and \eqref{eq:waypoint_constraint_update} are equivalent to \eqref{eq:velocity_constraint} and \eqref{eq:velocity_constraint_update}, except for the fact that the quantity in \eqref{eq:waypoint_constraint_D} is always a positive scalar.
@@
 \zyang{plot new simpler example, add collision avoidance}
-
- \subsubsection{Householder rotations}\label{sec:householder}
- \rtron{Move to right after the definition of differential}
-  To formulate the operator $\Pi_\sZ$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
-This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
-With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection).
-We call our version of the operator a \emph{Householder rotation}.
-In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.
-
-  \begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u$ as
-    \begin{equation}
-      u'=\nu_\cF+\nu_\cE,\quad u =\frac{u'}{\norm{u'}}.
-    \end{equation}
-    The \emph{Householder rotation} $H(\nu_\cF,\nu_\cE)$ is defined as
-    \begin{equation}\label{eq:H definition}
-      H(\nu_\cF,\nu_\cE) = 2 u u\transpose-I.
-    \end{equation}
-  \end{definition}
-  The main property of interest for our application is the fact that $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
-  \begin{proposition}\label{prop:HProperidy}
-    The matrix $H$ has the following properties:
-    \begin{enumerate}
-    \item It is a rotation, i.e.
-      \begin{enumerate}
-      \item\label{it:orthonormality} $H\transpose H=I$;
-      \item\label{it:determinant} $\det(H)=1$.
-      \end{enumerate}
-    \item\label{it:transformation} $\nu_\cE=H \nu_\cF$.
-    \end{enumerate}
-  \end{proposition}
-
-  We compute the differential of $H$ implicitly using the relation \eqref{equ:dt_to_dx}.
-We will use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
-  \begin{equation}
-    \bmat{v_1\\v_2\\v_3}\mapsto \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
-  \end{equation}
-  such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. %One can verify by direct computation the following property:
-  %\begin{equation}\label{eq:asymmetric to cross}
-  %  wv\transpose-vw\transpose=\cross{\cross{v}w}.
-  %\end{equation}
-  \begin{proposition}\label{prop:Hderivitive}
-    Let $\nu_\cF(t)$ represent a parametric curve. Then we have
-    \begin{equation}
-      \dot{H}=H\cross{-2M\dot{\nu}_{\cF}}
-    \end{equation}
-    where the matrix $M\in\real{3\times3}$ is given by
-    \begin{equation}
-      M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\norm{u'} \norm{\nu_\cF}}.
-    \end{equation}
-  \end{proposition}
 
@@
     \centering
-    \includegraphics[width=0.6\linewidth]{Reachability}
-\rtron{Extend the figure to give a graphical representation of the canonical transformation}
+    \includegraphics[width=0.8\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}
     \caption{The ellipse showcases the reachability region.
-The black line is the planned trajectory of a robot, $q_1$ and $q_2$ are two locations this robot are expected at given time $t_1$ and $t_2$, blue and red line are possible trajectories if the robot is compromised in after reaching $q_1$.
-Robot that goes outside the reachability region to forbidden region can only reach $q_{2}'$ instead of $q_{2}$ at time $t_{2}$, even if it drives directly toward $q_{2}$ at full speed $v_{max}$ after the intrusion into forbidden region.}
+The black line is the planned trajectory of a robot, $q_1$ and $q_2$ are two locations this robot are expected at given time $t_1$ and $t_2$, dashed line is a possible trajectory if the robot is compromised after reaching $q_1$.
+Axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
+}
     \label{fig:EllipseConstraintExample}
@@
 \begin{equation}\label{eq:ellipse-point-projection}
-\pi_{p\cE}=\argmin_{q_p\in\cE^c} &\quad \norm{q_{avoid}-q_p}^2 
+\pi_{p\cE}=\argmin_{q_p\in\cE^c} \quad \norm{q_{avoid}-q_p}^2 
 \end{equation}
@@
 And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse, which is discussed below.
-
-  \subsubsection{Projection to the standard ellipse}\rtron{Move to the appendix or refer to the conference paper}
-  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
-  \begin{align}
-    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
-  \end{align}
-  with $c=\frac{\norm{q_2-q_1}}{2}$.
-
-  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
-  \begin{equation}\label{equ:standard-ellipse}
-    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
-  \end{equation}
-  where
-  \begin{equation}
-    Q = \diag(a^{-2},b^{-2},b^{-2}),
-  \end{equation}
-  and $b = \sqrt{a^2-c^2}$.
-  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
-
-  % Using the transformation defined in Section~\ref{sec:rotation2Standard}, the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
-  % \begin{equation}
-  %   \Fframe{E}(\Fframe{x}) = (\Fframe{x}-o_\cE)\transpose H\transpose Q H (\Fframe{x}-o_\cE) - 1
-  % \end{equation}
 

### 2023-09-06 paper.tex
update

@@
   To simplify the notation, in the following we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
-
-%\subsection{Reachability constraints using ellipsoidal constraints and their differential}\label{sec:ellipoid constraints}
-\rtron{Make sure that, throughout the paper, we use reachability ellipsoid instead of ellipsoidal regions}
+  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
+  \begin{align}
+    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
+  \end{align}
+  with $c=\frac{\norm{q_2-q_1}}{2}$.
+
+  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
+  \begin{equation}\label{equ:standard-ellipse}
+    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
+  \end{equation}
+  where
+  \begin{equation}
+    Q = \diag(a^{-2},b^{-2},b^{-2}),
+  \end{equation}
+  and $b = \sqrt{a^2-c^2}$.
+  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
+
+For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the defined transformation function.
+
 We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon.
@@
 And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse, which is discussed below.
+
+  \subsubsection{Projection to the standard ellipse}\rtron{Move to the appendix or refer to the conference paper}
+  % Using the transformation defined in Section~\ref{sec:rotation2Standard}, the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
+  % \begin{equation}
+  %   \Fframe{E}(\Fframe{x}) = (\Fframe{x}-o_\cE)\transpose H\transpose Q H (\Fframe{x}-o_\cE) - 1
+  % \end{equation}
 

### 2023-09-07 paper.tex
Updates from Overleaf

@@
 
-In this section, we aims to enhance the security of MRSs against malicious takeovers and deviations by attackers.
+In this section, we aim to enhance the security of MRSs against malicious takeovers and deviations by attackers.
 Specifically, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
@@
 In this way, the plan ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
-\cite{wardega2019resilience} solved this problem in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but was unable to optimizing over arbitrary smooth cost functions.
-
-We formulate the planning problem into an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
-The security constraints, including those from the co-observation schedule, reachability analysis, and the traditional path planning constraints, are transformed into different types of spatio-temporal sets in the optimization problem.
+\cite{wardega2019resilience} solved this problem in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
+
+We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. 
 We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space.
 For a team of $n$ agents, and a task time horizon of $T$, the overall trajectory of the multi-agent system can be represented as an aggregated vector $\vq\in \real{n m T}$.
-The goal of our path planning problem is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, formally:
+The goal of our path planning problem is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$.
+The set $\Omega$ is given by the intersection of spatio-temporal sets given by the security constraints (co-observation schedule, reachability analysis) and the traditional path planning constraints.
+Formally:
 \begin{equation}\label{eq:general-problem}
@@
 To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.
-\begin{example} Assume that there exists an underlying slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
+\begin{example} Assume that there exists a slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
 To explore unknown spatially-distributed fields, autonomous agents are usually required to traverse the entire unknown environment while collecting sensory data to estimate a corresponding map (Figure~\ref{fig:ADMM-example-application}).
@@
 For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.
-
 We address the estimation problem using Kalman Filters (KFs)(cf.
@@
 We assume the robot provides field measurements at waypoints~$q$, with Gaussian radial basis function modeling radius and quality.
+\rtron{The previous paragraph can be written more compactly.}
+
 Our cost function $\varPhi(\vq)$ measures the maximum uncertainty $P_{j}$ among map locations of interest along the entire trajectory $\vq$, and our objective is to minimize this maximum uncertainty.
@@
 We begin by presenting the foundational mathematical concepts, notably the basic ADMM optimal trajectory solver.
-Subsequently, we seamlessly integrate security constraints, encompassing co-observation schedule and reachability constraints, into our proposed solver.
-Concluding this section, we present the obtained results alongside identifying limitations that will be addressed in the upcoming section.
+Subsequently, our solver allows us to seamlessly integrate security constraints, encompassing co-observation schedule and reachability constraints.
+Concluding this section, we present the obtained results alongside limitations (due to infeasibility) that are addressed in \Cref{sec:??}.
 
 \subsection{Preliminaries}
-In this section, we review various mathematical concepts that will provide the foundations and context for the solver.
+In this section, we review various mathematical concepts that will provide the foundations and context for the solver and constraints.
 
@@
 where $t\mapsto x(t)\in\real{n}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$.
-For later part of this paper, we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
-The differentials $\partial_x f$ is derived through (\ref{equ:dt_to_dx}) having $\dot f$ divided by $\dot x$.
-
-With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{R}\to\real{m\times n}$  Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although semantically different.
+For brevity we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
+The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.
+
+With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{R}\to\real{m\times n}$.
+Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to interpret $\partial_x f$ as a linear operator applied to $\dot{x}$.
 
  \subsubsection{Householder rotations}\label{sec:householder}
-  To formulate the operator $\Pi_\sZ$ for our novel constraint, we will define a differentiable transformation of the constraint set to a canonical form.
+ In the derivation of the reachability constraint in \Cref{sec:??}, we need to define a differentiable transformation to a canonical form.
 This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
@@
   \end{proposition}
+\rtron{State where the proof can be found}
 
 \subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
-The basic idea behind ADMM based solver \cite{zyang} is to split the constraints from the objective function using a different set of variables $\vz$, and then solve an Augmented Lagrangian formulation of the optimization problem in \eqref{eq:general-problem}.
+The basic idea behind our ADMM-based solver \cite{zyang} is to split the constraints from the objective function using a different set of variables $\vz$, and then solve an Augmented Lagrangian formulation of the optimization problem in \eqref{eq:general-problem}.
 More specifically, we can rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function.
-However, in the traditional application of ADMM, the duplicated variables $\vz$ are solved through a projection to the constraint set $\Omega$.
+In the traditional application of ADMM, the variables $\vz$ are duplicates of $\vx$ projected to the constraint set $\Omega$.
 However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
-To deal with this problem, we propose a minor generalization of the ADMM formulation~\eqref{equ:ADMMSetConstraint} where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy):
+To deal with this problem, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy):
 \begin{equation}\label{eq:ADMMSetConstraint_modified}
@@
 \end{subequations}
-where $\Pi_\mathcal{Z}$ is the new projection to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that intuitively accumulates the sum of primal residuals
+where $\Pi_\mathcal{Z}$ is the new projection to the modified constraint set $\mathcal{Z}$ \rtron{It is not clear where $\cZ$ comes from}, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
 \begin{equation}\label{eq:primal-residual}
@@
 Since $D(\vq)$ is the vertical concatenation of $D_i(\vq)$, the projection of each set $\mathcal{Z}_i$ is independent for each constraint and can be computed separately.
-The advantage of this formulation is that we can choose $D(\vq)$ such that the new constraint set~$Z$ becomes simple to compute; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vq$ in \eqref{eq:admm-mod-update-q}.
-Additionally, the function~$D(\vq)$ can be used to select only the subset of the variables on which a constraint depends.
-
-We consider the following types of traditional path planning constraints in the ADMM constraints:
-\subsubsection*{Velocity constraints}
+The advantage of this formulation is that we can choose $D(\vq)$ such that the new constraint set~$\cZ$ becomes simple to compute; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vq$ in \eqref{eq:admm-mod-update-q}.
+Additionally, the function~$D(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.
+
+We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for traditional path planning constraints (\Cref{sec:??}-\ref{sec:??}), co-observation security constraints (\Cref{sec:??}), and reachability constraints (\Cref{sec:??}).
+The latter are based on the definition of \emph{ellipsoidal reacability regions} (\Cref{sec:??}).
+\subsection{Velocity constraints}
   The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
@@
 
-\subsubsection*{Convex obstacles}
+\subsection{Convex polygonal obstacles collision constraints}
 
@@
 
-\subsubsection*{Waypoints with flexible deadlines}
+\subsection{Waypoints with flexible deadlines}
 It is common for security related constraints to require robot reach a specific location at specific time.
@@
  We write the function for the constraint as:
+\rtron{Use the constraint environment}
 \begin{align}
@@
   \end{equation}
-  The reverse transformation is $\Eframe{q}=R\transpose( \Fframe{q}-o)$.
+ % The reverse transformation is $\Eframe{q}=R\transpose( \Fframe{q}-o)$.
 
@@
 
+\rtron{You can use a definition to mirror definition 3}
   The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
@@
 
-\subsection{Point-ellipsoid constraint}\label{sec:ellipsoid-point}
+\subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
 As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
@@
 
-\subsection{Plane-ellipsoid constraint}\label{sec:ellipsoide-plane}
+\subsection{Plane-ellipsoid reachability constraint}\label{sec:ellipsoide-plane}
 
@@
 
-\subsection{Line-segment-ellipse constraint}\label{chapter:ellipse to segment}
+\subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
 
@@
 \end{equation}
-\subsection{Convex-polygon-ellipse constraint}\label{sec:ellipse-region-constraint} 
+\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
 To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse.

### 2023-09-11 paper.tex
update

@@
 	\centering
-    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.45\linewidth]{co-observ}}
-    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.45\linewidth]{cross-traj}}
+    \subfloat[Plan-deviation attack\label{fig:example-plan-dev}]{\includegraphics[width = 0.32\linewidth]{plan-deviation}}
+    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.32\linewidth]{co-observ}}
+    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.32\linewidth]{cross-traj}}
 
@@
 To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.
-\begin{example} Assume that there exists a slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
+
+\begin{example} 
+We consider the estimation of a slowly-varying scalar or vector field, denoted as $\vx$, at discrete locations within an unknown environment.
+Autonomous agents navigate this environment, collecting sensory data to construct a corresponding map (see Figure~\ref{fig:ADMM-example-application}).
+Our map comprises points of interest arranged on a grid, each associated with a slowly-changing value.
+Our goal is to find paths that minimize uncertainty and effectively reconstruct the field.
+We utilize Kalman Filters (KFs)~(cf.
+\cite{anderson2012optimal}) to estimate uncertainty through the covariance $P_j$.
+Additionally, the robot provides field measurements at waypoints $q$ using a Gaussian radial basis function for radius and quality modeling.
+
+%Assume that there exists a slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
 To explore unknown spatially-distributed fields, autonomous agents are usually required to traverse the entire unknown environment while collecting sensory data to estimate a corresponding map (Figure~\ref{fig:ADMM-example-application}).
@@
 For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.
-We address the estimation problem using Kalman Filters (KFs)(cf.
+
+%We address the estimation problem using Kalman Filters (KFs)(cf.
 \cite{anderson2012optimal}), with a focus on the estimated covariance $P_j$, to calculate the map model uncertainty.
 We assume the robot provides field measurements at waypoints~$q$, with Gaussian radial basis function modeling radius and quality.
-\rtron{The previous paragraph can be written more compactly.}
+%\rtron{The previous paragraph can be written more compactly.}
 
@@
   The main property of interest for our application is the fact that $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
-  \begin{proposition}\label{prop:HProperidy}
+  \begin{proposition}\label{prop:HProperty}
     The matrix $H$ has the following properties:
@@
   \end{proposition}
+  \begin{proof}
+  	See Appendix \ref{proof:HProperty}.
+  \end{proof}
 
@@
   \end{proposition}
-\rtron{State where the proof can be found}
+  \begin{proof}
+  	See Appendix \ref{proof:Hderivitive}.
+  \end{proof}
 
@@
 
-We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for traditional path planning constraints (\Cref{sec:??}-\ref{sec:??}), co-observation security constraints (\Cref{sec:??}), and reachability constraints (\Cref{sec:??}).
-The latter are based on the definition of \emph{ellipsoidal reacability regions} (\Cref{sec:??}).
-\subsection{Velocity constraints}
+We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for traditional path planning constraints (\Cref{sec:velocity-constraint}-\Cref{sec:waypoint-constraint}), co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:??}).
+The latter are based on the definition of \emph{ellipsoidal reacability regions} (\Cref{sec:reachability}).
+\subsection{Velocity constraints}\label{sec:velocity-constraint}
   The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
@@
 \end{constraint}
-\rtron{Put all the constraints using this \LaTeX environment.}
-\rtron{Make sure notation for $\sZ$ is consistent}
-%The projection operator $\Pi_\zeta(z)$ for this constraint  is simply a projection of $z$ to the interior of a sphere centered at the origin and having radius $v_{max}$.
-This constraint could be adapted to enforce more refined dynamical models.
-
-%implies that the projection of the vector $z$ is inside a sphere with a radius of $v_{max}$ which can then be written as:
-%\begin{equation}\label{eq:velocity_constraint_update}
-%    \Pi_{\zeta}(z) = \begin{cases}
-% v_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > v_{max},\\
-%z	& otherwise.
-%\end{cases}
-%\end{equation}
-
-\subsection{Convex polygonal obstacles collision constraints}
+
+\subsection{Convex polygonal obstacles collision constraints} \label{sec:obstacle-constraint}
 
@@
    z  & \textrm{otherwise}
-   \end{cases}
+   \end{cases} \label{eq:zoneConstraintProjection}
 \end{align}
@@
 
-The motivating idea for \eqref{eq:zoneConstraintMap} and \eqref{eq:zoneConstraintProjection} is to identify waypoints within a specific region and project them to the closest boundary.
+The motivating idea for \eqref{eq:obstacle_constraint} and \eqref{eq:zoneConstraintProjection} is to identify waypoints within a specific region and project them to the closest boundary.
 Non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
@@
 
-\subsection{Waypoints with flexible deadlines}
+\subsection{Waypoints with flexible deadlines}\label{sec:waypoint-constraint}
 It is common for security related constraints to require robot reach a specific location at specific time.
@@
      	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr)\\
-\label{eq:obstacle_constraint}
+\label{eq:waypoint_constraint}
   \sZ &= \{z \mid z < z_{max} \},\\
@@
 Note that this function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
-
-%Note that \eqref{eq:waypoint_constraint} and \eqref{eq:waypoint_constraint_update} are equivalent to \eqref{eq:velocity_constraint} and \eqref{eq:velocity_constraint_update}, except for the fact that the quantity in \eqref{eq:waypoint_constraint_D} is always a positive scalar.
-
 \rtron{Give example application here, and include application of ADMM without the security constraints, but highlighting a path that would break the security}
@@
 %\subsection{Secure Multi-robot path planning using co-observation and reachability constraints}
-\subsection{Co-observation schedule constraint}
+\subsection{Co-observation schedule constraint}\label{sec:co-observation-constraint}
 The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
@@
  We write the function for the constraint as:
-\rtron{Use the constraint environment}
+\begin{constraint}[Co-observation constraint]
 \begin{align}
-D(\vq) = \overrightarrow{q_{aj}q_{bj}},
-\end{align}
-where $a,b$ are the indices of the pair of agents required for a mutual inspection. The corresponding constraint set is simply
-\begin{equation}
-\sZ= \{z \mid z \leq d_{max} \},
-\end{equation}
-with a projection function:
-\begin{equation}\label{eq:co-observation_constraint_update}
-\Pi_{\sZ}(z) = \begin{cases}
+D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:waypoint_constraint}\\
+  \sZ &= \{z \mid z \leq d_{max} \},\\
+   \Pi_\sZ(z) & = \begin{cases}
 d_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > d_{max},\\
@@
 \end{cases}
-\end{equation}
-The locations $q_{aj}$ and $q_{bj}$ where the co-observation performed are computed as part of the optimization.
+\end{align}
+\end{constraint}
+
+where $a,b$ are the indices of the pair of agents required for a mutual inspection. The locations $q_{aj}$ and $q_{bj}$ where the co-observation performed are computed as part of the optimization.
 
@@
 The reachability ellipsoid is an over-approximation of the exact reachability region; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
+
 \subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
-  To simplify the problem, a canonical rigid body transformation is used to transform the ellipse $\cE$ from a global frame $\cF$ to a canonical frame $\cF_\cE$.
-The latter is defined such that the center of the ellipsoid is located at the origin and the foci are aligned with the first axis of $\cF_\cE$.
-Since the transformation depends on the two foci, i.e., two waypoints of an agent, the challenge here is to construct the transformation in a differentiable way.
-  For the convenience of derivation, we define the coordinate transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, from now on we simply refer to as $R$ and $o$, respectively.
+To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$.
+In this new frame, the ellipsoid's center aligns with the origin, and its foci align with the first axis of $\cF_\cE$.
+We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
+
+For the convenience of derivation, we define the coordinate transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we simply refer to as $R$ and $o$, respectively.
 The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the formulation:
@@
   \end{equation}
- % The reverse transformation is $\Eframe{q}=R\transpose( \Fframe{q}-o)$.
 
@@
 Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$.
-We then define the rotation $R$ using a Householder rotation, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
+We then define the rotation $R$ using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
   \begin{align} 
@@
   \end{align}
-  To simplify the notation, in the following we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
+  In the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
   The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
@@
   with $c=\frac{\norm{q_2-q_1}}{2}$.
-
-\rtron{You can use a definition to mirror definition 3}
+\begin{definition}
   The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
@@
   The ellipse parameters $a$,$b$ represent the lengths of the major axes.
+\end{definition}
 
@@
 The goal is to design the trajectory $q(t)$ such that $q_{avoid}\notin\mathcal{E}(q_1,q_2)$.
-We first define a projection function $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$, which returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
-
-\rtron{For these constraints, add $\pi$ inside the constraint environment, then follow that environment with the proposition with the differential of $\pi$.}
-
+This constraint can be written as,
+
+\begin{constraint}[Point-ellipsoid reachability constraint]
+\begin{align}
+D(\vq) &=  \begin{cases}
+      \pi_{p\cE}(q) - q_{avoid} & q_{avoid} \in \cE, \\
+      {0} & \textrm{otherwise}.
+    \end{cases} \label{eq:point_ellipsoid_constraint}\\
+  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
+   \Pi_\sZ(z) & = 0, 
+\end{align}
+\end{constraint}
+
+where $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$ is a projection function that returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
 \begin{equation}\label{eq:ellipse-point-projection}
@@
 \begin{center}
-\includegraphics[width=0.6\linewidth]{Ellipse2point}
-\caption{Point-ellipsoid constraint, a point $f$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$.}
+\includegraphics[width=0.6\linewidth, trim = 1.5cm 2.5cm 1.5cm 3cm, clip]{Ellipse2point}
+\caption{Point-ellipsoid constraint, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$.}
 \label{fig:Ellipse-to-point}
@@
 
-  Then, the constraint $q_{avoid}\notin\mathcal{E}(q(t_1),q(t_2))$ can be written as:
-  \begin{equation}
-    D(q) = \pi_{p\cE}(q_{avoid};q(t_1),q(t_2),r)-q_{avoid} = 0
-  \end{equation}
-
   For cases where $q_{avoid} \notin \cE(q(t_2),q(t_1),r)$, $\pi_{p\cE}(q_{avoid}) = q_{avoid}$.
-And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse, which is discussed below.
+And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse.
+
+  \zyang{can this be treated as proposition}
+  \begin{proposition} \label{prop:ellipse-project-canonical}
+  In canonical frame $\cF_{\cE}$, the projection from a point $q^{\cE}_{avoid}\in \cE$ inside the ellipse to the boundary of $\cE$:
+  \begin{equation}
+  	q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid}
+  \end{equation}
+  %where $S=(I+sQ)\inverse$.Using the fact that since $q^\cE_p$ is a point on the ellipse, 
+  where $s$ can be solved as the root of the equation obtained by substituting \eqref{eq:qp from S} in $\Eframe E(\Eframe q)$:
+  \begin{equation}
+    0=F(s)={q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1,
+  \end{equation}
+  where
+  \begin{equation}
+    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right)
+  \end{equation}
+ Detailed methods for computing $s$ can be found in \cite{eberly}. 
+  \end{proposition}
+  \begin{proof}
+  Proof can be found in Appendix~\Cref{proof:ellipse-project-canonical}
+  \end{proof}
 
@@
 
-  The point to project, $q_{avoid}$, can be likewise expressed in $\cF_\cE$ as $\Eframe{q}_{avoid} =  H (\Fframe q_{avoid}-o)$.
-
+  %The point to project, $q_{avoid}$, can be likewise expressed in $\cF_\cE$ as $\Eframe{q}_{avoid} =  H (\Fframe q_{avoid}-o)$.
 We now turn our attention to the problem of projecting $\Eframe{q}_{avoid}$ on the zero level set of $E^\cE$ (i.e., the reachability ellipsoid in the canonical frame).
@@
 
-  Let $q^\cE_p$ be the point on the surface of the ellipsoid, i.e., $\Eframe E(q^\cE_p) = 0$, corresponding to the projection of the point $q^\cE_{avoid}$.
+  %Let $q^\cE_p$ be the point on the surface of the ellipsoid, i.e., $\Eframe E(q^\cE_p) = 0$, corresponding to the projection of the point $q^\cE_{avoid}$.
 Using Lagrange multipliers applied to the constrained optimization problem \eqref{eq:ellipse-point-projection} (after transforming it in the canonical frame), one can show that the vector from a point to its projection, $q^\cE_{avoid}- q^\cE_p$, must be collinear with the gradient of $\Eframe \cE$, i.e.
-  \begin{equation}
-    q^\cE_p- q^\cE_{avoid} = s \partial_q \Eframe E(q^\cE_p)\transpose = s Q q^\cE_p
-  \end{equation}
-  for some scale $s\in\real{}$;
-  thus $q^\cE_p$ can be written as:
-  \begin{equation}\label{eq:qp from S}
-    q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid}
-    % \bmat{\frac{a^{2}}{s+a^{2}}& 0 & 0 \\
-    % 0 & \frac{b^{2}}{s+b^{2}}&0 \\
-    % 0&0&\frac{b^{2}}{s+b^{2}}} q^\cE_{avoid} =
-  \end{equation}
-  where $S=(I+sQ)\inverse$.
-  Using the fact that since $q^\cE_p$ is a point on the ellipse, $s$ can be solved as the root of the equation obtained by substituting \eqref{eq:qp from S} in $\Eframe E(\Eframe q)$:
-  \begin{equation}
-    0=F(s)={q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1,
-  \end{equation}
-  where
-  \begin{equation}
-    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right)
-  \end{equation}
- Detailed methods for computing $s$ can be found in \cite{eberly}.
-
-  Then the point-to-ellipse projection function can be represented as:
+ % \begin{equation}
+ %   q^\cE_p- q^\cE_{avoid} = s \partial_q \Eframe E(q^\cE_p)\transpose = s Q q^\cE_p
+  %\end{equation}
+  %for some scale $s\in\real{}$;
+ % thus $q^\cE_p$ can be written as:
+
+  Then the point-to-ellipse projection function in $\cF$ can be represented as:
   \begin{multline}\label{equ:Point2EllipseProjection}
@@
   \end{multline}
+
   In our derivations, we consider only the 3-D case ($m=3$); for the 2-D case, let $P=\bmat{I & 0}\in\real{2\times 3}$: then $\pi_{p\cE}^{\textrm{2D}}=P\pi_{p\cE}^{\textrm{3D}}(P\transpose q_{avoid}; P\transpose q_1, P\transpose q_2,a)$.
-
-  \subsubsection{ADMM constraints}
-  The corresponding constraint is written as
-  \begin{equation}
-    D_{p}(q) = \begin{cases}
-      \pi_{p\cE}(q) - q_{avoid} & q_{avoid} \in \cE, \\
-      {0} & \textrm{otherwise}.
-    \end{cases}
-  \end{equation}
-  and feasible set and projection function as:
-  \begin{equation}
-    \zeta = \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\quad \Pi(D_p(q)) = {0}
-  \end{equation}
 
@@
 
-\subsection{Proof of proposition \ref{prop:HProperidy}}
-\begin{proof}
+\subsection{Proof of proposition \ref{prop:HProperty}} \label{proof:HProperty}
     For subclaim~\ref{it:orthonormality}:
@@
     \end{equation}
-\end{proof}
-
-\subsection{Proof or proposition \ref{prop:Hderivitive}}
-\begin{proof}
+
+\subsection{Proof or proposition \ref{prop:Hderivitive}} \label{proof:Hderivitive}
     From the definition of $H$ in \eqref{eq:H definition}, we have
@@
     which is equivalent to the claim.
-  \end{proof}
-
-  \subsection{Proof of proposition \ref{prop:Ellipse2PointDiff}}
-  \begin{proof}
+
+  \subsection{Proof of proposition \ref{prop:Ellipse2PointDiff}}\label{proof:Ellipse2PointDiff}
       To make the notation more compact, we will use $\partial_q f$ instead of $\partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} f$ for the remainder of the proof.
@@
     from which the claim follows.
-  \end{proof}
-
-  \subsection{Proof of proposition \ref{prop:dpi_ne dt}}
-  \begin{proof}
+
+  \subsection{Proof of proposition \ref{prop:dpi_ne dt}}\label{proof:dpi_ne dt}
     We first need to derive $\dot{d}_\cE$ and $\dot{d}_{\cE t}$
@@
     subtracting $\dot q$ from (\ref{equ:dpl_dt}) and (\ref{equ:dplt_dt}), we can derive the result shown in (\ref{equ:ProjectPoint})
-  \end{proof}
 

### 2023-09-12 paper.tex
Updates from Overleaf

@@
  \end{figure}
+ \rtron{Make sure we refer back to Example 1 when makes sense}
 
@@
 
-The result of the simulation is shown in Fig.\ref{fig:ReachabilitySimulation}.
+The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}.
 The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3.
@@
 
-To address the feasibility challenge and performance trade-off of the ADMM problem discussed in Section \ref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
-Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
-
-In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.
-Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
+To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams \rtronref{refer to introductory figure}.
+These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
+Note that \emph{cross-trajectory co-observation}, are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
+\rtronref{(More discussion in Sec.
+??)}.
+
+\rtronhl{Move to discussion}{In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.}
 
@@
 
-Assume we have a total of $N$ robots in the system.
-We define a partition $\cI=\union_p \cI_p$ of the robots such that robots in \emph{sub-team} $\cI_p$ have the same nominal trajectory.
-We use the planner introduced in Chapter \ref{chapter:Multi-agent-ADMM} to generate multi-robot trajectories with $N_{p}<N$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{0,\ldots,N_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, t_{e}\}$.
+\rtron{Introduce $n_p$ in the previous Section.}
+
+In \Cref{sec:??} we assumed that the number of robot is equal to the number of routes $n_p$.
+In this section, we  assume that we have a total of $n>n_p$ robots  available.
+\rtronhl{Clarify: since the robots change teams, this partition is time-varying, or can we get by without defining this partition explicitly?} We define a partition $\cI=\union_p \cI_p$ of the robots such that robots in \emph{sub-team} $\cI_p$ have the same nominal trajectory.
+We use the planner introduced in  \Cref{chapter:Multi-agent-ADMM} to generate multi-robot trajectories with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{0,\ldots,N_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, t_{e}\}$.
+\rtron{Again, make sure notation is consistent}
 Within each sub-team, at least one robot is required to follow the reference trajectory to fulfill the required tasks.
 Meanwhile, the additional robots can switch from one reference trajectory to another in order to perform co-observation with different sub-teams.
-We refer to the new type of co-observations as \emph{cross-trajectory co-observation}s.
-The goal is to find the cross trajectory co-observation plan to secure an unsecured MRS trajectory as with a minimal number of additional robots.
-
-To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$.
+We refer to the new type of co-observations as \emph{cross-trajectory co-observations}.
+The goal is to find the cross trajectory co-observation plan to secure an unsecured MRS trajectory with a minimal number of additional robots.
+
+\rtronhl{This can be summarized more, since it is discussed later in this same page}{To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$.
 Vertices $V_{q}$ are a key locations in $\{q_p\}$ that are used to perform co-observations.
@@
 The cross-trajectory edges $E_{c}$ connect vertices on different reference trajectories, with at least one of the vertices being a checkpoint.
-These edges represent the potential paths that robots can take to travel and perform co-observations between trajectories of different sub-teams.
-Similar to the work done by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.
-
-In this chapter, we present a solution to the cross-trajectory co-observation planning problem.
-This approach consists of two components: constructing the checkpoint graph based on unsecured multi-robot trajectories, which includes the location of security checkpoints and cross-trajectory paths, and the formulation of the network flow problem to solve for the co-observation plan.
+These edges represent the potential paths that robots can take to travel and perform co-observations between trajectories of different sub-teams.} Similar to the work done by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.
+
+This section presents the two components of our approach: constructing the checkpoint graph based on unsecured multi-robot trajectories, and the formulation and solution of the network flow problem.
 
 \subsection{Rapidly-exploring Random Trees}
-In this section, we utilize the \rrtstar{} \cite{karaman2010incremental} algorithm to address the task of determining path feasibility from a single starting location to multiple destination points (reference trajectories of other robots in this application).
-Our objective here is not to optimize specific constraints but to ascertain the existence of feasible paths.
-While the ADMM based solver \ref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
-RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for our specific task.
-
-As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and multiple potential goals.
+In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method).
+\rtronhl{Move to the end of this RRT* section}{Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
+While the ADMM based solver \Cref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
+RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.}
+
+As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree.
 We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
-Key functions from \rrtstar{} that are called by the algorithm in this section are
+Key functions from \rrtstar{} that are also used during constructions of the checkpoint graph are
 \begin{description}
 \item[$\texttt{Cost}(v)$] This function assigns a non-negative cost (total travel distance in our application) to the unique path from the initial position to $v$ . 
-\item[$\texttt{Parent}(v)$] This is a function that maps the vertex $v$ to $v'\in V$ such that $(v',v)\in E$
+\item[$\texttt{Parent}(v)$] This is a function that maps the vertex $v$ to $v'\in V$ such that $(v',v)\in E$.
 \end{description}
@@
 
-In this section, we describe in detail how we define and search for security checkpoints and use the checkpoints to find cross-trajectory edges and construct a directed security graph $G_{q}=(V_{q},E_{q})$.
+In this section, we describe in detail how we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
 
@@
 A checkpoint $v_i=(q_{i},t_{i})$ is a pair composed of a location $q_{i}=q_{p}(t_{i})$ and a time $t_{i}$ representing a co-observation between a sub-team $\cI_p$'s member and robots either from the same sub-team or different ones.
-For convenience, let $\cI_{v_{i}}$ represent the corresponding sub-team $v_{i}$ belongs to.
-
-Similar to the requirements of co-observations introduced in Chapter \ref{chapter:Reachability_Constraints}, checkpoints $V_{p}=\{ v_{p_{1}}, \dots ,v_{p_{e}}\} \subset V_{q}$ for a reference trajectory $\{q_{p}(t)\}$ of sub-team $p$ need to guarantee that the reachability region between consecutive checkpoints $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}})$ does not intersect with any of the forbidden areas.
-For convenience, we denote the union of all forbidden areas as $F$; then the requirement can be written as $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}}) \intersect F = \emptyset$, for every $i$.
-
-We provide a heuristic approach to locate the checkpoints on given trajectories; an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose.
-We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon.
+For convenience, let $\cI_{v_{i}}$ represent the sub-team $v_{i}$ belongs to.
+
+Similar to the requirements of co-observations introduced in  \Cref{chapter:Reachability_Constraints}, \rtronhl{Consider wrapping this in definition environment} {we define checkpoints $V_{p}=\{ v_{p_{1}}, \dots ,v_{p_{e}}\} \subset V_{q}$ for a reference trajectory $\{q_{p}(t)\}$ of sub-team $p$ in a way that guarantees that the reachability region between consecutive checkpoints $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}})$ does not intersect with any of the forbidden areas.}  The requirement can be formally stated as $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$.
+
+We provide a heuristic approach to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose). 
+\rtron{State this as an Algorithm?} We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon.
 Then, we search for the waypoint $q_{p}(t_{1})$ with the largest $t_{1} \in \{t_{0}, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
@@
 Thus, at least one end of the edges must be a security checkpoint $v_{p} \in \union_p V_p$.
-Additionally, assuming that only one robot is sent at a time between trajectories, the cross-trajectory edges must satisfy the reachability constraints from Chapter~\ref{chapter:Reachability_Constraints} to ensure that no deviation to forbidden areas can be performed while switching trajectories.
+Additionally, assuming that only one robot is sent at a time between trajectories, the cross-trajectory edges must satisfy the reachability constraints from~\Cref{chapter:Reachability_Constraints} to ensure that no deviation to forbidden areas can be performed while switching trajectories.
 
@@
 
-To find cross-trajectory edges, we base our approach on RRT*.
-First, we search for feasible paths between each security checkpoint in each reference trajectory and all other trajectories, as shown in Figure \ref{fig:RRT*}.
-Since paths returned by RRT* are optimal and bidirectional, we can analyze the travel time and reachability for each candidate cross-trajectories, and  add these edges to the checkpoint graph if they are feasible.
-
-More vigorously, After a fixed iterations of RRT*, we find all possible and close to optimal paths between one security checkpoint $v_{p}=(q_{p},t_{p}) \in V_{p}$ for sub-team $\cI_p$, and $V_{r} = \{ (q_{{r}_{i}}, t_{{r}_{i}}) \}$ where  $q_{{r}_{i}} = q_{r}(t_{{r}_{i}})$ are the entire waypoints on a reference trajectories for a different sub-team $\cI_{r}$ for a fixed number of RRT* iterations.
+To find cross-trajectory edges, we first find trees of feasible paths using \rrtstar{} and position information alone; we then prune these trees by considering time constraints (that consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints) and ellipsoidal rechability constraints.
+
+We search for feasible paths between each security checkpoint and all other trajectories (ignoring, for the moment, any timing constraint), as shown in \Cref{fig:RRT*} \rtron{Missing figure}. 
+%Paths returned by RRT* are optimal and bidirectional.%, we can analyze the travel time and reachability for each candidate cross-trajectories, and  add these edges to the checkpoint graph if they are feasible.
+More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint $v_{p}=(q_{p},t_{p}) \in V_{p}$ for sub-team $\cI_p$, and $V_{r} = \{ (q_{{r}_{i}}, t_{{r}_{i}}) \}$ where  $q_{{r}_{i}} = q_{r}(t_{{r}_{i}})$ are the entire waypoints on a reference trajectories for a different sub-team $\cI_{r}$.
 We can calculate the minimal travel time $t=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path.

### 2023-09-13 paper.tex
update

@@
   The ellipse parameters $a$,$b$ represent the lengths of the major axes.
+  And the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
+   \begin{equation}
+     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
+     \end{equation}
 \end{definition}
@@
 \subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
+\zyang{change this to a circle by adding radius to projection?}
 As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
@@
 And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse.
-
-  \zyang{can this be treated as proposition}
-  \begin{proposition} \label{prop:ellipse-project-canonical}
-  In canonical frame $\cF_{\cE}$, the projection from a point $q^{\cE}_{avoid}\in \cE$ inside the ellipse to the boundary of $\cE$:
+In canonical frame $\cF_{\cE}$, the projected point $q^{\cE}_{p}$ can be written as:
   \begin{equation}
@@
   %where $S=(I+sQ)\inverse$.Using the fact that since $q^\cE_p$ is a point on the ellipse, 
-  where $s$ can be solved as the root of the equation obtained by substituting \eqref{eq:qp from S} in $\Eframe E(\Eframe q)$:
-  \begin{equation}
-    0=F(s)={q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1,
+  where $s$ can be solved as the root of the \eqref{equ:standard-ellipse}:
+  \begin{equation}
+    {q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1=0
   \end{equation}
@@
   \end{equation}
- Detailed methods for computing $s$ can be found in \cite{eberly}. 
-  \end{proposition}
-  \begin{proof}
-  Proof can be found in Appendix~\Cref{proof:ellipse-project-canonical}
-  \end{proof}
-
-  \subsubsection{Projection to the standard ellipse}\rtron{Move to the appendix or refer to the conference paper}
-  % Using the transformation defined in Section~\ref{sec:rotation2Standard}, the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
-  % \begin{equation}
-  %   \Fframe{E}(\Fframe{x}) = (\Fframe{x}-o_\cE)\transpose H\transpose Q H (\Fframe{x}-o_\cE) - 1
-  % \end{equation}
+ Detailed methods for computing $s$ can be found in \cite{yang2021multi} \cite{yang2020multi} \cite{eberly}.
 
@@
   \end{proposition}
+  \begin{proof}
+  See \Cref{proof:Ellipse2PointDiff}.
+  \end{proof}
   The differential of $D_p$ is the same as the one for $\pi_{p\cE}$.
@@
 \begin{center}
-\includegraphics[width=0.6\linewidth]{Ellipse2line_V2}
+\includegraphics[width=0.6\linewidth, trim = 0cm 1.5cm 0cm 1cm, clip]{Ellipse2line_V2}
 \caption{Plane-ellipse constraint.
@@
 
-For a intermediate step to get the relationship between a polygon shaped forbidden region, we first consider a forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
+For forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
 The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-  Using the transformation introduced in (\ref{sec:rotation2Standard}), the ellipse can be transferred into a standard one with the new hyperplane in the form of $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
-  \begin{equation}
-    n_\cE = H(q_1,q_2)n
-\end{equation}
-\begin{equation} 
-	d_\cE =-\vn\transpose o + d
-  \end{equation}
-\subsubsection{Projection via the tangent interpolation point}
-  For each $\cL_\cE$, there exist two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse, where
-  \begin{equation}
-    d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}.
-  \end{equation}
-  The corresponding tangent points are given as 
-  \begin{equation}
-    p^\cE_{1} = \frac{  d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},
-  \end{equation}
-  \begin{equation}
-   p^\cE_{2} = -  p^\cE_{1}.
-  \end{equation}
-  \rtron{Refer to figure}
-  We use these two tangent points to define a novel measure of displacement between a plane and an ellipse.
-  \begin{definition}
-    The \emph{tangent interpolation point} is defined as 
-    \begin{equation}\label{equ:ProjectPoint}
-      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}
-    \end{equation}
-  \end{definition}
-  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively. 
-  % it is easy to see that $\Eframe p_{\cL} \in \mathcal{L}$, and $p_{\mathcal{L}}$ can be used to indicate the relationship between the $\mathcal{L}$ and $\mathcal{E}$, which is shown below.
-\zyang{how to emphaise this?
-maybe a graph here?}
-  %The reason such that a specific point is used is for the convenience of evaluating ellipse-plane-segment relationship in Section~\ref{chapter:ellipse to segment}.
-  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
-Using this fact, we define the following projection operator:
+When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
+  \begin{equation}
+    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d
+\end{equation}
+The corresponding constraint can be written as:
+
+\begin{constraint}[Plane-ellipsoid reachability constraint]
+\begin{align}
+D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
+  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \},\\
+   \Pi_\sZ(z) & = \overrightarrow{0}, 
+\end{align}
+\end{constraint}
+where $\pi^\cE_{\vn \cE}(q)$ is the projection operator defined as:
   \begin{equation}\label{equ:plane2ellipse}
@@
   \end{equation}
-  \subsubsection{ADMM constraints}
-  Transforming the projection $\pi^\cE$ back to $\cF$ we have:
-  \begin{equation}\label{equ:constraint plane to ellipse}
-    D_{\vn}(q)= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o,
-  \end{equation}
-  with the corresponding constraint written as
-  \begin{equation}
-    \zeta_\vn = \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \}
-  \end{equation}
-  \begin{equation}
-   \quad\Pi_\vn(D_{\vn}(q)) = {0}
-  \end{equation}
-
-  \subsubsection{Gradients for the projection function}
-  \begin{proposition}\label{prop:dpi_ne dt}
-    The differential of the projection function $\Eframe \Pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
+$p^{\cE}_{1}$ and $p^{\cE}_{2}$ are tangent points on two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse (\Cref{fig:Ellipse-to-plane}), defined as
+ \begin{equation}
+    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
+  \end{equation}
+where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$. And the \emph{tangent interpolation point} is defined as 
+    \begin{equation}\label{equ:ProjectPoint}
+      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}.
+    \end{equation}
+  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.
+
+  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
+
+  \begin{proposition}\label{prop:dpi_ne_dt}
+    The differential of the projection function $\Eframe \pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
     \begin{equation}
@@
   \end{proposition}
-  Based on the previous proposition, the differential of (\ref{equ:constraint plane to ellipse}) can be written as:
+  \begin{proof}
+  See \Cref{proof:dpi_ne_dt}.
+  \end{proof}
+  Based on the previous proposition, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
   \begin{equation}
@@
 
-To avoid (or stay in) a region defined by several hyperplanes, the relative position between the ellipse and segment of the hyperplane needs to be studied instead of the whole plane.
+For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied.
 Assume the segment has endpoints $p_1$ and $p_2$, the segment can be defined as:
@@
 
-To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams \rtronref{refer to introductory figure}.
+To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams \rtron{refer to introductory figure}.
 These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
 Note that \emph{cross-trajectory co-observation}, are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
-\rtronref{(More discussion in Sec.
+\rtron{(More discussion in Sec.
 ??)}.
@@
 In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method).
-\rtronhl{Move to the end of this RRT* section}{Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
+\rtronhl{Move to the end of this RRT* section} Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
 While the ADMM based solver \Cref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
-RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.}
+RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
 
@@
 
-  \subsection{Proof of proposition \ref{prop:dpi_ne dt}}\label{proof:dpi_ne dt}
+  \subsection{Proof of proposition \ref{prop:dpi_ne_dt}}\label{proof:dpi_ne_dt}
     We first need to derive $\dot{d}_\cE$ and $\dot{d}_{\cE t}$
@@
 \bibliographystyle{unsrt}
-\bibliography{ADMM_planning,ACC}
+\bibliography{ADMM_planning,ACC,tron,ziqi}
 }

### 2023-09-14 paper.tex
update

@@
 \begin{definition}\label{def:Reachability}
-	The \emph{reachability ellipsoid} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{maq}}{2}(t_2-t_1)$.
+	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{maq}}{2}(t_2-t_1)$.
 \end{definition}
@@
 To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$. 
-In this new frame, the ellipsoid's center aligns with the origin, and its foci align with the first axis of $\cF_\cE$.
-We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
-
-For the convenience of derivation, we define the coordinate transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we simply refer to as $R$ and $o$, respectively.
-The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the formulation:
-  \begin{equation}
+\rtronhl{Make this sentence as "The canonical frame $\cF_\cE$ is defined as..."}{In this new frame, the ellipsoid's center aligns with the origin, and its foci align with the first axis of $\cF_\cE$.} We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
+We parametrize the transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we refer to as $R$ and $o$, respectively. 
+The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the rigid body transformations:
+  \begin{equation}\label{eq:transformations}
     \Fframe{q}=R\Eframe{q}+o,\label{eq:E to F transform}\quad
@@
 Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$.
-We then define the rotation $R$ using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} we see that $o$ represents the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
+From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
   \begin{align} 
@@
   \end{align}
-  In the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
+  To simplify notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
   The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
@@
 \begin{definition}
-  The ellipsoid $\cE$ in the canonical frame can be described as the zero level set of the quadratic function
+  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
   \begin{equation}\label{equ:standard-ellipse}
@@
   and $b = \sqrt{a^2-c^2}$.
-  The ellipse parameters $a$,$b$ represent the lengths of the major axes.
-  And the original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
-   \begin{equation}
+  The ellipse parameters $a$, $b$ represent the lengths of the major axes.
+\end{definition}
+\begin{lemma}
+The original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
+   \begin{equation}\label{eq:ellpsoid from canonical}
      \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
      \end{equation}
-\end{definition}
-
-For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the defined transformation function.
+\end{lemma}
+\begin{proof}
+    The claim follows by substituting  \eqref{eq:transformations} into \eqref{equ:standard-ellipse}, and from the definition of $R$ and $o$.
+\end{proof}
+For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the transformation \eqref{eq:transformations}.
 
@@
 \includegraphics[width=0.6\linewidth, trim = 0cm 1.5cm 0cm 1cm, clip]{Ellipse2line_V2}
+\rtron{Add $d_{\cE t}$}
 \caption{Plane-ellipse constraint.
@@
   \begin{equation}
-    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d
-\end{equation}
-The corresponding constraint can be written as:
+    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d.
+\end{equation}
+Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$.
+
+\rtron{Move the definition of tangents, tangent points, and tangent interpolation point here}
+
+With these definitions, the constraint can be written as:
 
@@
 \begin{align}
-D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn \cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
+D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn_\cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
   \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \},\\
@@
 \end{constraint}
-where $\pi^\cE_{\vn \cE}(q)$ is the projection operator defined as:
+\rtron{Check that $q$ is $\vq$ where necessary. Also sometimes you use $q(t_1),q(t_2)$ and sometimes $q_1,q_2$, check for consistency.}
+where $\pi^\cE_{\vn_\cE}(q)$ is the projection operator defined as:
   \begin{equation}\label{equ:plane2ellipse}
-    \pi^\cE_{\vn \cE}(q) =\begin{cases}
-      p^\cE_{t1}-p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
-      p^\cE_{t2}-p^\cE_{\cL} &  d_\cE \in [- d_{\cE t},0), \\
+    \pi^\cE_{\vn_\cE}(q) =\begin{cases}
+      p^\cE_{1}-p^\cE_{\cL} & \textrm{ if } d_\cE \in [0, d_{\cE t}], \\
+      p^\cE_{2}-p^\cE_{\cL} &  \textrm{ if } d_\cE \in [- d_{\cE t},0), \\
       {0} & \textrm{otherwise}.
@@
   \end{equation}
-$p^{\cE}_{1}$ and $p^{\cE}_{2}$ are tangent points on two planes $\Eframe \cL_{1} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\Eframe \cL_{2} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$ that are parallel to $\cL$ and tangent to the ellipse (\Cref{fig:Ellipse-to-plane}), defined as
+$p^\cE_1$ and $p^\cE_2$ are tangent points on two planes that are parallel to $\cL$ and tangent to the ellipse, $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
+Analytically, these points can be found as
  \begin{equation}
@@
   \end{equation}
-where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$. And the \emph{tangent interpolation point} is defined as 
+where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent planes $\cL_1^\cE$, $\cL_2^\cE$ and the origin (i.e., the center of the ellipse $\cE$).
+The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
     \begin{equation}\label{equ:ProjectPoint}
@@
     \end{equation}
-  Note that $p^\cE_{\cL} \in \mathcal{L}$ and when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.
-
-  It is clear that when $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
+  Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
+  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.
+When $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
 
   \begin{proposition}\label{prop:dpi_ne_dt}
-    The differential of the projection function $\Eframe \pi_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
+    The differential of the projection function $\pi^\cE_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
     \begin{equation}
@@
 For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
-Assume the segment has endpoints $p_1$ and $p_2$, the segment can be defined as:
+Assume the segment has endpoints $p_1$ and $p_2$; then the segment can be defined as:
 \begin{equation}
@@
 \end{equation}
-And using the $p_{\cL}$ defined in (\ref{equ:ProjectPoint}), we define
-\begin{equation}
-D_{seg}(q) = \begin{cases}
+\rtron{Needs an additiona constraint that $p$ needs to be on the line $p_1p_2$.}
+\begin{constraint}[Line-segment-ellipsoid reachability constraint]
+\begin{align}
+D(\vq) &=  \begin{cases}
 D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
 D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
-D_2(p_{\cL}) & otherwise
-\end{cases}
-\end{equation}
-where $D_{p\cE}$ and $D_{\vn\cE}$ are corresponding constraint function introduced in section \ref{sec:ellipsoid-point} and \ref{sec:ellipsoide-plane}
-with the constraint set and projection written as:
-\begin{equation}
-\zeta_{seg} = \{q\in\mathbb{R}^{nm}:\norm{D_{seg}(q)} = 0 \}
-\end{equation}
-\begin{equation}
-\Pi_{seg}(D_{seg}(q)) = {0}
-\end{equation}
+D_2(p_{\cL}) & \textrm{otherwise}
+\end{cases} \label{eq:segment_ellipsoid_constraint}\\
+  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
+   \Pi_\sZ(z) & = 0, 
+\end{align}
+\end{constraint}
+
+\rtron{Define $D_1$, $D_2$. Give intuition about what they represent.}
 \subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
-To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse.
-And a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) is also added to prevent cases where the ellipse is a subset of the region.
-Similar to \eqref{equ:ProjectPoint}, we define
-\begin{equation}
-D_{cp}(q) = \bmat{D_{seg1}\\D_{seg2}\\ \vdots}
-\end{equation}
-with the constraint set and projection written as:
-\begin{equation}
-\zeta_{cp} = \{q\in\mathbb{R}^{nm}:\norm{D_{cp}(q)} = 0 \}
-\end{equation}
-\begin{equation}
-\Pi_{cp}(D_{cp}(q)) = {0}
-\end{equation}
+To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse. Similar to \eqref{equ:ProjectPoint}, we define
+\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
+\begin{align}
+D(\vq) &= \bmat{D_{seg1}\\D_{seg2}\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
+  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
+   \Pi_\sZ(z) & = 0, 
+\end{align}
+\end{constraint}
+\rtron{$D_{seg1}, D_{seg2}$ need to be defined.}
+ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) to prevent cases where the ellipse is a subset of the region.
 
@@
 stationary security camera) need to be incorporated in order to generated an attack-proof solution.
-Additional solutions to avoid these checkpoints will be discussed in Chapter \ref{chapter:cross-trajectory}.
+Additional solutions to avoid these checkpoints will be discussed in \Cref{chapter:cross-trajectory}.
 

### 2023-09-21 paper.tex
update

@@
 However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
-To deal with this problem, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy):
+To allow for a easier projection step, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ :
 \begin{equation}\label{eq:ADMMSetConstraint_modified}
@@
 \end{subequations}
-where $\Pi_\mathcal{Z}$ is the new projection to the modified constraint set $\mathcal{Z}$ \rtron{It is not clear where $\cZ$ comes from}, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
+where $\Pi_\mathcal{Z}$ is the new projection to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
 \begin{equation}\label{eq:primal-residual}
@@
 \begin{equation}\label{eq:dual-residual}
-	\vs^{k}=-\rho(z^{k}-z^{k-1}),
+	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1}),
 \end{equation}
@@
 
-We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for traditional path planning constraints (\Cref{sec:velocity-constraint}-\Cref{sec:waypoint-constraint}), co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:??}).
-The latter are based on the definition of \emph{ellipsoidal reacability regions} (\Cref{sec:reachability}).
+We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for traditional path planning constraints (\Cref{sec:velocity-constraint}-\Cref{sec:waypoint-constraint}), co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:ellipsoid-point}-\Cref{eq:region_ellipsoid_constraint}).
+The latter are based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
+
 \subsection{Velocity constraints}\label{sec:velocity-constraint}
@@
 \label{eq:velocity_constraint}
-   \sZ_{ij} &=\bigl\{z \mid \norm{z} \leq v_{max}\bigr\}\\
-   \Pi_{\sZ_{ij}}(z)&=\begin{cases}
-   v_{\max}\frac{z}{\norm{z}} \textrm{ if } \norm{z}>v_{\max}\\
-   z\textrm{ otherwise}
+   \sZ_{ij} &=\bigl\{\vz \mid \norm{\vz} \leq v_{max}\bigr\}\\
+   \Pi_{\sZ_{ij}}(\vz)&=\begin{cases}
+   v_{\max}\frac{\vz}{\norm{\vz}} \textrm{ if } \norm{\vz}>v_{\max}\\
+   \vz\textrm{ otherwise}
    \end{cases}
@@
 \subsection{Waypoints with flexible deadlines}\label{sec:waypoint-constraint}
-It is common for security related constraints to require robot reach a specific location at specific time.
-We assume robot $i$ is required to reach a given point $p$ within a radius of $d_{max}$ at some time instant $j$ belonging to a given time window $[t_1,t_2]$.
-The constraint function $D(\vq)$ to return the smallest distance from the point $p$ to waypoint on the trajectory restricted to the relevant time window.
+Security-related constraints often necessitate that a robot reaches a specified location at a particular time.
+We assume robot $i$ is tasked with reaching a given point $p$ within a radius of $d_{max}$ at some time instant $j$ within a predefined time window $[t_1,t_2]$.
+We defined a constraint this constraint as follow.
+
 \begin{constraint}[Waypoint constraint]
@@
 \subsection{Co-observation schedule constraint}\label{sec:co-observation-constraint}
-The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
+The co-observation constraint ensures that two robots come into close proximity at scheduled times to observe each other's behavior.
+This constraint is represented as a relative distance requirement between the two robots at a specific time instant, ensuring they are within a defined radius to inspect each other or exchange data.
+Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \Cref{sec:reachability}, do not intersect with any forbidden regions.
+
+%The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
 This constraint is modeled as a relative distance constraint between two robots at some time instant $j$ (i.e., to require two agents see each other within a certain radius to inspect each other, or to exchange data).
-The location of the co-observation location should make sure that the ellipsoidal reachability region between each co-observation, considered in later sections \ref{sec:reachability}, has an empty intersection with all forbidden regions.
+The location of the co-observation should make sure that the ellipsoidal reachability region between each co-observation, considered in later sections \ref{sec:reachability}, has an empty intersection with all forbidden regions.
+
  We write the function for the constraint as:
@@
 D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:waypoint_constraint}\\
-  \sZ &= \{z \mid z \leq d_{max} \},\\
+  \sZ &= \{\vz \mid \norm{\vz} \leq d_{max} \},\\
    \Pi_\sZ(z) & = \begin{cases}
-d_{max}\frac{z}{\norm{z}} &\text{if } \norm{z} > d_{max},\\
-z	& otherwise.
+d_{max}\frac{\vz}{\norm{\vz}} &\text{if } \norm{\vz} > d_{max},\\
+\vz	& otherwise.
 \end{cases}
@@
 To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$. 
-\rtronhl{Make this sentence as "The canonical frame $\cF_\cE$ is defined as..."}{In this new frame, the ellipsoid's center aligns with the origin, and its foci align with the first axis of $\cF_\cE$.} We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
+The canonical frame $\cF_\cE$ is defined as the origin aligns with the ellipsoid's center, and the first axis aligns with the foci.
+We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
 We parametrize the transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we refer to as $R$ and $o$, respectively. 
@@
   \begin{equation}\label{eq:transformations}
-    \Fframe{q}=R\Eframe{q}+o,\label{eq:E to F transform}\quad
+    \Fframe{q}=R\Eframe{q}+o,\quad
     \Eframe{q}=R\transpose(\Fframe{q}-o).
@@
 Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$.
-From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation}, while from \eqref{eq:E to F transform} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
+From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation}, while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
   \begin{align} 
@@
 \end{equation}
-Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$.
-
+Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
+For every $\Eframe \cL(\tilde{q})$, there always exist two planes that are parallel to $\cL$ and tangent to the ellipse, $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
 \rtron{Move the definition of tangents, tangent points, and tangent interpolation point here}

### 2023-09-21 paper.tex
Updates from Overleaf

@@
 Meanwhile, the additional robots can switch from one reference trajectory to another in order to perform co-observation with different sub-teams.
+\rtron{$\star$}\rtron{Give a little more details about how cross-trajectory co-observations are defined to ensure safety.}
 We refer to the new type of co-observations as \emph{cross-trajectory co-observations}.
@@
 In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method).
-\rtronhl{Move to the end of this RRT* section} Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
+\rtronhl{Move to the end of this RRT* section}{Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
 While the ADMM based solver \Cref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
-RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
+RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.}
 
@@
 More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint $v_{p}=(q_{p},t_{p}) \in V_{p}$ for sub-team $\cI_p$, and $V_{r} = \{ (q_{{r}_{i}}, t_{{r}_{i}}) \}$ where  $q_{{r}_{i}} = q_{r}(t_{{r}_{i}})$ are the entire waypoints on a reference trajectories for a different sub-team $\cI_{r}$.
-We can calculate the minimal travel time $t=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path.
-We call all nodes $v_{{r}_{i}} \in V_{r}$ \emph{arrival node}s if there exist a path between $v_{{r}_{i}}$ and $v_{p}$ with $t_{p}+t<t_{{r}_{i}}$, and the reachability ellipsoid $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.
-Similarly, \emph{departure node}s are defined for $v_{{r}_{i}}$ with $t_{p}>t_{{r}_{i}}+t$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
+We can calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path.
+
+\rtron{Combine the definitions of arrival and earliest arrival, and of departure and latest departure}
+
+\begin{description}
+\item We call a node $v_{{r}_{i}} \in V_{r}$ an \emph{arrival node} if \rrtstar{} found a path from $v_p$ to  $v_{{r}_{i}}$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and the reachability ellipsoid associated with the path endpoints does not intersect the forbidden region, $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$ \rtron{Consolidate the notation $q_r(t_{r_i}), q_{r_i}, v_{r_i}$}.[Latest departure node $q_{r}(t^{d}_r)$] is the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
+\item
+ Similarly, a node $v_{r_i}\in\cV_r$ is a \emph{departure node} for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
 Given a point $v_{p} \in V_{p}$, we define the \emph{latest departure node} $q_{r}(t^{d}_r)$, and the \emph{earliest arrival node} $q_{r}(t^{a}_r)$ as follows:
-
-\begin{description}
-\item[Latest departure node $q_{r}(t^{d}_r)$]: is the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
-\item[Earliest arrival node $q_{r}(t^{a}_r)$]: is waypoint with the earliest time $t^{a}_r$ such that a robot from sub-team $\cI_p$ deviating from $v_{p}$ can meet with sub-team $\cI_r$.
+[Earliest arrival node $q_{r}(t^{a}_r)$] is waypoint with the earliest time $t^{a}_r$ such that a robot from sub-team $\cI_p$ deviating from $v_{p}$ can meet with sub-team $\cI_r$.
 \end{description}
 
-For $v_{p} \in V_{p}$, latest departure node $v_{d}=(q_{r}(t^{d}_r),t^{d}_r)$ and earliest arrival node $v_{a}= (q_{r}(t^{a}_r),t^{a}_r)$, if feasible, are added to $V_{q}$.
-Cross-trajectory edges $(v_{p} \to v_{a})$ and $(v_{d} \to v_{p})$ are added to $E_{q}$.
-Examples are shown in Figure \ref{fig:two-edges}.
-Full algorithm is shown in Algorithm \ref{alg:cross-trajectory-edges}.
+For each $v_{p} \in V_{p}$, we add all the latest departure and earliest arrival nodes to $V_{q}$, and their corresponding paths as cross-trajectory edges $E_{q}$.
+Examples are shown in Figure \ref{fig:two-edges}, while the full algorithm is shown in Algorithm \ref{alg:cross-trajectory-edges}.
 
@@
 %With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-All checkpoints $V_{q}$ found in Section~\ref{sec:security-checkpoint} and \ref{sec:cross-traj-edges}, can be divided by the corresponding sub-team and sorted in ascending order of time into $N_{p}$ subsets $V_{p}=\{v^{p}_{0}, v^{p}_{1}, \dots , v^{p}_{T}\}$ where $p\in \{1,\dots, N_{p}\}$.
-Consecutive edges in the same subset are added to $E_{q}$ as in-trajectory edges $(v^{p}_{i}\rightarrow v^{p}_{i+1} )$.
-Example are shown in Figure \ref{fig:security-graph-generate}.
+We add to $E_q$ the \emph{in-trajectory edges} $(v^{p}_{i}\rightarrow v^{p}_{i+1})$ obtained by connecting all checkpoints $v^p_{i}\in V_q$ found in Section~\ref{sec:security-checkpoint} with the checkpoints $v^p_{i+1}$ that  follow them in their original trajectories.
+%For all  and \ref{sec:cross-traj-edges}, can be divided by the corresponding sub-team and sorted in ascending order of time into $N_{p}$ subsets $V_{p}=\{v^{p}_{0}, v^{p}_{1}, \dots , v^{p}_{T}\}$ where $p\in \{1,\dots, N_{p}\}$.
+Consecutive edges in the same subset are added to $E_{q}$ as  .
+Examples are shown in Figure \ref{fig:security-graph-generate}.
 \begin{figure}[htbp]
@@
 In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network flow problem, and solve it using mixed-integer linear programs (MILP).
-We assume that there are always \emph{reference robot}s in each sub-team following the reference trajectory.
-We want to plan the routes for additional \emph{cross-trajectory robots} to perform co-observation with the reference robots.
-
-To formulate the planning problem as a network multi flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
-The vertices of the new graph are defined as $V= V_{q} \union \{v^{+},v^{-}\}$,  a \emph{virtual source} $v^{+}$ and a \emph{virtual sink} node $v^{-}$ are added to $V$.
-The edges of the new graph are defined as $ E = E_{q} \union \{( v^{e}_{p},v_{-})\}_{p} \union \{(v_{+},v^{0}_{p})\}_{p}$, where directed edges are added to $E$ from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^e_p$ representing the start and end vertices of sub-team $\cI_p$.
-
-Assume that all the robots starting from the virtual source $v^{+}$ and end in the virtual sink $v^{-}$.
-Each robot may move from vertex $v_{i}$ to $v_{j}$ if $(v_{i},v_{j})\in E_{q}$.
-The path of a robot $k$ can be represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $(v_{i},v_{j})$.
-As required by the security guarantee, reference robots must be seen by at least one surveillance robot at every checkpoint.
+We assume that $n_p$ \emph{reference robots} are dedicated (one in each sub-team) to follow the reference trajectory.
+The goal of this section is to minimize the number and plan the routes of $n-n_p$  additional \emph{cross-trajectory robots} dedicated to perform co-observations with the reference robots.
+
+\begin{remark}
+\rtron{Note that we assign fixed roles to reference robots for convenience in explaining the multiflow formulation.
+In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation.}
+\end{remark}
+
+To formulate the planning problem as a network multi-flow problem \rtron{Check that multiflow/multi-flow/flow problem is indicated consistently across the entire paper}, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
+The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is a \emph{virtual source} node, and $v^{-}$ is a \emph{virtual sink} node.
+The edges of the new graph are defined as $E = E_{q} \union \{( v^{e}_{p},v_{-})\}_{p} \union \{(v_{+},v^{0}_{p})\}_{p}$, i.e., we add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^e_p$ representing the start and end vertices of sub-team $\cI_p$.
+
+Our goal is then to find a path in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
+%,  Each robot then may move according to the edges in $G$ from vertex $v_{i}$ to $v_{j}$ if $(v_{i},v_{j})\in E_{q}$. 
+The path of a robot $k$ can be represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
+\rtronhl{Spell out this requirement at the beginning of the section (around $\star$, and reference it here}{As required by the security guarantee, reference robots must be seen by at least one cross-reference robot at every checkpoint.}
 Thus, the planning problem can then be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $V_{p}$ is included in at least one path in $F$.
-Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations are preferred compared to co-observation within the same team.
-This is achieved with the weights for edges $(v_{i},v_{j})\in E$ defined as:
+Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
+\rtron{Finally, edges from the virtual source and to the virtual sink should have zero cost, to allow robots to automatically get assigned to the starting point that is most convenient for the overall solution.}
+These requirements are achieved with the weights for edges $(v_{i},v_{j})\in E$ defined as:
 \begin{equation}
@@
 
-With the formulation above, the planning problem can be written as an optimization problem, where we want to balance between the co-observation performance and total number of flows (cross-trajectory robots) needed.
-For convenience, we use $(ij)$ to represent the edge $(v_{i},v_{j})$, and $(+i)$ to represent the edge $(v^{+},v_{i})$.
-
+With the formulation above, the planning problem can be written as an optimization problem, where the optimization cost balances between the co-observation performance and total number of flows (cross-trajectory robots) needed:
  \begin{subequations} \label{eq:flow-coverage-problem}
@@
  \end{subequations}
-
-The first term in \ref{eq:flow-cost} is total outgoing flow from the source $v^{+}$ while the second term is the total cost of all flows which represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges).
-The constant $\rho$ is a penalty parameter manually elected to balance between two terms in the cost function.
+where, for convenience, we used $(ij)$ to represent the edge $(v_{i},v_{j})$, and $(+i)$ to represent the edge $(v^{+},v_{i})$.
+
+The first term in \ref{eq:flow-cost} is total outgoing flow from the source $v^{+}$ while the second term is the total cost of all flows representing the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges).
+The constant $\rho$ is a manually selected penalty parameter to balance between two terms in the cost function.
 The constraint \eqref{eq:FlowBalanceConstraint} is the flow conservation constraint, which ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).

### 2023-09-25 paper.tex
update

--- 2023-09-21 paper.tex
@@
 \begin{center}
-\includegraphics[width=0.6\linewidth, trim = 1.5cm 2.5cm 1.5cm 3cm, clip]{Ellipse2point}
+\includegraphics[width=0.6\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}
 \caption{Point-ellipsoid constraint, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$.}
@@
 \begin{center}
-\includegraphics[width=0.6\linewidth, trim = 0cm 1.5cm 0cm 1cm, clip]{Ellipse2line_V2}
-\rtron{Add $d_{\cE t}$}
+\includegraphics[width=0.6\linewidth, trim = 0.3cm 1cm 0.3cm 1cm, clip]{Ellipse2line_V2}
 \caption{Plane-ellipse constraint.
@@
 Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
-For every $\Eframe \cL(\tilde{q})$, there always exist two planes that are parallel to $\cL$ and tangent to the ellipse, $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
-\rtron{Move the definition of tangents, tangent points, and tangent interpolation point here}
+
+For every $\Eframe \cL(\tilde{q})$, there always exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e.
+resulting in a unique intersection point), $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
+And the intersection point can be written as:
+\begin{equation}
+    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
+\end{equation}
+where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent planes $\cL_1^\cE$, $\cL_2^\cE$ and the origin (i.e., the center of the ellipse $\cE$).
+
+We introduce the concept of a tangent interpolation point on the hyperplane to characterize the relationship between the plane and the ellipse.
+
+\begin{definition}
+The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
+    \begin{equation}\label{equ:ProjectPoint}
+      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}.
+    \end{equation}
+  Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
+  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.
+When $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
+\end{definition}
 
@@
 \begin{align}
-D(\vq) &= H^{-1}(q(t_1),q(t_2))\pi^\cE_{\vn_\cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
-  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_{\vn}(q)} = 0 \},\\
+D(\vq) &= H^{-1}(q_{1},q_2)\pi^\cE_{\vn_\cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{\vn}(\vq)} = 0 \},\\
    \Pi_\sZ(z) & = \overrightarrow{0}, 
@@
 \end{constraint}
-\rtron{Check that $q$ is $\vq$ where necessary. Also sometimes you use $q(t_1),q(t_2)$ and sometimes $q_1,q_2$, check for consistency.}
 where $\pi^\cE_{\vn_\cE}(q)$ is the projection operator defined as:
@@
   \end{equation}
-$p^\cE_1$ and $p^\cE_2$ are tangent points on two planes that are parallel to $\cL$ and tangent to the ellipse, $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
-Analytically, these points can be found as
- \begin{equation}
-    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
-  \end{equation}
-where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent planes $\cL_1^\cE$, $\cL_2^\cE$ and the origin (i.e., the center of the ellipse $\cE$).
-The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
-    \begin{equation}\label{equ:ProjectPoint}
-      p^\cE_{\cL} = \frac{ d_\cE Q^{-1} n_\cE}{ n_\cE\transpose Q^{-1} n_\cE}.
-    \end{equation}
-  Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
-  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.
-When $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
 

### 2023-09-25 paper.tex
update

@@
 
-For forbidden region in the shape of a hyperplane $\mathcal{L}(\tilde{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
+For forbidden region in the shape of a hyperplane $\mathcal{L}(\Eframe{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
 The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
@@
   \end{proof}
-  Based on the previous proposition, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
+  Based on the \Cref{prop:dpi_ne_dt}, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
   \begin{equation}
@@
 For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
-Assume the segment has endpoints $p_1$ and $p_2$; then the segment can be defined as:
-\begin{equation}
-\bmat{(p_1-p_2)\transpose\\(p_2-p_1)\transpose} p \leq \bmat{p_2\transpose\\-p_1\transpose}(p_1-p_2)
+Assume the segment on hyperplane $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$ has endpoints $p_1$ and $p_2$; then the segment can be defined as:
+\begin{equation}
+\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), 
 \end{equation}

### 2023-10-16 paper.tex
update

@@
 This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
-These challenges are addressed in Chapter \ref{chapter:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
+These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
 
@@
 Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
-In this paper, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in Chapter \ref{chapter:task-assignment}), making it more difficult for attackers to successfully plan and execute attacks.
+In this paper, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in later works, making it more difficult for attackers to successfully plan and execute attacks.
 Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
@@
 
-\section{Multi-robot trajectory planning with co-observation}
+\section{Multi-robot trajectory planning with co-observation}\label{sec:ADMM-planning}
 
@@
 We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space.
-For a team of $n$ agents, and a task time horizon of $T$, the overall trajectory of the multi-agent system can be represented as an aggregated vector $\vq\in \real{n m T}$.
+For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$.
 The goal of our path planning problem is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$.
@@
 Subsequently, our solver allows us to seamlessly integrate security constraints, encompassing co-observation schedule and reachability constraints.
-Concluding this section, we present the obtained results alongside limitations (due to infeasibility) that are addressed in \Cref{sec:??}.
+Concluding this section, we present the obtained results alongside limitations (due to infeasibility) that are addressed in \Cref{sec:cross-trajectory}.
 
@@
  \subsubsection{Householder rotations}\label{sec:householder}
- In the derivation of the reachability constraint in \Cref{sec:??}, we need to define a differentiable transformation to a canonical form.
+ In the derivation of the reachability constraint in \Cref{sec:reachability,sec:ellipse-region-constraint}, we need to define a differentiable transformation to a canonical form.
 This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
@@
 \subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
-The basic idea behind our ADMM-based solver \cite{zyang} is to split the constraints from the objective function using a different set of variables $\vz$, and then solve an Augmented Lagrangian formulation of the optimization problem in \eqref{eq:general-problem}.
+The basic idea behind our ADMM-based solver \cite{yang2020multi} is to split the constraints from the objective function using a different set of variables $\vz$, and then solve an Augmented Lagrangian formulation of the optimization problem in \eqref{eq:general-problem}.
 More specifically, we can rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function.
@@
 \begin{align}
-D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:waypoint_constraint}\\
+D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:coobservation_constraint}\\
   \sZ &= \{\vz \mid \norm{\vz} \leq d_{max} \},\\
@@
 D(\vq) &=  \begin{cases}
-      \pi_{p\cE}(q) - q_{avoid} & q_{avoid} \in \cE, \\
+      \pi_{p\cE}(\vq) - q_{avoid} & q_{avoid} \in \cE, \\
       {0} & \textrm{otherwise}.
     \end{cases} \label{eq:point_ellipsoid_constraint}\\
-  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
-   \Pi_\sZ(z) & = 0, 
+  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(\vq)} = 0 \},\\
+   \Pi_\sZ(\vz) & = 0, 
 \end{align}
@@
 
-For forbidden region in the shape of a hyperplane $\mathcal{L}(\Eframe{q}) = \{\tilde{q}\in\mathbb{R}^n: \vn\transpose \tilde{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
+For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^n: \vn\transpose \Fframe{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
 The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$, where,
-  \begin{equation}
-    n_\cE = H(q_1,q_2)n, \quad d_\cE =-\vn\transpose o + d.
+When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, where,
+  \begin{equation}
+    \vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d.
 \end{equation}
@@
 
-For every $\Eframe \cL(\tilde{q})$, there always exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e.
-resulting in a unique intersection point), $\cL_1^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\tilde{q}\in\mathbb{R}^m: \vn_\cE \transpose \tilde{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
+For every $\Eframe \cL(\Eframe{q})$, there always exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e.
+resulting in a unique intersection point), $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
 And the intersection point can be written as:
 \begin{equation}
-    p^\cE_{1} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{2} = -  p^\cE_{1},
-\end{equation}
-where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent planes $\cL_1^\cE$, $\cL_2^\cE$ and the origin (i.e., the center of the ellipse $\cE$).
+    p^\cE_{t_{1}} = \frac{ d_{\cE t} Q^{-1}   n_\cE}{ n_\cE \transpose Q^{-1}  n_\cE} = \frac{Q^{-1} n_\cE}{ d_{\cE t}},\quad  p^\cE_{t_{2}} = -  p^\cE_{t_{1}},
+\end{equation}
+where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$).
 
@@
   Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
-  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{1}$ or $p^\cE_{\cL}=p^\cE_{2}$, respectively.
+  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{t_1}$ or $p^\cE_{\cL}=p^\cE_{t_2}$, respectively.
 When $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
@@
 \begin{align}
-D(\vq) &= H^{-1}(q_{1},q_2)\pi^\cE_{\vn_\cE}(q)+o, \label{eq:plane_ellipsoid_constraint}\\
+D(\vq) &= H^{-1}(q_{1},q_2)\pi^\cE_{\vn_\cE}(\vq)+o, \label{eq:plane_ellipsoid_constraint}\\
   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{\vn}(\vq)} = 0 \},\\
-   \Pi_\sZ(z) & = \overrightarrow{0}, 
+   \Pi_\sZ(\vz) & = \overrightarrow{0}, 
 \end{align}
@@
   \begin{equation}\label{equ:plane2ellipse}
-    \pi^\cE_{\vn_\cE}(q) =\begin{cases}
-      p^\cE_{1}-p^\cE_{\cL} & \textrm{ if } d_\cE \in [0, d_{\cE t}], \\
-      p^\cE_{2}-p^\cE_{\cL} &  \textrm{ if } d_\cE \in [- d_{\cE t},0), \\
+    \pi^\cE_{\vn_\cE}(\vq) =\begin{cases}
+      p^\cE_{t_1}-p^\cE_{\cL} & \textrm{ if } d_\cE \in [0, d_{\cE t}], \\
+      p^\cE_{t_2}-p^\cE_{\cL} &  \textrm{ if } d_\cE \in [- d_{\cE t},0), \\
       {0} & \textrm{otherwise}.
@@
   \begin{proposition}\label{prop:dpi_ne_dt}
-    The differential of the projection function $\pi^\cE_{\vn \cE}(q)$ with respect to the foci $q_1$ and $q_2$ is given by:
+    The differential of the projection function $\pi^\cE_{\vn \cE}(\vq)$ with respect to the foci $q_1$ and $q_2$ is given by:
     \begin{equation}
@@
 \begin{center}
-\includegraphics[width=0.6\linewidth]{Ellipse2safezone_V2}
-\caption{Polygon-ellipse constraint. This constraint is simplified to either a plane-ellipse constraint or a point-ellipse constraint.}
+\includegraphics[width=0.6\linewidth,trim = 0cm 1cm 0.3cm 0.5cm, clip]{Ellipse2safezone_V2}
+\caption{Polygon-ellipse constraint. This constraint is simplified to either a plane-ellipse constraint $D_{1}$ or a point-ellipse constraint $D_{2}$.}
 \label{fig:Ellipse-to-safezone}
@@
 For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
-Assume the segment on hyperplane $\Eframe \cL(\tilde{q}) = \{  \tilde{q}\in\mathbb{R}^m:  \vn_\cE\transpose \tilde{q} = d_{\cE}\}$ has endpoints $p_1$ and $p_2$; then the segment can be defined as:
-\begin{equation}
-\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), 
-\end{equation}
-\rtron{Needs an additiona constraint that $p$ needs to be on the line $p_1p_2$.}
+Assume the segment on hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ has endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; then the segment can be defined as:
+\begin{equation}
+\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
+\end{equation}
+For cases, where the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
+red region in \Cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies between $\Eframe{p_{1}}$ and $\Eframe{p_{2r}}$), the constraint can be seen as a plane-ellipse constraint in \Cref{sec:ellipsoide-plane}.
+Otherwise (i.e.
+brown region in \Cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies outside $\Eframe{p_{1}}$ and $\Eframe{p_{2b}}$), the constraint can be seen as a point-ellipse constraint in \Cref{sec:ellipsoid-point}.
+
 \begin{constraint}[Line-segment-ellipsoid reachability constraint]
@@
 D(\vq) &=  \begin{cases}
-D_1(p_1) & (p_1-p_2)\transpose (p_{\cL}-p_2)<0\\
-D_1(p_2) & (p_2-p_1)\transpose (p_{\cL}-p_1)<0\\
-D_2(p_{\cL}) & \textrm{otherwise}
+D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
+D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
+D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
 \end{cases} \label{eq:segment_ellipsoid_constraint}\\
-  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
-   \Pi_\sZ(z) & = 0, 
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
+   \Pi_\sZ(\vz) & = 0, 
 \end{align}
 \end{constraint}
-
-\rtron{Define $D_1$, $D_2$. Give intuition about what they represent.}
+where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$ in \eqref{eq:point_ellipsoid_constraint}, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint with respect to frame $\Eframe {\cL}$ in \eqref{eq:plane_ellipsoid_constraint}.
+
 \subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
@@
 \begin{align}
-D(\vq) &= \bmat{D_{seg1}\\D_{seg2}\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
-  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(q)} = 0 \},\\
-   \Pi_\sZ(z) & = 0, 
+D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
+   \Pi_\sZ(\vz) & = 0, 
 \end{align}
 \end{constraint}
-\rtron{$D_{seg1}, D_{seg2}$ need to be defined.}
-ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle}) to prevent cases where the ellipse is a subset of the region.
+where $D_{seg}$ are the constraint functions for each line segment used to define convex polygon region.
+ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle-constraint}) to prevent cases where the ellipse is a subset of the region.
 
@@
 All robots have the task of collecting sensor information on the underlying vector field, with agent 3 having an additional task to visit the \emph{checkpoint} at time $8$.
-Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:trajectories-base}).
+Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:ADMM-example-application}).
 We first set up an co-observation schedules considering two forbidden regions using the APMAPF algorithm, and add reachability constraints ensure a empty intersection between all robots' reachability regions between co-observations and forbidden regions.
@@
 stationary security camera) need to be incorporated in order to generated an attack-proof solution.
-Additional solutions to avoid these checkpoints will be discussed in \Cref{chapter:cross-trajectory}.
+Additional solutions to avoid these checkpoints will be discussed in \Cref{sec:cross-trajectory}.
 
@@
 Agent 3 in the Figure \ref{fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas.
-Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:trajectories-more-constraint} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
+Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:ADMM-example-application} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
 This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
-These challenges are addressed in Chapter \ref{chapter:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
-
-\section{Cross-trajectory co-observation planning}
-
-To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams \rtron{refer to introductory figure}.
+These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
+
+\section{Cross-trajectory co-observation planning}\label{sec:cross-trajectory}
+
+To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set})
 These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
-Note that \emph{cross-trajectory co-observation}, are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
-\rtron{(More discussion in Sec.
-??)}.
-
-\rtronhl{Move to discussion}{In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.}
+To prevent potential situations where the entire sub-team is compromised and take the advantage of the decentralized blocklist protocol introduced in \cite{wardega2023byzantine} for additional Byzantine resilience, we always prefer \emph{cross-trajectory co-observation} when feasible.
+
+%\rtronhl{Move to discussion}{In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.}
 
@@
 
-\rtron{Introduce $n_p$ in the previous Section.}
-
-In \Cref{sec:??} we assumed that the number of robot is equal to the number of routes $n_p$.
+\zyang{change all later te to T}
+\zyang{security or safety?}
+
+In \Cref{sec:ADMM-planning} we assumed that the number of robot is equal to the number of routes $n_p$.
 In this section, we assume that we have a total of $n>n_p$ robots available.
-\rtronhl{Clarify: since the robots change teams, this partition is time-varying, or can we get by without defining this partition explicitly?} We define a partition $\cI=\union_p \cI_p$ of the robots such that robots in \emph{sub-team} $\cI_p$ have the same nominal trajectory.
-We use the planner introduced in  \Cref{chapter:Multi-agent-ADMM} to generate multi-robot trajectories with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{0,\ldots,N_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, t_{e}\}$.
-\rtron{Again, make sure notation is consistent}
-Within each sub-team, at least one robot is required to follow the reference trajectory to fulfill the required tasks.
-Meanwhile, the additional robots can switch from one reference trajectory to another in order to perform co-observation with different sub-teams.
-\rtron{$\star$}\rtron{Give a little more details about how cross-trajectory co-observations are defined to ensure safety.}
+During initialization, $n$ robots are formed into \emph{sub-teams} by a time-varying partition $\cI(t)=\union_p \cI_p(t)$ of the robots where robots in \emph{sub-team} $\cI_p$ have the same nominal trajectory.
+The planner introduced in \Cref{sec:ADMM-planning} is used to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
+
+Expanding upon the concept introduced in \Cref{sec:co-observation-constraint}, where robots can collaborate through co-observation to enhance security while traveling in close proximity to one another, we capitalize on the presence of additional $n_p-n$ robots to enhance security.
+In scenarios where at least one robot is mandated to adhere to the reference trajectory to fulfill essential tasks, these additional robots' initial focus are on performing co-observations within their respective sub-teams.
+Whenever necessary, they are designed to seamlessly transition between sub-teams.
+By deviating from their original sub-team's route and joining teams requiring heightened attention, they become instrumental in providing co-observations at critical junctures.
+
 We refer to the new type of co-observations as \emph{cross-trajectory co-observations}.
-The goal is to find the cross trajectory co-observation plan to secure an unsecured MRS trajectory with a minimal number of additional robots.
-
-\rtronhl{This can be summarized more, since it is discussed later in this same page}{To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$.
-Vertices $V_{q}$ are a key locations in $\{q_p\}$ that are used to perform co-observations.
-Part of these vertices are \emph{checkpoints} which are selected to guarantee that, if robots deviate and reach forbidden regions, they will miss the scheduled co-observations.
-Other vertices are selected to connect checkpoints on different trajectories.
-The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges of two types, trajectory edges $E_{t}$ and cross-trajectory edges $E_{c}$, representing paths which robots can take.
-The trajectory edges $E_{t}$ represent the reference trajectories, where each edge connects two waypoints on the trajectory of the same sub-team.
-The cross-trajectory edges $E_{c}$ connect vertices on different reference trajectories, with at least one of the vertices being a checkpoint.
-These edges represent the potential paths that robots can take to travel and perform co-observations between trajectories of different sub-teams.} Similar to the work done by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.
+Our objective is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.
+
+To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
+Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires attention.
+The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.
+Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.
 
@@
 In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method).
-\rtronhl{Move to the end of this RRT* section}{Our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
-While the ADMM based solver \Cref{chapter:ADMM review} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
-RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.}
 
@@
 
+ Notice that our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
+While the ADMM based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
+RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
+
 \subsection{Checkpoint graph construction}
@@
 \subsubsection{Checkpoints}\label{sec:security-checkpoint}
-Let $q\in\real{nmT}$ be the MRS trajectory found in Chapter \ref{chapter:Multi-agent-ADMM} for $m$ sub-teams with time horizon $T=t_{e}$, with $q_{p}(t)$ be the reference trajectory waypoint for sub-team $p$ at time $t$.
-A checkpoint $v_i=(q_{i},t_{i})$ is a pair composed of a location $q_{i}=q_{p}(t_{i})$ and a time $t_{i}$ representing a co-observation between a sub-team $\cI_p$'s member and robots either from the same sub-team or different ones.
-For convenience, let $\cI_{v_{i}}$ represent the sub-team $v_{i}$ belongs to.
-
-Similar to the requirements of co-observations introduced in  \Cref{chapter:Reachability_Constraints}, \rtronhl{Consider wrapping this in definition environment} {we define checkpoints $V_{p}=\{ v_{p_{1}}, \dots ,v_{p_{e}}\} \subset V_{q}$ for a reference trajectory $\{q_{p}(t)\}$ of sub-team $p$ in a way that guarantees that the reachability region between consecutive checkpoints $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}})$ does not intersect with any of the forbidden areas.}  The requirement can be formally stated as $\mathcal{E}(q_{p_{i}}, q_{p_{i+1}}, t_{p_{i}},t_{p_{i+1}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$.
+Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$. 
+\begin{definition}
+Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$. 
+\end{definition}
+For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, \zyanghl{Is this necessary?}{and let $q_{v_{pi}} = q_{pi}$, $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$}.
+
+Using the idea of co-observation and reachability constraints introduced in \Cref{sec:ADMM-planning}, we define a set of checkpoints for the trajectory of sub-team $p$ to provide security.
+\zyang{definition or remark?}
+
+\begin{definition}
+The set of $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) that can be used to secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas.
+The requirement can be formally stated as $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$.
+\end{definition}
 
 We provide a heuristic approach to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
-\rtron{State this as an Algorithm?} We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon.
+The approach is shown in \Cref{alg:checkpoint-gen}, and a toy example is shown in Figure \ref{fig:checkpoint-generate}.
+% We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon.
 Then, we search for the waypoint $q_{p}(t_{1})$ with the largest $t_{1} \in \{t_{0}, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
@@
 The search is stopped when $t_{0}>t_{2}$, or when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$.
-A toy example is shown in Figure \ref{fig:checkpoint-generate}.
+
+\begin{algorithm}
+  \caption{Secure Checkpoint Generate for sub-team $p$}\label{alg:checkpoint-gen}
+  \begin{algorithmic}
+  \State $v_{p0} \gets (q_{p}(0),0)$; $v_{pT} \gets (q_{p}(T),T)$
+  \State $V_p = \{v_{p0}, v_{pT}\}$
+  \State $t_0 \gets 0$; $t_1 \gets T$
+  \While {$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}),t_{0},t_{1}) \intersect F \neq \emptyset$ or $t_1 - t_0 > 1$}
+    \State $i \gets 1$; $j\gets 1$
+    \While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{0}+i),t_{0},t_0+i) \intersect F = \emptyset$ and $t_0+i > t_1$}
+      \State $v_{pf} \gets (q_{p}(t_0+i),t_0+i)$
+      \State $i \gets i+1$
+    \EndWhile
+    \State $V_p\gets V_p\union v_{pf}$
+    \While{$\mathcal{E}(q_{p}(t_{1}-j),q_{p}(t_{1}),t_{1}-j,t_{1}) \intersect F = \emptyset$ and $t_0+i \geq t_1-j$}
+    \State $v_{pb} \gets (q_{p}(t_1-j),t_1-j)$
+    \State $j \gets j+1$
+    \EndWhile
+    \If {$t_0+i \neq t_1-j$}
+    \State $V_p\gets V_p\union v_{pb}$
+    \EndIf
+  \EndWhile
+  \end{algorithmic}
+  \end{algorithm}
 
@@
 \subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
-After locating checkpoints $\union_p V_p$ for all sub-teams, we can search for cross-trajectory edges to connected all checkpoints to trajectories.
-Cross-trajectory edges represents feasible paths between two references trajectories that allow robots to reach a different reference trajectories and perform co-observations with the corresponding sub-teams.
-Thus, at least one end of the edges must be a security checkpoint $v_{p} \in \union_p V_p$.
-Additionally, assuming that only one robot is sent at a time between trajectories, the cross-trajectory edges must satisfy the reachability constraints from~\Cref{chapter:Reachability_Constraints} to ensure that no deviation to forbidden areas can be performed while switching trajectories.
+After identifying checkpoints $\union_p V_p$ for all sub-teams, the next step is to search for cross-trajectory edges connecting all checkpoints to the respective trajectories.
+These cross-trajectory edges define viable paths between two reference trajectories, allowing robots to closely approach and collaborate with robots on a different reference trajectory for co-observations with the relevant sub-teams.
+Consequently, at least one endpoint of each edge must correspond to a security checkpoint $v_{p} \in \union_p V_p$.
+Assuming a single robot is transferred at a time between trajectories, the cross-trajectory edges must adhere to the reachability constraints detailed in ~\Cref{sec:reachability} to ensure that no deviations into forbidden areas can occur during trajectory switches.
 
@@
 
-We search for feasible paths between each security checkpoint and all other trajectories (ignoring, for the moment, any timing constraint), as shown in \Cref{fig:RRT*} \rtron{Missing figure}. 
-%Paths returned by RRT* are optimal and bidirectional.%, we can analyze the travel time and reachability for each candidate cross-trajectories, and  add these edges to the checkpoint graph if they are feasible.
-More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint $v_{p}=(q_{p},t_{p}) \in V_{p}$ for sub-team $\cI_p$, and $V_{r} = \{ (q_{{r}_{i}}, t_{{r}_{i}}) \}$ where  $q_{{r}_{i}} = q_{r}(t_{{r}_{i}})$ are the entire waypoints on a reference trajectories for a different sub-team $\cI_{r}$.
+We search for feasible paths between each security checkpoint and all other trajectories (ignoring, for the moment, any timing constraint), as shown in \Cref{fig:RRT*}
+More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and the entire waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on a reference trajectories for a different sub-team $\cI_{r}$.
 We can calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path. 
-
-\rtron{Combine the definitions of arrival and earliest arrival, and of departure and latest departure}
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.6\linewidth]{RRT_example_new}
+\caption{ALL viable path found from a waypoint to all reference trajectories of other sub-teams.}
+\label{fig:RRT*}
+  \end{center}
+\end{figure}
 
 \begin{description}
-\item We call a node $v_{{r}_{i}} \in V_{r}$ an \emph{arrival node} if \rrtstar{} found a path from $v_p$ to  $v_{{r}_{i}}$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and the reachability ellipsoid associated with the path endpoints does not intersect the forbidden region, $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$ \rtron{Consolidate the notation $q_r(t_{r_i}), q_{r_i}, v_{r_i}$}.[Latest departure node $q_{r}(t^{d}_r)$] is the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
-\item
- Similarly, a node $v_{r_i}\in\cV_r$ is a \emph{departure node} for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
+\item[Arrival node] We call a node $v_{{r}_{i}}=(q_r(t_{r_i}),t_{r_i}) \in V_{r}$ an \emph{arrival node} if \rrtstar{} found a path from $v_p$ to $v_{{r}_{i}}$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and %the reachability ellipsoid associated with the path endpoints does not intersect the forbidden region,
+ $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.[Latest departure node $q_{r}(t^{d}_r)$] is the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
+\item[Departure node] Similarly, a node $v_{r_i}\in\cV_r$ is a \emph{departure node} for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
 Given a point $v_{p} \in V_{p}$, we define the \emph{latest departure node} $q_{r}(t^{d}_r)$, and the \emph{earliest arrival node} $q_{r}(t^{a}_r)$ as follows:

### 2023-10-23 paper.tex
Updates from Overleaf

@@
 Specifically, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
-This achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
+This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
 In this way, the plan ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
-\cite{wardega2019resilience} solved this problem in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
+\zyang{avoid start with reference} \cite{wardega2019resilience} solved this problem in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
 
@@
 The goal of our path planning problem is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$.
-The set $\Omega$ is given by the intersection of spatio-temporal sets given by the security constraints (co-observation schedule, reachability analysis) and the traditional path planning constraints.
+The set $\Omega$ is given by the intersection of spatio-temporal sets given by  security constraints (co-observation schedule, reachability analysis) and traditional path planning constraints.
 Formally:
@@
 Our goal is to find paths that minimize uncertainty and effectively reconstruct the field.
-We utilize Kalman Filters (KFs)~(cf.
-\cite{anderson2012optimal}) to estimate uncertainty through the covariance $P_j$.
-Additionally, the robot provides field measurements at waypoints $q$ using a Gaussian radial basis function for radius and quality modeling.
+We associate a Kalman Filter (KF)~(cf.
+\cite{anderson2012optimal}) to each point $j$, and use it to track the uncertainty through its estimated covariance $P_j$.
+The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality.
 
@@
 
-Our cost function $\varPhi(\vq)$ measures the maximum uncertainty $P_{j}$ among map locations of interest along the entire trajectory $\vq$, and our objective is to minimize this maximum uncertainty.
-Constraints $\Omega$ includes traditional constraints like velocity constraints, convex obstacles, waypoints to reach with deadlines, and security constraints including co-observation constraints and reachability constraints.
+\rtron{Cite conference article for details on the problem formulation.}
+The optimization objective $\varPhi(\vq)$ is the maximum uncertainty $\max_j P_{j}$.
+The set $\Omega$ includes traditional constraints like bounded velocity, convex obstacles, waypoints to reach with deadlines, in addition to security constraints including co-observation and reachability constraints.
 \end{example}
@@
  This section is organized as follows.
-We begin by presenting the foundational mathematical concepts, notably the basic ADMM optimal trajectory solver.
+We begin with foundational mathematical concepts, such as the basic ADMM optimal trajectory solver.
 Subsequently, our solver allows us to seamlessly integrate security constraints, encompassing co-observation schedule and reachability constraints.
-Concluding this section, we present the obtained results alongside limitations (due to infeasibility) that are addressed in \Cref{sec:cross-trajectory}.
+Concluding this section, we present the obtained results alongside limitations (due to infeasibility) that are then addressed in \Cref{sec:cross-trajectory}.
 
 \subsection{Preliminaries}
-In this section, we review various mathematical concepts that will provide the foundations and context for the solver and constraints.
+We review in this section the mathematical foundations for our ADMM solver and the constraints that we will use.
 
@@
 For brevity we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
-The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.
+%The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.
 
 With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{R}\to\real{m\times n}$.
-Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to interpret $\partial_x f$ as a linear operator applied to $\dot{x}$.
+Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.
 
  \subsubsection{Householder rotations}\label{sec:householder}
- In the derivation of the reachability constraint in \Cref{sec:reachability,sec:ellipse-region-constraint}, we need to define a differentiable transformation to a canonical form.
-This transformation will include a rotation that we derive from a modified version of Householder transformations \cite{householder1958unitary}.
+ In the derivation of the reachability constraint in \Cref{sec:reachability,sec:ellipse-region-constraint}, we need to define a differentiable transformation to a canonical ellipse.
+This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}.
 With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection).
@@
 
-  We compute the differential of $H$ implicitly using the relation \eqref{equ:dt_to_dx}.
-We will use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
-  \begin{equation}
-    \bmat{v_1\\v_2\\v_3}\mapsto \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
+  We compute the differential of $H$ implicitly using its definition \eqref{equ:dt_to_dx}.
+We use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
+  \begin{equation}
+    \bmat{v_1\\v_2\\v_3}_\times= \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
   \end{equation}
@@
   \begin{proposition}\label{prop:Hderivitive}
-    Let $\nu_\cF(t)$ represent a parametric curve. Then we have
-    \begin{equation}
-      \dot{H}=H\cross{-2M\dot{\nu}_{\cF}}
+    Let $\nu_\cF(t)$ represent a parametric curve. Then
+    \begin{equation}
+      \dot{H}=H\cross{-2M\dot{\nu}_{\cF}},
     \end{equation}
@@
 More specifically, we can rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function. 
-In the traditional application of ADMM, the variables $\vz$ are duplicates of $\vx$ projected to the constraint set $\Omega$.
+In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$.
 However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
-To allow for a easier projection step, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ :
+To allow for an easier projection step, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$.
+In summary, we transform \rtronref{(1)} into
 \begin{equation}\label{eq:ADMMSetConstraint_modified}
@@
 
-The update steps of the ADMM algorithm can be then denoted as \cite{Boyd2011}:
+The update steps of the ADMM algorithm are then derived as \cite{Boyd2011}:
 \begin{subequations}\label{eq:ADMMupdate}
 	\begin{align}
-		\label{eq:admm-mod-update-q}\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2)\\
-		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k) \\
+		\label{eq:admm-mod-update-q}\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\\
+		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \\
 		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1},
@@
 \begin{equation}\label{eq:dual-residual}
-	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1}),
-\end{equation}
-after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed large number of iterations.
+	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
+\end{equation}
+after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed number of iterations.
 Since $D(\vq)$ is the vertical concatenation of $D_i(\vq)$, the projection of each set $\mathcal{Z}_i$ is independent for each constraint and can be computed separately.
-The advantage of this formulation is that we can choose $D(\vq)$ such that the new constraint set~$\cZ$ becomes simple to compute; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vq$ in \eqref{eq:admm-mod-update-q}.
-Additionally, the function~$D(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.
+The advantage of this formulation is that we can choose $D(\vq)$ such that the new constraint set~$\cZ$ becomes simple to compute, and the function~$D(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vq$ in \eqref{eq:admm-mod-update-q}.
 
@@
 \subsection{Velocity constraints}\label{sec:velocity-constraint}
-  The movement of each agent is constrained by a maximum distance in any direction over a single discrete time step.
-We then define the function $D(\vq)$ to return the velocity vectors for the $i$-th agent at time step $j$; its result then needs to be constrained to a sphere.
+  The movement of each agent is constrained by a maximum velocity defined as the distance in any direction over a single discrete time step.
+We define the function $D(\vq)$ to return the velocity vectors for the $i$-th agent at time step $j$, and constrain its result to a sphere.
 
@@
 \begin{align}
-     D_{ij}(\vq) &= q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\}\\
+     D_{ij}(\vq) &= q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\},\\
 \label{eq:velocity_constraint}
-   \sZ_{ij} &=\bigl\{\vz \mid \norm{\vz} \leq v_{max}\bigr\}\\
+   \sZ_{ij} &=\bigl\{\vz \mid \norm{\vz} \leq v_{max}\bigr\},\\
    \Pi_{\sZ_{ij}}(\vz)&=\begin{cases}
-   v_{\max}\frac{\vz}{\norm{\vz}} \textrm{ if } \norm{\vz}>v_{\max}\\
-   \vz\textrm{ otherwise}
+   v_{\max}\frac{\vz}{\norm{\vz}} \textrm{ if } \norm{\vz}>v_{\max},\\
+   \vz\textrm{ otherwise.}
    \end{cases}
@@
 
-We use convex polygons to model regions defining solid obstacles and forbidden regions that cannot be entered by agents.
+We use convex polygons to model regions defined by solid obstacles and forbidden regions that cannot be entered by agents.
 The convex region $\cP$ is defined using a collection of $l$ hyperplanes $n_{k} q = m_{k}$, where $n_k$ is the normal vector pointing toward the outside of the obstacle and $m_k$ is the scalar offset defining the $k$-th hyperplane.
@@
 \end{equation}
-We then defined function $D(\vq)$ to return the maximum distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, and set constraint on $z$ that it is a non-negative scalar.
+We define the function $D(\vq)$ to return the maximum distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, and  constraint $z$ to be a non-negative scalar.
 This constraint is applied to all $q_{ij} \in \vq$.
@@
 \begin{align}
-     	D(q_{ij}) &= \max_{k=1,\dots,l} (d_{k}(q_{ij},\cP))\\
+     	D(q_{ij}) &= \max_{k=1,\dots,l} (d_{k}(q_{ij},\cP)),\\
 \label{eq:obstacle_constraint}
@@
    \Pi_\sZ(z) & = \begin{cases}
-   0 & \textrm{if} \quad z < 0\\
-   z  & \textrm{otherwise}
+   0 & \textrm{if} \quad z < 0,\\
+   z  & \textrm{otherwise.}
    \end{cases} \label{eq:zoneConstraintProjection}
@@
 Non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
-By setting the normal vector pointing toward the inside of the region, this method can also serve to constrain the robots within the designated workspace region.
+By using outward-pointing normals, this method can also serve to constrain the robots within a designated workspace region.
 
@@
 Security-related constraints often necessitate that a robot reaches a specified location at a particular time.
-We assume robot $i$ is tasked with reaching a given point $p$ within a radius of $d_{max}$ at some time instant $j$ within a predefined time window $[t_1,t_2]$.
-We defined a constraint this constraint as follow.
+We assume that robot $i$ is tasked with reaching a given point $p$ within a radius of $d_{max}$ at some time instant $j$ within a predefined time window $[t_1,t_2]$, leading to the following:
 
@@
 \begin{align}
-     	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr)\\
+     	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),\\
 \label{eq:waypoint_constraint}
   \sZ &= \{z \mid z < z_{max} \},\\
-   \Pi_\sZ(z) & = \min(z, d_{max}).
-\end{align}
+   \Pi_\sZ(z) & = \min(z, d_{max}),
+\end{align}
+where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
 \end{constraint}
 
-where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
  Note that this function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
-\rtron{Give example application here, and include application of ADMM without the security constraints, but highlighting a path that would break the security}
+%\rtron{Give example application here, and include application of ADMM without the security constraints, but highlighting a path that would break the security}
 \zyang{plot new simpler example, add collision avoidance}
@@
 This constraint is represented as a relative distance requirement between the two robots at a specific time instant, ensuring they are within a defined radius to inspect each other or exchange data.
-Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \Cref{sec:reachability}, do not intersect with any forbidden regions.
+%Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \Cref{sec:reachability}, do not intersect with any forbidden regions.
 
@@
 
- We write the function for the constraint as:
-\begin{constraint}[Co-observation constraint]
+% We write the function for the constraint as:
+\begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
 \begin{align}
@@
 d_{max}\frac{\vz}{\norm{\vz}} &\text{if } \norm{\vz} > d_{max},\\
-\vz	& otherwise.
+\vz	& otherwise,
 \end{cases}
 \end{align}
+where $a,b$ are the indices of the pair of agents required for a mutual inspection.
 \end{constraint}
 
-where $a,b$ are the indices of the pair of agents required for a mutual inspection. The locations $q_{aj}$ and $q_{bj}$ where the co-observation performed are computed as part of the optimization.
+ The locations $q_{aj}$ and $q_{bj}$ where the co-observation is performed are computed as part of the optimization.
 
@@
 The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be
-  These will be used in the ADMM formulation in section \ref{chapter:ADMM review}.
+  Together with \Cref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide our security guarantees.
 
@@
 The region $\cE(q_1,q_2)$ is an ellipsoid with foci at $q_1,q_2$, center $o_{\cE} = \frac{1}{2}(q_1+q_2)$, and the major radius equal to $a$.
-Let $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ be the distance from the center to a foci.
-
-The reachability ellipsoid is an over-approximation of the exact reachability region; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
+We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.
+The reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
 
@@
 To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$.
-The canonical frame $\cF_\cE$ is defined as the origin aligns with the ellipsoid's center, and the first axis aligns with the foci.
-We perform this transformation in a differentiable manner, with respect to the two foci serving as waypoints for a robot.
+
+The canonical frame $\cF_\cE$ is defined with the origin at the ellipsoid's center, and the first axis aligned with the foci \rtronref{Figure 3}.
+We perform this transformation in a differentiable manner, with the two foci serving as waypoints for a robot.
 We parametrize the transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we refer to as $R$ and $o$, respectively. 
@@
   \end{align}
-  To simplify notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
-  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, where the coordinates of the two foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ are
+  To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
+  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, with foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ defined as
   \begin{align}
@@
   \end{align}
-  with $c=\frac{\norm{q_2-q_1}}{2}$.
+  and semi-axis distance $c=\frac{\norm{q_2-q_1}}{2}$.
 \begin{definition}
@@
 \end{equation}
-where $\cE^{c}$ is the set complement of the region $\cE$.
+where $\cE^{c}$ is the set complement of region $\cE$.
 
@@
 And for cases where $q_{avoid} \in \cE(q_1,q_2,r)$, $D(q)$ needs to be projected to the boundary of the ellipse.
-In canonical frame $\cF_{\cE}$, the projected point $q^{\cE}_{p}$ can be written as:
+In the canonical frame $\cF_{\cE}$, the projected point $q^{\cE}_{p}$ can be written as:
   \begin{equation}
@@
   %where $S=(I+sQ)\inverse$.Using the fact that since $q^\cE_p$ is a point on the ellipse, 
-  where $s$ can be solved as the root of the \eqref{equ:standard-ellipse}:
+where $s$ can be solved as the root of the level set \eqref{equ:standard-ellipse}:
   \begin{equation}
@@
   \end{equation}
- Detailed methods for computing $s$ can be found in \cite{yang2021multi} \cite{yang2020multi} \cite{eberly}.
+ Detailed methods for computing $s$ can be found in \cite{yang2021multi,yang2020multi,eberly}.
 
@@
 
-  Then the point-to-ellipse projection function in $\cF$ can be represented as:
+The point-to-ellipse projection function in $\cF$ is then:
   \begin{multline}\label{equ:Point2EllipseProjection}
@@
   \begin{proposition}\label{prop:Ellipse2PointDiff}
-    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (where we use $q$ as a shorthand notation for $q^\cE_{avoid}$)
+    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (using $q$ as a shorthand notation for $q^\cE_{avoid}$)
     \begin{multline}
@@
 
-For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^n: \vn\transpose \Fframe{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}).
-The reachability constraint now can then be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-When transformed into canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, where,
+For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^n: \vn\transpose \Fframe{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}), the reachability constraint can be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, where,
   \begin{equation}
@@
 
-To find cross-trajectory edges, we first find trees of feasible paths using \rrtstar{} and position information alone; we then prune these trees by considering time constraints (that consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints) and ellipsoidal rechability constraints.
+To find cross-trajectory edges, we first find trees of feasible paths using \rrtstar{} and position information alone; we then prune these trees by considering time constraints (that consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints) and ellipsoidal reachability constraints.
 
@@
 More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and the entire waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on a reference trajectories for a different sub-team $\cI_{r}$.
-We can calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path. 
+We then calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path in order to see if the deviating robot is able to catch up with the corresponding sub-team when merging to a different reference trajectory.
+Among all the viable paths, two type of nodes could be found.
 \begin{figure}
@@
 \begin{description}
-\item[Arrival node] We call a node $v_{{r}_{i}}=(q_r(t_{r_i}),t_{r_i}) \in V_{r}$ an \emph{arrival node} if \rrtstar{} found a path from $v_p$ to $v_{{r}_{i}}$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and %the reachability ellipsoid associated with the path endpoints does not intersect the forbidden region,
- $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.[Latest departure node $q_{r}(t^{d}_r)$] is the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
-\item[Departure node] Similarly, a node $v_{r_i}\in\cV_r$ is a \emph{departure node} for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
+\item[Arrival node] the waypoints that a robot from sub-team $\cI_p$, deviating from $(q_r(t_{r_i}),t_{r_i})$, can meet with sub-team $\cI_r$.
+We call a node $(q_r(t_{r_i}),t_{r_i})$ an \emph{arrival node} if \rrtstar{} found a path from $v_p$ to $v_{{r}_{i}}$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.
+The smallest $t_{r_i}$ that can be found $t^{a}_r$ is named as \emph{earliest arrival time}, together with the \emph{earliest arrival node} $(q_{r}(t^{a}_r),t^{a}_r)$.
+\item[Departure node] are the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$ can meet with robots in sub-team $\cI_p$ at $v_{p}$ Similarly, a node $v_{r_i}\in\cV_r$ is a \emph{departure node} for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
+
 Given a point $v_{p} \in V_{p}$, we define the \emph{latest departure node} $q_{r}(t^{d}_r)$, and the \emph{earliest arrival node} $q_{r}(t^{a}_r)$ as follows:
 [Earliest arrival node $q_{r}(t^{a}_r)$] is waypoint with the earliest time $t^{a}_r$ such that a robot from sub-team $\cI_p$ deviating from $v_{p}$ can meet with sub-team $\cI_r$.
+Arrival nodes are the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
+[Latest departure node $q_{r}(t^{d}_r)$]latest time
 \end{description}

### 2023-10-23 paper.tex
update

@@
 \newcommand{\rrtstar}{$\texttt{RRT}^\texttt{*}$}
+\newcommand{\SubItem}[1]{
+    {\setlength\itemindent{15pt} \item[-] #1}
+}
+
 \newtheorem{constraint}{ADMM constraint}
@@
 This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
-In this way, the plan ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
-\zyang{avoid start with reference} \cite{wardega2019resilience} solved this problem in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
+\begin{definition}\label{def:secured-plan}
+  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\end{definition}
+
+This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
 
@@
 To allow for an easier projection step, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$.
-In summary, we transform \rtronref{(1)} into
+In summary, we transform \Cref{eq:general-problem} into
 \begin{equation}\label{eq:ADMMSetConstraint_modified}
@@
 
-The canonical frame $\cF_\cE$ is defined with the origin at the ellipsoid's center, and the first axis aligned with the foci \rtronref{Figure 3}.
+The canonical frame $\cF_\cE$ is defined with the origin at the ellipsoid's center, and the first axis aligned with the foci \Cref{fig:EllipseConstraintExample} .
 We perform this transformation in a differentiable manner, with the two foci serving as waypoints for a robot.
@@
 In this section, we assume that we have a total of $n>n_p$ robots available.
-During initialization, $n$ robots are formed into \emph{sub-teams} by a time-varying partition $\cI(t)=\union_p \cI_p(t)$ of the robots where robots in \emph{sub-team} $\cI_p$ have the same nominal trajectory.
+During initialization, $n$ robots are formed into \emph{sub-teams} by a time-varying partition $\cI(t)=\union_p \cI_p(t)$ of the robots where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
 The planner introduced in \Cref{sec:ADMM-planning} is used to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
-
-Expanding upon the concept introduced in \Cref{sec:co-observation-constraint}, where robots can collaborate through co-observation to enhance security while traveling in close proximity to one another, we capitalize on the presence of additional $n_p-n$ robots to enhance security.
+\zyang{should we mention admm is used here but other planners can be used as well?}
+
+Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as,
+\begin{remark}\label{rmk:revised-security}
+  a multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
+\end{remark}
+
+We capitalize on the presence of additional $n_p-n$ robots to enhance security.
 In scenarios where at least one robot is mandated to adhere to the reference trajectory to fulfill essential tasks, these additional robots' initial focus are on performing co-observations within their respective sub-teams.
@@
 \begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth]{two_edges}
-\caption{For checkpoints of the red trajectory, latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.}
-\label{fig:two-edges}
-\end{center}
+  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth]{two_edges}}
+  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth]{security_graph}}
+  \caption{\Cref{fig:two-edges}, Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
+\Cref{fig:security-graph-generate}, example of a full checkpoint graph where round vertices are checkpoint generated through the heuristic search and triangle vertices are added with the cross-trajectory edges.
+Virtual source $v^{+}$ and sink $v^{-}$ are added to be used later in planning problem.}
 \end{figure}
@@
 \begin{description}
-\item[Arrival node] the waypoints that a robot from sub-team $\cI_p$, deviating from $(q_r(t_{r_i}),t_{r_i})$, can meet with sub-team $\cI_r$.
-We call a node $(q_r(t_{r_i}),t_{r_i})$ an \emph{arrival node} if \rrtstar{} found a path from $v_p$ to $v_{{r}_{i}}$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.
-The smallest $t_{r_i}$ that can be found $t^{a}_r$ is named as \emph{earliest arrival time}, together with the \emph{earliest arrival node} $(q_{r}(t^{a}_r),t^{a}_r)$.
-\item[Departure node] are the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$ can meet with robots in sub-team $\cI_p$ at $v_{p}$ Similarly, a node $v_{r_i}\in\cV_r$ is a \emph{departure node} for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
-
-Given a point $v_{p} \in V_{p}$, we define the \emph{latest departure node} $q_{r}(t^{d}_r)$, and the \emph{earliest arrival node} $q_{r}(t^{a}_r)$ as follows:
-[Earliest arrival node $q_{r}(t^{a}_r)$] is waypoint with the earliest time $t^{a}_r$ such that a robot from sub-team $\cI_p$ deviating from $v_{p}$ can meet with sub-team $\cI_r$.
-Arrival nodes are the waypoint with the latest time $t^{d}_r$ such that a robot from sub-team $\cI_r$  can meet with robots in sub-team $\cI_p$ at $v_{p}$.
-[Latest departure node $q_{r}(t^{d}_r)$]latest time
+\item[Arrival node] are waypoints on $\{q_r\}$ where robots from sub-team $\cI_p$, deviating at $v_p$, can meet with sub-team $\cI_r$ at $(q_r(t_{r_i}),t_{r_i})$.
+\emph{Arrival node}s need to satisfy that \rrtstar{} can find a path from $v_p$ to $q_{r}(t^{a}_r)$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.
+
+\emph{Earliest arrival node} $(q_{r}(t^{a}_r),t^{a}_r)$ is defined as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
+%$t^{a}_r$ is designated as the \emph{earliest arrival time}.
+
+\item[Departure node] are the waypoints on $\{q_r\}$ such that a robot from sub-team $\cI_r$, deviating from $(q_{r}(t_{{r}_{i}}),t_{{r}_{i}})$, can meet with robots in sub-team $\cI_p$ at $v_{p}$.
+\emph{Departure node}s need to satisfy that \rrtstar{} can find a path from $v_p$ to $q_{r}(t_{{r}_{i}})$ for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
+
+\emph{Latest departure node} $(q_{r}(t^{d}_r),t^{d}_r)$ is defined as the departure node characterized by the maximum $t^{d}_r$ discovered.
+% $t^{d}_r$ is designated as the \emph{latest departure time}.
 \end{description}
 
-For each $v_{p} \in V_{p}$, we add all the latest departure and earliest arrival nodes to $V_{q}$, and their corresponding paths as cross-trajectory edges $E_{q}$.
-Examples are shown in Figure \ref{fig:two-edges}, while the full algorithm is shown in Algorithm \ref{alg:cross-trajectory-edges}.
-
-\begin{algorithm}
-\caption{Cross-trajectory edges generation}\label{alg:cross-trajectory-edges}
-\begin{algorithmic}
-\Procedure{CrossTrajectoryEdges}{$V$}
-\State $V_{q} \gets V$; $E_{q}\gets 0$;
-\ForAll {$v\in V$}
-	\ForAll{$\vq_{r}$ that $\cI_{r} \neq \cI_{v}$}
-		\State $V_{q},E_{q} \gets \textsc{AddEdges} (q_{v}, \vq_{r}, V_{q}, E_{q}) $;
-	\EndFor
-\EndFor
-\State \Return $V_{q}, E_{q}$
-\EndProcedure
-\Procedure{AddEdges}{$q_{v}, \vq_{r}, V_{q},E_{q}$}
-\State $t^{d}_r \gets -\infty $; $t^{a}_r \gets \infty$;
-\State $\cV_{goal}=RRT^*(q_{v}, \vq_{r})$;
-    \ForAll{$ q \in \cV_{goal} $ that $\texttt{Parent}(q)\neq \emptyset $}
-        \If{$\texttt{Cost}(q)/ v_{max} < t_{q}-t_{v}$ and $\cE(q, v_{p},t_{q}, t_{v_{p}})\union F = \emptyset$}
-        		\If{$t_{q}<t^{a}_r$}
-			\State $t^{a}_r \gets t_{q}$;
-		\EndIf
-        \ElsIf{$\texttt{Cost}(q)/ v_{max} < t_{v} - t_{q}$ and $\cE(q, v_{p},t_{q},t_{v_{p}})\union F = \emptyset$}
-        		\If{$t_{q}>t^{d}_r$}
-			\State $t^{d}_r \gets t_{q}$;
-		\EndIf
-        \EndIf
-    \EndFor
-    \If{$t^{d}_r \neq -\infty $ and $t^{a}_r \neq \infty$}
-    \State $v_{a} \gets (q(t^{a}_r),t^{a}_r)$; $v_{d} \gets(q(t^{d}_r), t^{d}_r)$;
-    \State $V_{q}\gets V_{q} \union v_{a}$; $V_{q}\gets V_{q} \union v_{d}$;
-    \State $E_{q}\gets E_{q} \union (v_{p} \rightarrow v_{a})$; $E_{q}\gets E_{q} \union (v_{d} \rightarrow v_{p})$
-    \EndIf
-    \State \Return $V_{q},E_{q}$
-    \EndProcedure
-   \end{algorithmic}
-\end{algorithm}
+For each $v_{p} \in V_{p}$ found through \Cref{alg:checkpoint-gen}, we add all the latest departure and earliest arrival nodes to $V_{q}$, and their corresponding paths as cross-trajectory edges $E_{q}$.
+Examples are shown in Figure \ref{fig:two-edges}.
 
@@
 %With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-We add to $E_q$ the \emph{in-trajectory edges} $(v^{p}_{i}\rightarrow v^{p}_{i+1})$ obtained by connecting all checkpoints $v^p_{i}\in V_q$ found in Section~\ref{sec:security-checkpoint} with the checkpoints $v^p_{i+1}$ that  follow them in their original trajectories.
-%For all  and \ref{sec:cross-traj-edges}, can be divided by the corresponding sub-team and sorted in ascending order of time into $N_{p}$ subsets $V_{p}=\{v^{p}_{0}, v^{p}_{1}, \dots , v^{p}_{T}\}$ where $p\in \{1,\dots, N_{p}\}$.
-Consecutive edges in the same subset are added to $E_{q}$ as  .
+For all $V_{p}=\union_p \{v^0_{p}, \dots ,v^T_{p}\}$ found in \Cref{sec:security-checkpoint,sec:cross-traj-edges} arranged in ascending order of $t_{v^i_{p}}$.
+We add to $E_q$ the \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ obtained by connecting all consecutive checkpoints $v^i_{p}\in V_q$ with the checkpoints $v^{i+1}_{p}$ that follow them in their original trajectories.
 Examples are shown in Figure \ref{fig:security-graph-generate}.
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth]{security_graph}
-\caption{Example of a two trajectory security graph.
-Round vertices are checkpoint generated through the heuristic search and triangle vertices are added with the cross-trajectory edges.
-Additional virtual source $v^{+}$ and sink $v^{-}$ is used later in planning problem.}
-\label{fig:security-graph-generate}
-\end{center}
-\end{figure}
+\zyang{any better explaination?}
 
@@
 \begin{remark}
-\rtron{Note that we assign fixed roles to reference robots for convenience in explaining the multiflow formulation.
-In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation.}
+Note that we assign fixed roles to reference robots for convenience in explaining the multiflow formulation.
+In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
 \end{remark}
 
-To formulate the planning problem as a network multi-flow problem \rtron{Check that multiflow/multi-flow/flow problem is indicated consistently across the entire paper}, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
-The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is a \emph{virtual source} node, and $v^{-}$ is a \emph{virtual sink} node.
-The edges of the new graph are defined as $E = E_{q} \union \{( v^{e}_{p},v_{-})\}_{p} \union \{(v_{+},v^{0}_{p})\}_{p}$, i.e., we add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^e_p$ representing the start and end vertices of sub-team $\cI_p$.
-
-Our goal is then to find a path in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
-%,  Each robot then may move according to the edges in $G$ from vertex $v_{i}$ to $v_{j}$ if $(v_{i},v_{j})\in E_{q}$. 
+To formulate the planning problem as a network multi-flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
+The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is the \emph{virtual source} node, and $v^{-}$ is the \emph{virtual sink} node.
+The edges of the new graph are defined as $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$, i.e., we add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$.
+
+Our goal is to find a path in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
 The path of a robot $k$ can be represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
-\rtronhl{Spell out this requirement at the beginning of the section (around $\star$, and reference it here}{As required by the security guarantee, reference robots must be seen by at least one cross-reference robot at every checkpoint.}
+As required by the security guarantee in \Cref{rmk:revised-security}, reference robots must be seen by at least one cross-reference robot at every checkpoint.
 Thus, the planning problem can then be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $V_{p}$ is included in at least one path in $F$.

### 2023-10-23 paper.tex
update

@@
 
-This section presents the two components of our approach: constructing the checkpoint graph based on unsecured multi-robot trajectories, and the formulation and solution of the network flow problem.
+This section presents the two components of our approach: constructing the checkpoint graph based on unsecured multi-robot trajectories, and the formulation and solution of the network multi-flow problem.
 
@@
 \subsection{Co-observation planning problem}
-In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network flow problem, and solve it using mixed-integer linear programs (MILP).
+In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network multi-flow problem, and solve it using mixed-integer linear programs (MILP).
 We assume that $n_p$ \emph{reference robots} are dedicated (one in each sub-team) to follow the reference trajectory.
@@
 \begin{remark}
-Note that we assign fixed roles to reference robots for convenience in explaining the multiflow formulation.
+Note that we assign fixed roles to reference robots for convenience in explaining the multi-flow formulation.
 In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
@@
 The path of a robot $k$ can be represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
-As required by the security guarantee in \Cref{rmk:revised-security}, reference robots must be seen by at least one cross-reference robot at every checkpoint.
-Thus, the planning problem can then be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $V_{p}$ is included in at least one path in $F$.
+In order to perform co-observations as required by the security introduced in \Cref{rmk:revised-security}, reference robots must be seen by at least one cross-trajectory robot at every checkpoint.
+Thus, the planning problem can be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $V_{p}$ is included in at least one path in $F$.
 Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
-\rtron{Finally, edges from the virtual source and to the virtual sink should have zero cost, to allow robots to automatically get assigned to the starting point that is most convenient for the overall solution.}
+
+Finally, edges from the virtual source and to the virtual sink should have zero cost, to allow robots to automatically get assigned to the starting point that is most convenient for the overall solution.
 These requirements are achieved with the weights for edges $(v_{i},v_{j})\in E$ defined as:
@@
      \begin{align}
-        \min & \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
+        \min_{F} & \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
         s.t. & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij},  \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
@@
 The constratin \eqref{eq:FlowCoverage} is the flow coverage constraints, which ensures that all security checkpoints $ \{V^{s}_{p}\}$ have been visited by at least one flow (robot).
-Since the security graph $G_{q}$ is acyclic, this problem is in complexity class $P$, and can be solved in polynominal time \cite{ntafos1979path}.
+Since the security graph $G_{q}$ is acyclic, this problem is in complexity class $P$, and can be solved in polynominal time \cite{1702662}.
 
@@
 Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
-Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{\cE} \in F$ that is empty, i.e.
-$f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{\cE}$, these flow will not increase the cost and will not have any impact on the solution.
-The trade-off between the number of surveillance robots used, and the overall security performance is a critical consideration in this case.
-Increasing the number of robots generally contributes to improved security by enabling more cross-trajectory co-observations.
-However, adding more robots can lead to diminishing returns, as the benefits gained from additional robots may be counterbalanced by increased complexity and coordination challenges.
-To capture this trade-off, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} allows us to fine-tune the balance between the number of robots employed and the desired task performance.
-By optimizing this parameter, we can strike a suitable equilibrium between security enhancement and operational efficiency.
-
-To find such tradeoff, we employ an iterative approach.
-We start with $\cK=1$ and gradually increase it until $F$ contains a empty flow.
-This indicates that the performance can no longer be improved by adding more robots.
-To ensure that the value of $\cK$ does not grow unbounded, penalty parameter $\rho$ need to ensure that the second term for a single flow in \eqref{eq:flow-cost} $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}$ is always smaller than $1$.
+Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{e} \in F$ that is empty, i.e.
+$f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$, these flow will not increase the cost and will not have any impact on the solution.
+The trade-off between the number of surveillance robots and security performance is crucial, with an increase in robots generally enhancing security via cross-trajectory co-observations.
+However, this improvement can be offset by heightened complexity and coordination challenges.
+To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency.
+An iterative approach with $\cK=1$ gradually increases until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
+To control unbounded growth, $\rho$ regulates the second term for a single flow in \eqref{eq:flow-cost} $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}$ is always smaller than $1$.
 
@@
 We model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories.
-We have shown that the co-observation planning problem across different trajectories can be transformed into a multi flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.
+We have shown that the co-observation planning problem across different trajectories can be transformed into a multi-flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.
 

### 2023-10-30 paper.tex
Updates from Overleaf

@@
 \begin{definition}\label{def:secured-plan}
-  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+  A multi-robot trajectory plan is secure against single-agent plan-deviation attacks if any deviation reaching a forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
 \end{definition}
 
-This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
+This problem is first solved by \cite{wardega2019resilience} in a grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
 
@@
 
-For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^n: \vn\transpose \Fframe{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}), the reachability constraint can be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, where,
+For forbidden region in the shape of a hyperplane $\mathcal{L} = \{\Fframe{q}\in\mathbb{R}^n: \vn\transpose \Fframe{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}), the reachability constraint can be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, where,
   \begin{equation}
@@
 \end{equation}
-Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
-
-For every $\Eframe \cL(\Eframe{q})$, there always exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e.
-resulting in a unique intersection point), $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
-And the intersection point can be written as:
+Intuitively, $d_\cE$ can be thought as a distance between the plane $\cL$ and the origin (i.e., the center of $\cE$).
+
+For every $\Eframe \cL$, there always exist two planes that are both parallel to $\cL$ and tangent to the ellipse (i.e.
+that have exactly one intersection point): $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$  (see \Cref{fig:Ellipse-to-plane}).
+The intersection point for each plane can be written as:
 \begin{equation}
@@
 
-We introduce the concept of a tangent interpolation point on the hyperplane to characterize the relationship between the plane and the ellipse.
+We introduce the concept of a tangent interpolation point to characterize the relation between the original constraint hyperplane $\cL$ and the ellipse.
 
 \begin{definition}
-The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
+The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is the point on the constraint hyperplane $\cL$ defined by 
     \begin{equation}\label{equ:ProjectPoint}
@@
     \end{equation}
+\end{definition}
 Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
-  Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{t_1}$ or $p^\cE_{\cL}=p^\cE_{t_2}$, respectively.
-When $ d_\cE \in [- d_{\cE t},  d_{\cE t}]$, the plane $\cL$ and the ellipsoid $\cE$ have at least one intersection, thus violating our desired reachability constraint.
-\end{definition}
-
-With these definitions, the constraint can be written as:
-
+When $ d_\cE \in (- d_{\cE t},  d_{\cE t})$, the plane $\cL$ and the ellipsoid $\cE$ have two intersections and when $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{t_1}$ or $p^\cE_{\cL}=p^\cE_{t_2}$, respectively.
+We can therefore use $d_\cE$ to define our desired reachability constraint, and $p^\cE_\cL$ to compute the corresponding differential.
 \begin{constraint}[Plane-ellipsoid reachability constraint]
@@
 
-For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
-Assume the segment on hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ has endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; then the segment can be defined as:
+This section builds upon the hyperplane case in \rtronref{previous section}, with the difference that we consider a segment of finite dimensions.
+This represents an intermediate step toward polygon-shaped forbidden regions in \rtronref{next section}.
+
+Assume a segment on hyperplane $\Eframe \cL = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; the segment can be defined as:
 \begin{equation}
@@
 where $D_{seg}$ are the constraint functions for each line segment used to define convex polygon region. 
-ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle-constraint}) to prevent cases where the ellipse is a subset of the region.
+Second, the ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle-constraint}) to prevent cases where the ellipse is a subset of the region.
 
@@
 In this section, we apply our ADMM path planning algorithm to an instance of a map exploration problem (Figure~\ref{fig:ADMM-example-application}), and test the algorithm in both simulations and an experimental testbed.
-The environment to be explored, with three agents, is a $10m\times10m$ region and two forbidden regions \emph{Zone 2, 3} which is shown in Fig.\ref{fig:Grid-example-application}.We assume that the robots can meaningfully collect information on the underlying vector field for data locations no further than $3m$.
-The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.
-
-We utilize the APMAPF solver introduced in \cite{wardega2019resilience} to generate a MAPF plan with co-observation schedule on a grid-world application (Fig.\ref{fig:Grid-example-application}) and transform the result to a continuous configuration space, under the map exploration tasks.
-All robots have the task of collecting sensor information on the underlying vector field, with agent 3 having an additional task to visit the \emph{checkpoint} at time $8$.
-Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:ADMM-example-application}).
-We first set up an co-observation schedules considering two forbidden regions using the APMAPF algorithm, and add reachability constraints ensure a empty intersection between all robots' reachability regions between co-observations and forbidden regions.
-
-As shown in Fig.\ref{fig:Grid-example-application}, no task has been assigned to the agent besides the start and goal location.
-Agent 1 and 2 need to meet at time 8 and 14, whereas agent 2 and 3 need to meet at time 18.
-This result is also used as the initial trajectory input for the ADMM solver.
-
-Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained.
+The environment to be explored, with three agents, is a $10m\times10m$ region and two forbidden regions \emph{Zone 2, 3} which is shown in Fig.\ref{fig:Grid-example-application}.
+We assume that the robots can meaningfully collect information on the underlying vector field for data locations no further than $3m$.
+The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ \rtronhl{clarify}{a time limit of 20}.
+
+We utilize the APMAPF solver introduced in \cite{wardega2019resilience} to generate a MAPF plan with co-observation schedule on a grid-world approximation (Fig.\ref{fig:Grid-example-application}) and transform the result to a continuous configuration space, under the map exploration tasks.
+All robots have the task of collecting sensor information on the underlying vector field.
+Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon-like pattern (like the unconstraint result in Figure~\ref{fig:ADMM-example-application}).
+We first set up a co-observation schedules considering two forbidden regions using the APMAPF algorithm, and add reachability constraints ensure a empty intersection between all robots' reachability regions between co-observations and forbidden regions.
+
+%As shown in Fig.\ref{fig:Grid-example-application}, no task has been assigned to the agent besides the start and goal location. 
+Agent 1 and 2 need to meet at time 8 and 14, whereas agent 2 and 3 need to meet at time 18. This result is also used as the initial trajectory input for the ADMM solver. 
+%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained.
+
+\rtron{Expand this discussion/merge with discussion of Limitations below}
+Agent 3 has an additional task to visit the \emph{checkpoint} at time $8$. 
 Notice that additional checkpoint (i.e.
@@
 The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3.
-Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles.
-Therefore, the intersections between obstacles and ellipsoids, i.e.
-the case here between agent 3 and zone 1, are tolerable.
-All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task.
+Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have basic obstacle avoidance capability and cannot physically penetrate hard obstacles.
+Therefore, intersections between obstacles and ellipsoids (e.g., the case here between agent 3 and zone 1), are tolerable.
+All constraints have been satisfied and the agents spread out across the map to perform the best possible exploration task under the given constraints.
 
@@
 Agent 3 in the Figure \ref{fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas.
-Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:ADMM-example-application} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
-This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
-These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
+Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:ADMM-example-application} and \ref{fig:ReachabilitySimulation}: after the introduction of THE security constraints, the top left corner is never explored by any robot.
+This is might be concerning given that system performance is a key factor in multi-agent systems.
+These challenges are addressed by relaxing the solution (while still maintaining the security guarantees) via the introduction of additional agents in \Cref{sec:cross-trajectory} below.
+%, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
 

### 2023-10-30 paper.tex
update

--- 2023-10-23 paper.tex
@@
 \begin{abstract}
-This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control.
-Such compromises could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission.
-To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots as an additional security measure.
-Our approach guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations.
-We achieve this by introducing \emph{reachability} constraints into continuous trajectory planning algorithm.
-These constraints ensure an empty intersection between the sets of locations that the agents could potentially reach and the forbidden regions.
-\rtron{The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.}
-Furthermore, to enhance system resilience and feasibility of the planning problem, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments.
-This redundancy enables robots to deviate from their assigned sub-teams and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories simultaneously.
-To efficiently plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories.
-\rtron{This second part fixes the feasiblity problems of the first one, and uses the same reacheability constraints to build inter-team trajectories.}
+This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control which could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission.
+To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots, and introducing  \emph{reachability} constraints as additional security measures.
+By enforcing an empty intersection between the locations that the agents could potentially reach (using reachability constraint) and the forbidden regions, we provide guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations.
+The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.
+
+Furthermore, to further enhance system resilience and address the feasibility challenges encountered in the initial stage, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments.
+This allows redundant robots to deviate for co-observations across different sub-teams, ensuring the security of multiple trajectories without the need for trajectory modifications of the entire sub-team.
+To plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories,
+
 We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
@@
 Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
-The use of MRS offers numerous advantages, but it also introduces new cybersecurity challenges, including unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
-Given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats.
+The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g.
+unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}).
 In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}.
@@
 
-These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience} \zyang{add most recent articles}.
-The work of \cite{wardega2019resilience} provide exact solution for grid-world configuration.
-Using the onboard sensing capabilities, robots can perform inter-robot observations as an additional security measure.
+These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi} \zyang{add most recent articles}.
+These works initial solution for grid-world configuration, where robots is tasked perform inter-robot observations (usilizing the onboard sensing capabilities) as an additional security measure.
 Each robot' self-report includes not only its own status, but also additional observations of other robots' status.
 For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''.
-Similarly, robot $j$ also reports its observations of robot $i$ to the CE.
+Similarly, robot $j$ also reports its observations of robot $i$ to the CE \cite{wardega2019resilience}.
 This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.
@@
 $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$, these flow will not increase the cost and will not have any impact on the solution.
+
 The trade-off between the number of surveillance robots and security performance is crucial, with an increase in robots generally enhancing security via cross-trajectory co-observations.
@@
 The planning result in the workspace is shown in \ref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \ref{fig:security-graph-3-flow}.
-Notice that flows represent the robot co-observation plan instead of actual robots, such that the red flow, for example, shows that the sub-team 2 is expecting a robot from sub-team 1, departing at $t=0$ and arriving at $t=10$, and needs to send a robot (not necessarily the same one received from sub-team 1) to sub-team 3, departing at $t=67$ and arriving at $t=79$.
 This plan is not ideal in terms of our security criteria since co-observations happens between the same pair of surveillance robot and sub-team for the majority of the time with only three cross-trajectory edges that are covered.

### 2023-11-01 paper.tex
Updates from Overleaf

@@
 
+\rtron{Put proposition showing relation between ellipsoids and Definition 1 here.}
+
 \subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
@@
 
-To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set})
-These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
-To prevent potential situations where the entire sub-team is compromised and take the advantage of the decentralized blocklist protocol introduced in \cite{wardega2023byzantine} for additional Byzantine resilience, we always prefer \emph{cross-trajectory co-observation} when feasible.
+To address the feasibility and performance trade-offs of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set})
+These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
+Technically, \rtron{we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team.
+While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
+For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.}\rtron{Probably move this later.}
 
@@
 In this section, we assume that we have a total of $n>n_p$ robots available.
-During initialization, $n$ robots are formed into \emph{sub-teams} by a time-varying partition $\cI(t)=\union_p \cI_p(t)$ of the robots where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
+During initialization, $n$ robots are divided into \emph{sub-teams}, i.e., we define a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each sub-team $\cI_p$ share the same nominal trajectory.
 The planner introduced in \Cref{sec:ADMM-planning} is used to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
-\zyang{should we mention admm is used here but other planners can be used as well?}
-
-Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as,
+\zyang{should we mention admm is used here but other planners can be used as well?
+\rtron{Yes}}
+
+Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as, \rtron{Turn this into a proposition, and introduce it in Section II}
 \begin{remark}\label{rmk:revised-security}
@@
 
-We capitalize on the presence of additional $n_p-n$ robots to enhance security.
-In scenarios where at least one robot is mandated to adhere to the reference trajectory to fulfill essential tasks, these additional robots' initial focus are on performing co-observations within their respective sub-teams.
-Whenever necessary, they are designed to seamlessly transition between sub-teams.
-By deviating from their original sub-team's route and joining teams requiring heightened attention, they become instrumental in providing co-observations at critical junctures.
-
-We refer to the new type of co-observations as \emph{cross-trajectory co-observations}.
-Our objective is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.
-
-To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
-Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires attention.
+Since only $n_p$ robots are necessary to follow the initial routes, we capitalize on the remaining $n_p-n$ robots to enhance security. 
+Each team will then have one robot to follow the reference trajectory and fulfill the basic sensing task, while the additional robots are dedicated to perform co-observations within their respective sub-teams.
+We assume the robots to be interchangeable by design, so that they can seamlessly transition between sub-teams.
+\rtronhl{Not clear to me}{By deviating from their original sub-team's route and joining teams requiring heightened attention, they become instrumental in providing co-observations at critical junctures.
+}
+We refer to this new type of co-observations as \emph{cross-trajectory co-observations}.
+Our objective is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured MRS path finding solution, while minimizing the number of additional robots required.
+
+To solve this problem, we model the planned trajectories $\{q_p\}_{p=1}^{N_p}$ with a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
+Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires \rtronhl{this term is not well defined}{attention}.
 The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.
-Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.
+Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general \rtron{Mixed-Integer?}{Linear Programming} techniques.
 
@@
 \subsection{Rapidly-exploring Random Trees}
-In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method).
+In this section, we will use the \rrtstar{} \cite{karaman2010incremental} algorithm as a component of our method.
+In particular, \rrtstar{} will be used to find paths from a single starting location to multiple destination points, i.e., the reference trajectories of other robots, in our method.
 
@@
 We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
-Key functions from \rrtstar{} that are also used during constructions of the checkpoint graph are
+While we refer the reader to \cite{karaman2010incremental,Choset:book05} for a full review of the \rrtstar{} algorithm, we highlight here two key functions that are also used during constructions of the checkpoint graph:
 \begin{description}
@@
  Notice that our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
-While the ADMM based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
-RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
+While the ADMM-based solver presented earlier in \Cref{sec:ADMM-planning} offers a broader range of constraint handling, \rrtstar's efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
 
@@
 \begin{definition}
-Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$. 
+Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$. 
 \end{definition}
@@
 
-\begin{definition}
-The set of $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) that can be used to secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas.
-The requirement can be formally stated as $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$.
+\begin{definition}\label{def:checkpoint vertices}
+A set $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) is a valid set of vertices for the checkpoint graph if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas.
 \end{definition}
-
-We provide a heuristic approach to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
+A sufficient condition for a set $V_p$ to satisfy \ref{def:checkpoint vertices} is that $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas.
+
+We provide a heuristic approach to locate valid checkpoint vertices on given trajectories (we do not consider an optimal selection, since finding this solution would likely be NP-hard, and the approach below works well enough for our purpose).
 The approach is shown in \Cref{alg:checkpoint-gen}, and a toy example is shown in Figure \ref{fig:checkpoint-generate}.
@@
 After identifying checkpoints $\union_p V_p$ for all sub-teams, the next step is to search for cross-trajectory edges connecting all checkpoints to the respective trajectories. 
+\rtron{Add a definition mirroring Definition 8}
 These cross-trajectory edges define viable paths between two reference trajectories, allowing robots to closely approach and collaborate with robots on a different reference trajectory for co-observations with the relevant sub-teams.

### 2023-11-01 paper.tex
update

--- 2023-10-30 paper.tex
@@
 \section{Introduction}\label{sec:introduction}
-Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
+%Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
 The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g.
@@
 
-These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi} \zyang{add most recent articles}.
-These works initial solution for grid-world configuration, where robots is tasked perform inter-robot observations (usilizing the onboard sensing capabilities) as an additional security measure.
-Each robot' self-report includes not only its own status, but also additional observations of other robots' status.
-For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''.
-Similarly, robot $j$ also reports its observations of robot $i$ to the CE \cite{wardega2019resilience}.
-This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.
-
-When transforming the solution to continuous configuration spaces, additional analysis is needed on the reachability of robots in order for the security of co-observation schedule to hold.
-More broadly, the problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.
-This constraint is formulated using an ellipsoidal bound of the reachability region, and the idea of using an ellipsoidal bound to limit the search space is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm.
-
+Multi-robot systems (MRS) have found wide applications in various fields, including warehouse organization, surveillance and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
+While MRS offers numerous advantages, their distributed nature and dependence on network communication render them vulnerable to cyber threats, introducing new cybersecurity challenges such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
+This paper addresses the specific scenario in which attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}.
+We define these restricted regions as \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+
+We focus on countering deliberate deviations, termed \emph{plan-deviation attacks}, identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}.
+As a security measure, robots perform inter-robot observations using their onboard sensing capabilities.
+Each robot's self-report includes its own status and additional observations of other robots' status.
+This mutual observation and reporting establish an observation schedule for the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
+
+In this paper, we transform the solution to continuous configuration spaces, allowing for more flexible objectives.
+We provide additional analysis on the reachability of robots to ensure the security of the co-observation schedule.
+Solving the path optimization problem with constraints based on the sets of locations that the agents could potentially reach, referred to as \emph{reachability regions}, is a novel contribution to the literature.
+
+A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
+Our proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
+Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
+We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.
+
+In this paper, we first transform the solution to continuous configuration spaces and allows for more flexible objectives, providing additional analysis on the reachability of robots in order for the security of co-observation schedule to hold.
+This problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.
+
+A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
 We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.
-The idea is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm; in that case, an ellipsoidal bound is used to limit the search space with the initial and goal states fixed.
+Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm, we use an ellipsodial bound to limit the search space and formulated the ellipsoid as the reachability region constraint.
 In our case, we use a similar bound to optimize the location of the two states to exclude the forbidden region from the ellipsoidal region.
-We propose a mathematical formulation of reachability regions that is compatible with the solver from \zyang{cite ADMM} as a spatio-temporal constraint.
-
-A preliminary version of the paper was presented at conferences \zyang{cite CDC IROS}.
-This paper extend the previous works by fixing two main challenges identified in \cite{wardega2023hola} \zyang{previous works}.
+We propose a mathematical formulation of reachability regions that is compatible with the solver from  as a spatio-temporal constraint.
+
+This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi,yang2021multi}.
 Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other.

### 2023-11-13 paper.tex
update before merge

@@
 
-In this paper, we first transform the solution to continuous configuration spaces and allows for more flexible objectives, providing additional analysis on the reachability of robots in order for the security of co-observation schedule to hold.
+%In this paper, we first transform the solution to continuous configuration spaces and allows for more flexible objectives, providing additional analysis on the reachability of robots in order for the security of co-observation schedule to hold.
 This problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.
 
-A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
+%A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
 We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.
@@
 During initialization, $n$ robots are formed into \emph{sub-teams} by a time-varying partition $\cI(t)=\union_p \cI_p(t)$ of the robots where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
-The planner introduced in \Cref{sec:ADMM-planning} is used to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints, where the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
+The planner introduced in \Cref{sec:ADMM-planning} is used to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ \rtronhl{It seems that this obviates the need for Section II; instead phrase it such that we use it to fix the feasibility problems of Section II}{without reachability and co-observation constraints}, where the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
 \zyang{should we mention admm is used here but other planners can be used as well?}
 
+\rtronhl{As we discussed, this will become a proposition and moved in the previous section}
 Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as,
 \begin{remark}\label{rmk:revised-security}
-  a multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
+  A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
 \end{remark}
@@
 After identifying checkpoints $\union_p V_p$ for all sub-teams, the next step is to search for cross-trajectory edges connecting all checkpoints to the respective trajectories. 
+\rtron{Add definition here for edges to be the counterpart of Definition 8}
 These cross-trajectory edges define viable paths between two reference trajectories, allowing robots to closely approach and collaborate with robots on a different reference trajectory for co-observations with the relevant sub-teams.
@@
 \begin{figure}[htbp]
-  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth]{two_edges}}
+    \centering
+  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth]{two_edges}}\hspace{2mm}
   \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth]{security_graph}}
@@
 We search for feasible paths between each security checkpoint and all other trajectories (ignoring, for the moment, any timing constraint), as shown in \Cref{fig:RRT*}
-More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and the entire waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on a reference trajectories for a different sub-team $\cI_{r}$.
-We then calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path in order to see if the deviating robot is able to catch up with the corresponding sub-team when merging to a different reference trajectory.
-Among all the viable paths, two type of nodes could be found.
+More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and all the waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on any reference trajectory for a different sub-team $\cI_{r}$.
+We then calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path.
+In order to see if the deviating robot is able to catch up and merge with the corresponding sub-team, we define two types of nodes.
 \begin{figure}
@@
     \includegraphics[width=0.6\linewidth]{RRT_example_new}
-\caption{ALL viable path found from a waypoint to all reference trajectories of other sub-teams.}
+\caption{All viable path found from a waypoint to all reference trajectories of other sub-teams.}
 \label{fig:RRT*}
@@
 \begin{description}
-\item[Arrival node] are waypoints on $\{q_r\}$ where robots from sub-team $\cI_p$, deviating at $v_p$, can meet with sub-team $\cI_r$ at $(q_r(t_{r_i}),t_{r_i})$.
-\emph{Arrival node}s need to satisfy that \rrtstar{} can find a path from $v_p$ to $q_{r}(t^{a}_r)$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.
-
-\emph{Earliest arrival node} $(q_{r}(t^{a}_r),t^{a}_r)$ is defined as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
+\item[Arrival nodes] are waypoints on $\{q_r\}$ where robots from sub-team $\cI_p$, deviating at $v_p$, can meet with sub-team $\cI_r$ at $(q_r(t_{r_i}),t_{r_i})$.
+For these, \rrtstar{} must have found a path from $v_p$ to $q_{r}(t^{a}_r)$ with $t_{p}+t_{\textrm{path}}<t_{{r}_{i}}$, and $\mathcal{E}(q_{r}(t_{{r}_{i}}),q_{p},t_{{r}_{i}},t_{p}) \intersect F = \emptyset$.
+
+For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $(q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
 %$t^{a}_r$ is designated as the \emph{earliest arrival time}.
 
-\item[Departure node] are the waypoints on $\{q_r\}$ such that a robot from sub-team $\cI_r$, deviating from $(q_{r}(t_{{r}_{i}}),t_{{r}_{i}})$, can meet with robots in sub-team $\cI_p$ at $v_{p}$.
-\emph{Departure node}s need to satisfy that \rrtstar{} can find a path from $v_p$ to $q_{r}(t_{{r}_{i}})$ for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
-
-\emph{Latest departure node} $(q_{r}(t^{d}_r),t^{d}_r)$ is defined as the departure node characterized by the maximum $t^{d}_r$ discovered.
+\item[Departure nodes] are the waypoints on $\{q_r\}$ such that a robot from sub-team $\cI_r$, deviating from $(q_{r}(t_{{r}_{i}}),t_{{r}_{i}})$, can meet with robots in sub-team $\cI_p$ at $v_{p}$.
+For these nodes, \rrtstar{} must find a path from $v_p$ to $q_{r}(t_{{r}_{i}})$ for $v_p$ if  $t_{p}>t_{{r}_{i}}+t_{\textrm{path}}$ and $\mathcal{E}(q_{p}, q_{r}(t_{{r}_{i}}),t_{p}, t_{{r}_{i}}) \intersect F = \emptyset$.
+
+For each trajectory $r\neq p$, we define the \emph{latest departure node} $(q_{r}(t^{d}_r),t^{d}_r)$ as the departure node characterized by the maximum $t^{d}_r$ discovered.
 % $t^{d}_r$ is designated as the \emph{latest departure time}.
@@
 %With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-For all $V_{p}=\union_p \{v^0_{p}, \dots ,v^T_{p}\}$ found in \Cref{sec:security-checkpoint,sec:cross-traj-edges} arranged in ascending order of $t_{v^i_{p}}$.
-We add to $E_q$ the \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ obtained by connecting all consecutive checkpoints $v^i_{p}\in V_q$ with the checkpoints $v^{i+1}_{p}$ that follow them in their original trajectories.
+We arrange all $V_{p}=\union_p \{v^0_{p}, \dots ,v^T_{p}\}$ found in \Cref{sec:security-checkpoint,sec:cross-traj-edges} in ascending order of $t_{v^i_{p}}$.
+We then add to $E_q$ the \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ obtained by connecting all consecutive checkpoints $v^i_{p}\in V_q$ with the checkpoints $v^{i+1}_{p}$ that follow them in their original trajectories.
 Examples are shown in Figure \ref{fig:security-graph-generate}.
-\zyang{any better explaination?}
+%\zyang{any better explaination?}
 
@@
 We assume that $n_p$ \emph{reference robots} are dedicated (one in each sub-team) to follow the reference trajectory.
-The goal of this section is to minimize the number and plan the routes of $n-n_p$  additional \emph{cross-trajectory robots} dedicated to perform co-observations with the reference robots.
+The goal of this section is to minimize the number and plan the routes of the $n-n_p$  additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations.
 
@@
 To formulate the planning problem as a network multi-flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
-The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is the \emph{virtual source} node, and $v^{-}$ is the \emph{virtual sink} node.
+The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is a \emph{virtual source} node, and $v^{-}$ is a \emph{virtual sink} node.
 The edges of the new graph are defined as $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$, i.e., we add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$.
@@
 
+\rtron{Move remark about the distributed blocklist here}
+
 Finally, edges from the virtual source and to the virtual sink should have zero cost, to allow robots to automatically get assigned to the starting point that is most convenient for the overall solution.
@@
         & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1, \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
-        & f^k_{ij} \in \{0,1\} ,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
+        & f^k_{ij} \in \{0,1\} \,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
      \end{align}
@@
 
-The first term in \ref{eq:flow-cost} is total outgoing flow from the source $v^{+}$ while the second term is the total cost of all flows representing the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges).
-The constant $\rho$ is a manually selected penalty parameter to balance between two terms in the cost function.
+The first term in the cost \ref{eq:flow-cost} is total outgoing flow from the source $v^{+}$ while the second term is the total cost of all flows representing the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
 The constraint \eqref{eq:FlowBalanceConstraint} is the flow conservation constraint, which ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
@@
 Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{e} \in F$ that is empty, i.e.
-$f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$, these flow will not increase the cost and will not have any impact on the solution.
-
-The trade-off between the number of surveillance robots and security performance is crucial, with an increase in robots generally enhancing security via cross-trajectory co-observations.
-However, this improvement can be offset by heightened complexity and coordination challenges.
-To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency.
-An iterative approach with $\cK=1$ gradually increases until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
-To control unbounded growth, $\rho$ regulates the second term for a single flow in \eqref{eq:flow-cost} $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}$ is always smaller than $1$.
+$f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$; these flow will not increase the cost and can be discarded from the solution.
+
+The constant $\rho$ selects the trade-off between the number of surveillance robots and security performance.
+An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.
+%To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency.
+\begin{remark} 
+The value of row $\rho$ is upper bounded such that the second term for each single flow in \eqref{eq:flow-cost} is always smaller than one, i.e., $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}\leq 1$.
+This is because, otherwise \rtron{...
+explain why the optimal cost would be unbounded}.
+\end{remark}
+
+In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
 
@@
 \begin{figure}[t]
+\rtron{Collect these four figures into a single figure. Maybe plot the graphs rotated 90 degrees so that "time" goes from left to right, and to use the space more efficiently.}
 \begin{center}
@@
 The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph.
-The planning result in the workspace is shown in \ref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \ref{fig:security-graph-3-flow}.
+The planning result in the workspace is shown in \Cref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \Cref{fig:security-graph-3-flow}.
 This plan is not ideal in terms of our security criteria since co-observations happens between the same pair of surveillance robot and sub-team for the majority of the time with only three cross-trajectory edges that are covered.
@@
 For the case where $\cK=4$, the results are shown in Figure \ref{fig:security-graph-4-flow}-\ref{fig:workspace-4-flow}.
-With one additional robot added, there are significant increase in the total cross-trajectory edges covered, and sub-teams performs co-observation with different robots during the task period.
-
-If we further increase $\cK>4$, we do not get a better result; instead, the planner will generate 4 flows with the rest $\cK-4$ flows empty.
+With one additional robot added, there is a significant increase in the total cross-trajectory edges covered, and sub-teams performs co-observation with different robots during the task period.
+If we further increase $\cK>4$, we do not get a better result; instead, the planner will generate four flows with the rest $\cK-4$ flows empty. \rtron{Reference Fig. 15}
 
@@
 
+\rtron{Run the ADMM planner again on Fig. 14, and show that you get a $\Phi(q)$ (i.e., better mapping).}
+
 \section{Summary}
@@
 This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories.
-We model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories.
+For cases where the secured planning problem is infeasible (or where the user desires to improve the optimality of the trajectories), we model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories.
 We have shown that the co-observation planning problem across different trajectories can be transformed into a multi-flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.

### 2023-11-15 paper.tex
modifi unsavedchanges for merge

--- 2023-11-01 paper.tex
@@
 While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
-For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.}\rtron{Probably move this later.}
+For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.}\rtron{Probably move this later.
+}
 

### 2023-11-20 paper.tex

--- 2023-11-13 paper.tex
@@
 
+Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as,
+\begin{remark}\label{rmk:revised-security}
+  A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
+\end{remark}
+
 \subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
@@
 
-To address the feasibility challenge and performance trade-off of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set})
-These \emph{cross-trajectory co-observations} allow sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
-To prevent potential situations where the entire sub-team is compromised and take the advantage of the decentralized blocklist protocol introduced in \cite{wardega2023byzantine} for additional Byzantine resilience, we always prefer \emph{cross-trajectory co-observation} when feasible.
+To address the feasibility and performance trade-offs of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set}).
+These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
+
+Technically, we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team.
+While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
+For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.
 
@@
 
-\zyang{change all later te to T}
-\zyang{security or safety?}
-
-In \Cref{sec:ADMM-planning} we assumed that the number of robot is equal to the number of routes $n_p$.
-In this section, we assume that we have a total of $n>n_p$ robots available.
-During initialization, $n$ robots are formed into \emph{sub-teams} by a time-varying partition $\cI(t)=\union_p \cI_p(t)$ of the robots where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
-The planner introduced in \Cref{sec:ADMM-planning} is used to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ \rtronhl{It seems that this obviates the need for Section II; instead phrase it such that we use it to fix the feasibility problems of Section II}{without reachability and co-observation constraints}, where the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
-\zyang{should we mention admm is used here but other planners can be used as well?}
-
-\rtronhl{As we discussed, this will become a proposition and moved in the previous section}
-Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as,
-\begin{remark}\label{rmk:revised-security}
-  A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
-\end{remark}
-
-We capitalize on the presence of additional $n_p-n$ robots to enhance security.
-In scenarios where at least one robot is mandated to adhere to the reference trajectory to fulfill essential tasks, these additional robots' initial focus are on performing co-observations within their respective sub-teams.
+To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map), we first use planner (in this paper, an ADMM-based planner introduced in \Cref{sec:ADMM-planning} is used, but other planners are applicable) to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints.
+Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
+Instead of having the number of robot equal to the number of routes $n_p$, in this section, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
+\zyang{refrased}Tasking at least one robot to adhere to the reference trajectory to fulfill essential tasks, we capitalize on the presence of additional $n_p-n$ robots to enhance security.
+These additional robots are initialized to focus are on performing co-observations within their respective sub-teams and
+
 Whenever necessary, they are designed to seamlessly transition between sub-teams.

### 2023-11-29 paper.tex
update

@@
 \section{Introduction}\label{sec:introduction}
-%Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
-The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g.
-unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}).
-In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}.
-We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.
-
 Multi-robot systems (MRS) have found wide applications in various fields, including warehouse organization, surveillance and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
 While MRS offers numerous advantages, their distributed nature and dependence on network communication render them vulnerable to cyber threats, introducing new cybersecurity challenges such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
-This paper addresses the specific scenario in which attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}.
-We define these restricted regions as \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
-
-We focus on countering deliberate deviations, termed \emph{plan-deviation attacks}, identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}.
-As a security measure, robots perform inter-robot observations using their onboard sensing capabilities.
-Each robot's self-report includes its own status and additional observations of other robots' status.
-This mutual observation and reporting establish an observation schedule for the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
-
-In this paper, we transform the solution to continuous configuration spaces, allowing for more flexible objectives.
-We provide additional analysis on the reachability of robots to ensure the security of the co-observation schedule.
-Solving the path optimization problem with constraints based on the sets of locations that the agents could potentially reach, referred to as \emph{reachability regions}, is a novel contribution to the literature.
+This paper addresses the specific scenario in which attackers compromise robots and direct them to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+Such countering deliberate deviations, termed \emph{plan-deviation attacks}, are identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}.
+As a security measure, robots perform inter-robot co-observations using their onboard sensing capabilities to check for unusual behavior.
+These mutual observation establish an co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
 
 A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
-Our proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
+When extanding the solution from \cite{wardega2019resilience} in grid-world to continuous configuration spaces, additional reachability analysis is erquired for additional security.
+Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
+One typical approach involves computing an over-approximation of the reachable space for checking safety properities.
+Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric extrapolations, such as zonotopes and ellipsoids, to represent a compact enclosure of the reachability sets.
+In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
+In contrast, our work shifts the focus to reachability analysis during the planning phase, addressing the path optimization problem by incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}.
+This contribution adds a novel perspective to the existing literature.
+
+This proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
 Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
@@
 
-%In this paper, we first transform the solution to continuous configuration spaces and allows for more flexible objectives, providing additional analysis on the reachability of robots in order for the security of co-observation schedule to hold.
-This problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.
-
-%A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
-We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.
-Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm, we use an ellipsodial bound to limit the search space and formulated the ellipsoid as the reachability region constraint.
-In our case, we use a similar bound to optimize the location of the two states to exclude the forbidden region from the ellipsoidal region.
-We propose a mathematical formulation of reachability regions that is compatible with the solver from  as a spatio-temporal constraint.
-
-This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi,yang2021multi}.
+This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}, the feasibility problem and optimality problem.
 Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other.
-In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path.
-Agent 3 in the Figure \zyang{ref fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas.
-Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \zyang{ref fig:trajectories-more-constraint} and \zyang{ref fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
-This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
-These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
-
-We propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
-Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
-In this paper, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in later works, making it more difficult for attackers to successfully plan and execute attacks.
+Secondly, security requirements may come at the cost of overall system performance, which is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
+In \Cref{sec:cross-trajectory}, these challenges are addressed through introducing additional robots into the MRS.
+Robots are formed into \emph{sub-teams} and tasked to follow an optimal trajectory without security constraints.
+The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from the .
 Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
@@
 
-\paragraph{Paper contributions} In this paper, we formulate a way to enforce an empty intersection between forbidden region and reachability regions, such that if an attacker takes control of the robots, they cannot perform an undetected attack by entering forbidden regions and meeting co-observation schedules at the same time.
-The constraints are formulated using an ellipsoidal bound of the reachability region.
-
-We propose to incorporate redundancy in the form of \emph{sub-team}s of multiple robots in place of individual robots along each route.
-This allows robots to deviate from their assigned sub-team, and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories.
-We propose a formulation of the multi-flow problem on unsecured MRS trajectories to plan the cross-trajectory co-observations that can preserve the security against plan-deviation attacks.
+\paragraph*{Paper contributions} 
+In this paper, two main contributions have been presented.
+
+\begin{itemize}
+  \item We present an innovative method to integrate reachability analysis into the ADMM-based optimal trajectory solver for multi-robot systems, preventing attackers from executing undetected attacks by simultaneously entering forbidden areas and adhering to co-observation schedules.
+  \item We introduce additional robots to form \emph{sub-teams} for both intra-sub-team and cross-sub-team co-observations.
+A new co-observation planning algorithm is formulated that can generate a resilient multi-robot trajectory with a co-observation plan that still preserve the optimal performance against arbitrary tasks.
+We also find the minimum redundant robots required for the security.
+\end{itemize}
+
+\paragraph*{paper ourline}
+The rest of this paper is organized as follows.
+In \Cref{sec:ADMM-planning}, we begin by providing an overview of the ADMM-based optimal trajectory solver.
+We then introduced the ellipsoidal reachability region and formulate it to different constraints with respect to different type of forbidden regions.
+In \Cref{sec:cross-trajectory}, we proposed the formulation of sub-teams and introduced the planning algorithm of the cross-trajectory co-observation planning problem.
+Finally, in \Cref{sec:summary}, we provide summary of this paper.
+
+\section{Literature review}
+\subsection{Reachability analysis}
+Reachability analysis is a common step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
+A common method is to compute an over-approximation of the reachable space for checking safety properities.
+Various researches rely on a geometrical extrapolation of the system states like zonotopes and ellipsoids as representation of a compact enclosure of the reachability sets \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive,maiga2015comprehensive}.
+The work in \cite{}
 
@@
 The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality.
-
-%Assume that there exists a slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations.
-To explore unknown spatially-distributed fields, autonomous agents are usually required to traverse the entire unknown environment while collecting sensory data to estimate a corresponding map (Figure~\ref{fig:ADMM-example-application}).
-We model the map as a set of locations of interests arranged on a regular grid, where at each location, we assume that there is a corresponding slowly-time-varying quantity.
-For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.
-
-%We address the estimation problem using Kalman Filters (KFs)(cf.
-\cite{anderson2012optimal}), with a focus on the estimated covariance $P_j$, to calculate the map model uncertainty.
-We assume the robot provides field measurements at waypoints~$q$, with Gaussian radial basis function modeling radius and quality.
-%\rtron{The previous paragraph can be written more compactly.}
 
@@
 
-Technically, we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team.
-While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
-For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.
-
 %\rtronhl{Move to discussion}{In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.}
@@
 \zyang{refrased}Tasking at least one robot to adhere to the reference trajectory to fulfill essential tasks, we capitalize on the presence of additional $n_p-n$ robots to enhance security.
-These additional robots are initialized to focus are on performing co-observations within their respective sub-teams and
-
-Whenever necessary, they are designed to seamlessly transition between sub-teams.
-By deviating from their original sub-team's route and joining teams requiring heightened attention, they become instrumental in providing co-observations at critical junctures.
-
+These additional robots are initialized to focus are on performing co-observations within their respective sub-teams and whenever necessary, they are designed to deviate from their original sub-team's route and joining teams requiring heightened attention (i.e.
+travelling near forbidden regions) and providing necessary co-observations.
 We refer to the new type of co-observations as \emph{cross-trajectory co-observations}.
-Our objective is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.
+The objective of this section is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.
 
 To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
-Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires attention.
+Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires co-observation to achieve security as described in \Cref{rmk:revised-security}.
 The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.
-Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.
+Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general Mixed-Intiger Linear Programming techniques as specialized solver.
 
@@
 Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$.
-\begin{definition}
+We locate checkpoints among $q_p$ that requires co-observations in order for the MRS trajectories to be secured as defined in \Cref{rmk:revised-security}.
 Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$.
-\end{definition}
-For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, \zyanghl{Is this necessary?}{and let $q_{v_{pi}} = q_{pi}$, $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$}.
-
-Using the idea of co-observation and reachability constraints introduced in \Cref{sec:ADMM-planning}, we define a set of checkpoints for the trajectory of sub-team $p$ to provide security.
-\zyang{definition or remark?}
-
-\begin{definition}
-The set of $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) that can be used to secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas.
+For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, and let $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
+
+\begin{remark}
+A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas.
 The requirement can be formally stated as $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$.
-\end{definition}
-
-We provide a heuristic approach to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
-The approach is shown in \Cref{alg:checkpoint-gen}, and a toy example is shown in Figure \ref{fig:checkpoint-generate}.
-% We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon.
-Then, we search for the waypoint $q_{p}(t_{1})$ with the largest $t_{1} \in \{t_{0}, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
-$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$.
-Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1}, \dots ,t_{2}\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$.
-$q_{p}(t_{1})$ and $q_{p}(t_{3})$ are then added to $V_{q}$.
-Afterwards, we set $t_{0}=t_{1}$, $t_{2}=t_{3}$ and repeat the same process.
-The search is stopped when $t_{0}>t_{2}$, or when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$.
+\end{remark}
+
+A heuristic approach is provided (\Cref{alg:checkpoint-gen}) to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose) with a toy example shown in Figure \ref{fig:checkpoint-generate}.
 
@@
 \subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
-After identifying checkpoints $\union_p V_p$ for all sub-teams, the next step is to search for cross-trajectory edges connecting all checkpoints to the respective trajectories. 
-\rtron{Add definition here for edges to be the counterpart of Definition 8}
-These cross-trajectory edges define viable paths between two reference trajectories, allowing robots to closely approach and collaborate with robots on a different reference trajectory for co-observations with the relevant sub-teams.
-Consequently, at least one endpoint of each edge must correspond to a security checkpoint $v_{p} \in \union_p V_p$.
-Assuming a single robot is transferred at a time between trajectories, the cross-trajectory edges must adhere to the reachability constraints detailed in ~\Cref{sec:reachability} to ensure that no deviations into forbidden areas can occur during trajectory switches.
+In order for co-observation to happen cross different trajectories at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories allowing robots deviate from one sub-team to approach, perform co-observation with robots on a different sub-team.
+\begin{remark}
+  Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$.
+The cross-trajectory edges must also adhere to the reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden areas can occur during trajectory switches.
+\end{remark}
 
@@
 
-\rtron{Move remark about the distributed blocklist here}
+Technically, we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team.
+While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
+For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.
 
@@
      \begin{align}
-        \min_{F} & \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
+        \min_{F} &\sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
         s.t. & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij},  \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
@@
 An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.
-%To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency.
+
+In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
+
 \begin{remark} 
 The value of row $\rho$ is upper bounded such that the second term for each single flow in \eqref{eq:flow-cost} is always smaller than one, i.e., $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}\leq 1$.
-This is because, otherwise \rtron{...
-explain why the optimal cost would be unbounded}.
+Otherwise, the iteration continues indefinitely as adding additional flow introduce a negative term $\sum_{(+i)\in E} f^{k}_{+i} - \rho\sum_{(ij)\in E} w_{ij} f^k_{ij} = 1- \rho\sum_{(ij)\in E} w_{ij} f^k_{ij}<0$ which always makes the cost \eqref{eq:flow-cost} smaller.
 \end{remark}
-
-In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
 
@@
 
-\section{Summary}
+\section{Summary}\label{sec:summary}
 In this paper, we provide a method to enhance the security of a multi-robot system without sacrificing the performance.
@@
 We have shown that the co-observation planning problem across different trajectories can be transformed into a multi-flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.
+
+While this work consider only the high-level path planning, the assignment of the duties within the sub-team can performed dynamically making it more difficult for attackers to successfully plan and execute attacks.
 
@@
 \bibliographystyle{unsrt}
-\bibliography{ADMM_planning,ACC,tron,ziqi}
+\bibliography{ADMM_planning,ACC,tron,ziqi,reachability}
 }

### 2023-11-29 paper.tex
update

@@
 In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
+
 In contrast, our work shifts the focus to reachability analysis during the planning phase, addressing the path optimization problem by incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}.
 This contribution adds a novel perspective to the existing literature.
-
 This proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
@@
 Robots are formed into \emph{sub-teams} and tasked to follow an optimal trajectory without security constraints.
-The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from the .
+The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from one sub-team and join another.
 Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
+
+Our algorithm in \Cref{sec:cross-trajectory} focus on the formulation the co-observation planning problem.
+This algorithm focus on the movement plan for the additional robots (other than the robots needed for objective tasks), their movement are limited follow a pre-defined trajectory with the sub-team, except for situations where they are tasked to perform co-observations with other sub-teams.
+Only in such case, these robots can deviate from the sub-team and switch the reference trajectory to the corresponding sub-team that requires co-observing, and they will automatically join the sub-team after co-observation.
+The planning problem can be
 
@@
 Finally, in \Cref{sec:summary}, we provide summary of this paper.
-
-\section{Literature review}
-\subsection{Reachability analysis}
-Reachability analysis is a common step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
-A common method is to compute an over-approximation of the reachable space for checking safety properities.
-Various researches rely on a geometrical extrapolation of the system states like zonotopes and ellipsoids as representation of a compact enclosure of the reachability sets \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive,maiga2015comprehensive}.
-The work in \cite{}
 

### 2024-01-19 paper.tex
finished version

--- 2023-11-29 paper.tex
@@
 %        1         2         3         4         5         6         7         8
-\documentclass[journal]{IEEEtran}  % Comment this line out
-
+%\documentclass[journal]{IEEEtran}  % Comment this line out
+\documentclass[10pt,twocolumn,twoside]{IEEEtran} 
 \IEEEoverridecommandlockouts                       % This command is only
@@
 
+%\documentclass[journal,twoside,web]{ieeecolor}
 % The following packages can be found on http:\\www.ctan.org
@@
 
+\usepackage[export]{adjustbox} 
 \usepackage{cleveref}
@@
 
-Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories}
-
-\author{Ziqi Yang and Roberto Tron\thanks{This project is supported by the National Science Foundation grant "CPS: Medium: Collaborative Research: Multiagent Physical Cognition and Control Synthesis Against Cyber Attacks" (Award number 1932162).}}
+Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow}
+
+\author{Ziqi Yang, Roberto Tron \IEEEmembership{Member, IEEE} 
+\thanks{This project is supported by the National Science Foundation grant "CPS: Medium: Collaborative Research: Multiagent Physical Cognition and Control Synthesis Against Cyber Attacks" (Award number 1932162).}
+\thanks{Ziqi Yang is with the Department of Systems Engineering,
+Boston University, Boston, MA 02215 USA (e-mail: zy259@bu.edu).
+}
+\thanks{Roberto Tron is with the Faculty of Mechanical Engineering and Systems Engineering, Boston University, Boston, MA 02215 USA (e-mail:
+tron@bu.edu).}}
 
@@
 \begin{abstract}
-This paper addresses the critical issue of security in multi-robot systems (MRS) when facing threats from adversaries attempting to compromise the robots' control which could lead to unauthorized access to forbidden areas, potentially causing harm or disrupting the mission.
-To tackle this problem, we propose a novel multi-robot planning algorithm that leverages mutual observations between robots, and introducing  \emph{reachability} constraints as additional security measures.
-By enforcing an empty intersection between the locations that the agents could potentially reach (using reachability constraint) and the forbidden regions, we provide guarantees that even in the face of adversarial movement by attackers, compromised robots cannot reach forbidden regions without missing scheduled co-observations.
-The reachability constraint is implemented with ellipsoidal over-approximation; this allows to quickly check intersection and compute gradients.
-
-Furthermore, to further enhance system resilience and address the feasibility challenges encountered in the initial stage, we introduce the concept of \emph{sub-teams}, where multiple robots form cohesive units along each route, replacing individual robot assignments.
-This allows redundant robots to deviate for co-observations across different sub-teams, ensuring the security of multiple trajectories without the need for trajectory modifications of the entire sub-team.
-To plan cross-trajectory co-observations that maintain security against plan-deviation attacks, we formulate the multi-flow problem on unsecured MRS trajectories,
-
+This paper addresses security challenges in multi-robot systems (MRS) where adversaries may compromise robot control, risking unauthorized access to forbidden areas.
+We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability} constraints for enhanced security.
+This ensures that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations.
+The reachability constraint uses ellipsoidal over-approximation for efficient intersection checking and gradient computation.
+To enhance system resilience and tackle feasibility challenges, we also introduce \emph{sub-teams}.
+These cohesive units replace individual robot assignments along each route, enabling redundant robots to deviate for co-observations across sub-teams, securing multiple trajectories without requiring modifications.
+The planning of cross-trajectory co-observations that maintain security against plan-deviation attacks is sloved by formulating the multi-flow problem on unsecured MRS trajectories.
 We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
@@
 \section{Introduction}\label{sec:introduction}
-Multi-robot systems (MRS) have found wide applications in various fields, including warehouse organization, surveillance and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}.
-While MRS offers numerous advantages, their distributed nature and dependence on network communication render them vulnerable to cyber threats, introducing new cybersecurity challenges such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
-This paper addresses the specific scenario in which attackers compromise robots and direct them to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+Multi-robot systems (MRS) have found wide applications in various fields.
+While offering numerous advantages, the distributed nature and dependence on network communication render the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
+This paper addresses a specific scenario in which  robots are compromised by attacker and directed to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
 Such countering deliberate deviations, termed \emph{plan-deviation attacks}, are identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}.
-As a security measure, robots perform inter-robot co-observations using their onboard sensing capabilities to check for unusual behavior.
-These mutual observation establish an co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
-
-A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}.
-When extanding the solution from \cite{wardega2019resilience} in grid-world to continuous configuration spaces, additional reachability analysis is erquired for additional security.
-Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
-One typical approach involves computing an over-approximation of the reachable space for checking safety properities.
-Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric extrapolations, such as zonotopes and ellipsoids, to represent a compact enclosure of the reachability sets.
-In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
-In contrast, our work shifts the focus to reachability analysis during the planning phase, addressing the path optimization problem by incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}.
-This contribution adds a novel perspective to the existing literature.
-
-This proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
+As a security measure, we utilized onboard sensing capabilities of the robots to perform inter-robot co-observations and check for unusual behavior.
+These mutual observation establish a co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
+
+A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}.
+Extanding the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in the ADMM-based trajectory optimization solver to accomodate for more flexible objectives.
+In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
+This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
 Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
-We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.
-
-This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}, the feasibility problem and optimality problem.
-Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other.
-Secondly, security requirements may come at the cost of overall system performance, which is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
-In \Cref{sec:cross-trajectory}, these challenges are addressed through introducing additional robots into the MRS.
-Robots are formed into \emph{sub-teams} and tasked to follow an optimal trajectory without security constraints.
-The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from the .
-Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.
+We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.
+
+However, such plans are not guaranteed to exist, and the secured trajectory always come at the cost of overall system performance.
+In this paper, we also address these feasibility and optimality challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}.
+For a MRS with unsecured optimal trajectorys (without security constraints), we introduce redundant robots and formed into \emph{sub-teams} with the original ones.
+These redundant robots are assigned the task of establishing additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
+The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another.
+This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in Figure \ref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events.
+The cross-trajectory co-observation problem is transformed as a multi-agent path finding problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.
 
@@
 
-\paragraph*{Paper contributions} 
+\noindent\myparagraph{Related research} Trajectory planning problem of MRS systems remained as a subject of intense study for many decades, and optimization is a common approaches in such area.
+Optimization based approaches are customizable to a variable of constraints (e.g.
+speed limit, avoid obstacles) and task specifications (e.g.
+maximum surveillance coverage, minimal energy cost).
+In constract to our work in \Cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}.
+Several optimization techniques like MIQP~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity, and to incorporate more complex non-convex constraints.
+
+Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and Multi-Agent Path Finding (MAPF) problems \cite{stern2019multi}.
+In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions and solved as a network flow problem \cite{yu2013multi,yu2016optimal}.
+This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem.
+%In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
+
+In \Cref{sec:ADMM-planning}, we incorporate reachability constraints to increase overall security Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
+One typical approach involves computing an over-approximation of the reachable space for checking safety properities.
+Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric representation, such as zonotopes and ellipsoids, as a compact enclosure of the reachability sets.
+In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
+
+\noindent\myparagraph{Paper contributions} 
 In this paper, two main contributions have been presented.
@@
 
-\paragraph*{paper ourline}
+\noindent\myparagraph{Paper Outline}
 The rest of this paper is organized as follows.
@@
 
-\section{Literature review}
-\subsection{Reachability analysis}
-Reachability analysis is a common step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
-A common method is to compute an over-approximation of the reachable space for checking safety properities.
-Various researches rely on a geometrical extrapolation of the system states like zonotopes and ellipsoids as representation of a compact enclosure of the reachability sets \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive,maiga2015comprehensive}.
-The work in \cite{}
-
 \section{Multi-robot trajectory planning with co-observation}\label{sec:ADMM-planning}
 
-In this section, we aim to enhance the security of MRSs against malicious takeovers and deviations by attackers.
-Specifically, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
+In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
 This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
@@
 
-This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
+%This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
 
@@
 For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$.
-The goal of our path planning problem is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$.
-The set $\Omega$ is given by the intersection of spatio-temporal sets given by  security constraints (co-observation schedule, reachability analysis) and traditional path planning constraints.
+The overall goal is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis).
 Formally:
@@
 \begin{example} 
-We consider the estimation of a slowly-varying scalar or vector field, denoted as $\vx$, at discrete locations within an unknown environment.
-Autonomous agents navigate this environment, collecting sensory data to construct a corresponding map (see Figure~\ref{fig:ADMM-example-application}).
-Our map comprises points of interest arranged on a grid, each associated with a slowly-changing value.
+Robots are tasked to navigate, collecting sensory data to construct a corresponding map for the slowly-varying field, denoted as $\vx$, of an unknown environment (see Figure~\ref{fig:SecurityBreak}).
+The map comprises points of interest arranged on a grid, each associated with a slowly-changing value.
 Our goal is to find paths that minimize uncertainty and effectively reconstruct the field.
@@
 The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality.
-
-\rtron{Cite conference article for details on the problem formulation.}
-The optimization objective $\varPhi(\vq)$ is the maximum uncertainty $\max_j P_{j}$.
-The set $\Omega$ includes traditional constraints like bounded velocity, convex obstacles, waypoints to reach with deadlines, in addition to security constraints including co-observation and reachability constraints.
+The optimization objective $\varPhi(\vq)$ is written as the maximum uncertainty $\max_j P_{j}$ (detailed formulation can be found in \cite{yang2020multi}).
+%The set $\Omega$ includes traditional constraints like bounded velocity, convex obstacles, waypoints to reach with deadlines, in addition to security constraints including co-observation and reachability constraints.
 \end{example}
@@
      \centering
-     \subfloat[Continuous world trajectory \label{fig:ADMM-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{Example_application}}
      \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+     \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{SecurityBreak}}
      \caption{Trajectory design of an example map exploration task for a three-robot system with start locations and destinations fixed.
@@
 Fig~\ref{fig:Grid-example-application} shows the planned trajectory with co-observation schedule in grid-world.
-Fig~\ref{fig:ADMM-example-application} shows the trajectory design in continuous world optimized with respect to a map exploration task}
+Fig~\ref{fig:SecurityBreak} shows the unsecured trajectory design in continuous world optimized with respect to a map exploration task where Zone 1 and 2 are considered together as one obstacle.
+A potential path that could break the security by entering region 1 is highlighted in dashline.}
      \label{fig:example-application}
  \end{figure}
- \rtron{Make sure we refer back to Example 1 when makes sense}
-
- This section is organized as follows.
-We begin with foundational mathematical concepts, such as the basic ADMM optimal trajectory solver.
-Subsequently, our solver allows us to seamlessly integrate security constraints, encompassing co-observation schedule and reachability constraints.
-Concluding this section, we present the obtained results alongside limitations (due to infeasibility) that are then addressed in \Cref{sec:cross-trajectory}.
+
+% This section is organized as follows.
+We begin with foundational mathematical concepts needed for the optimal trajectory solver and reachability constraints.
+Subsequently, we integrate security constraints, including co-observation schedule and reachability constraints.
+Finally, we present the obtained results alongside limitations that are then addressed in \Cref{sec:cross-trajectory}.
 
 \subsection{Preliminaries}
-We review in this section the mathematical foundations for our ADMM solver and the constraints that we will use.
-
 \subsubsection{Differentials}
@@
  \subsubsection{Householder rotations}\label{sec:householder}
- In the derivation of the reachability constraint in \Cref{sec:reachability,sec:ellipse-region-constraint}, we need to define a differentiable transformation to a canonical ellipse.
+  We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \Cref{sec:reachability,sec:ellipse-region-constraint}.
 This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}.
@@
   \end{definition}
-  The main property of interest for our application is the fact that $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
+  Here $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
   \begin{proposition}\label{prop:HProperty}
@@
 \subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
-The basic idea behind our ADMM-based solver \cite{yang2020multi} is to split the constraints from the objective function using a different set of variables $\vz$, and then solve an Augmented Lagrangian formulation of the optimization problem in \eqref{eq:general-problem}.
-More specifically, we can rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function. 
-In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$.
+The basic idea of the ADMM-based solver introduced in \cite{yang2020multi} is to separate the constraints from the objective function using a different set of variables $\vz$, and then solve separately in \eqref{eq:general-problem}.
+More specifically, we rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function (details can be found in \cite{yang2020multi}). 
+%In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$.
 However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
-To allow for an easier projection step, we propose a minor generalization of the ADMM formulation where we allow $\vz$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$.
+We allow $\vz = D(\vq)$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy in general ADMM formulation), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ to allow for an easier projection step in \Cref{eq:z-update}.
 In summary, we transform \Cref{eq:general-problem} into
@@
 where $D(\vq)= [D_1(\vq)^T,\dots,D_l(\vq)^T]^T$ is a vertical concatenation of different functions for different constraints.
-
-The update steps of the ADMM algorithm are then derived as \cite{Boyd2011}:
+This makes each constraint set $\mathcal{Z}_i$ independent and thus can be computed separately in later updating steps.
+$D_i(\vq)$ is chosen that the new constraint set~$\cZ_i$ becomes simple to compute which is illustrated in later secitons.
+% and the function~$D_i(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.
+
+The update steps of the algorithm are then derived as \cite{Boyd2011}:
 \begin{subequations}\label{eq:ADMMupdate}
@@
 		\label{eq:admm-mod-update-q}\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\\
-		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \\
+		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
 		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1},
@@
 \end{subequations}
-where $\Pi_\mathcal{Z}$ is the new projection to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
+where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
 \begin{equation}\label{eq:primal-residual}
@@
 after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed number of iterations.
-Since $D(\vq)$ is the vertical concatenation of $D_i(\vq)$, the projection of each set $\mathcal{Z}_i$ is independent for each constraint and can be computed separately.
-The advantage of this formulation is that we can choose $D(\vq)$ such that the new constraint set~$\cZ$ becomes simple to compute, and the function~$D(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations; however, the drawback is that we move the non-convexity to the primal cost function, i.e., in the update for $\vq$ in \eqref{eq:admm-mod-update-q}.
-
-We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for traditional path planning constraints (\Cref{sec:velocity-constraint}-\Cref{sec:waypoint-constraint}), co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:ellipsoid-point}-\Cref{eq:region_ellipsoid_constraint}).
+
+We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for security constraints including co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:ellipsoid-point}-\Cref{eq:region_ellipsoid_constraint}).
 The latter are based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
-
-\subsection{Velocity constraints}\label{sec:velocity-constraint}
-  The movement of each agent is constrained by a maximum velocity defined as the distance in any direction over a single discrete time step.
-We define the function $D(\vq)$ to return the velocity vectors for the $i$-th agent at time step $j$, and constrain its result to a sphere.
-
-  \begin{constraint}[Velocity constraint]
-\begin{align}
-     D_{ij}(\vq) &= q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\},\\
-\label{eq:velocity_constraint}
-   \sZ_{ij} &=\bigl\{\vz \mid \norm{\vz} \leq v_{max}\bigr\},\\
-   \Pi_{\sZ_{ij}}(\vz)&=\begin{cases}
-   v_{\max}\frac{\vz}{\norm{\vz}} \textrm{ if } \norm{\vz}>v_{\max},\\
-   \vz\textrm{ otherwise.}
-   \end{cases}
-\end{align}
-\end{constraint}
-
-\subsection{Convex polygonal obstacles collision constraints} \label{sec:obstacle-constraint}
-
-We use convex polygons to model regions defined by solid obstacles and forbidden regions that cannot be entered by agents.
-The convex region $\cP$ is defined using a collection of $l$ hyperplanes $n_{k} q = m_{k}$, where $n_k$ is the normal vector pointing toward the outside of the obstacle and $m_k$ is the scalar offset defining the $k$-th hyperplane.
-The distance between a single waypoint $q_{ij}$ and the $k$th hyperplane $d_{k}(q_{ij},\cP)$ is defined as:
-\begin{equation}
-    d_{k}(q_{ij},\cP)= p_{ij}\transpose n_k - m_k.
-\end{equation}
-We define the function $D(\vq)$ to return the maximum distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, and  constraint $z$ to be a non-negative scalar.
+Formulation of traditional path planning constraints like velocity constraints, convex obstacle constraints can be found in \cite{yang2020multi}.
+
+% \subsection{Velocity constraints}\label{sec:velocity-constraint}
+% We constraint for the movement of each agent by a maximum velocity defined as the distance in any direction over a single discrete time step.
+The function $D(\vq)$ returns the velocity vectors for the $i$-th agent at each time step $j$, and constrain its result to a sphere.
+% \begin{constraint}[Velocity constraint]
+% \begin{align}
+%      D_{ij}(\vq) &= q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\},\\
+% \label{eq:velocity_constraint}
+%    \sZ_{ij} &=\bigl\{\vz \mid \norm{\vz} \leq v_{max}\bigr\},\\
+%    \Pi_{\sZ_{ij}}(\vz)&=\begin{cases}
+%    v_{\max}\frac{\vz}{\norm{\vz}} \textrm{ if } \norm{\vz}>v_{\max},\\
+%    \vz\textrm{ otherwise.}
+%    \end{cases}
+% \end{align}
+% \end{constraint}
+
+% \subsection{Convex polygonal obstacles collision constraints} \label{sec:obstacle-constraint}
+% We use convex polygons $\cP$ to model regions  that cannot be entered by agents (solid obstacles and forbidden regions).
+$\cP$ is defined using a collection of $l$ hyperplanes $n_{k}\transpose q = m_{k}$, where $n_k$ is the normal vector pointing toward the outside of the obstacle and $m_k$ is the scalar offset defining the $k$-th hyperplane.We define the function $D(\vq)$ to return the maximum distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, and  constraint $z$ to be a non-negative scalar.
 This constraint is applied to all $q_{ij} \in \vq$.
 
-\begin{constraint}[Obstacle constraint]
-\begin{align}
-     	D(q_{ij}) &= \max_{k=1,\dots,l} (d_{k}(q_{ij},\cP)),\\
-\label{eq:obstacle_constraint}
-  \sZ &= \{z \mid z \geq 0 \},\\
-   \Pi_\sZ(z) & = \begin{cases}
-   0 & \textrm{if} \quad z < 0,\\
-   z  & \textrm{otherwise.}
-   \end{cases} \label{eq:zoneConstraintProjection}
-\end{align}
-\end{constraint}
-
-The motivating idea for \eqref{eq:obstacle_constraint} and \eqref{eq:zoneConstraintProjection} is to identify waypoints within a specific region and project them to the closest boundary.
-Non-convex obstacles can be handled by the union of (possibly overlapping) convex obstacles.
-By using outward-pointing normals, this method can also serve to constrain the robots within a designated workspace region.
-
-\subsection{Waypoints with flexible deadlines}\label{sec:waypoint-constraint}
-Security-related constraints often necessitate that a robot reaches a specified location at a particular time.
+% Non-convex obstacles can be handled by a union of (possibly overlapping) convex obstacles.
+And by using outward-pointing normals for $n_k$, this method can also serve to constrain the robots within a designated workspace region.
+% \begin{constraint}[Obstacle constraint]
+% \begin{align}
+%      	D(q_{ij}) &= \max_{k=1,\dots,l} (d_{k}(q_{ij},\cP)),\\
+% \label{eq:obstacle_constraint}
+%   \sZ &= \{z \mid z \geq 0 \},\\
+%    \Pi_\sZ(z) & = \begin{cases}
+%    0 & \textrm{if} \quad z < 0,\\
+%    z  & \textrm{otherwise.}
+%    \end{cases} \label{eq:zoneConstraintProjection}
+% \end{align}
+% where $d_{k}(q_{ij},\cP)= p_{ij}\transpose n_k - m_k$ returns the distance between a single waypoint $q_{ij}$ and the $k$th hyperplane .
+% \end{constraint}
+% %The motivating idea for \eqref{eq:obstacle_constraint} and \eqref{eq:zoneConstraintProjection} is to identify waypoints within a specific region and project them to the closest boundary.
+
+% \subsection{Waypoints with flexible deadlines}\label{sec:waypoint-constraint}
+% Security-related constraints often necessitate that a robot reaches a specified location at a particular time.
 We assume that robot $i$ is tasked with reaching a given point $p$ within a radius of $d_{max}$ at some time instant $j$ within a predefined time window $[t_1,t_2]$, leading to the following:
 
-\begin{constraint}[Waypoint constraint]
-\begin{align}
-     	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),\\
-\label{eq:waypoint_constraint}
-  \sZ &= \{z \mid z < z_{max} \},\\
-   \Pi_\sZ(z) & = \min(z, d_{max}),
-\end{align}
-where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
-\end{constraint}
-
- Note that this function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
-%\rtron{Give example application here, and include application of ADMM without the security constraints, but highlighting a path that would break the security}
-\zyang{plot new simpler example, add collision avoidance}
-
-%\subsection{Secure Multi-robot path planning using co-observation and reachability constraints}
+% \begin{constraint}[Waypoint constraint]
+% \begin{align}
+%      	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),\\
+% \label{eq:waypoint_constraint}
+%   \sZ &= \{z \mid z < z_{max} \},\\
+%    \Pi_\sZ(z) & = \min(z, d_{max}),
+% \end{align}
+% where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
+% \end{constraint}
+
+% This function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
+
 \subsection{Co-observation schedule constraint}\label{sec:co-observation-constraint}
@@
 \end{constraint}
-
 The locations $q_{aj}$ and $q_{bj}$ where the co-observation is performed are computed as part of the optimization.
@@
 \subsection{Definition of ellipsoidal reachability regions}\label{sec:reachability}
-  In this section, we define  \emph{ellipsoidal reachability regions} based on pairs of locations on a trajectory, and a transformation of such region in axis-aligned form.
-These definitions will be used to define different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon), their projections, and differentials in subsequent sections.
-  %differentiable map to transform such region in a canonical axis-aligned form where the operator $\Pi_\zeta$ and its differential can be obtained; these operators are then extended to the general case via the aforementioned transform.
-The overall goal is to define the functions $D(q)$, its differential, and the operator $\Pi_\zeta$ for \emph{ellipsoidal reachability regions} with respect to the forbidden regions that can then be
-  Together with \Cref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide our security guarantees.
+In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form.
+Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections.
+Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}
-    \caption{The ellipse showcases the reachability region.
-The black line is the planned trajectory of a robot, $q_1$ and $q_2$ are two locations this robot are expected at given time $t_1$ and $t_2$, dashed line is a possible trajectory if the robot is compromised after reaching $q_1$.
+    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}}
+    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}}
+
+    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth, trim = 0.3cm 1cm 0.3cm 1cm, clip]{Ellipse2line_V2}}
+    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth,trim = 0cm 1cm 0.3cm 0.5cm, clip]{Ellipse2safezone_V2}}
+
+    \caption{ \Cref{fig:EllipseConstraintExample} showcases the ellipsodial reachability region.
+Black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations the robot are expected at given time $t_1$ and $t_2$, dashed lines show possible trajectory of a compromised robot during unobserved period.
 Axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
-}
-    \label{fig:EllipseConstraintExample}
+    In \Cref{fig:Ellipse-to-point}, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$. 
+    In \Cref{fig:Ellipse-to-plane}, the projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.
+    In \Cref{fig:Ellipse-to-safezone}, this constraint is simplified to either a plane-ellipse constraint $D_{1}$ or a point-ellipse constraint $D_{2}$.}
+    \label{fig:Reachability_full}
   \end{figure}
@@
 We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.
-The reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}; the difference between the two is due to the discretization of the trajectory, and the fact that $\cE$ does not consider the presence of obstacles.
+This reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}.
 
@@
 
-\subsubsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
-To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$.
-
-The canonical frame $\cF_\cE$ is defined with the origin at the ellipsoid's center, and the first axis aligned with the foci \Cref{fig:EllipseConstraintExample} .
-We perform this transformation in a differentiable manner, with the two foci serving as waypoints for a robot.
+\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
+To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, and perform this transformation in a differentiable manner with respect to the two foci serving as waypoints for a robot.
+The canonical frame $\cF_\cE$ is defined with the origin at the ellipsoid's center, and the first axis aligned with the foci \Cref{fig:EllipseConstraintExample}.
+
+For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the transformation \eqref{eq:transformations}.
 We parametrize the transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we refer to as $R$ and $o$, respectively.
@@
 \end{proof}
-For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the transformation \eqref{eq:transformations}.
-
-We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon.
-For each one, our goal is to define the function $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$ that can be incorporated in the ADMM optimization (\ref{eq:ADMMSetConstraint_modified}).
+
+We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon which is is done by defining $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$.
 
 \subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
-\zyang{change this to a circle by adding radius to projection?}
 As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
@@
 where $\cE^{c}$ is the set complement of region $\cE$.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}
-\caption{Point-ellipsoid constraint, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$.}
-\label{fig:Ellipse-to-point}
-\end{center}
-\end{figure}
 
@@
 \subsection{Plane-ellipsoid reachability constraint}\label{sec:ellipsoide-plane}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth, trim = 0.3cm 1cm 0.3cm 1cm, clip]{Ellipse2line_V2}
-\caption{Plane-ellipse constraint.
-Projected a ellipsoid to one side of a plane.
-The projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.}
-\label{fig:Ellipse-to-plane}
-\end{center}
-\end{figure}
 
@@
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth,trim = 0cm 1cm 0.3cm 0.5cm, clip]{Ellipse2safezone_V2}
-\caption{Polygon-ellipse constraint. This constraint is simplified to either a plane-ellipse constraint $D_{1}$ or a point-ellipse constraint $D_{2}$.}
-\label{fig:Ellipse-to-safezone}
-\end{center}
-\end{figure}
-
 For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
@@
 where $D_{seg}$ are the constraint functions for each line segment used to define convex polygon region.
-ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in section \ref{sec:obstacle-constraint}) to prevent cases where the ellipse is a subset of the region.
-
-\subsection{Secured planning results and limitation}
-In this section, we apply our ADMM path planning algorithm to an instance of a map exploration problem (Figure~\ref{fig:ADMM-example-application}), and test the algorithm in both simulations and an experimental testbed.
-The environment to be explored, with three agents, is a $10m\times10m$ region and two forbidden regions \emph{Zone 2, 3} which is shown in Fig.\ref{fig:Grid-example-application}.We assume that the robots can meaningfully collect information on the underlying vector field for data locations no further than $3m$.
+ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
+
+\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
+
+In this section, we apply the newly introduced security constraints to a map exploration problem, illustrated in \Cref{fig:example-application}.
+The algorithm is tested in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
+The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$.
+All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent.
+%robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}).
+%We apply the new security constraints on the map exploration problem shown in \Cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed.
+The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}.
 The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.
 
-We utilize the APMAPF solver introduced in \cite{wardega2019resilience} to generate a MAPF plan with co-observation schedule on a grid-world application (Fig.\ref{fig:Grid-example-application}) and transform the result to a continuous configuration space, under the map exploration tasks.
+We employ the APMAPF solver from \cite{wardega2019resilience} to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
+This result serves as the initial trajectory input for the ADMM solver.
+This obtained plan is then transformed to a continuous configuration space, addressing map exploration tasks.
+Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions.
+Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions.
+It's important to note that the secured attack-proof solution is initially infeasible in the continues setting, unless additional checkpoints (e.g., stationary security cameras) are incorporated (additional task added for agent 3 to visit the \emph{checkpoint} at time $8$).
+Further solutions to avoid these checkpoints are discussed in \Cref{sec:cross-trajectory}.
+
+The simulation result, shown in Fig.~\ref{fig:ReachabilitySimulation}, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3.
+Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots.
+The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable.
+All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.
+
+%As depicted in Fig.\ref{fig:Grid-example-application}, no explicit tasks are assigned besides the start and goal locations.
+Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
+This result serves as the initial trajectory input for the ADMM solver.
+Considering this schedule, reachability for all agents in-between scheduled co-observations is constrained and kept away from the forbidden regions.
+% It's important to note that additional checkpoints (e.g., stationary security cameras) need to be incorporated to generate an attack-proof solution.
+Further solutions to avoid these checkpoints are discussed in \Cref{sec:cross-trajectory}.
+
+%We utilize the APMAPF solver introduced in \cite{wardega2019resilience} to generate a MAPF plan with co-observation schedule on a grid-world application (Fig.\ref{fig:Grid-example-application}) and transform the result to a continuous configuration space, under the map exploration tasks.
 All robots have the task of collecting sensor information on the underlying vector field, with agent 3 having an additional task to visit the \emph{checkpoint} at time $8$.
-Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:ADMM-example-application}).
+Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:SecurityBreak}).
 We first set up an co-observation schedules considering two forbidden regions using the APMAPF algorithm, and add reachability constraints ensure a empty intersection between all robots' reachability regions between co-observations and forbidden regions.
 
-As shown in Fig.\ref{fig:Grid-example-application}, no task has been assigned to the agent besides the start and goal location.
+%As shown in Fig.\ref{fig:Grid-example-application}, no task has been assigned to the agent besides the start and goal location.
 Agent 1 and 2 need to meet at time 8 and 14, whereas agent 2 and 3 need to meet at time 18.
@@
 
-Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained.
+%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained.
 Notice that additional checkpoint (i.e.
@@
 Additional solutions to avoid these checkpoints will be discussed in \Cref{sec:cross-trajectory}.
-
-The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}.
+%The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}.
 The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3.
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.6\linewidth]{FinalResult}
-\caption{Simulation result for map exploration task. Reachability regions are shown as black ellipses in the result. Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones}
+  \includegraphics[width=0.6\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}
+  \caption{Securd result using co-observation and reachability constraints.}
 \label{fig:ReachabilitySimulation}
@@
 
+% \begin{figure}[htbp]
+% \centering
+% %\subfloat[Unsecured optimal trajectory\label{fig:SecurityBreak}]{\includegraphics[width=0.47\linewidth, trim =1cm 2cm 1cm 2cm, clip]{SecurityBreak}}
+% \subfloat[Secured trajectory\label{fig:ReachabilitySimulation}]{\includegraphics[width=0.6\linewidth]{FinalResult}}
+
+% \caption{ is the securd result with co-observation and reachability constraints.}
+% \label{fig:2_ADMM_result}
+% \end{figure}
+
 \subsubsection{Limitations}\label{sec:reachability-discussion}
-Our solution shows that planning with reachability and co-observation is a promising approach to enhance the security of multi-agent systems.
+Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.
+However, two primary challenges need to be addressed.
+Firstly, achieving a co-observation and reachability-secured plan may not always be feasible when robots are separated by obstacles or forbidden regions, making it impossible for them to establish co-observation schedules or find a reachability-secured path.
+For example, Agent 3 in Figure \ref{fig:ReachabilitySimulation} required an additional security checkpoint to create secured reachability areas.
+Secondly, meeting security requirements may impact overall system performance, as illustrated by the comparison between Figure \ref{fig:SecurityBreak} and \ref{fig:ReachabilitySimulation}.
+The introduction of security constraints led to the top left corner being unexplored by any robots.
+This trade-off between security and system performance is particularly significant given that system performance plays a crucial role in the decision to employ multi-agent systems.
+These challenges are addressed in Chapter \ref{sec:cross-trajectory} to ensure the effective use of planning with reachability and co-observation in securing multi-agent systems.
+
+%Our solution shows that planning with reachability and co-observation is a promising approach to enhance the security of multi-agent systems.
 However, two main challenges have been identified in \cite{wardega2023hola}.
@@
 Agent 3 in the Figure \ref{fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas.
-Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:ADMM-example-application} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
+Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:SecurityBreak} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
 This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
@@
 \section{Cross-trajectory co-observation planning}\label{sec:cross-trajectory}
-
-To address the feasibility and performance trade-offs of the ADMM problem discussed in \Cref{sec:reachability-discussion}, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams (as shown in \Cref{fig:cross-traj-comparison-set}).
+To address the feasibility and performance trade-offs, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
 These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
-
-%\rtronhl{Move to discussion}{In this section, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.}
-
 \subsection{Problem overview}
-
-To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map), we first use planner (in this paper, an ADMM-based planner introduced in \Cref{sec:ADMM-planning} is used, but other planners are applicable) to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints.
+%To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map),
+We start with an unsecured MRS trajectory with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ (the ADMM-based planner in \Cref{sec:ADMM-planning} without security constraints is used, but other planners are applicable).
 Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
-Instead of having the number of robot equal to the number of routes $n_p$, in this section, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
-\zyang{refrased}Tasking at least one robot to adhere to the reference trajectory to fulfill essential tasks, we capitalize on the presence of additional $n_p-n$ robots to enhance security.
-These additional robots are initialized to focus are on performing co-observations within their respective sub-teams and whenever necessary, they are designed to deviate from their original sub-team's route and joining teams requiring heightened attention (i.e.
-travelling near forbidden regions) and providing necessary co-observations.
-We refer to the new type of co-observations as \emph{cross-trajectory co-observations}.
-The objective of this section is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.
-
-To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
-Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires co-observation to achieve security as described in \Cref{rmk:revised-security}.
-The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.
+Introducing redundant robots into the MRS, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
+To ensure the fulfillment of essential tasks, at least one robot is assigned to adhere to the reference trajectory.
+The remaining redundant $n_p-n$ robots are strategically utilized to enhance security.
+These robots focus on co-observations either within their respective sub-teams, or when necessary, deviate and join another sub-team to provide necessary co-observations.
+The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation} that the resulting MRS plan meet the security in \Cref{rmk:revised-security} while minimizing the number of additional robots required.
+
+We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ represent key locations requiring co-observation (as required by \Cref{rmk:revised-security}), and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist.
+Inspired by \cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph.
+This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
+
+%To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$.
+Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires co-observation as described in \Cref{rmk:revised-security}.
+Edges $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.
 Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general Mixed-Intiger Linear Programming techniques as specialized solver.
@@
 \subsection{Rapidly-exploring Random Trees}
-In this section, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a single starting location to multiple destination points (i.e., the reference trajectories of other robots, in our method).
-
+To find edges between different nominal trajectories, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a waypoint on one trajectory to multiple destination points (i.e., reference trajectories of other sub-teams, in our method).
 As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree.
@@
 
- Notice that our objective is not to optimize specific constraints but to ascertain the existence of feasible paths.
-While the ADMM based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, the RRT* algorithm is better suited to the problem in this section.
-RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
+Our objective here is to ascertain the existence of feasible paths instead of optimize specific tasks.
+While the ADMM based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
 
@@
 
-In this section, we describe in detail how we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
+In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
 
 \subsubsection{Checkpoints}\label{sec:security-checkpoint}
-Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$.
+Let $q_p\in\real{nT}$ represent the trajectory for sub-team $p$ with time horizon $T$, where $q_{p}(t) \in \real{n}$ denotes the reference waypoint at time $t$.
+We identify checkpoints within $q_p$ that require co-observations for securty, as outlined in \Cref{rmk:revised-security}.
+Checkpoint $v_{pi}=(q_{pi},t_{i})$ signifies a required co-observation for sub-team $p$, defined by a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
+For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
+To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden areas.
+This requirement can be formally stated as:
+
+%Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$.
 We locate checkpoints among $q_p$ that requires co-observations in order for the MRS trajectories to be secured as defined in \Cref{rmk:revised-security}.
-Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$.
+Checkpoint $v_{pi}=(q_{pi},t_{i})$ representing a required co-observation for sub-team $p$ composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$.
 For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, and let $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
+To secure the reference trajectory for one sub-team, the reachability region between consecutive checkpoints can not intersect with any of the forbidden areas.
+This requirement can be formally stated as:
 
 \begin{remark}
-A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas.
-The requirement can be formally stated as $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$.
+A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas.
 \end{remark}
 
-A heuristic approach is provided (\Cref{alg:checkpoint-gen}) to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose) with a toy example shown in Figure \ref{fig:checkpoint-generate}.
+A heuristic approach is provided (\Cref{alg:checkpoint-gen}) to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
+%with a toy example shown in Figure \ref{fig:checkpoint-generate}.
 
@@
   \State $v_{p0} \gets (q_{p}(0),0)$; $v_{pT} \gets (q_{p}(T),T)$
-  \State $V_p = \{v_{p0}, v_{pT}\}$
+  \State $V_{p} = \{v_{p0}, v_{pT}\}$
   \State $t_0 \gets 0$; $t_1 \gets T$
@@
     \EndWhile
-    \State $V_p\gets V_p\union v_{pf}$
+    \State $V_{p}\gets V_{p}\union v_{pf}$
     \While{$\mathcal{E}(q_{p}(t_{1}-j),q_{p}(t_{1}),t_{1}-j,t_{1}) \intersect F = \emptyset$ and $t_0+i \geq t_1-j$}
@@
     \If {$t_0+i \neq t_1-j$}
-    \State $V_p\gets V_p\union v_{pb}$
+    \State $V_{p}\gets V_{p}\union v_{pb}$
     \EndIf
@@
 
-\begin{figure}
-	\centering
-    \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_1}}
-    \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_2}}
-    \caption{Checkpoint generation example}\label{fig:checkpoint-generate}
-\end{figure}
+% \begin{figure}
+% 	\centering
+%     \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_1}}
+%     \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_2}}
+%     \caption{Checkpoint generation example}\label{fig:checkpoint-generate}
+% \end{figure}
 
 \subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
-In order for co-observation to happen cross different trajectories at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories allowing robots deviate from one sub-team to approach, perform co-observation with robots on a different sub-team.
-\begin{remark}
+To enable co-observation cross different sub-team at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories, allowing robots deviate from one sub-team to perform co-observation with a different sub-team.
+%\begin{remark}
+
 Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$.
-The cross-trajectory edges must also adhere to the reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden areas can occur during trajectory switches.
-\end{remark}
+The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden areas can occur during trajectory switches.
+%\end{remark}
 
@@
     \centering
-  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth]{two_edges}}\hspace{2mm}
+  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth]{two_edges}}
   \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth]{security_graph}}
@@
 
-To find cross-trajectory edges, we first find trees of feasible paths using \rrtstar{} and position information alone; we then prune these trees by considering time constraints (that consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints) and ellipsoidal reachability constraints.
-
-We search for feasible paths between each security checkpoint and all other trajectories (ignoring, for the moment, any timing constraint), as shown in \Cref{fig:RRT*}
-More precisely, after a fixed number of  iterations, \rrtstar{}  finds all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and all the waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on any reference trajectory for a different sub-team $\cI_{r}$.
-We then calculate the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path.
-In order to see if the deviating robot is able to catch up and merge with the corresponding sub-team, we define two types of nodes.
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.6\linewidth]{RRT_example_new}
-\caption{All viable path found from a waypoint to all reference trajectories of other sub-teams.}
-\label{fig:RRT*}
-  \end{center}
-\end{figure}
+%We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone through \rrtstar{} (ignoring, for the moment, any timing constraint).
+Then, we prune these trees by considering time constraints (that consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints) and ellipsoidal reachability constraints.
+
+We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone (ignoring, for the moment, any timing constraint). 
+More precisely, through \rrtstar{}, we find all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and all the waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on any reference trajectory for a different sub-team $\cI_{r}$.
+Then, to prune these trees, we consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints.
+This is done by calculating the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path.
+Two types of connecting nodes can be found.
 
@@
 
-For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $(q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
+For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $v_{ea} = (q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
 %$t^{a}_r$ is designated as the \emph{earliest arrival time}.
@@
 
-For each trajectory $r\neq p$, we define the \emph{latest departure node} $(q_{r}(t^{d}_r),t^{d}_r)$ as the departure node characterized by the maximum $t^{d}_r$ discovered.
+For each trajectory $r\neq p$, we define the \emph{latest departure node} $v_{ld}=(q_{r}(t^{d}_r),t^{d}_r)$ as the departure node characterized by the maximum $t^{d}_r$ discovered.
 % $t^{d}_r$ is designated as the \emph{latest departure time}.
@@
 
-For each $v_{p} \in V_{p}$ found through \Cref{alg:checkpoint-gen}, we add all the latest departure and earliest arrival nodes to $V_{q}$, and their corresponding paths as cross-trajectory edges $E_{q}$.
+For each $v_{p} \in V_{p}$ found through \Cref{alg:checkpoint-gen}, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$.
 Examples are shown in Figure \ref{fig:two-edges}.
@@
 %With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-We arrange all $V_{p}=\union_p \{v^0_{p}, \dots ,v^T_{p}\}$ found in \Cref{sec:security-checkpoint,sec:cross-traj-edges} in ascending order of $t_{v^i_{p}}$.
+We arrange all $V_q =\union_p \{v^0_{p}, \dots ,v^T_{p}\}$ found in \Cref{sec:security-checkpoint,sec:cross-traj-edges} in ascending order of $t_{v^i_{p}}$.
 We then add to $E_q$ the \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ obtained by connecting all consecutive checkpoints $v^i_{p}\in V_q$ with the checkpoints $v^{i+1}_{p}$ that follow them in their original trajectories.
@@
 \subsection{Co-observation planning problem}
-In this section, we describe in detail how to formulate the cross-trajectory planning problem as a network multi-flow problem, and solve it using mixed-integer linear programs (MILP).
-We assume that $n_p$ \emph{reference robots} are dedicated (one in each sub-team) to follow the reference trajectory.
-The goal of this section is to minimize the number and plan the routes of the $n-n_p$  additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations.
+In this section, we formulate the cross-trajectory planning problem as a network multi-flow problem, and solve it using mixed-integer linear programs (MILP).
+We assume that $n_p$ robots are dedicated (one in each sub-team) to follow the reference trajectory (named \emph{reference robots}).
+The goal is to plan the routes of the $n-n_p$ additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations, and potentially minimize the number of ross-trajectory robots needed.
 
 \begin{remark}
-Note that we assign fixed roles to reference robots for convenience in explaining the multi-flow formulation.
-In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
+Note that we assign fixed roles to robots for convenience in explaining the multi-flow formulation.
+In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory.
+% (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
 \end{remark}
 
-To formulate the planning problem as a network multi-flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
+To formulate the problem as a network multi-flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
 The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is a \emph{virtual source} node, and $v^{-}$ is a \emph{virtual sink} node.
-The edges of the new graph are defined as $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$, i.e., we add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$.
-
-Our goal is to find a path in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
-The path of a robot $k$ can be represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
-In order to perform co-observations as required by the security introduced in \Cref{rmk:revised-security}, reference robots must be seen by at least one cross-trajectory robot at every checkpoint.
-Thus, the planning problem can be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $V_{p}$ is included in at least one path in $F$.
-Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
+We add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$.
+The edges of the new graph are defined as $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$.
+
+%The goal is to find paths in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
+The path of a robot $k$ all starts from $v^{+}$ and ends at $v^{-}$, and are represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
+The planning problem can be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \Cref{rmk:revised-security}).
+%Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
 
@@
 
-Finally, edges from the virtual source and to the virtual sink should have zero cost, to allow robots to automatically get assigned to the starting point that is most convenient for the overall solution.
+Finally, edges from the virtual source and to the virtual sink should have zero cost, to allow robots to automatically get assigned to the starting point that is most convenient for the overall solution (lower cost when taking cross-trajectory edges).
 These requirements are achieved with the weights for edges $(v_{i},v_{j})\in E$ defined as:
@@
 
-With the formulation above, the planning problem can be written as an optimization problem, where the optimization cost balances between the co-observation performance and total number of flows (cross-trajectory robots) needed:
+With the formulation, the planning problem is written as an optimization problem, where the optimization cost balances between the co-observation performance and total number of flows (cross-trajectory robots) needed:
  \begin{subequations} \label{eq:flow-coverage-problem}
@@
 
-The first term in the cost \ref{eq:flow-cost} is total outgoing flow from the source $v^{+}$ while the second term is the total cost of all flows representing the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
-The constraint \eqref{eq:FlowBalanceConstraint} is the flow conservation constraint, which ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
-The constratin \eqref{eq:FlowCoverage} is the flow coverage constraints, which ensures that all security checkpoints $ \{V^{s}_{p}\}$ have been visited by at least one flow (robot).
-Since the security graph $G_{q}$ is acyclic, this problem is in complexity class $P$, and can be solved in polynominal time \cite{1702662}.
+The first term in the cost \eqref{eq:flow-cost} represents the total number of robot used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
+\eqref{eq:FlowBalanceConstraint} is the flow conservation constraint to ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
+\eqref{eq:FlowCoverage} is the flow coverage constraints to ensures that all security checkpoints $ \{V^{s}_{p}\}$ have been visited co-observed.
+The security graph $G_{q}$ is acyclic, making this problem in complexity class $P$, thus, can be solved in polynominal time \cite{1702662}.
 
@@
 Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
-Additionally, for a fixed number of robots $\cK \geq N_{p}$, it is possible to have a subset of flows $F_{e} \in F$ that is empty, i.e.
+%Additionally, for a fixed number of robots $\cK \geq N_{p}$,
+It is possible for the resulting flows to have a subset of flows $F_{e} \in F$ that is empty, i.e.
 $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$; these flow will not increase the cost and can be discarded from the solution.
@@
 An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.
-
-In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
+In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
 
@@
 \subsection{Result and simulation}
-In this section, we test the proposed method starting from the results in Figure \ref{fig:trajectories-more-constraint}, where three trajectories are provided for the map exploration task with no security related constraints (co-observation schedule and reachability).
-We use the same environment and dynamic setup, where we have a $10m\times10m$ task space, two forbidden regions (two rectangles in  \ref{fig:trajectories-more-constraint}) and robots with a max velocity of $0.5m/dt$.
-
-\begin{figure}[t]
-\rtron{Collect these four figures into a single figure. Maybe plot the graphs rotated 90 degrees so that "time" goes from left to right, and to use the space more efficiently.}
-\begin{center}
-\includegraphics[width=0.4\linewidth]{graph_flow_result_3}
-\caption{Security Graph and result for 3 flows}
-\label{fig:security-graph-3-flow}
-\end{center}
+
+\begin{figure}
+  \centering
+  \subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.47\linewidth, trim = 4cm 2cm 4cm 2cm,valign=c]{old_result}}
+  \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 4cm 1cm 4cm 1cm,valign=c]{old_result_graph.png}}
+  \caption{\Cref{fig:previous_result_plan} showcase an unsecured 4-robot map exploration task.
+The cross-trajectory co-observation plan is shown as dotted arrors on top of the original plan in \Cref{fig:previous_result_plan}.
+The checkpoint graph and resulting flows are shown in \Cref{fig:previous_result_graph}.}
+  \label{fig:3-team-ctco}
 \end{figure}
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth]{3_flow_result}
-\caption{Result of 3 surveillance agents' plan in workspace}
-\label{fig:workspace-3-flow}
-\end{center}
+We first test the proposed method for the example application in \Cref{fig:example-application,fig:ReachabilitySimulation}, using the same setup in \Cref{sec:ADMM-simulation}.
+Using the parameters $w_{c}=10$, $w_{t}=1$ and $\rho = 0.01$, the result returns a total of $\cK=3$ surveillance robots with cross-trajectory plan shown in \Cref{fig:3-team-ctco}.
+%In \Cref{fig:previous_result_grap}, each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
+The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph \Cref{fig:previous_result_graph}, where each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
+The planning result in the workspace is shown in \Cref{fig:previous_result_plan} as dash-dotted arrows with the same color used for each flow in \Cref{fig:previous_result_graph}.
+Compared with the result in \Cref{fig:ReachabilitySimulation}, it is easy to see that there is a significant improvement in map coverage in \Cref{fig:previous_result_plan}.
+At the same time, unsecured deviations to the forbidden regions of robots are secured through cross-trajectory observations.
+
+The problem shows no solution for $\cK\leq 2$.
+For cases $\cK=3$, problem return the optimal result as shown in \Cref{fig:Cross-trajectory-result}.
+If we further increase $\cK>3$, we do not get a better result; instead, the planner will return four flows with the rest $\cK-3$ flows empty.
+
+We then test the proposed method for a 4-team and 7-team case with result shown in Figure \ref{fig:Cross-trajectory-result}, where four trajectories are provided for a map exploration task with no security related constraints (co-observation schedule and reachability).
+We have a $10m\times10m$ task space, three forbidden regions (rectangle regions in \Cref{fig:Result-plan}) and robots with a max velocity of $0.5m/dt$.
+
+\begin{figure}
+  \centering
+  %\subfloat[Unsecured plan\label{fig:unsecured-plan}]{\includegraphics[width=0.31\linewidth, trim = 3cm 2cm 3cm 2cm, clip,valign=c]{SecurityBreak}}
+  \subfloat[4-agent co-observation plan\label{fig:Result-plan}]{\includegraphics[width=0.47\linewidth,trim = 4cm 2cm 4cm 2cm, clip,valign=c]{Traj_result}}
+  %\subfloat[Graph flow result\label{fig:result-graph}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{Graph_result}}
+  \subfloat[7-agent co-observation plan\label{fig:Result-plan-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 2cm 4cm 2cm, clip,valign=c]{7-team-plan.png}}
+  %\subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
+  \caption{Cross-trajectory co-observation result of a 4 sub-teams task (\Cref{fig:Result-plan}) and a 7 sub-teams task \Cref{fig:Result-plan-7-team}}\label{fig:Cross-trajectory-result}
 \end{figure}
 
-We start by adding a total of $\cK=3$ surveillance robots into the workspace using the parameters $w_{c}=10$, $w_{t}=1$ and $\rho = 0.01$.
-The three trajectories are transformed into the graph $G$ shown in Figure \ref{fig:security-graph-3-flow}, where the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
-Vertices in each column belong to the same trajectory, and edges across different columns are cross-trajectory edges.
-
-The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph.
-The planning result in the workspace is shown in \Cref{fig:workspace-3-flow} as dash-dotted arrows with the same color used for each flow in \Cref{fig:security-graph-3-flow}.
-This plan is not ideal in terms of our security criteria since co-observations happens between the same pair of surveillance robot and sub-team for the majority of the time with only three cross-trajectory edges that are covered.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.4\linewidth]{graph_flow_result_4}
-\caption{Security Graph and result for 4 flows.}
-\label{fig:security-graph-4-flow}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth]{4_flow_result}
-\caption{Result of 3 surveillance agents' plan in work space.}
-\label{fig:workspace-4-flow}
-\end{center}
-\end{figure}
-
-For the case where $\cK=4$, the results are shown in Figure \ref{fig:security-graph-4-flow}-\ref{fig:workspace-4-flow}.
-With one additional robot added, there is a significant increase in the total cross-trajectory edges covered, and sub-teams performs co-observation with different robots during the task period.
-If we further increase $\cK>4$, we do not get a better result; instead, the planner will generate four flows with the rest $\cK-4$ flows empty. \rtron{Reference Fig. 15}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\linewidth]{nflow_vs_cost}
-\caption{Plan reach optimality when $\cK=4$, further increase of $\cK$ does not increase the cost of objectives.}
-\label{fig:flow-n-vs-cost}
-\end{center}
-\end{figure}
-
-\rtron{Run the ADMM planner again on Fig. 14, and show that you get a $\Phi(q)$ (i.e., better mapping).}
+% \begin{figure}
+%   \centering
+%    \subfloat[Cross-trajectory co-observation plan\label{fig:Result-plan-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 2cm 4cm 2cm, clip,valign=c]{7-team-plan.png}}
+%   \subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
+%   \caption{Cross-trajectory co-observation result of a 7 sub-teams task.}\label{fig:Cross-trajectory-result-7}
+% \end{figure}
 
 \section{Summary}\label{sec:summary}
-In this paper, we provide a method to enhance the security of a multi-robot system without sacrificing the performance.
-This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories.
-For cases where the secured planning problem is infeasible (or where the user desires to improve the optimality of the trajectories), we model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories.
-We have shown that the co-observation planning problem across different trajectories can be transformed into a multi-flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.
-
-While this work consider only the high-level path planning, the assignment of the duties within the sub-team can performed dynamically making it more difficult for attackers to successfully plan and execute attacks.
+This paper introduces security measures to protect Multi-Robot Systems (MRS) from plan-deviation attacks.
+By incorporating co-observation schedules and ensuring the reachability of robots during unobserved periods avoid forbidden regions, we present a secured trajectory optimized for specific scenarios.
+This guarantees that any deviations into forbidden regions will break the schedule and trigger detection.
+In scenarios where a secured plan is infeasible or better task performance is needed, we propose the use of redundant robots for cross-trajectory co-observations.
+We formulate the co-observation plan for the redundant robots by solving a network flow coverage problem on the checkpoint graph generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
+
+However, given the time-sensitive nature of co-observation and the need for close proximity, collision avoidance during co-observation planning becomes crucial.
+Future work will focus on integrating collision avoidance into the planning phase.
+Additionally, dynamic assignment of duties within sub-teams will be explored, making it more challenging for attackers to plan and execute successful attacks.
+Real-time task assignment and control will be a key area of investigation
+
+%In this paper, we provide methods to enhance the security of a MRS against plan-deviation attacks.
+First, by introducing co-observation schedule and keeping reachability region during unobserved periods away from the forbidden regions, we provide an secured trajectory optimized for certain scenarios with guarantees that any deviations to forbidden regions will for sure break the schedule and get detected.
+Additionally, for scenarios that requires better task performance or when a secured plan is not feasible, we introduce redundant robots to performs cross-trajectory co-observations that can provide any unsecured MRS trajectories with the same security guarantee.
+
+%As co-observation is time-sensitive and requires robots to be in close proximity, it is important to consider the possible collision during co-observation planning.
+The main future work will focus on including collision avoidance in the planning phase.
+Additionally, the assignment of the duties within the sub-team can performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.
+This makes realtime task assignment and control another topic worth looking into.
 
 \appendix
-
 \subsection{Proof of proposition \ref{prop:HProperty}} \label{proof:HProperty}
@@
 
-    Inserting $HH\transpose=I$ in (\ref{equ:H_dot original}), and using \ref{eq:asymmetric to cross}, we finally have
+    Inserting $HH\transpose=I$ in (\ref{equ:H_dot original}), we have
     \begin{equation}

### 2024-01-25 paper.tex
final version

@@
 \end{abstract}
+\begin{IEEEkeywords}
+  Multi-robot system, cyber-physical attack, trajectory optimization, reachability analysis, network flow
+\end{IEEEkeywords}
 
@@
 However, such plans are not guaranteed to exist, and the secured trajectory always come at the cost of overall system performance.
-In this paper, we also address these feasibility and optimality challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}.
+As an extension of the previous works \cite{yang2020multi,yang2021multi}, we also address the feasibility and optimality challenges.
 For a MRS with unsecured optimal trajectorys (without security constraints), we introduce redundant robots and formed into \emph{sub-teams} with the original ones.

### 2024-01-25 paper/1.py

@@ -1,368 +1,0 @@
-import math
-import pygame as pg
-import numpy as np
-from pygame.math import Vector2
-import time
-import quadprog
-import cvxopt
-from cvxopt import matrix
-import matplotlib.pyplot as plt
-
-#r0 is the radius of the task region
-#(x0, y0) is the position of the center of the task region
-r0=50
-x0=250
-y0=250
-
-# 1,2 represents the obstalces
-r1=25
-x1=250
-y1=320
-
-r2=30
-x2=180
-y2=325
-
-r4=40
-x4=320
-y4=350
-
-r5=40
-x5=120
-y5=200
-
-#3 represent the connectivity circle
-r3=400
-x3=250
-y3=350
-
-#t_max is the deadline
-#v_max is the maximum velocity
-t_max=20
-v_max=15
-
-#w1, w2 are weights, see equation (14) in the paper
-w1=0.1
-w2=0.5
-w3=0.01
-
-# beta is a weight, see equation (12)
-beta=0.06
-
-#lamda is a weight for adjusting the angle speed
-lamda=0.3
-
-def theta_fi(theta,fi):
-    if abs(theta-fi)<=180:
-        result=theta-fi
-    elif theta>fi:
-        result=theta-fi-360
-    else:
-        result=theta-fi+360
-    return result
-
-#convex optimization solver
-def cvxopt_solve_qp(P, q, G=None, h=None, A=None, b=None):
-    P = .5 * (P + P.T)  # make sure P is symmetric
-    args = [matrix(P), matrix(q)]
-    if G is not None:
-        args.extend([matrix(G), matrix(h)])
-        if A is not None:
-            args.extend([matrix(A), matrix(b)])
-    sol = cvxopt.solvers.qp(*args)
-    if 'optimal' not in sol['status']:
-        return None
-    return numpy.array(sol['x']).reshape((P.shape[1],))
-
-#quadratic program solver
-def quadprog_solve_qp(P, q, G=None, h=None, A=None, b=None):
-    qp_G = .5 * (P + P.T)   # make sure P is symmetric
-    qp_a = -q
-    if A is not None:
-        qp_C = -numpy.vstack([A, G]).T
-        qp_b = -numpy.hstack([b, h])
-        meq = A.shape[0]
-    else:  # no equality constraint
-        qp_C = -G.T
-        qp_b = -h
-        meq = 0
[…]

### 2024-01-25 paper/move.py

@@ -1,292 +1,0 @@
-import math
-import pygame as pg
-import numpy as np
-from pygame.math import Vector2
-import time
-import quadprog
-import cvxopt
-from cvxopt import matrix
-import matplotlib.pyplot as plt
-
-#r0 is the radius of the task region
-#(x0, y0) is the position of the center of the task region
-r0=50
-x0=250
-y0=250
-
-#t_max is the deadline
-#v_max is the maximum velocity
-t_max=15
-v_max=15
-
-#w1, w2 are weights, see equation (14) in the paper
-w1=0.5
-w2=10
-
-# beta is a weight, see equation (12)
-beta=0.03
-
-#lamda is a weight for adjusting the angle speed
-lamda=0.3
-
-def theta_fi(theta,fi):
-    if abs(theta-fi)<=180:
-        result=theta-fi
-    elif theta>fi:
-        result=theta-fi-360
-    else:
-        result=theta-fi+360
-    return result
-
-#convex optimization solver
-def cvxopt_solve_qp(P, q, G=None, h=None, A=None, b=None):
-    P = .5 * (P + P.T)  # make sure P is symmetric
-    args = [matrix(P), matrix(q)]
-    if G is not None:
-        args.extend([matrix(G), matrix(h)])
-        if A is not None:
-            args.extend([matrix(A), matrix(b)])
-    sol = cvxopt.solvers.qp(*args)
-    if 'optimal' not in sol['status']:
-        return None
-    return numpy.array(sol['x']).reshape((P.shape[1],))
-
-#quadratic program solver
-def quadprog_solve_qp(P, q, G=None, h=None, A=None, b=None):
-    qp_G = .5 * (P + P.T)   # make sure P is symmetric
-    qp_a = -q
-    if A is not None:
-        qp_C = -numpy.vstack([A, G]).T
-        qp_b = -numpy.hstack([b, h])
-        meq = A.shape[0]
-    else:  # no equality constraint
-        qp_C = -G.T
-        qp_b = -h
-        meq = 0
-    return quadprog.solve_qp(qp_G, qp_a, qp_C, qp_b, meq)[0]
-
-def distance(x):
-    return ((x[0]-x0)**2+(x[1]-y0)**2)**0.5-r0
-
-class Player(pg.sprite.Sprite):
-    # initialize the robot as a circle
-    def __init__(self, pos=(420, 420), rgb=(50,120,180),width=0):
-        super(Player, self).__init__()
[…]

### 2024-01-25 paper/obstacle.py

@@ -1,302 +1,0 @@
-import math
-import pygame as pg
-import numpy as np
-from pygame.math import Vector2
-import time
-import quadprog
-import matplotlib.pyplot as plt
-import random
-
-r0=50
-x0=250
-y0=250
-
-r_d=30
-x_d=220
-y_d=350
-
-t_max=23
-v_max=15
-d=40
-deta=2
-
-w1=0.2
-w2=8
-w3=0.01
-
-w_alpha=0.03
-
-labda=1.5
-
-def theta_fi(theta,fi):
-    if abs(theta-fi)<=180:
-        result=theta-fi
-    elif theta>fi:
-        result=theta-fi-360
-    else:
-        result=theta-fi+360
-    return result
-
-def quadprog_solve_qp(P, q, G=None, h=None, A=None, b=None):
-    qp_G = .5 * (P + P.T)   # make sure P is symmetric
-    qp_a = -q
-    if A is not None:
-        qp_C = -numpy.vstack([A, G]).T
-        qp_b = -numpy.hstack([b, h])
-        meq = A.shape[0]
-    else:  # no equality constraint
-        qp_C = -G.T
-        qp_b = -h
-        meq = 0
-    return quadprog.solve_qp(qp_G, qp_a, qp_C, qp_b, meq)[0]
-
-def distance(x):
-    return ((x[0]-x0)**2+(x[1]-y0)**2)**0.5-r0
-
-class Player(pg.sprite.Sprite):
-
-    def __init__(self, pos=(420, 420), rgb=(50,120,180),width=0, radius=15, obs=False):
-        super(Player, self).__init__()
-        self.image = pg.Surface((radius*2, radius*2), pg.SRCALPHA)
-        pg.draw.circle(self.image, rgb, (radius,radius),radius,width)
-        if obs==False:
-            pg.draw.circle(self.image,(150,30,30),(26,15),4,width)
-        self.original_image = self.image
-        self.rect = self.image.get_rect(center=pos)
-        self.position = Vector2(pos)
-        self.direction = Vector2(1, 0)  # A unit vector pointing rightward.
-        self.speed = 0
-        self.angle_speed = 0
-        self.angle = 0
-        self.alpha=0
-        self.weight=0
-        self.alphadot=0
-
-    def h_c(self,t):
-        return t_max-t-distance(self.position)/v_max  
-    
-    def h_d(self, pos):
-        return ((self.position[0]- pos[0])**2+(self.position[1]- pos[1])**2)**0.5-r_d
-
[…]

### 2024-11-12 paper.tex

@@
 %In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
+\rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}
 
@@
 \begin{definition}\label{def:secured-plan}
-  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensures that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
 \end{definition}
@@
 
+\rtron{Clarify when we use bold symbols. Make sure this is used consistently.}
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
@@
 %The set $\Omega$ includes traditional constraints like bounded velocity, convex obstacles, waypoints to reach with deadlines, in addition to security constraints including co-observation and reachability constraints.
+\rtron{Relate to Fig. 2}
 \end{example}
@@
 
-  \begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u$ as
+  \begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$).
+\rtron{Add the explicit dependency of $u$, $u'$ on $\nu_F,\nu_E$.} Define the normalized vector $u$ as
     \begin{equation}
@@
   \end{definition}
-  Here $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
+  Here $H$ is a rotation mapping \rtronhl{Remove hats}{$\hat{\nu_\cF}$ to $\hat{\nu_\cE}$}, as shown by the following.
   \begin{proposition}\label{prop:HProperty}
@@
 after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed number of iterations.
+\rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}
 
@@
 \begin{definition}\label{sec:ellipsoidal definition}
-	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the workspace such that there exist a trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$.
+	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \rtronhl{free configuration space}{workspace} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}.
 \end{definition}
@@
 \begin{definition}\label{def:Reachability}
-	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{maq}}{2}(t_2-t_1)$.
+	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
 \end{definition}
@@
 We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.
-This reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}.
+This reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition} \rtron{because the ellipsoid does not consider obstacles}.
 
@@
 \subsection{Problem overview}
+\rtron{Move definition of Checkpoint somewhere in this section}
 %To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map),
@@
 Let $q_p\in\real{nT}$ represent the trajectory for sub-team $p$ with time horizon $T$, where $q_{p}(t) \in \real{n}$ denotes the reference waypoint at time $t$.
-We identify checkpoints within $q_p$ that require co-observations for securty, as outlined in \Cref{rmk:revised-security}.
+\rtronhl{We need to put this in a formal definition of checkpoint that appears the first time we mention them}{We identify checkpoints within $q_p$ that require co-observations for securty,} as outlined in \Cref{rmk:revised-security}.
 Checkpoint $v_{pi}=(q_{pi},t_{i})$ signifies a required co-observation for sub-team $p$, defined by a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
@@
 \begin{algorithm}
-  \caption{Secure Checkpoint Generate for sub-team $p$}\label{alg:checkpoint-gen}
+  \caption{Secure Checkpoint Generation for a Sub-Team $p$}\label{alg:checkpoint-gen}
   \begin{algorithmic}
@@
   \end{algorithmic}
+  \rtron{It is probably better to substitute this with a description in words. If you want to keep the pseudocode, move it to the appendix.}
   \end{algorithm}

### 2024-11-12 paper.tex
Updates from Overleaf

@@
 \end{abstract}
-\begin{IEEEkeywords}
-  Multi-robot system, cyber-physical attack, trajectory optimization, reachability analysis, network flow
-\end{IEEEkeywords}
 
@@
 However, such plans are not guaranteed to exist, and the secured trajectory always come at the cost of overall system performance.
-As an extension of the previous works \cite{yang2020multi,yang2021multi}, we also address the feasibility and optimality challenges.
+In this paper, we also address these feasibility and optimality challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}.
 For a MRS with unsecured optimal trajectorys (without security constraints), we introduce redundant robots and formed into \emph{sub-teams} with the original ones.

### 2024-11-12 paper.tex
update local

--- 2024-01-25 paper.tex
@@
 To enhance system resilience and tackle feasibility challenges, we also introduce \emph{sub-teams}.
-These cohesive units replace individual robot assignments along each route, enabling redundant robots to deviate for co-observations across sub-teams, securing multiple trajectories without requiring modifications.
-The planning of cross-trajectory co-observations that maintain security against plan-deviation attacks is sloved by formulating the multi-flow problem on unsecured MRS trajectories.
+These cohesive units replace individual robot assignments along each route, enabling redundant robots to deviate for co-observations across different trajectories, securing multiple sub-teams without requiring modifications.
+We formulate the \emph{cross-trajectory co-observation} plan by solving a network flow coverage problem on the checkpoint graph generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
 We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
@@
 The rest of this paper is organized as follows.
-In \Cref{sec:ADMM-planning}, we begin by providing an overview of the ADMM-based optimal trajectory solver.
-We then introduced the ellipsoidal reachability region and formulate it to different constraints with respect to different type of forbidden regions.
-In \Cref{sec:cross-trajectory}, we proposed the formulation of sub-teams and introduced the planning algorithm of the cross-trajectory co-observation planning problem.
-Finally, in \Cref{sec:summary}, we provide summary of this paper.
-
-\section{Multi-robot trajectory planning with co-observation}\label{sec:ADMM-planning}
-
-In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
-This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
-\begin{definition}\label{def:secured-plan}
-  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
-\end{definition}
-
+\Cref{sec:ADMM-planning}provide an overview of the ADMM-based optimal trajectory solver and introduce the security constraints including co-observation constraints and ellipsoidal reachability constraints.
+\Cref{sec:cross-trajectory} introduced the enhanced security planning algorithm by the incorporation of redundant robots for cross-trajectory co-observation.
+\Cref{sec:summary} concludes this article.
+
+\section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
+
+%In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
+%This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
 %This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
@@
 
-\begin{figure}
-     \centering
-     \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-     \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{SecurityBreak}}
-     \caption{Trajectory design of an example map exploration task for a three-robot system with start locations and destinations fixed.
-Task are planned in a $8 \times 8$ grid world.
-Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones.
-Fig~\ref{fig:Grid-example-application} shows the planned trajectory with co-observation schedule in grid-world.
-Fig~\ref{fig:SecurityBreak} shows the unsecured trajectory design in continuous world optimized with respect to a map exploration task where Zone 1 and 2 are considered together as one obstacle.
-A potential path that could break the security by entering region 1 is highlighted in dashline.}
-     \label{fig:example-application}
- \end{figure}
+To incorporate the security against malicious deviations (through co-observation and reachability analysis) as constraints in the optimal trajectory planning problem, we define the security as:
+\begin{definition}\label{def:secured-plan}
+  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\end{definition}
 
@@
 The latter are based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
-Formulation of traditional path planning constraints like velocity constraints, convex obstacle constraints can be found in \cite{yang2020multi}.
+Formulation of traditional path planning constraints like velocity constraints, convex obstacle constraints can be found in \cite{yang2020multi}, thus are omitted in this paper.
 
@@
 
-In this section, we apply the newly introduced security constraints to a map exploration problem, illustrated in \Cref{fig:example-application}.
-The algorithm is tested in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
+We test the newly introduced security constraints to a map exploration problem, illustrated in \Cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
 The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$.
-All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent.
+%All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent.
 %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}).
@@
 
-We employ the APMAPF solver from \cite{wardega2019resilience} to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
-Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
+We employ the APMAPF solver (\cite{wardega2019resilience}) to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+%Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
 This result serves as the initial trajectory input for the ADMM solver.
@@
 All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task.
-
 \begin{figure}
-\begin{center}
-  \includegraphics[width=0.6\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}
-  \caption{Securd result using co-observation and reachability constraints.}
-\label{fig:ReachabilitySimulation}
-\end{center}  
+  \centering
+  \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{SecurityBreak}}
+
+  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.6\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}}
+  \caption{Trajectory design of an example map exploration task for a three-robot system with start locations and destinations fixed.
+Task are planned in a $8 \times 8$ grid world.
+Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones.
+\Cref{fig:Grid-example-application} shows the planned trajectory with co-observation schedule in grid-world.
+\Cref{fig:SecurityBreak} shows the unsecured trajectory design in continuous world optimized with respect to a map exploration task where Zone 1 and 2 are considered together as one obstacle.
+A potential path that could break the security by entering region 1 is highlighted in dashline.
+\Cref{fig:ReachabilitySimulation} shows the secured trajectory with the incorporation of co-observation and reachability constraints.}
+  \label{fig:example-application}
 \end{figure}
+
+% \begin{figure}
+% \begin{center}
+%   \includegraphics[width=0.6\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}
+%   \caption{Securd result using co-observation and reachability constraints.}
+% \label{fig:ReachabilitySimulation}
+% \end{center}  
+% \end{figure}
 
@@
 \section{Summary}\label{sec:summary}
-This paper introduces security measures to protect Multi-Robot Systems (MRS) from plan-deviation attacks.
-By incorporating co-observation schedules and ensuring the reachability of robots during unobserved periods avoid forbidden regions, we present a secured trajectory optimized for specific scenarios.
-This guarantees that any deviations into forbidden regions will break the schedule and trigger detection.
-In scenarios where a secured plan is infeasible or better task performance is needed, we propose the use of redundant robots for cross-trajectory co-observations.
-We formulate the co-observation plan for the redundant robots by solving a network flow coverage problem on the checkpoint graph generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
-
+
+This paper introduces security measures for protecting Multi-Robot Systems (MRS) from plan-deviation attacks.
+We establish a mutual observation schedule to ensure that any deviations into forbidden regions break the schedule, triggering detection.
+Co-observation requirements and reachability analysis are incorporated into the trajectory planning phase, formulated as constraints for the optimal problem.
+In scenarios where a secured plan is infeasible or enhanced task performance is necessary, we propose using redundant robots for cross-trajectory co-observations, offering the same security guarantees against plan-deviation attacks.
+However, the time-sensitive and proximity-dependent nature of co-observation necessitates a focus on collision avoidance during planning.
+Future work will integrate collision avoidance and explore dynamic duty assignments within sub-teams, increasing the challenge for potential attackers.
+
+%This paper introduces security measures to protect Multi-Robot Systems (MRS) from plan-deviation attacks by setting up mutual obversation schedule to guarangee that any deviations into forbidden regions will break the schedule and trigger detection.
+We incorporate the co-observation requirements and reachability analysis into the trajectory planning phase and formulate them as constraints for the optimal problem.
+In scenarios where a secured plan is infeasible or better task performance is needed, we propose the use of redundant robots for cross-trajectory co-observations, providing the same security guarantees against plan-deviation attacks.
 However, given the time-sensitive nature of co-observation and the need for close proximity, collision avoidance during co-observation planning becomes crucial.
@@
 Additionally, dynamic assignment of duties within sub-teams will be explored, making it more challenging for attackers to plan and execute successful attacks.
-Real-time task assignment and control will be a key area of investigation
 

### 2024-11-12 paper.tex

@@
 
-%In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
-%This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
+In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
+This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
+\begin{definition}\label{def:secured-plan}
+  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensures that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\end{definition}
+
 %This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
 
+\rtron{Clarify when we use bold symbols. Make sure this is used consistently.}
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.

### 2024-11-12 paper.tex
update

@@
 This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
-Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
+We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
 We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.
@@
 %In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
-\rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}
-
-In \Cref{sec:ADMM-planning}, we incorporate reachability constraints to increase overall security Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
+% \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}
+
+Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
 One typical approach involves computing an over-approximation of the reachable space for checking safety properities.
@@
 In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
+With the incorporation of an additional security measure that provides two known states instead of one, we can simplify the reachable region using an ellipsoidal over-approximation.
+The use of ellipsoids is well-established in path planning methods due to their smooth, continuous boundaries and defined geometric properties, which enable efficient optimization.
+Notable examples include Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}.
+Both IRIS and SFC utilize ellipsoids to approximate the free configuration space; however, these methods are designed to plan specific, safe paths with dynamics in mind, rather than mapping all possible outcomes.
+This focus limits their applicability in security contexts.
+Our work is inspired by another ellipsoidal application, the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the framework of the $\mathtt{RRT^*}$ path planning algorithm.
 
@@
 
+\noindent\myparagraph{Notation} 
+In this paper, we use non-bold symbols like to denote single-agent states (i.e.
+$q_{ij}$), while bold symbols represent aggregated states involving multiple agents (i.e.
+$\vq$).
+\zyang{does regular scalers need mention?}
+
 \section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
@@
 %This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
-
-\rtron{Clarify when we use bold symbols. Make sure this is used consistently.}
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
@@
 {\small
-\bibliographystyle{unsrt}
+\bibliographystyle{IEEEtran}
 \bibliography{ADMM_planning,ACC,tron,ziqi,reachability}

### 2024-11-20 paper.tex
update

--- 2024-11-12 paper.tex
@@
 \usepackage[export]{adjustbox} 
-\usepackage{cleveref}
+\usepackage[capitalise]{cleveref}
+\usepackage{xcolor}
+\newcommand{\new}[1]{\textcolor{blue}{#1}}
+\newcommand{\news}{\color{blue}}
 \graphicspath{{Figs/}}
@@
 \begin{abstract}
-This paper addresses security challenges in multi-robot systems (MRS) where adversaries may compromise robot control, risking unauthorized access to forbidden areas.
+This paper addresses security challenges in multi-robot systems (MRS) where adversaries may compromise robot control, risking unauthorized access to forbidden regions.
 We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability} constraints for enhanced security.
@@
 A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}.
-Extanding the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in the ADMM-based trajectory optimization solver to accomodate for more flexible objectives.
+Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in the ADMM-based trajectory optimization solver to accomodate for more flexible objectives.
 In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
 This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
-Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
+We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
 We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.
@@
 As an extension of the previous works \cite{yang2020multi,yang2021multi}, we also address the feasibility and optimality challenges.
-For a MRS with unsecured optimal trajectorys (without security constraints), we introduce redundant robots and formed into \emph{sub-teams} with the original ones.
+For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.
 These redundant robots are assigned the task of establishing additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
@@
 %In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
-
-In \Cref{sec:ADMM-planning}, we incorporate reachability constraints to increase overall security Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
+% \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}
+
+% Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
 One typical approach involves computing an over-approximation of the reachable space for checking safety properities.
@@
 In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
+\new{Reachability analysis is essential for security and safety verification in cyber-physical systems (CPSs) \cite{gueguen2009safety, ding2020secure}, often involving an over-approximation of reachable space to verify safety properties.
+Geometric methods like zonotopes and ellipsoids are commonly used to compactly enclose reachability sets \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}.
+For online safety assessments against cyber attacks, \cite{kwon2017reachability} computed reachable CPS states under attacks and compared them with a safe region based on state estimation.
+By incorporating an additional security measure that provides two secured states, the reachability region in our work is over-approximated using ellipsoids.
+This is inspired by the ellipsoidal \emph{heuristic sampling domain} in \cite{gammell2014informed} for the $\mathtt{RRT^*}$ algorithm to simplify the sampling region between start and goal locations.
+Ellipsoids are also used in other path planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}.
+Differs from reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximate the safe collision-free space rather than addressing security applications.}
 
 \noindent\myparagraph{Paper contributions} 
-In this paper, two main contributions have been presented.
-
+Two main contributions have been presented. 
 \begin{itemize}
-  \item We present an innovative method to integrate reachability analysis into the ADMM-based optimal trajectory solver for multi-robot systems, preventing attackers from executing undetected attacks by simultaneously entering forbidden areas and adhering to co-observation schedules.
+  \item We present an innovative method to integrate reachability analysis into the ADMM-based optimal trajectory solver for multi-robot systems, preventing attackers from executing undetected attacks by simultaneously entering forbidden regions and adhering to co-observation schedules.
   \item We introduce additional robots to form \emph{sub-teams} for both intra-sub-team and cross-sub-team co-observations.
@@
 
-\noindent\myparagraph{Paper Outline}
 The rest of this paper is organized as follows.
-\Cref{sec:ADMM-planning}provide an overview of the ADMM-based optimal trajectory solver and introduce the security constraints including co-observation constraints and ellipsoidal reachability constraints.
-\Cref{sec:cross-trajectory} introduced the enhanced security planning algorithm by the incorporation of redundant robots for cross-trajectory co-observation.
+\Cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and introduce the security constraints.
+\Cref{sec:cross-trajectory} introduces the enhanced security planning algorithm through cross-trajectory co-observation.
 \Cref{sec:summary} concludes this article.
 
+\noindent\myparagraph{Notation} 
+In this paper, we use non-bold symbols like to denote single-agent states (e.g.
+$q_{ij}$) and scalers, while bold symbols represent aggregated states involving single robot or multiple robots (e.g.
+$\vq$).
+
 \section{Secured Multi-robot trajectory planning}\label{sec:ADMM-planning}
-
-%In this section, we design an inter-robot observation plan (co-observation schedule) to ensures that, during the task period, robots are constantly in proximity to one another according to a schedule, in order to observe and detect potential hazardous behaviors.
-%This is achieved by keeping the potential region that the robots can possibly reach between each consecutive co-observations away from the forbidden regions. 
-%This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.
-
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
@@
 
-\begin{example} 
-Robots are tasked to navigate, collecting sensory data to construct a corresponding map for the slowly-varying field, denoted as $\vx$, of an unknown environment (see Figure~\ref{fig:SecurityBreak}).
+\begin{example}\label{example:map_exploration}
+\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\Cref{fig:illustration}).
+The space is modeled as grid points, each with an associated value.
+The goal is to find paths that minimize uncertainty in reconstructing the field.
+Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot.
+The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}
+
+% Robots are tasked to navigate, collecting sensory data of an unknown task space to map a slowly-varying field, denoted as $\vx$, (see Figure~\ref{fig:SecurityBreak}).
 The map comprises points of interest arranged on a grid, each associated with a slowly-changing value.
@@
 The optimization objective $\varPhi(\vq)$ is written as the maximum uncertainty $\max_j P_{j}$ (detailed formulation can be found in \cite{yang2020multi}).
-%The set $\Omega$ includes traditional constraints like bounded velocity, convex obstacles, waypoints to reach with deadlines, in addition to security constraints including co-observation and reachability constraints.
 \end{example}
+\begin{figure}
+  \centering
+  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
+  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+  \caption{\new{Grid world example of a task planned in a $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
+\end{figure}
+
+% \begin{definition}\label{def:secured-plan}
+%   A multi-robot trajectory plan is secure again plan-deviation attacks if it ensures that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+% \end{definition}
 
@@
 Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.
-
- \subsubsection{Householder rotations}\label{sec:householder}
-  We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \Cref{sec:reachability,sec:ellipse-region-constraint}.
-This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}.
-With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection).
-We call our version of the operator a \emph{Householder rotation}.
-In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.
-
-  \begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u$ as
-    \begin{equation}
-      u'=\nu_\cF+\nu_\cE,\quad u =\frac{u'}{\norm{u'}}.
-    \end{equation}
-    The \emph{Householder rotation} $H(\nu_\cF,\nu_\cE)$ is defined as
-    \begin{equation}\label{eq:H definition}
-      H(\nu_\cF,\nu_\cE) = 2 u u\transpose-I.
-    \end{equation}
-  \end{definition}
-  Here $H$ is a rotation mapping $\hat{\nu_\cF}$ to $\hat{\nu_\cE}$, as shown by the following.
-  \begin{proposition}\label{prop:HProperty}
-    The matrix $H$ has the following properties:
-    \begin{enumerate}
-    \item It is a rotation, i.e.
-      \begin{enumerate}
-      \item\label{it:orthonormality} $H\transpose H=I$;
-      \item\label{it:determinant} $\det(H)=1$.
-      \end{enumerate}
-    \item\label{it:transformation} $\nu_\cE=H \nu_\cF$.
-    \end{enumerate}
-  \end{proposition}
-  \begin{proof}
-  	See Appendix \ref{proof:HProperty}.
-  \end{proof}
-
-  We compute the differential of $H$ implicitly using its definition \eqref{equ:dt_to_dx}.
-We use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
-  \begin{equation}
-    \bmat{v_1\\v_2\\v_3}_\times= \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
-  \end{equation}
-  such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. %One can verify by direct computation the following property:
-  %\begin{equation}\label{eq:asymmetric to cross}
-  %  wv\transpose-vw\transpose=\cross{\cross{v}w}.
-  %\end{equation}
-  \begin{proposition}\label{prop:Hderivitive}
-    Let $\nu_\cF(t)$ represent a parametric curve. Then
-    \begin{equation}
-      \dot{H}=H\cross{-2M\dot{\nu}_{\cF}},
-    \end{equation}
-    where the matrix $M\in\real{3\times3}$ is given by
-    \begin{equation}
-      M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\norm{u'} \norm{\nu_\cF}}.
-    \end{equation}
-  \end{proposition}
-  \begin{proof}
-  	See Appendix \ref{proof:Hderivitive}.
-  \end{proof}
 
@@
 	\begin{align}
-		\label{eq:admm-mod-update-q}\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\\
+		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
 		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
-		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1},
+		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
 	\end{align}
@@
 after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed number of iterations.
+{\news
+\begin{remark}
+In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via nonlinear optimization solver like \emph{fmincon}, while \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solution.
+\end{remark}
+}
+% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}
 
@@
 \begin{definition}\label{sec:ellipsoidal definition}
-	The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the workspace such that there exist a trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$.
+  \new{Let robot $i$ be observed at location $q_{1}$ at time $t_1$ and location $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory $\tilde\vq = \{\tilde{q}_{it_1}\dots \tilde{q}_{it_2}\}$ where $\tilde{q}_{it'} = q'$ for some $t_1 \leq t' \leq t_2$, and $\tilde\vq$ satisfies the velocity constraint $d(\tilde q_t,\tilde q_{t+1})\leq v_{max}$, where $d(\cdot,\cdot)$ represents the distance between two points}
+	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}.
 \end{definition}
@@
 
-    \caption{ \Cref{fig:EllipseConstraintExample} showcases the ellipsodial reachability region.
+    \caption{ \cref{fig:EllipseConstraintExample} showcases the ellipsodial reachability region.
 Black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations the robot are expected at given time $t_1$ and $t_2$, dashed lines show possible trajectory of a compromised robot during unobserved period.
 Axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
-    In \Cref{fig:Ellipse-to-point}, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$. 
-    In \Cref{fig:Ellipse-to-plane}, the projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.
-    In \Cref{fig:Ellipse-to-safezone}, this constraint is simplified to either a plane-ellipse constraint $D_{1}$ or a point-ellipse constraint $D_{2}$.}
+    In \cref{fig:Ellipse-to-point}, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$. 
+    In \cref{fig:Ellipse-to-plane}, the projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.
+    In \cref{fig:Ellipse-to-safezone}, this constraint is simplified to either a plane-ellipse constraint $D_{1}$ or a point-ellipse constraint $D_{2}$.}
     \label{fig:Reachability_full}
@@
 This reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}.
+\new{Notice that the ellipsoid does not consider obstacles}.
 
@@
 \subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
-To simplify the problem, we employ a canonical rigid body transformation that repositions the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, and perform this transformation in a differentiable manner with respect to the two foci serving as waypoints for a robot.
-The canonical frame $\cF_\cE$ is defined with the origin at the ellipsoid's center, and the first axis aligned with the foci \Cref{fig:EllipseConstraintExample}.
-
-For all reachability ellipsoid constraints, we first solve the problem in the canonical frame $\cF_{\cE}$, and transform the solutions to the global frame $\cF$ using the transformation \eqref{eq:transformations}.
-We parametrize the transformation from $\cF$ to $\cF_\cE$ using a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$, which, to simplify the notation, we refer to as $R$ and $o$, respectively.
-The transformation of a point from the frame $\cF_\cE$ to the frame $\cF$ and its inverse are given by the rigid body transformations:
+{\news To simplify the problem, we apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center and the first axis of $\cF_\cE$ aligns with the foci \Cref{fig:EllipseConstraintExample}.
+For all reachability ellipsoid constraints, we solve the problem in $\cF_\cE$ and transform the solutions back to $\cF$ using \eqref{eq:transformations}.
+The transformation and its inverse is parametrized by a rotation $R^\cF_\cE$ (denoted $R$) and a translation $o^\cF_\cE$ (denoted $o$) as:
 \begin{equation}\label{eq:transformations}
@@
 \end{equation}
-
-  We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
-  \begin{align}
-    \nu'_\cF&=q_2-q_1, & \nu_\cF &= \frac{\nu'_\cF}{\norm{\nu_\cF}}, & \nu_\cE&=[1,0,0]^T;
-  \end{align}
-  see Fig.\ref{fig:EllipseConstraintExample} for an illustration.
-Note that $\nu_\cE$ is constant while, for the sake of clarity, $\nu_{\cF}$ depends on $q_1,q_2$.
-From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation}, while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:
-  \begin{align} 
-    R&=H(\nu_\cF(q_1,q_2),\nu_\cE(q_1,q_2)), &o&=\frac{1}{2}(q_1+q_2).
-  \end{align}
-  To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. 
-  The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, with foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ defined as
-  \begin{align}
-    q^\cE_1=\bmat{c & 0 & 0}\transpose, && q^\cE_2=\bmat{-c & 0 & 0}\transpose,
-  \end{align}
-  and semi-axis distance $c=\frac{\norm{q_2-q_1}}{2}$.
-\begin{definition}
-  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
-  \begin{equation}\label{equ:standard-ellipse}
-    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
-  \end{equation}
-  where
-  \begin{equation}
-    Q = \diag(a^{-2},b^{-2},b^{-2}),
-  \end{equation}
-  and $b = \sqrt{a^2-c^2}$.
-  The ellipse parameters $a$, $b$ represent the lengths of the major axes.
-\end{definition}
-\begin{lemma}
-The original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
-   \begin{equation}\label{eq:ellpsoid from canonical}
-     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
-     \end{equation}
-\end{lemma}
-\begin{proof}
-    The claim follows by substituting  \eqref{eq:transformations} into \eqref{equ:standard-ellipse}, and from the definition of $R$ and $o$.
-\end{proof}
-
-We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon which is is done by defining $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$.
+where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is formed using \emph{Householder rotation} $H$ (a differentiable linear transformation used to represent rotation between two vectors, more details in \cref{sec:householder}), and $o =\frac{1}{2}(q_1+q_2)$.
+$\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$ represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively.
+To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e.
+$H(q_1,q_2)$.
+More details of this transformation is introduced in \cref{apx:transformation}.
+  % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
+  % \begin{align}
+  %   \nu_\cF &= \frac{q_2-q_1}{\norm{q_2-q_1}}, & \nu_\cE&=[1,0,0]^T;
+  % \end{align}
+  % \new{see Fig.\ref{fig:EllipseConstraintExample} for an illustration.
+Note that $\nu_{\cF}$ is a function of $q_1,q_2$ while $\nu_\cE$ is constant.
+From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation} (see \cref{sec:householder}), while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:}
+  % \begin{align} 
+  %   R&=H(\nu_\cF(q_1,q_2),\nu_\cE), &o&=\frac{1}{2}(q_1+q_2).
+  % \end{align}
+
+  Reachability constraints are formulated with respect to different types of forbidden regions a point, a plane, a segment, and a convex polygon.}
+  % We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon which is is done by defining $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$.
 
 \subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
-As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
+% As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
 The goal is to design the trajectory $q(t)$ such that $q_{avoid}\notin\mathcal{E}(q_1,q_2)$.
 This constraint can be written as,
-
+{\news For a forbidden region in the shape of a single point $q_{avoid}$ (\cref{fig:Ellipse-to-point}), the constraint is written as:}
 \begin{constraint}[Point-ellipsoid reachability constraint]
@@
 
-For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^n: \vn\transpose \Fframe{q} = d\}$ (as shown in Figure \ref{fig:Ellipse-to-plane}), the reachability constraint can be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, where,
-  \begin{equation}
-    \vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d.
-\end{equation}
-Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
-
-For every $\Eframe \cL(\Eframe{q})$, there always exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e.
-resulting in a unique intersection point), $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$  (\Cref{fig:Ellipse-to-plane}).
-And the intersection point can be written as:
+For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^m: \vn\transpose \Fframe{q} = d\}$ (as shown in~\cref{fig:Ellipse-to-plane}), the reachability constraint can be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, \new{with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.}
+% Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
+
+For every $\Eframe \cL(\Eframe{q})$, there exist two planes that are both parallel to $\cL$ and tangential to the ellipse (i.e.
+resulting in a unique intersection point \cref{fig:Ellipse-to-plane}), $\cL_1^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} =  d_{\cE t} \}$ and $\cL_2^{\cE} = \{\Eframe{q}\in\mathbb{R}^m: \vn_\cE \transpose \Eframe{q} = - d_{\cE t} \}$.
+The intersection point can be written as:
 \begin{equation}
@@
 where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$).
-
-We introduce the concept of a tangent interpolation point on the hyperplane to characterize the relationship between the plane and the ellipse.
+The concept of \emph{tangent interpolation point}s is introduced to characterize the relationship between the plane and the ellipsoid.
 
@@
 With these definitions, the constraint can be written as:
-
 \begin{constraint}[Plane-ellipsoid reachability constraint]
@@
 
-For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied. 
-Assume the segment on hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ has endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; then the segment can be defined as:
+% For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied.
+{\news As an intermediate step to consider polygon shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
+For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
 \begin{equation}
@@
 \end{equation}
-For cases, where the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
-red region in \Cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies between $\Eframe{p_{1}}$ and $\Eframe{p_{2r}}$), the constraint can be seen as a plane-ellipse constraint in \Cref{sec:ellipsoide-plane}.
+For cases that the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
+red region in \cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies between $\Eframe{p_{1}}$ and $\Eframe{p_{2r}}$), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}.
 Otherwise (i.e.
-brown region in \Cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies outside $\Eframe{p_{1}}$ and $\Eframe{p_{2b}}$), the constraint can be seen as a point-ellipse constraint in \Cref{sec:ellipsoid-point}.
+brown region in \cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies outside $\Eframe{p_{1}}$ and $\Eframe{p_{2b}}$), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.
 
@@
 \end{constraint}
-where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$ in \eqref{eq:point_ellipsoid_constraint}, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint with respect to frame $\Eframe {\cL}$ in \eqref{eq:plane_ellipsoid_constraint}.
+where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}.
+with respect to frame $\Eframe {\cL}$.
 
 \subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
-To keep an ellipse away from a convex polygon, first, we need to keep all segments of the hyperplanes outside the ellipse. Similar to \eqref{equ:ProjectPoint}, we define
+For reachability constraints with respect to a convex polygon, the first step is to keep all segments that defines the hyperplane outside the reachability ellipsoid.
+Similar to \eqref{equ:ProjectPoint}, we define
 \begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
@@
 \end{constraint}
-where $D_{seg}$ are the constraint functions for each line segment used to define convex polygon region.
-ADMM constraint~\ref{constraint:polygon-ellipsoid} needs to be supplemented with a convex obstacle constraint for the polygon (as introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
+where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region.
+This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e.
+keep foci waypoints outside the region, introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
 
@@
 
-We test the newly introduced security constraints to a map exploration problem, illustrated in \Cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
+We test the newly introduced security constraints to~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
 The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$.
@@
 
-We employ the APMAPF solver (\cite{wardega2019resilience}) to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+We employ the APMAPF solver \cite{wardega2019resilience} to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
 %Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
@@
   \centering
-  \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
   \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{SecurityBreak}}
-
-  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.6\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}}
-  \caption{Trajectory design of an example map exploration task for a three-robot system with start locations and destinations fixed.
-Task are planned in a $8 \times 8$ grid world.
+  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.45\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}}
+  \caption{Trajectory design of a map exploration task forthree-robot system based on result in grid world result~\Cref{fig:Grid-example-application}.
 Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones.
-\Cref{fig:Grid-example-application} shows the planned trajectory with co-observation schedule in grid-world.
 \Cref{fig:SecurityBreak} shows the unsecured trajectory design in continuous world optimized with respect to a map exploration task where Zone 1 and 2 are considered together as one obstacle.
@@
 Let $q_p\in\real{nT}$ represent the trajectory for sub-team $p$ with time horizon $T$, where $q_{p}(t) \in \real{n}$ denotes the reference waypoint at time $t$.
-We identify checkpoints within $q_p$ that require co-observations for securty, as outlined in \Cref{rmk:revised-security}.
+\rtronhl{We need to put this in a formal definition of checkpoint that appears the first time we mention them}{We identify checkpoints within $q_p$ that require co-observations for securty,} as outlined in \Cref{rmk:revised-security}.
 Checkpoint $v_{pi}=(q_{pi},t_{i})$ signifies a required co-observation for sub-team $p$, defined by a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
 For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
-To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden areas.
+To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
 This requirement can be formally stated as:
@@
 \begin{remark}
-A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas.
+A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
 \end{remark}
@@
 Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$.
-The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden areas can occur during trajectory switches.
+The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur during trajectory switches.
 %\end{remark}
@@
 \appendix
-\subsection{Proof of proposition \ref{prop:HProperty}} \label{proof:HProperty}
+{\news
+\subsection{Transformation of reachability ellipsoid to canonical frame}\label{apx:transformation}
+The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, with foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ defined as
+$q^\cE_1=\bmat{c & 0 & 0}\transpose, q^\cE_2=\bmat{-c & 0 & 0}\transpose$, and semi-axis distance $c=\frac{\norm{q_2-q_1}}{2}$.
+\begin{definition}
+  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
+  \begin{equation}\label{equ:standard-ellipse}
+    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
+  \end{equation}
+  where
+  \begin{equation}
+    Q = \diag(a^{-2},b^{-2},b^{-2}),
+  \end{equation}
+  and $b = \sqrt{a^2-c^2}$.
+  The ellipse parameters $a$, $b$ represent the lengths of the major axes.
+\end{definition}
+\begin{lemma}
+The original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
+   \begin{equation}\label{eq:ellpsoid from canonical}
+     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
+     \end{equation}
+\end{lemma}
+\begin{proof}
+    The claim follows by substituting  \eqref{eq:transformations} into \eqref{equ:standard-ellipse}, and from the definition of $R$ and $o$.
+\end{proof}
+\subsection{Householder rotations}\label{sec:householder}
+\new{We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \Cref{sec:reachability,sec:ellipse-region-constraint}.
+This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}.
+% With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection). 
+We call our version of the operator a \emph{Householder rotation}.
+In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.}
+
+\begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u = \frac{\nu_\cF+\nu_\cE}{\norm{\nu_\cF+\nu_\cE}}$,
+  % \begin{equation}
+  %   u=\nu_\cF+\nu_\cE,\quad u =\frac{u'}{\norm{u'}}.
+  % \end{equation}
+the \emph{Householder rotation} $H(\nu_\cF,\nu_\cE)$ is defined as
+  \begin{equation}\label{eq:H definition}
+    H(\nu_\cF,\nu_\cE) = 2 u u\transpose-I.
+  \end{equation}
+\end{definition}
+Here $H$ is a rotation mapping $\nu_\cF$ to $\nu_\cE$, as shown by the following.
+\begin{proposition}\label{prop:HProperty}
+  The matrix $H$ has the following properties:
+  \begin{enumerate}
+  \item It is a rotation, i.e.
+    \begin{enumerate}
+    \item\label{it:orthonormality} $H\transpose H=I$;
+    \item\label{it:determinant} $\det(H)=1$.
+    \end{enumerate}
+  \item\label{it:transformation} $\nu_\cE=H \nu_\cF$.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
   For subclaim~\ref{it:orthonormality}:
@@
 
-    For subclaim~\ref{it:determinant}, let $U=\bmat{u & u^\bot_{1},u^\bot_{2}}$, where $u^\bot_{1},u^\bot_{2}$ are two orthonormal vectors such that $I=UU\transpose=uu\transpose + u^\bot_{1}(u^\bot_{1})\transpose+u^\bot_{2}(u^\bot_{2})\transpose$; then, substituting $I$ in \eqref{eq:H definition}, we have that the eigenvalue decomposition of $H$ is given by
+  For subclaim~\ref{it:determinant}, let $U=\bmat{u & u^\bot_{1} & u^\bot_{2}}$, where $u^\bot_{1},u^\bot_{2}$ are two orthonormal vectors such that $I=UU\transpose=uu\transpose + u^\bot_{1}(u^\bot_{1})\transpose+u^\bot_{2}(u^\bot_{2})\transpose$; then, substituting $I$ in \eqref{eq:H definition}, we have that the eigenvalue decomposition of $H$ is given by
   \begin{equation}
@@
   \end{equation}
-
-\subsection{Proof or proposition \ref{prop:Hderivitive}} \label{proof:Hderivitive}
+\end{proof}
+We compute the differential of $H$ implicitly using its definition \eqref{equ:dt_to_dx}.
+We use the notation $\cross{v}:\real{3}\to\real{3\times 3}$ to denote the matrix representation of the cross product with the vector $v$, i.e.,
+\begin{equation}
+  \bmat{v_1\\v_2\\v_3}_\times= \bmat{0 & -v_3 &v_2\\v_3 & 0 & -v_1\\-v_2 & v_1 & 0},
+\end{equation}
+such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. %One can verify by direct computation the following property:
+%\begin{equation}\label{eq:asymmetric to cross}
+%  wv\transpose-vw\transpose=\cross{\cross{v}w}.
+%\end{equation}
+\begin{proposition}\label{prop:Hderivitive}
+  Let $\nu_\cF(t)$ represent a parametric curve. Then
+  \begin{equation}
+    \dot{H}=H\cross{-2M\dot{\nu}_{\cF}},
+  \end{equation}
+  where the matrix $M\in\real{3\times3}$ is given by
+  \begin{equation}
+    M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\norm{u'} \norm{\nu_\cF}}.
+  \end{equation}
+\end{proposition}
+\begin{proof}
     From the definition of $H$ in \eqref{eq:H definition}, we have
@@
     which is equivalent to the claim.
-
+  \end{proof}
+}
   \subsection{Proof of proposition \ref{prop:Ellipse2PointDiff}}\label{proof:Ellipse2PointDiff}

### 2024-11-22 paper.tex
update

@@
   \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
-  \caption{\new{Grid world example of a task planned in a $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
+  \caption{\new{(a) Grid world example of a task planned in a $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
 \end{figure}
@@
 
-We test the newly introduced security constraints to~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
+We test the newly introduced security constraints with~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
 The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$.
@@
 
-We employ the APMAPF solver \cite{wardega2019resilience} to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
-%Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
-This result serves as the initial trajectory input for the ADMM solver.
-This obtained plan is then transformed to a continuous configuration space, addressing map exploration tasks.
+We employ the APMAPF solver \cite{wardega2019resilience} on a 8 by 8 grid world with similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with additional task function targeting the map exploration task.
 Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions.
 Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions.
-It's important to note that the secured attack-proof solution is initially infeasible in the continues setting, unless additional checkpoints (e.g., stationary security cameras) are incorporated (additional task added for agent 3 to visit the \emph{checkpoint} at time $8$).
-Further solutions to avoid these checkpoints are discussed in \Cref{sec:cross-trajectory}.
+{\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space.
+In this cases, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids.
+Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated.
+For instance, in this scenario, we deploy a security camera as additional checkpoint to observe agent 3 at time $8$ to ensure security.}
 
@@
 \subsubsection{Limitations}\label{sec:reachability-discussion}
-Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.
-However, two primary challenges need to be addressed.
-Firstly, achieving a co-observation and reachability-secured plan may not always be feasible when robots are separated by obstacles or forbidden regions, making it impossible for them to establish co-observation schedules or find a reachability-secured path.
-For example, Agent 3 in Figure \ref{fig:ReachabilitySimulation} required an additional security checkpoint to create secured reachability areas.
-Secondly, meeting security requirements may impact overall system performance, as illustrated by the comparison between Figure \ref{fig:SecurityBreak} and \ref{fig:ReachabilitySimulation}.
-The introduction of security constraints led to the top left corner being unexplored by any robots.
-This trade-off between security and system performance is particularly significant given that system performance plays a crucial role in the decision to employ multi-agent systems.
-These challenges are addressed in Chapter \ref{sec:cross-trajectory} to ensure the effective use of planning with reachability and co-observation in securing multi-agent systems.
+Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.{\news However, two primary challenges need to be addressed.
+Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths.
+For example, agent 3 in~\cref{fig:ReachabilitySimulation} requires additional security measures to create secured reachability areas.
+Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~\cref{fig:SecurityBreak} and \cref{fig:ReachabilitySimulation}.
+The introduction of security constraints resulted in the top left corner remaining unexplored by any robots.
+This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments.
+These challenges are further addressed in \cref{sec:cross-trajectory}, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}
 

### 2024-11-25 paper.tex
update

@@
 A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}.
-Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in the ADMM-based trajectory optimization solver to accomodate for more flexible objectives.
+Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accomodate for more flexible objectives.
 In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
@@
 
-    \caption{\ref{fig:example-co-observation} Limited by the co-observation requirement, both red and blue robot follow the co-observation secured routes (solid lines) and abandon the optimal ones (dashed line).
-\ref{fig:example-cross-traj} Through cross-trajectory co-observations, the blue team sends one robot to follow the red team (solid blue line) and performs co-observation while having the rest of the robots following the optimal trajectory.}\label{fig:cross-traj-comparison-set}
+    \caption{{\news \ref{fig:example-plan-dev} Attacker deviate the red robot into forbidden region.\ref{fig:example-co-observation} Red and blue robot tasked to co-observe each other during task resulting a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
+\ref{fig:example-cross-traj} The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots following the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
 \end{figure}
@@
 maximum surveillance coverage, minimal energy cost).
-In constract to our work in \Cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}.
-Several optimization techniques like MIQP~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity, and to incorporate more complex non-convex constraints.
+In contrast to our work in \Cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}.
+Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity, and to incorporate more complex non-convex constraints.
 
@@
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
-We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space.
-For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$.
-The overall goal is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis).
-Formally:
+{\news \zyang{is this right?}We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space.
+For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = [\vq_1,\dots,\vq_{n_p}]\in \real{m (n_p\times T)}$.
+}
+\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis).} Formally:
 \begin{equation}\label{eq:general-problem}
@@
 \begin{definition}\label{def:secured-plan}
-  A multi-robot trajectory plan is secure again plan-deviation attacks if it ensure that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
 \end{definition}
@@
 \subsubsection{Differentials}
-We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
+\zyang{Dim of function f use the same as before}We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
 \begin{equation}\label{equ:dt_to_dx}
@@
 
-With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{R}\to\real{m\times n}$.
-Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.
+\new{With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments\zyang{need double check for dim} $f:\real{m\times n\times T}\to\real{l}$.
+Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.}
 
@@
 \end{align}
-where $a,b$ are the indices of the pair of agents required for a mutual inspection.
+where $a,b$ are the indices of the pair of agents required for a mutual inspection, \zyanghl{Any better ways?}{$d_{max}$ is the constant maximum distance between a pair of robots to perform co-observation which depends on the co-observation method.}
 \end{constraint}
@@
 \begin{definition}\label{sec:ellipsoidal definition}
-  \new{Let robot $i$ be observed at location $q_{1}$ at time $t_1$ and location $q_{2}$ at time $t_2$.
-The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory $\tilde\vq = \{\tilde{q}_{it_1}\dots \tilde{q}_{it_2}\}$ where $\tilde{q}_{it'} = q'$ for some $t_1 \leq t' \leq t_2$, and $\tilde\vq$ satisfies the velocity constraint $d(\tilde q_t,\tilde q_{t+1})\leq v_{max}$, where $d(\cdot,\cdot)$ represents the distance between two points}
+  \new{ \zyanghl{is this enough?
+since ellipsoids is defined later}{Let robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory that contains $q'$ while satisfies the dynamic constraints.}}
 	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}.
 \end{definition}
-This region can be analytically bounded via an ellipsoid:
+\new{If only considering the maximum velocity constraint, this region can be analytically bounded via an ellipsoid:}
 \begin{definition}\label{def:Reachability}
-	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
+	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, where $d(\cdot,\cdot)$ represents the euclidean distance between two points.
 \end{definition}
-
+\begin{remark}
+  \zyang{add analysis}
+\end{remark}
  \begin{figure}
@@
 
-    \caption{ \cref{fig:EllipseConstraintExample} showcases the ellipsodial reachability region.
-Black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations the robot are expected at given time $t_1$ and $t_2$, dashed lines show possible trajectory of a compromised robot during unobserved period.
+    \caption{\news (\ref{fig:EllipseConstraintExample}) Black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations the robot are expected at given time $t_1$ and $t_2$, dashed lines show possible trajectory of a compromised robot during unobserved period.
 Axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
-    In \cref{fig:Ellipse-to-point}, a point $q_{avoid}$ inside ellipsoid is projected to the areas outside the ellipsoid $f_{p}$. 
-    In \cref{fig:Ellipse-to-plane}, the projection is simplified to the point-ellipse constraint as projecting a point inside ellipse $p_{L}$ to $p_{t}$ on outside the ellipse.
-    In \cref{fig:Ellipse-to-safezone}, this constraint is simplified to either a plane-ellipse constraint $D_{1}$ or a point-ellipse constraint $D_{2}$.}
+    (\ref{fig:Ellipse-to-point}) For point-ellipsoid constraint, $q_{avoid}$ is projected to the areas outside the ellipsoid to $q_{p}$. 
+    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projecting point $p_{L}$ outside the ellipse to $p_{t}$.
+    (\ref{fig:Ellipse-to-safezone}) For convec-polygon-ellipsoid constraint, the projection either a plane-ellipse constraint $D_{1}$ (for red region) or a point-ellipse constraint $D_{2}$ (for brown region).}
     \label{fig:Reachability_full}
@@
 This reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}.
-\new{Notice that the ellipsoid does not consider obstacles}.
+\new{Notice that the ellipsoid does not consider obstacles}.\zyang{asked for a proof?}
 
@@
 
-where $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$ is a projection function that returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
+\zyang{move $q_{avoid}, a$ to somewhere else to avoid confusion?}where $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$ is a projection function that returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
 \begin{equation}\label{eq:ellipse-point-projection}
@@
 
-  In our derivations, we consider only the 3-D case ($m=3$); for the 2-D case, let $P=\bmat{I & 0}\in\real{2\times 3}$: then $\pi_{p\cE}^{\textrm{2D}}=P\pi_{p\cE}^{\textrm{3D}}(P\transpose q_{avoid}; P\transpose q_1, P\transpose q_2,a)$.
+\zyang{dim of I is 2 how to indicate?}  In our derivations, we consider only the 3-D case ($m=3$); for the 2-D case, let $P=\bmat{I & 0}\in\real{2\times 3}$: then $\pi_{p\cE}^{\textrm{2D}}=P\pi_{p\cE}^{\textrm{3D}}(P\transpose q_{avoid}; P\transpose q_1, P\transpose q_2,a)$.
 
@@
 \begin{definition}
-The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
+The \emph{tangent interpolation point} {\news between the plane $\cL$ and the ellipsoid $\cE$} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
     \begin{equation}\label{equ:ProjectPoint}
@@
 
-We employ the APMAPF solver \cite{wardega2019resilience} on a 8 by 8 grid world with similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+We employ the \new{attack-proof MAPF(APMAPF)} solver \cite{wardega2019resilience} on a 8 by 8 grid world with similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
 This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with additional task function targeting the map exploration task.
@@
 \subsection{Problem overview}
-\rtron{Move definition of Checkpoint somewhere in this section}
-%To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map),
-We start with an unsecured MRS trajectory with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ (the ADMM-based planner in \Cref{sec:ADMM-planning} without security constraints is used, but other planners are applicable).
+We start with an unsecured MRS trajectory with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ (the ADMM-based planner in \cref{sec:ADMM-planning} without security constraints is used, but other planners are applicable).
 Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
@@
 These robots focus on co-observations either within their respective sub-teams, or when necessary, deviate and join another sub-team to provide necessary co-observations.
-The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation} that the resulting MRS plan meet the security in \Cref{rmk:revised-security} while minimizing the number of additional robots required.
-
+The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation} that the resulting MRS plan meet the security in \cref{rmk:revised-security} while minimizing the number of additional robots required.
+
+{\news First, we introduce the idea of \emph{checkpoint}.
+\begin{definition}
+  Checkpoints are a subset of waypoints along a trajectory for a robot team.
+At each checkpoint, the robot following the trajectory is observed by at least one other robot.
+Checkpoints are chosen to ensure that the reachability region between any two consecutive checkpoints does not intersect with any forbidden regions.
+\end{definition}
+}
 We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ represent key locations requiring co-observation (as required by \Cref{rmk:revised-security}), and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist.
@@
 \subsubsection{Checkpoints}\label{sec:security-checkpoint}
-Let $q_p\in\real{nT}$ represent the trajectory for sub-team $p$ with time horizon $T$, where $q_{p}(t) \in \real{n}$ denotes the reference waypoint at time $t$.
-\rtronhl{We need to put this in a formal definition of checkpoint that appears the first time we mention them}{We identify checkpoints within $q_p$ that require co-observations for securty,} as outlined in \Cref{rmk:revised-security}.
+Let $q_p\in\real{mT}$ represent the trajectory for sub-team $p$ with time horizon $T$, where $q_{p}(t) \in \real{m}$ denotes the reference waypoint at time $t$.
+We identify checkpoints within $q_p$ that require co-observations for securty, as outlined in \Cref{rmk:revised-security}.
 Checkpoint $v_{pi}=(q_{pi},t_{i})$ signifies a required co-observation for sub-team $p$, defined by a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
@@
 We assume that $n_p$ robots are dedicated (one in each sub-team) to follow the reference trajectory (named \emph{reference robots}).
-The goal is to plan the routes of the $n-n_p$ additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations, and potentially minimize the number of ross-trajectory robots needed.
+The goal is to plan the routes of the $n-n_p$ additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations, and potentially minimize the number of cross-trajectory robots needed.
 
@@
   \caption{\Cref{fig:previous_result_plan} showcase an unsecured 4-robot map exploration task.
-The cross-trajectory co-observation plan is shown as dotted arrors on top of the original plan in \Cref{fig:previous_result_plan}.
+The cross-trajectory co-observation plan is shown as dotted arrows on top of the original plan in \Cref{fig:previous_result_plan}.
 The checkpoint graph and resulting flows are shown in \Cref{fig:previous_result_graph}.}
@@
 In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.}
-
-\begin{definition} Let $\nu_\cF$ and $\nu_\cE$ be two unitary vectors ($\norm{\nu_\cF}=\norm{\nu_\cE}=1$). Define the normalized vector $u = \frac{\nu_\cF+\nu_\cE}{\norm{\nu_\cF+\nu_\cE}}$,
+\zyang{$\nu_\cF$ is defined in main content, i changed it to $\nu_1$ and $\nu_2$}
+\begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
   % \begin{equation}
-  %   u=\nu_\cF+\nu_\cE,\quad u =\frac{u'}{\norm{u'}}.
+  %   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
   % \end{equation}
-the \emph{Householder rotation} $H(\nu_\cF,\nu_\cE)$ is defined as
+the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
   \begin{equation}\label{eq:H definition}
-    H(\nu_\cF,\nu_\cE) = 2 u u\transpose-I.
+    H(\nu_1,\nu_2) = 2 u u\transpose-I.
   \end{equation}
 \end{definition}
-Here $H$ is a rotation mapping $\nu_\cF$ to $\nu_\cE$, as shown by the following.
+Here $H$ is a rotation mapping $\nu_1$ to $\nu_2$, as shown by the following.
 \begin{proposition}\label{prop:HProperty}
@@
     \end{enumerate}
-  \item\label{it:transformation} $\nu_\cE=H \nu_\cF$.
+  \item\label{it:transformation} $\nu_2=H \nu_1$.
   \end{enumerate}
@@
   For subclaim~\ref{it:transformation}, first note that $Hu=2uu\transpose u - u=u$.
-  It follows that the sum of $\nu_\cF$ and $\nu_\cE$ is invariant under $H$:
+  It follows that the sum of $\nu_1$ and $\nu_2$ is invariant under $H$:
   \begin{equation}\label{equ:H(u1+u2)}
-    H(\nu_\cF+\nu_\cE)=H u \norm{\nu_\cF+\nu_\cE}
-    = u\norm{\nu_\cF+\nu_\cE} =\nu_\cF+\nu_\cE,
+    H(\nu_1+\nu_2)=H u \norm{\nu_1+\nu_2}
+    = u\norm{\nu_1+\nu_2} =\nu_1+\nu_2,
   \end{equation}
@@
   \begin{equation}\label{equ:H(u1-u2)}
-    H(\nu_\cF-\nu_\cE) = 2uu\transpose (\nu_\cF-\nu_\cE) - (\nu_\cF-\nu_\cE)^2 = -(\nu_\cF-\nu_\cE).
+    H(\nu_1-\nu_2) = 2uu\transpose (\nu_1-\nu_2) - (\nu_1-\nu_2)^2 = -(\nu_1-\nu_2).
   \end{equation}
@@
   \begin{equation}
-    H\nu_\cF = \frac{1}{2}\bigl(H(\nu_\cF+\nu_\cE)+H(\nu_\cF-\nu_\cE)\bigr)
-    = \nu_\cE
+    H\nu_1 = \frac{1}{2}\bigl(H(\nu_1+\nu_2)+H(\nu_1-\nu_2)\bigr)
+    = \nu_2
   \end{equation}
@@
 \begin{proposition}\label{prop:Hderivitive}
-  Let $\nu_\cF(t)$ represent a parametric curve. Then
+  Let $\nu_1(t)$ represent a parametric curve. Then
   \begin{equation}
@@
   \begin{equation}
-    M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\norm{u'} \norm{\nu_\cF}}.
+    M=[u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_1 \nu_1\transpose \right)} {\norm{u'} \norm{\nu_1}}.
   \end{equation}
@@
         =  &  -2H [[u]_{\times} \dot u]_{\times} \\
-        = &  -2 H \left[ [u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_\cF \nu_\cF\transpose \right)} {\left\|u'\right\| \left\|\nu_\cF\right\|} \dot{\nu}_\cF\right]_{\times}\\
+        = &  -2 H \left[ [u]_{\times}  \frac{ \left( I - u u\transpose \right) \left( I- \nu_1 \nu_1\transpose \right)} {\left\|u'\right\| \left\|\nu_1\right\|} \dot{\nu}_\cF\right]_{\times}\\
         = & -2 H \cross{M \dot{\nu}_\cF},

### 2024-11-26 paper.tex
update

@@
 \end{align}
-where $a,b$ are the indices of the pair of agents required for a mutual inspection, \zyanghl{Any better ways?}{$d_{max}$ is the constant maximum distance between a pair of robots to perform co-observation which depends on the co-observation method.}
+where $a,b$ are the indices of the pair of agents required for a mutual inspection, \zyang{Any better ways?} \new{$d_{max}$ is the constant maximum distance between a pair of robots to perform co-observation which depends on the co-observation method.}
 \end{constraint}
@@
 \subsection{Definition of ellipsoidal reachability regions}\label{sec:reachability}
-In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form.
+
+\new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory.
+Subsequently, we introduce various reachability constraints involving an ellipsoid and other geometric entities, such as points, lines, line segments, and polygons.
+These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning presented in \cref{chapter:ADMM review}.
+}
+% In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form.
 Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections.
 Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
-
 %The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
-
+{\news
 \begin{definition}\label{sec:ellipsoidal definition}
-  \new{ \zyanghl{is this enough?
-since ellipsoids is defined later}{Let robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
-The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory that contains $q'$ while satisfies the dynamic constraints.}}
+Let robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory that contains $q'$ while satisfies the dynamic constraints.
 	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}.
 \end{definition}
-\new{If only considering the maximum velocity constraint, this region can be analytically bounded via an ellipsoid:}
+When considering only the velocity constraint, the \emph{reachability} set for $q'$ can be simplified as $\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
+\begin{remark}
+  The set $\mathcal{E}$ represents a region bounded by the sum of distances from $q'$ to two fixed points $q_1$ and $q_2$.
+Geometrically, this describes an ellipsoid-like shape where the sum of distances from any point on the boundary $q'\in \{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)=v_{max}(t_2-t_1)\}$ to $q_1,q_2$ is constant.\zyang{is this redundant?}
+\end{remark}
+To make this connection explicit, we defined the \emph{reachability ellipsoid $\cE$} as:}
 \begin{definition}\label{def:Reachability}
-	The \emph{reachability ellipsoid $\cE$} is defined as the region  $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q}+q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, where $d(\cdot,\cdot)$ represents the euclidean distance between two points.
+	The reachability ellipsoid $\cE$ is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
 \end{definition}
-\begin{remark}
-  \zyang{add analysis}
-\end{remark}
+\zyanghl{is this part still needed?}{The region $\cE(q_1,q_2)$ is an ellipsoid with foci at $q_1,q_2$, center $o_{\cE} = \frac{1}{2}(q_1+q_2)$, and the major radius equal to $a$.
+We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.}
+
  \begin{figure}
@@
 
-The region $\cE(q_1,q_2)$ is an ellipsoid with foci at $q_1,q_2$, center $o_{\cE} = \frac{1}{2}(q_1+q_2)$, and the major radius equal to $a$.
-We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.
-This reachability ellipsoid is an over-approximation of the exact reachability region in \Cref{sec:ellipsoidal definition}.
-\new{Notice that the ellipsoid does not consider obstacles}.\zyang{asked for a proof?}
-
-Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \Cref{def:secured-plan} can be written as,
+{\news For a robot be observed at $p_1$, $t_1$, if the reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region, any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot unable to be observed at $p_2$, $t_2$.
+Notice that the intersection with obstacles are not considered here.} Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \cref{def:secured-plan} can be written as,
 \begin{remark}\label{rmk:revised-security}
@@
 
-\zyang{move $q_{avoid}, a$ to somewhere else to avoid confusion?}where $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$ is a projection function that returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
+where $\pi_{p\cE}(q_{avoid};q_1,q_2,a) = q_p$ is a projection function that returns a projected point $q_p$ of $q_{avoid}$ outside the ellipse, i.e., as the solution to
 \begin{equation}\label{eq:ellipse-point-projection}
@@
 
-{\news First, we introduce the idea of \emph{checkpoint}.
+{\news \zyang{this version right?} To avoid confusion, \zyanghl{Can i do this?
+since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} We introduce \emph{checkpoint}s to devide the trajectory into observed and un-observed sections.
 \begin{definition}
-  Checkpoints are a subset of waypoints along a trajectory for a robot team.
-At each checkpoint, the robot following the trajectory is observed by at least one other robot.
-Checkpoints are chosen to ensure that the reachability region between any two consecutive checkpoints does not intersect with any forbidden regions.
+The $i$th checkpoint $v_{pi}=(q_{pi},t_{i})$ for sub-team $p$ is defined by waypoint $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ where robot is observed one (or both) of its adjacent waypoints $q_{p}(t_i-1)$ and $q_{p}(t_i+1)$.
 \end{definition}
+For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
+To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
+This requirement can be formally stated as:
 }
-We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ represent key locations requiring co-observation (as required by \Cref{rmk:revised-security}), and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist.
-Inspired by \cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph.
+We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ are checkpoints and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist.
+Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph.
 This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
 
-%To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$.
-Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires co-observation as described in \Cref{rmk:revised-security}.
-Edges $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.
-Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general Mixed-Intiger Linear Programming techniques as specialized solver.
-
 This section presents the two components of our approach: constructing the checkpoint graph based on unsecured multi-robot trajectories, and the formulation and solution of the network multi-flow problem.
@@
 \subsection{Rapidly-exploring Random Trees}
-To find edges between different nominal trajectories, we use the \rrtstar{} \cite{karaman2010incremental} algorithm to find paths from a waypoint on one trajectory to multiple destination points (i.e., reference trajectories of other sub-teams, in our method).
+To find edges between different nominal trajectories, we use the \rrtstar{}~\cite{karaman2010incremental} algorithm to find paths from a waypoint on one trajectory to multiple destination points (i.e., reference trajectories of other sub-teams, in our method).
 As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree.
@@
 \subsubsection{Checkpoints}\label{sec:security-checkpoint}
-Let $q_p\in\real{mT}$ represent the trajectory for sub-team $p$ with time horizon $T$, where $q_{p}(t) \in \real{m}$ denotes the reference waypoint at time $t$.
-We identify checkpoints within $q_p$ that require co-observations for securty, as outlined in \Cref{rmk:revised-security}.
-Checkpoint $v_{pi}=(q_{pi},t_{i})$ signifies a required co-observation for sub-team $p$, defined by a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
-For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
-To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
-This requirement can be formally stated as:
-
-%Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$.
-We locate checkpoints among $q_p$ that requires co-observations in order for the MRS trajectories to be secured as defined in \Cref{rmk:revised-security}.
-Checkpoint $v_{pi}=(q_{pi},t_{i})$ representing a required co-observation for sub-team $p$ composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$.
-For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, and let $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
-To secure the reference trajectory for one sub-team, the reachability region between consecutive checkpoints can not intersect with any of the forbidden areas.
-This requirement can be formally stated as:
-
+{\news To ensure the security of the un-observed part of the trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
+This requirement can be formally stated as:}
 \begin{remark}

### 2024-11-28 paper.tex
update

@@
 {\news \zyang{is this right?}We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space.
-For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = [\vq_1,\dots,\vq_{n_p}]\in \real{m (n_p\times T)}$.
+For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
 }
@@
 \subsubsection{Differentials}
-\zyang{Dim of function f use the same as before}We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
+We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
 \begin{equation}\label{equ:dt_to_dx}
@@
 \new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory.
-Subsequently, we introduce various reachability constraints involving an ellipsoid and other geometric entities, such as points, lines, line segments, and polygons.
+We then use the ellipsoids to introduce various reachability constraints with respect to other geometric entities, such as points, lines, line segments, and polygons.
 These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning presented in \cref{chapter:ADMM review}.
@@
 \begin{definition}\label{sec:ellipsoidal definition}
-Let robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
-The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space such that there exists a trajectory that contains $q'$ while satisfies the dynamic constraints.
+Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
 	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}.
 \end{definition}
-When considering only the velocity constraint, the \emph{reachability} set for $q'$ can be simplified as $\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
-\begin{remark}
-  The set $\mathcal{E}$ represents a region bounded by the sum of distances from $q'$ to two fixed points $q_1$ and $q_2$.
-Geometrically, this describes an ellipsoid-like shape where the sum of distances from any point on the boundary $q'\in \{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)=v_{max}(t_2-t_1)\}$ to $q_1,q_2$ is constant.\zyang{is this redundant?}
-\end{remark}
-To make this connection explicit, we defined the \emph{reachability ellipsoid $\cE$} as:}
+
+For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
 \begin{definition}\label{def:Reachability}
-	The reachability ellipsoid $\cE$ is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
+	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
 \end{definition}
-\zyanghl{is this part still needed?}{The region $\cE(q_1,q_2)$ is an ellipsoid with foci at $q_1,q_2$, center $o_{\cE} = \frac{1}{2}(q_1+q_2)$, and the major radius equal to $a$.
-We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.}
-
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less then $2a$, where a is the major radius of the ellipsoid.
+\rtronhl{It seems we do not use $c_\cE$ in the main text, move to the appendix where it is used}{We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.}}
+
+ %Geometrically, this describes an ellipsoid shape where the sum of distances from any point on the boundary $q'\in \{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)=v_{max}(t_2-t_1)\}$ to $q_1,q_2$ is constant.\zyang{is this redundant?}
  \begin{figure}
@@
 
-{\news For a robot be observed at $p_1$, $t_1$, if the reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region, any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot unable to be observed at $p_2$, $t_2$.
-Notice that the intersection with obstacles are not considered here.} Expanding upon the concept of \emph{co-observation} and \emph{reachability}, \cref{def:secured-plan} can be written as,
-\begin{remark}\label{rmk:revised-security}
+{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot  to miss a potentia observation at $p_2$, $t_2$.} \Cref{def:secured-plan} can then be restated as follows
+\begin{definition}\label{rmk:revised-security}
   A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
-\end{remark}
+\end{definition}
 
 \subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
-{\news To simplify the problem, we apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center and the first axis of $\cF_\cE$ aligns with the foci \Cref{fig:EllipseConstraintExample}.
-For all reachability ellipsoid constraints, we solve the problem in $\cF_\cE$ and transform the solutions back to $\cF$ using \eqref{eq:transformations}.
-The transformation and its inverse is parametrized by a rotation $R^\cF_\cE$ (denoted $R$) and a translation $o^\cF_\cE$ (denoted $o$) as:
+\newcommand{\oFE}{o}
+{\news To use the definition of reachability ellipsoid from the section above in a computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration).
+%For all reachability ellipsoid constraints, we solve the problem in $\cF_\cE$ and transform the solutions back to $\cF$ using \eqref{eq:transformations}.
+From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
+The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
 \begin{equation}\label{eq:transformations}
-  \Fframe{q}=R\Eframe{q}+o,\quad
-  \Eframe{q}=R\transpose(\Fframe{q}-o).
-\end{equation}
-where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is formed using \emph{Householder rotation} $H$ (a differentiable linear transformation used to represent rotation between two vectors, more details in \cref{sec:householder}), and $o =\frac{1}{2}(q_1+q_2)$.
-$\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$ represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively.
+  q=R\Eframe{q}+\oFE,\quad
+  \Eframe{q}=R\transpose(q-\oFE).
+\end{equation}
+where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see \cref{sec:householder} for details), and $o =\frac{1}{2}(q_1+q_2)$.
 To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e.
 $H(q_1,q_2)$.
-More details of this transformation is introduced in \cref{apx:transformation}.
+More details on \eqref{eq:transformations} are given in \cref{apx:transformation}.
   % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
@@
 We start with an unsecured MRS trajectory with $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ (the ADMM-based planner in \cref{sec:ADMM-planning} without security constraints is used, but other planners are applicable).
-Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$.
+Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $p$-th sub-team at time $t\in\{0, \dots, T\}$.
 Introducing redundant robots into the MRS, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory.
@@
 
-{\news \zyang{this version right?} To avoid confusion, \zyanghl{Can i do this?
-since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} We introduce \emph{checkpoint}s to devide the trajectory into observed and un-observed sections.
+{\news %\zyang{this version right?} To avoid confusion, \zyanghl{Can i do this? since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} 
+Our strategy is based on the following concept:
 \begin{definition}
-The $i$th checkpoint $v_{pi}=(q_{pi},t_{i})$ for sub-team $p$ is defined by waypoint $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ where robot is observed one (or both) of its adjacent waypoints $q_{p}(t_i-1)$ and $q_{p}(t_i+1)$.
+The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ at which a robot is co-observed by its teammates, and where it can leave or join a new team.
 \end{definition}
-For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.
-To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
-This requirement can be formally stated as:
+For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. %, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding location and time for checkpoint $v_{pi}$.
+To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
 }
@@
 
-\subsection{Checkpoint graph construction}
+\subsection{Checkpoint graph construction}\label{sec:security-checkpoint}
 
@@
 
-\subsubsection{Checkpoints}\label{sec:security-checkpoint}
 {\news To ensure the security of the un-observed part of the trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.

### 2024-12-01 paper.tex
update

@@
 The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another.
-This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in Figure \ref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events.
+This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events.
 The cross-trajectory co-observation problem is transformed as a multi-agent path finding problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.
@@
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
-{\news \zyang{is this right?}We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space.
+{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space and $T$ is the time horizon.
 For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
@@
 
-% This section is organized as follows.
-We begin with foundational mathematical concepts needed for the optimal trajectory solver and reachability constraints.
-Subsequently, we integrate security constraints, including co-observation schedule and reachability constraints.
-Finally, we present the obtained results alongside limitations that are then addressed in \Cref{sec:cross-trajectory}.
-
 \subsection{Preliminaries}
 \subsubsection{Differentials}
-We define the differential of a map $f(x):\real{m}\to\real{n}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{n\times m}$ such that
+\new{We define the differential of a map $f(x):\real{d_1}\to\real{d_2}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{d_1\times d_2}$ such that}
 \begin{equation}\label{equ:dt_to_dx}
@@
 \end{equation}
-where $t\mapsto x(t)\in\real{n}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$.
+where $t\mapsto x(t)\in\real{d_1}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$.
 For brevity we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
@@
 
-\new{With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments\zyang{need double check for dim} $f:\real{m\times n\times T}\to\real{l}$.
+\new{With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{d_1 \times d_3}\to\real{d_2}$.
 Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.}
@@
 \end{align}
-where $a,b$ are the indices of the pair of agents required for a mutual inspection, \zyang{Any better ways?} \new{$d_{max}$ is the constant maximum distance between a pair of robots to perform co-observation which depends on the co-observation method.}
+where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.}
 \end{constraint}
@@
 \end{definition}
-This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less then $2a$, where a is the major radius of the ellipsoid.
-\rtronhl{It seems we do not use $c_\cE$ in the main text, move to the appendix where it is used}{We denote as $c_\cE=\frac{1}{2}\norm{q_1-q_2}=\norm{o_\cE-q_1}$ the semi-axis distance from the center to a foci.}}
-
- %Geometrically, this describes an ellipsoid shape where the sum of distances from any point on the boundary $q'\in \{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)=v_{max}(t_2-t_1)\}$ to $q_1,q_2$ is constant.\zyang{is this redundant?}
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less then $2a$, where a is the major radius of the ellipsoid. }
  \begin{figure}
@@
 
-{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot  to miss a potentia observation at $p_2$, $t_2$.} \Cref{def:secured-plan} can then be restated as follows
+{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potentia observation at $p_2$, $t_2$.
+\Cref{def:secured-plan} can then be restated as follows:
 \begin{definition}\label{rmk:revised-security}
@@
 \end{definition}
+}
 
@@
 \newcommand{\oFE}{o}
-{\news To use the definition of reachability ellipsoid from the section above in a computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration).
-%For all reachability ellipsoid constraints, we solve the problem in $\cF_\cE$ and transform the solutions back to $\cF$ using \eqref{eq:transformations}.
+{\news To use the definition of reachability ellipsoid from the section above in a computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration).
 From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
@@
 \end{equation}
-where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see \cref{sec:householder} for details), and $o =\frac{1}{2}(q_1+q_2)$.
+where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see \cref{sec:householder} for details).
 To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e.
@@
 
-\zyang{dim of I is 2 how to indicate?}  In our derivations, we consider only the 3-D case ($m=3$); for the 2-D case, let $P=\bmat{I & 0}\in\real{2\times 3}$: then $\pi_{p\cE}^{\textrm{2D}}=P\pi_{p\cE}^{\textrm{3D}}(P\transpose q_{avoid}; P\transpose q_1, P\transpose q_2,a)$.
+In our derivations, we consider only the 3-D case ($m=3$); for the 2-D case, let $P=\bmat{I & 0}\in\real{2\times 3}$: then $\pi_{p\cE}^{\textrm{2D}}=P\pi_{p\cE}^{\textrm{3D}}(P\transpose q_{avoid}; P\transpose q_1, P\transpose q_2,a)$.
 
@@
 
-For forbidden region in the shape of a hyperplane $\mathcal{L}(\Fframe{q}) = \{\Fframe{q}\in\mathbb{R}^m: \vn\transpose \Fframe{q} = d\}$ (as shown in~\cref{fig:Ellipse-to-plane}), the reachability constraint can be defined as $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, \new{with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.}
+\new{For a hyperplane shaped forbidden region $\mathcal{L}(q) = \{q\in\mathbb{R}^m: \vn\transpose q = d\}$ (\cref{fig:Ellipse-to-plane}), the reachability constraint is $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.}
 % Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
@@
 \begin{definition}
-The \emph{tangent interpolation point} {\news between the plane $\cL$ and the ellipsoid $\cE$} $p^\cE_{\cL} \in \mathcal{L}$ is defined on the plane by 
+ {\news The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ between the plane $\cL$ and the ellipsoid $\cE$ is defined on the plane by } 
     \begin{equation}\label{equ:ProjectPoint}
@@
   \end{proof}
-  Based on the \Cref{prop:dpi_ne_dt}, the differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
-  \begin{equation}
-    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}
-  \end{equation}
-
+ The differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
+  \begin{equation}
+    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}.
+  \end{equation}
 \subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
-
-% For a intermediate step to get the relationship between a polygon shaped forbidden region, the relative position between the ellipse and segment of the hyperplane that defines the region is studied.
 {\news As an intermediate step to consider polygon shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
@@
 \end{equation}
-For cases that the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
-red region in \cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies between $\Eframe{p_{1}}$ and $\Eframe{p_{2r}}$), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}.
+When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
+red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}.
 Otherwise (i.e.
-brown region in \cref{fig:Ellipse-to-safezone}, where $\Eframe{p_{\cL}}$ lies outside $\Eframe{p_{1}}$ and $\Eframe{p_{2b}}$), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.
+brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.
 
@@
 To address the feasibility and performance trade-offs, we propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams.
-These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in Figure \ref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
+These \emph{cross-trajectory co-observations} allow sub-teams to obtain trajectories that are closer to the optimal (as shown in \cref{fig:cross-traj-comparison-set}), because they do not require the entire \emph{sub-team} to meet with other teams for co-observations, thus providing more flexibility.
 \subsection{Problem overview}
@@
 To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
+\begin{remark}
+  A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
+  \end{remark}
 }
-We model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where vertices $V_{q}$ are checkpoints and edges $E_{q} = E_{t} \union E_{c}$ connect pairs of vertices if possible paths exist.
+{\news \zyang{Any better ways since $V_c, E$ are all introduced later?} 
+% The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is illustrated as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ are union of checkpoints $V_p$ and connection verticies $V_c$, $E_{q} = E_{t} \union E_{c}$ are union of trajectory edges $E_t$ and connection edges $E_c$ (introduced later in \cref{sec:cross-trajectory}).
 Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph.
 This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
+The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ is a subset of waypoints on the planned trajectory, and $E_{q} = E_{t} \union E_{c}$ represents feasible paths connecting $V_q$.
+Specifically,
+\begin{itemize}
+  \item $V_p$ Checkpoints where additional robots are required for security through co-observation.
+  \item $E_t$ Trajectory edges representing the original planned path of the primary robot.
+  \item $E_c$ Connection edges with at least one endpoint as a checkpoint, representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support.
+  \item $V_c$ Connection vertices representing non-checkpoint locations linked via $E_c$.
+\end{itemize}
+The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G_q$.
+To satisfy security requirements, every checkpoint $V_p$ must be visited by at least one flow.This formulation reduces the co-observation problem to finding valid flow patterns in $G_q$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
+}
 
@@
 In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
-
-{\news To ensure the security of the un-observed part of the trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
-This requirement can be formally stated as:}
-\begin{remark}
-A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
-\end{remark}
-
-A heuristic approach is provided (\Cref{alg:checkpoint-gen}) to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
+A heuristic approach is provided to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
 %with a toy example shown in Figure \ref{fig:checkpoint-generate}.
-
-\begin{algorithm}
-  \caption{Secure Checkpoint Generation for a Sub-Team $p$}\label{alg:checkpoint-gen}
-  \begin{algorithmic}
-  \State $v_{p0} \gets (q_{p}(0),0)$; $v_{pT} \gets (q_{p}(T),T)$
-  \State $V_{p} = \{v_{p0}, v_{pT}\}$
-  \State $t_0 \gets 0$; $t_1 \gets T$
-  \While {$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}),t_{0},t_{1}) \intersect F \neq \emptyset$ or $t_1 - t_0 > 1$}
-    \State $i \gets 1$; $j\gets 1$
-    \While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{0}+i),t_{0},t_0+i) \intersect F = \emptyset$ and $t_0+i > t_1$}
-      \State $v_{pf} \gets (q_{p}(t_0+i),t_0+i)$
-      \State $i \gets i+1$
-    \EndWhile
-    \State $V_{p}\gets V_{p}\union v_{pf}$
-    \While{$\mathcal{E}(q_{p}(t_{1}-j),q_{p}(t_{1}),t_{1}-j,t_{1}) \intersect F = \emptyset$ and $t_0+i \geq t_1-j$}
-    \State $v_{pb} \gets (q_{p}(t_1-j),t_1-j)$
-    \State $j \gets j+1$
-    \EndWhile
-    \If {$t_0+i \neq t_1-j$}
-    \State $V_{p}\gets V_{p}\union v_{pb}$
-    \EndIf
-  \EndWhile
-  \end{algorithmic}
-  \rtron{It is probably better to substitute this with a description in words. If you want to keep the pseudocode, move it to the appendix.}
-  \end{algorithm}
+{\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{q}$, with $t_{0}=0$, $t_2=T$.
+Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
+$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$.
+Then $(q_{p}(t_{1}),t_1)$ is added to $V_{q}$.
+Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$.
+Then $(q_{p}(t_{3}),t_3)$ is added to $V_{q}$.
+Afterwards, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process.
+The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$.
+A toy example is shown in \cref{fig:checkpoint-generate}.
+}
+
+\begin{figure}
+	\centering
+    \subfloat[]{\includegraphics[width=0.45\linewidth,trim = 1.7cm 2cm 1cm 2.7cm, clip,valign=c]{SC_gen_1}}
+    \subfloat[]{\includegraphics[width=0.45\linewidth,trim = 1.7cm 2cm 1cm 2.7cm, clip,valign=c]{SC_gen_2}}
+    \caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
+\end{figure}
+
+% \begin{algorithm}
+%   \caption{Secure Checkpoint Generation for a Sub-Team $p$}\label{alg:checkpoint-gen}
+%   \begin{algorithmic}
+%   \State $v_{p0} \gets (q_{p}(0),0)$; $v_{pT} \gets (q_{p}(T),T)$
+%   \State $V_{p} = \{v_{p0}, v_{pT}\}$
+%   \State $t_0 \gets 0$; $t_1 \gets T$
+%   \While {$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}),t_{0},t_{1}) \intersect F \neq \emptyset$ or $t_1 - t_0 > 1$}
+%     \State $i \gets 1$; $j\gets 1$
+%     \While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{0}+i),t_{0},t_0+i) \intersect F = \emptyset$ and $t_0+i > t_1$}
+%       \State $v_{pf} \gets (q_{p}(t_0+i),t_0+i)$
+%       \State $i \gets i+1$
+%     \EndWhile
+%     \State $V_{p}\gets V_{p}\union v_{pf}$
+%     \While{$\mathcal{E}(q_{p}(t_{1}-j),q_{p}(t_{1}),t_{1}-j,t_{1}) \intersect F = \emptyset$ and $t_0+i \geq t_1-j$}
+%     \State $v_{pb} \gets (q_{p}(t_1-j),t_1-j)$
+%     \State $j \gets j+1$
+%     \EndWhile
+%     \If {$t_0+i \neq t_1-j$}
+%     \State $V_{p}\gets V_{p}\union v_{pb}$
+%     \EndIf
+%   \EndWhile
+%   \end{algorithmic}
+%   \rtron{It is probably better to substitute this with a description in words. If you want to keep the pseudocode, move it to the appendix.}
+%   \end{algorithm}
 
@@
   \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth]{security_graph}}
-  \caption{\Cref{fig:two-edges}, Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
-\Cref{fig:security-graph-generate}, example of a full checkpoint graph where round vertices are checkpoint generated through the heuristic search and triangle vertices are added with the cross-trajectory edges.
-Virtual source $v^{+}$ and sink $v^{-}$ are added to be used later in planning problem.}
+  \caption{{\news (\ref{fig:two-edges}) Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
+(\ref{fig:security-graph-generate}) Eexample of a full checkpoint graph where round vertices are checkpoint generated through the heuristic search and triangle vertices are arrival and departure nodes added with the cross-trajectory edges.
+Virtual source $v^{+}$ and sink $v^{-}$ are added to be used later in planning problem.}}
 \end{figure}
@@
 
-For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $v_{ea} = (q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
+For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $v_{ea} = (\q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
 %$t^{a}_r$ is designated as the \emph{earliest arrival time}.
@@
 
-For each $v_{p} \in V_{p}$ found through \Cref{alg:checkpoint-gen}, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$.
-Examples are shown in Figure \ref{fig:two-edges}.
+For each $v_{p} \in V_{p}$, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$.
+Examples are shown in \cref{fig:two-edges}.
 
@@
 We then add to $E_q$ the \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ obtained by connecting all consecutive checkpoints $v^i_{p}\in V_q$ with the checkpoints $v^{i+1}_{p}$ that follow them in their original trajectories.
-Examples are shown in Figure \ref{fig:security-graph-generate}.
+Examples are shown in \cref{fig:security-graph-generate}.
 %\zyang{any better explaination?}
@@
 
-We then test the proposed method for a 4-team and 7-team case with result shown in Figure \ref{fig:Cross-trajectory-result}, where four trajectories are provided for a map exploration task with no security related constraints (co-observation schedule and reachability).
+We then test the proposed method for a 4-team and 7-team case with result shown in \cref{fig:Cross-trajectory-result}, where four trajectories are provided for a map exploration task with no security related constraints (co-observation schedule and reachability).
 We have a $10m\times10m$ task space, three forbidden regions (rectangle regions in \Cref{fig:Result-plan}) and robots with a max velocity of $0.5m/dt$.
@@
    \begin{equation}\label{eq:ellpsoid from canonical}
-     \Fframe{E}(\Fframe{q}) = (\Fframe{q}-o_\cE)\transpose H\transpose Q H (\Fframe{q}-o_\cE) - 1
+     \Fframe{E}(q) = (q-o_\cE)\transpose H\transpose Q H (q-o_\cE) - 1
      \end{equation}

### 2024-12-02 paper.tex
update

@@
 }
-{\news \zyang{Any better ways since $V_c, E$ are all introduced later?} 
+{\news \zyang{Any better ways since $V_c, E$ are all introduced later?, also will $V_p$ and $V_q$ cause confusion?} 
 % The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is illustrated as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ are union of checkpoints $V_p$ and connection verticies $V_c$, $E_{q} = E_{t} \union E_{c}$ are union of trajectory edges $E_t$ and connection edges $E_c$ (introduced later in \cref{sec:cross-trajectory}).
@@
 This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
-The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ is a subset of waypoints on the planned trajectory, and $E_{q} = E_{t} \union E_{c}$ represents feasible paths connecting $V_q$.
+The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where verticies $V = (\union_p V_p) \union V_c$ are a subset of waypoints on the planned trajectory, and edges $E_{q} = E_{t} \union E_{c}$ represents feasible paths connecting $V_q$.
 Specifically,
-\begin{itemize}
-  \item $V_p$ Checkpoints where additional robots are required for security through co-observation.
-  \item $E_t$ Trajectory edges representing the original planned path of the primary robot.
-  \item $E_c$ Connection edges with at least one endpoint as a checkpoint, representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support.
-  \item $V_c$ Connection vertices representing non-checkpoint locations linked via $E_c$.
-\end{itemize}
-The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G_q$.
-To satisfy security requirements, every checkpoint $V_p$ must be visited by at least one flow.This formulation reduces the co-observation problem to finding valid flow patterns in $G_q$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
+\begin{description}
+  \item[$V_p$]: Checkpoints where additional robots are required for security through co-observation.
+  \item[$E_t$]: Trajectory edges representing the original planned path of the primary robot.
+  \item[$E_c$]: Cross-trajectory edges with at least one endpoint as a checkpoint, representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support.
+  \item[$V_c$]: Connection vertices representing non-checkpoint locations linked via $E_c$.
+\end{description}
+
+The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G$.
+To satisfy security requirements, every checkpoint $V$ must be visited by at least one flow.This formulation reduces the co-observation problem to finding valid flow patterns in $G$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
 }
@@
 We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
-Key functions from \rrtstar{} that are also used during constructions of the checkpoint graph are
+Key functions from \rrtstar{} that are also used during constructions of the checkpoint graph are \zyang{get back to check which is used}
 \begin{description}
@@
 %with a toy example shown in Figure \ref{fig:checkpoint-generate}.
-{\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{q}$, with $t_{0}=0$, $t_2=T$.
+
+{\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
 Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
 $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$.
-Then $(q_{p}(t_{1}),t_1)$ is added to $V_{q}$.
+Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$.
 Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$.
-Then $(q_{p}(t_{3}),t_3)$ is added to $V_{q}$.
-Afterwards, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process.
+Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$.
+Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process.
 The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$.
@@
     \centering
-  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth]{two_edges}}
-  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth]{security_graph}}
+  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0cm, clip, valign=c]{two_edges}}
+  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0.2cm, clip, valign=c]{security_graph}}
   \caption{{\news (\ref{fig:two-edges}) Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
-(\ref{fig:security-graph-generate}) Eexample of a full checkpoint graph where round vertices are checkpoint generated through the heuristic search and triangle vertices are arrival and departure nodes added with the cross-trajectory edges.
+(\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.
 Virtual source $v^{+}$ and sink $v^{-}$ are added to be used later in planning problem.}}
@@
 We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone (ignoring, for the moment, any timing constraint). 
-More precisely, through \rrtstar{}, we find all feasible, quasi-optimal paths between one security checkpoint location $q_{v_p}(t_{v_p})$ where $v_{p} \in V_{p}$ for sub-team $\cI_p$, and all the waypoints $\{q_{r}(t_{{r}_{i}}) \}$ on any reference trajectory for a different sub-team $\cI_{r}$.
+More precisely, \new{for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.}
 Then, to prune these trees, we consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints.
@@
 
-For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $v_{ea} = (\q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
+For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $v_{ea} = (q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered. 
 %$t^{a}_r$ is designated as the \emph{earliest arrival time}.
@@
 \end{description}
-
-For each $v_{p} \in V_{p}$, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$.
+% For each $v_{p} \in V_{p}$, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$.
 Examples are shown in \cref{fig:two-edges}.
+{\news $V_c$ is the collection of all the latest departure and earliest arrival nodes (if they are not identified as checkpoints already), and the corresponding paths are added as cross-trajectory edges $E_q$.
+A toy example is shown in \cref{fig:two-edges}.}
 
@@
 %With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-We arrange all $V_q =\union_p \{v^0_{p}, \dots ,v^T_{p}\}$ found in \Cref{sec:security-checkpoint,sec:cross-traj-edges} in ascending order of $t_{v^i_{p}}$.
-We then add to $E_q$ the \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ obtained by connecting all consecutive checkpoints $v^i_{p}\in V_q$ with the checkpoints $v^{i+1}_{p}$ that follow them in their original trajectories.
+\new{Let $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ represent the set of all vertices found in~\cref{sec:security-checkpoint,sec:cross-traj-edges}.
+We group these verticies by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
+For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing corresponding segment of the planned trajectory.
 Examples are shown in \cref{fig:security-graph-generate}.
-%\zyang{any better explaination?}
+}
 
@@
 
-To formulate the problem as a network multi-flow problem, we augment the checkpoint graph $G_{q}$ to a flow graph $G=(V, E)$.
-The vertices of the new graph $G$ are defined as $V= V_{q} \union \{v^{+},v^{-}\}$, where $v^{+}$ is a \emph{virtual source} node, and $v^{-}$ is a \emph{virtual sink} node.
-We add directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$, with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$.
-The edges of the new graph are defined as $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$.
+{\news To formulate the problem as a network multi-flow problem, we augment the checkpoint graph to a flow graph.
+A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node is added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$.
+Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}
 
@@
 In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.}
-\zyang{$\nu_\cF$ is defined in main content, i changed it to $\nu_1$ and $\nu_2$}
 \begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,

### 2024-12-03 paper.tex
from overleaf

@@
 \begin{abstract}
-This paper addresses security challenges in multi-robot systems (MRS) where adversaries may compromise robot control, risking unauthorized access to forbidden regions.
-We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability} constraints for enhanced security.
-This ensures that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations.
-The reachability constraint uses ellipsoidal over-approximation for efficient intersection checking and gradient computation.
-To enhance system resilience and tackle feasibility challenges, we also introduce \emph{sub-teams}.
-These cohesive units replace individual robot assignments along each route, enabling redundant robots to deviate for co-observations across different trajectories, securing multiple sub-teams without requiring modifications.
-We formulate the \emph{cross-trajectory co-observation} plan by solving a network flow coverage problem on the checkpoint graph generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
-We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
+We address security challenges in multi-robot systems (MRS) where adversaries may take control of compromised robots to gain unauthorized physical access to forbidden regions.
+We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability constraints} and \emph{co-observations} between robots to enhance security.
+Our formulation can guarantee that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations.
+We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation.
+Furthermore, to enhance system resilience and tackle feasibility challenges, we introduce the notion of \emph{sub-teams}; these cohesive units replace individual robots along each route; we plan \emph{cross-trajectory co-observation} that use redundant robots to switch between routes, securing multiple sub-teams without requiring modifications to the plans.
+We formulate cross-trajectories plans by solving a \emph{network-flow vertex path coverage problem} on the \emph{checkpoint graph} generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
+We demonstrate the effectiveness and robustness of our proposed algorithm through simulations, which significantly strengthen the security of multi-robot systems in the face of adversarial threats.
 \end{abstract}
@@
 }
-{\news \zyang{Any better ways since $V_c, E$ are all introduced later?, also will $V_p$ and $V_q$ cause confusion?} 
+{\news \zyang{Make this a definition} 
 % The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is illustrated as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ are union of checkpoints $V_p$ and connection verticies $V_c$, $E_{q} = E_{t} \union E_{c}$ are union of trajectory edges $E_t$ and connection edges $E_c$ (introduced later in \cref{sec:cross-trajectory}).
@@
 This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
-The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where verticies $V = (\union_p V_p) \union V_c$ are a subset of waypoints on the planned trajectory, and edges $E_{q} = E_{t} \union E_{c}$ represents feasible paths connecting $V_q$.
+The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where verticies $V = (\union_p V_p) \union V_c$ are a subset of waypoints on the planned trajectory, and edges $E = E_{t} \union E_{c}$ represents feasible paths connecting $V$.
 Specifically,
 \begin{description}
-  \item[$V_p$]: Checkpoints where additional robots are required for security through co-observation.
-  \item[$E_t$]: Trajectory edges representing the original planned path of the primary robot.
-  \item[$E_c$]: Cross-trajectory edges with at least one endpoint as a checkpoint, representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support.
-  \item[$V_c$]: Connection vertices representing non-checkpoint locations linked via $E_c$.
+  \item[Checkpoints $V_p$] where additional robots are required for security through co-observation.
+  \item[Tranectory edges $E_t$] representing the original planned path of the primary robot.
+  \item[Connection vertices $V_c$] representing non-checkpoint locations linked via $E_c$.
+  \item[Cross-trajectory edges $E_c$] representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support, at least one endpoint be a checkpoint.
 \end{description}
@@
 The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G$.
-To satisfy security requirements, every checkpoint $V$ must be visited by at least one flow.This formulation reduces the co-observation problem to finding valid flow patterns in $G$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
+To satisfy security requirements, every checkpoint $V$ must be visited by at least one flow.
+This formulation reduces the co-observation problem to finding valid flow patterns in $G$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
+\rtron{Add some references to MILP for multi-flow path planning}
 }
@@
 Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$.
-The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur during trajectory switches.
+The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur {\news while switching trajectories}.
 %\end{remark}
@@
   \caption{{\news (\ref{fig:two-edges}) Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
-(\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.
-Virtual source $v^{+}$ and sink $v^{-}$ are added to be used later in planning problem.}}
+(\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}}
 \end{figure}
@@
 We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone (ignoring, for the moment, any timing constraint). 
-More precisely, \new{for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.}
+More precisely, \new{for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on the reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.}
 Then, to prune these trees, we consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints.
@@
 Examples are shown in \cref{fig:two-edges}.
-{\news $V_c$ is the collection of all the latest departure and earliest arrival nodes (if they are not identified as checkpoints already), and the corresponding paths are added as cross-trajectory edges $E_q$.
+{\news The set $V_c$ contains all the \emph{latest departure} and \emph{earliest arrival} nodes (if they are not identified as checkpoints already); the corresponding paths are added as cross-trajectory edges $E_q$.
 A toy example is shown in \cref{fig:two-edges}.}
@@
 %With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-\new{Let $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ represent the set of all vertices found in~\cref{sec:security-checkpoint,sec:cross-traj-edges}.
+\new{\rtronhl{We already defined this}{Let $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ represent the set of all vertices} found in~\cref{sec:security-checkpoint,sec:cross-traj-edges}.
 We group these verticies by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
@@
 A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node is added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$.
-Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}
+Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v^{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v^{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}
 
@@
 The path of a robot $k$ all starts from $v^{+}$ and ends at $v^{-}$, and are represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
-The planning problem can be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \Cref{rmk:revised-security}).
+The planning problem can be formulated as a vertex path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \Cref{rmk:revised-security}).
 %Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
@@
 The first term in the cost \eqref{eq:flow-cost} represents the total number of robot used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
-\eqref{eq:FlowBalanceConstraint} is the flow conservation constraint to ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
-\eqref{eq:FlowCoverage} is the flow coverage constraints to ensures that all security checkpoints $ \{V^{s}_{p}\}$ have been visited co-observed.
-The security graph $G_{q}$ is acyclic, making this problem in complexity class $P$, thus, can be solved in polynominal time \cite{1702662}.
+The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
+The flow coverage constraint \eqref{eq:FlowCoverage} ensures that all checkpoints $ \{V^{s}_{p}\}$ have been visited and can support a co-observation.
+The checkpoint graph $G$ is acyclic, placing this problem in complexity class $P$; thus, it can be solved in polynominal time \cite{1702662}.
 
 \subsection{Co-observation performance}
-Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
+The network flow problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
 %Additionally, for a fixed number of robots $\cK \geq N_{p}$,
@@
 The constant $\rho$ selects the trade-off between the number of surveillance robots and security performance.
-An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.
-In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.
+An increase in robots generally enhances security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.
+In order to identify the minimum number of robots necessary, we propose an iterative approach in which we start with $\cK=1$ and gradually increase it until $F$ contains an empty flow, indicating the point where further additions of robots do not improve performance.
 
@@
 {\news
-\subsection{Transformation of reachability ellipsoid to canonical frame}\label{apx:transformation}
+\subsection{Transformation of a reachability ellipsoid to canonical frame}\label{apx:transformation}
 The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, with foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ defined as

### 2024-12-03 paper.tex
update

@@
 We address security challenges in multi-robot systems (MRS) where adversaries may take control of compromised robots to gain unauthorized physical access to forbidden regions.
-We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability constraints} and \emph{co-observations} between robots to enhance security.
+We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces {\news \emph{reachability constraints} and \emph{co-observations} between robots to enhance security}.
 Our formulation can guarantee that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations.
-We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation.
+\new{We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation.
 Furthermore, to enhance system resilience and tackle feasibility challenges, we introduce the notion of \emph{sub-teams}; these cohesive units replace individual robots along each route; we plan \emph{cross-trajectory co-observation} that use redundant robots to switch between routes, securing multiple sub-teams without requiring modifications to the plans.
 We formulate cross-trajectories plans by solving a \emph{network-flow vertex path coverage problem} on the \emph{checkpoint graph} generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
-We demonstrate the effectiveness and robustness of our proposed algorithm through simulations, which significantly strengthen the security of multi-robot systems in the face of adversarial threats.
+We demonstrate the effectiveness and robustness of our proposed algorithm through simulations, which significantly strengthen the security of multi-robot systems in the face of adversarial threats.}
 \end{abstract}
@@
 
-{\news %\zyang{this version right?} To avoid confusion, \zyanghl{Can i do this? since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} 
+{\news
 Our strategy is based on the following concept:
 \begin{definition}
-The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ at which a robot is co-observed by its teammates, and where it can leave or join a new team.
+The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
+It representes either the first or last instance where a robot is co-observed by a teammates, and serves as a point where the robot can leave or join a new team.
+% at which a robot is co-observed by its teammates, and where it can leave or join a new team. 
 \end{definition}
@@
 To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
-\begin{remark}
+\begin{remark}\label{rmk:checkpoints}
   A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
@@
 }
-{\news \zyang{Make this a definition} 
-% The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is illustrated as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ are union of checkpoints $V_p$ and connection verticies $V_c$, $E_{q} = E_{t} \union E_{c}$ are union of trajectory edges $E_t$ and connection edges $E_c$ (introduced later in \cref{sec:cross-trajectory}).
-Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph.
-This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
-The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where verticies $V = (\union_p V_p) \union V_c$ are a subset of waypoints on the planned trajectory, and edges $E = E_{t} \union E_{c}$ represents feasible paths connecting $V$.
-Specifically,
+{\news 
+\begin{definition}
+  The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where $V = (\union_p V_p) \union V_c$ is the set of verticies representing waypoints on the planned trajectory and $E = E_{t} \union E_{c}$ is the set of edges representing feasible paths connecting $V$.
+The components of the checkpoint graph are defined as follows:
   \begin{description}
@@
   \end{description}
-
-The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G$.
-To satisfy security requirements, every checkpoint $V$ must be visited by at least one flow.
-This formulation reduces the co-observation problem to finding valid flow patterns in $G$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
-\rtron{Add some references to MILP for multi-flow path planning}
+\end{definition}
+
+We assume that the planned trajectory for each sub-team has a robot operating on it.
+The co-observation planning problem is then transformed into a network multi-flow problem by modelling the additional robots as flows traveling through $G$.
+These flows either follow the planned trajectory via trajectory edges $E_t$ or switch teams via cross-trajectory edges $E_c$ to ensure valid and secured paths.
+Additionally, they are required to visit every checkpoint $V_p$ to meet the security requirements introduced in~\ref{rmk:checkpoints}.
+This formulation reduces the co-observation problem to finding valid flow patterns in $G$.
+The problem is then formulated into linear objectives and constraints, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
 }
@@
 We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
-Key functions from \rrtstar{} that are also used during constructions of the checkpoint graph are \zyang{get back to check which is used}
-\begin{description}
-\item[$\texttt{Cost}(v)$] This function assigns a non-negative cost (total travel distance in our application) to the unique path from the initial position to $v$ . 
-\item[$\texttt{Parent}(v)$] This is a function that maps the vertex $v$ to $v'\in V$ such that $(v',v)\in E$.
-\end{description}
+Key function from \rrtstar{} is used during constructions of the checkpoint graph, specifically
+{\news\begin{description}
+\item[$\texttt{Cost}(v)$] This function returns a total travel distance to the unique path from the initial position to $v$. 
+\end{description}}
 
@@
 \subsubsection{In-trajectory edges}\label{sec:Graph-intro}
-
-%With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
-\new{\rtronhl{We already defined this}{Let $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ represent the set of all vertices} found in~\cref{sec:security-checkpoint,sec:cross-traj-edges}.
-We group these verticies by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
+\new{We group $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
 For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing corresponding segment of the planned trajectory.
@@
 The first term in the cost \eqref{eq:flow-cost} represents the total number of robot used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
-The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
+{\news The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
 The flow coverage constraint \eqref{eq:FlowCoverage} ensures that all checkpoints $ \{V^{s}_{p}\}$ have been visited and can support a co-observation.
 The checkpoint graph $G$ is acyclic, placing this problem in complexity class $P$; thus, it can be solved in polynominal time \cite{1702662}.
+}
 

### 2024-12-04 response.tex
add response letter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Paper Response Letter. 
% LaTeX Template
% Version 1.0 (20/07/2023)
% 
% This template refers to the toolbox tutorial (in Chinese):
% https://liam.page/2016/07/22/using-the-tcolorbox-package-to-create-a-new-theorem-environment/
% Please refer to the tutorial for your customization. 
% 
% Template license: Creative Commons CC BY 4.0
%
% Author: Yuhan Xie
% Contact email: yhxie0107@gmail.com
% Any revision advice is welcome!
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}
%% Language and font encodings
\usepackage[english]{babel}
\usepackage{times} % make the section title in Times New Roman

\usepackage{booktabs}
\usepackage{tabu}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=2.5cm,bottom=2cm,left=1.7cm,right=1.7cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{threeparttable} 
\usepackage{multirow}
\usepackage{url}

\usepackage[most]{tcolorbox}
\newcommand{\rrtstar}{$\texttt{RRT}^\texttt{*}$}
\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}

\newtheorem{constraint}{ADMM constraint}
\newtheorem{example}{Example}

\usepackage[export]{adjustbox} 
\usepackage[capitalise]{cleveref}
\usepackage{xcolor}
\newcommand{\new}[1]{\textcolor{blue}{#1}}
\newcommand{\news}{\color{blue}}
\graphicspath{{Figs/}}

\begin{document}

\newtcbtheorem[auto counter, number within = section]{cmt}{Comment}{
	colbacktitle = black!60!white, colframe = black!60!white,
	colback = black!5!white,
	fonttitle=\bfseries,%fontupper=\itshape,
}{t}

\noindent
Dear Editor and Reviewers:

\vspace{0.2cm}
\noindent
First of all, we would like to express our sincere gratitude to the Editor-in-Chief, Associate
Editor and anonymous reviewers for their valuable comments and suggestions, which have
been incorporated into the revised manuscript such that the revised version is clearer, more
informative, thus more readable. In the revision, all the comments from the reviewers have
been carefully taken into account and thoroughly implemented. Meanwhile, the changes in the
revised version have been highlighted in blue. Our response to the reviewers’ comments (in
1:1 correspondence) is given as follows:
\vspace{0.2cm}
\noindent
Yours sincerely,

%\vspace{0.2cm}
\noindent
Author A, Author B...

\section*{Response to the Editor} 
\begin{cmt*}{}{}
Editor Comments.
\end{cmt*}

\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your response.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 1
\newpage
\section{Response to reviewer 1}

%%%%%%%%%%%%% Comment 1.1
\begin{cmt}{}{}

Comments 1.1

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 1.1

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 1.0
\begin{cmt*}{}{}        %% use * when do not need enumerate

Comments

\end{cmt*}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 1.2
\begin{cmt}{}{}

Comments 1.2

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 1.2

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 1.3
\begin{cmt}{}{}

Comments 1.3

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 1.3

\vspace{0.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 2
\newpage
\section{Response to reviewer 2}

%%%%%%%%%%%%% Comment 2.1
\begin{cmt}{}{}

Comments 2.1

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 2.1

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 2.2
\begin{cmt}{}{}

Comments 2.2

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 2.2

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 2.3
\begin{cmt}{}{}

Comments 2.3

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 2.3

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 2.4
\begin{cmt}{}{}

Comments 2.4

\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

Your Response 2.4

\vspace{0.3cm}

\end{document}

### 2024-12-05 response.tex
update

@@
 \noindent
-First of all, we would like to express our sincere gratitude to the Editor-in-Chief, Associate
-Editor and anonymous reviewers for their valuable comments and suggestions, which have
-been incorporated into the revised manuscript such that the revised version is clearer, more
-informative, thus more readable. In the revision, all the comments from the reviewers have
-been carefully taken into account and thoroughly implemented. Meanwhile, the changes in the
-revised version have been highlighted in blue. Our response to the reviewers’ comments (in
-1:1 correspondence) is given as follows:
+First and foremost, we sincerely thank the Editor-in-Chief, Associate Editor, and anonymous reviewers for their insightful comments and suggestions.
+These have been carefully incorporated into the revised manuscript, resulting in a clearer, more informative, and more readable version.
+All reviewer comments have been thoroughly addressed, and the corresponding changes have been highlighted in \new{blue} for ease of reference.
+Our detailed responses to the reviewers' comments are outlined below:
 \vspace{0.2cm}
@@
 \noindent
-Author A, Author B...
+Ziqi Yang, Roberto Tron
 

### 2024-12-05 paper.tex
update

@@
 While offering numerous advantages, the distributed nature and dependence on network communication render the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
-This paper addresses a specific scenario in which  robots are compromised by attacker and directed to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+This paper addresses a specific scenario in which robots are compromised by attackers and directed to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
 Such countering deliberate deviations, termed \emph{plan-deviation attacks}, are identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}.
-As a security measure, we utilized onboard sensing capabilities of the robots to perform inter-robot co-observations and check for unusual behavior.
+As a security measure, we utilized the onboard sensing capabilities of the robots to perform inter-robot co-observations and check for unusual behavior.
 These mutual observation establish a co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
@@
 A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}.
-Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accomodate for more flexible objectives.
+Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accommodate for more flexible objectives.
 In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
@@
 
-However, such plans are not guaranteed to exist, and the secured trajectory always come at the cost of overall system performance.
+However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance.
 As an extension of the previous works \cite{yang2020multi,yang2021multi}, we also address the feasibility and optimality challenges.
 For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.
-These redundant robots are assigned the task of establishing additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
+These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
 The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another.
 This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events.
-The cross-trajectory co-observation problem is transformed as a multi-agent path finding problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.
+The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.
 
@@
 
-Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and Multi-Agent Path Finding (MAPF) problems \cite{stern2019multi}.
+Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and MAPF problems \cite{stern2019multi}.
 In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions and solved as a network flow problem \cite{yu2013multi,yu2016optimal}.
@@
   % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 2cm 2cm 2cm 2cm]{SecurityBreak}}
-  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.45\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}}
-  \caption{Trajectory design of a map exploration task forthree-robot system based on result in grid world result~\Cref{fig:Grid-example-application}.
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.45\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
+  \caption{{\news Trajectory design of a map exploration task forthree-robot system based on result in grid world result~\Cref{fig:Grid-example-application}.
 Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones.
@@
 A potential path that could break the security by entering region 1 is highlighted in dashline.
-\Cref{fig:ReachabilitySimulation} shows the secured trajectory with the incorporation of co-observation and reachability constraints.}
+\Cref{fig:ReachabilitySimulation} shows the secured trajectory with the incorporation of co-observation and reachability constraints.}}
   \label{fig:example-application}

### 2024-12-06 paper.tex
update figures and fix gramma

@@
 \new{We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation.
-Furthermore, to enhance system resilience and tackle feasibility challenges, we introduce the notion of \emph{sub-teams}; these cohesive units replace individual robots along each route; we plan \emph{cross-trajectory co-observation} that use redundant robots to switch between routes, securing multiple sub-teams without requiring modifications to the plans.
+Furthermore, to enhance system resilience and tackle feasibility challenges, we introduce the notion of \emph{sub-teams}; these cohesive units replace individual robots along each trajectory; we plan \emph{cross-trajectory co-observation} that use redundant robots to switch between different trajectories, securing multiple sub-teams without requiring modifications to the plans.
 We formulate cross-trajectories plans by solving a \emph{network-flow vertex path coverage problem} on the \emph{checkpoint graph} generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
@@
 
-    \caption{{\news \ref{fig:example-plan-dev} Attacker deviate the red robot into forbidden region.\ref{fig:example-co-observation} Red and blue robot tasked to co-observe each other during task resulting a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
-\ref{fig:example-cross-traj} The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots following the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
+    \caption{{\news \ref{fig:example-plan-dev} The attacker deviates the red robot into a forbidden region.\ref{fig:example-co-observation} Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
+\ref{fig:example-cross-traj} The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
 \end{figure}
 
-\noindent\myparagraph{Related research} Trajectory planning problem of MRS systems remained as a subject of intense study for many decades, and optimization is a common approaches in such area.
-Optimization based approaches are customizable to a variable of constraints (e.g.
-speed limit, avoid obstacles) and task specifications (e.g.
+\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such area.
+Optimization-based approaches are customizable to a varity of constraints (e.g.
+speed limit, avoiding obstacles) and task specifications (e.g.
 maximum surveillance coverage, minimal energy cost).
 In contrast to our work in \Cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}.
-Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity, and to incorporate more complex non-convex constraints.
+Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity and to incorporate more complex non-convex constraints.
 
 Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and MAPF problems \cite{stern2019multi}.
-In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions and solved as a network flow problem \cite{yu2013multi,yu2016optimal}.
+In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions, and solved as a network flow problem \cite{yu2013multi,yu2016optimal}.
 This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem.
@@
 \new{Reachability analysis is essential for security and safety verification in cyber-physical systems (CPSs) \cite{gueguen2009safety, ding2020secure}, often involving an over-approximation of reachable space to verify safety properties.
-Geometric methods like zonotopes and ellipsoids are commonly used to compactly enclose reachability sets \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}.
+Geometric methods like zonotopes and ellipsoids are commonly used to enclose reachability sets compactly \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}.
 For online safety assessments against cyber attacks, \cite{kwon2017reachability} computed reachable CPS states under attacks and compared them with a safe region based on state estimation.
@@
 This is inspired by the ellipsoidal \emph{heuristic sampling domain} in \cite{gammell2014informed} for the $\mathtt{RRT^*}$ algorithm to simplify the sampling region between start and goal locations.
-Ellipsoids are also used in other path planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}.
-Differs from reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximate the safe collision-free space rather than addressing security applications.}
+Ellipsoids are also used in other path-planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}.
+Differing from the reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximating the safe collision-free space rather than addressing security applications.}
 
@@
   \item We introduce additional robots to form \emph{sub-teams} for both intra-sub-team and cross-sub-team co-observations.
-A new co-observation planning algorithm is formulated that can generate a resilient multi-robot trajectory with a co-observation plan that still preserve the optimal performance against arbitrary tasks.
+A new co-observation planning algorithm is formulated that can generate a resilient multi-robot trajectory with a co-observation plan that still preserves the optimal performance against arbitrary tasks.
 We also find the minimum redundant robots required for the security.
@@
 
-The rest of this paper is organized as follows.
-\Cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and introduce the security constraints.
+{\news The rest of this paper is organized as follows.
+\Cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and the security constraints.
 \Cref{sec:cross-trajectory} introduces the enhanced security planning algorithm through cross-trajectory co-observation.
@@
 In this paper, we use non-bold symbols like to denote single-agent states (e.g.
-$q_{ij}$) and scalers, while bold symbols represent aggregated states involving single robot or multiple robots (e.g.
+$q_{ij}$) and scalers, while bold symbols represent aggregated states of single robot and multiple robots (e.g.
 $\vq$).
+}
 
@@
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
-{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$ where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space and $T$ is the time horizon.
+{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
 For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
 }
-\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis).} Formally:
+\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraints and the security constraints (co-observation schedule, reachability analysis).} Formally:
 \begin{equation}\label{eq:general-problem}
@@
 The goal is to find paths that minimize uncertainty in reconstructing the field.
-Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot.
+Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot.
 The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}
@@
   \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
-  \caption{\new{(a) Grid world example of a task planned in a $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
+  \caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
 \end{figure}
@@
 \begin{equation}\label{equ:dt_to_dx}
-  \left.\dert f\bigl(x(t)\bigr)\right|_{t=0}=\partial_x f\bigl(x(0)\bigr) \dot{x}(0)
+  \left.\dert f\bigl(x(t)\bigr)\right|_{t=0}=\partial_x f\bigl(x(0)\bigr) \dot{x}(0),
 \end{equation}
 where $t\mapsto x(t)\in\real{d_1}$ is a smooth parametric curve such that $x(0)=x$ with any arbitrary tangent $\dot{x}(0)$.
-For brevity we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
+For brevity, we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
 %The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.
@@
 \subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
-The basic idea of the ADMM-based solver introduced in \cite{yang2020multi} is to separate the constraints from the objective function using a different set of variables $\vz$, and then solve separately in \eqref{eq:general-problem}.
-More specifically, we rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$, and include it in the objective function (details can be found in \cite{yang2020multi}). 
+The basic idea of the ADMM-based solver introduced in \cite{yang2020multi} is to separate the constraints from the objective function using a different set of variables $\vz$, then solve separately in \eqref{eq:general-problem}.
+More specifically, we rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$ and include it in the objective function (details can be found in \cite{yang2020multi}). 
 %In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$.
@@
 	\begin{aligned}
-		&\max\quad \varPhi(\vq)+\varTheta(\vz) \\
+		&\max\quad \varPhi(\vq)+\varTheta(\vz), \\
 		& \begin{array}{r@{\quad}c}
-			s.t.& D(\vq)-\vz=0
+			s.t.& D(\vq)-\vz=0,
 		\end{array} 
@@
 This makes each constraint set $\mathcal{Z}_i$ independent and thus can be computed separately in later updating steps.
-$D_i(\vq)$ is chosen that the new constraint set~$\cZ_i$ becomes simple to compute which is illustrated in later secitons.
+$D_i(\vq)$ is chosen such that the new constraint set~$\cZ_i$ becomes simple to compute which is illustrated in later sections.
 % and the function~$D_i(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.
@@
 \end{equation}
-Checking the primal residuals alongside with the dual residuals 
+Checking the primal residuals alongside the dual residuals 
 \begin{equation}\label{eq:dual-residual}
@@
 \end{equation}
-after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residual remains large after a fixed number of iterations.
+after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
 {\news
 \begin{remark}
-In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via nonlinear optimization solver like \emph{fmincon}, while \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solution.
+In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver like \emph{fmincon}, while \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
 \end{remark}
@@
 We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for security constraints including co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:ellipsoid-point}-\Cref{eq:region_ellipsoid_constraint}).
-The latter are based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
-Formulation of traditional path planning constraints like velocity constraints, convex obstacle constraints can be found in \cite{yang2020multi}, thus are omitted in this paper.
+The latter is based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
+Formulation of traditional path planning constraints like velocity constraints and convex obstacle constraints can be found in \cite{yang2020multi}, thus are omitted in this paper.
 
@@
 \end{definition}
-This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less then $2a$, where a is the major radius of the ellipsoid. }
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
  \begin{figure}
@@
 
-    \caption{\news (\ref{fig:EllipseConstraintExample}) Black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations the robot are expected at given time $t_1$ and $t_2$, dashed lines show possible trajectory of a compromised robot during unobserved period.
-Axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
+    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robot are expected at given time $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period.
+The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
     (\ref{fig:Ellipse-to-point}) For point-ellipsoid constraint, $q_{avoid}$ is projected to the areas outside the ellipsoid to $q_{p}$. 
-    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projecting point $p_{L}$ outside the ellipse to $p_{t}$.
-    (\ref{fig:Ellipse-to-safezone}) For convec-polygon-ellipsoid constraint, the projection either a plane-ellipse constraint $D_{1}$ (for red region) or a point-ellipse constraint $D_{2}$ (for brown region).}
+    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projects point $p_{L}$ outside the ellipse to $p_{t}$.
+    (\ref{fig:Ellipse-to-safezone}) For convec-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
     \label{fig:Reachability_full}
@@
 
-{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potentia observation at $p_2$, $t_2$.
+{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
 \Cref{def:secured-plan} can then be restated as follows:
 \begin{definition}\label{rmk:revised-security}
-  A multi-robot trajectory is secured against plan-deviation attacks if there exist a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
+  A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
 \end{definition}
@@
 \newcommand{\oFE}{o}
-{\news To use the definition of reachability ellipsoid from the section above in a computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration).
+{\news To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration).
 From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
@@
     \end{cases} \label{eq:point_ellipsoid_constraint}\\
-  \sZ &= \{q\in\mathbb{R}^{nm}:\norm{D_p(\vq)} = 0 \},\\
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_p(\vq)} = 0 \},\\
    \Pi_\sZ(\vz) & = 0, 
@@
 \begin{equation}\label{eq:ellipse-point-projection}
-\pi_{p\cE}=\argmin_{q_p\in\cE^c} \quad \norm{q_{avoid}-q_p}^2 
+\pi_{p\cE}=\argmin_{q_p\in\cE^c} \quad \norm{q_{avoid}-q_p}^2,
 \end{equation}
@@
   \begin{equation}
-  	q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid}
+  	q^\cE_{p} = {(I+sQ)}\inverse q^\cE_{avoid} = S q^\cE_{avoid},
   \end{equation}
@@
   \begin{equation}
-    {q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1=0
+    {q^\cE_p}\transpose Q q^\cE_p-1={q^\cE_{avoid}}\transpose Q'(s) q^\cE_{avoid} -1=0,
   \end{equation}
@@
   \begin{equation}
-    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right)
+    Q'(s) =S\transpose Q S = \diag\left(\frac{a^{2}}{(s+a^{2})^2}, \frac{b^{2}}{(s+b^{2})^2},\frac{b^{2}}{(s+b^{2})^2}\right).
   \end{equation}
@@
     = R^{-1}(q(t_1),q(t_2))Sq^\cE_{avoid}+o\\
-    = R^{-1}S R ( q_{avoid}- o)+o
+    = R^{-1}S R ( q_{avoid}- o)+o.
   \end{multline}
@@
       \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
-      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o
+      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o.
     \end{multline}
@@
 \end{equation}
-where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be thought as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$).
+where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be treated as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$).
 The concept of \emph{tangent interpolation point}s is introduced to characterize the relationship between the plane and the ellipsoid.
@@
     \end{equation}
-  Intuitively, the point $p^\cE_\cL$ is the point on $\cL$ which is closest to either $p^\cE_1$ or $p^\cE_2$.
+  Intuitively, the point $p^\cE_\cL$ is the closest point on $\cL$ to either $p^\cE_1$ or $p^\cE_2$.
   Note that when  $d_\cE=d_{\cE t}$ or $d_\cE=-d_{\cE t}$, $p^\cE_{\cL}=p^\cE_{t_1}$ or $p^\cE_{\cL}=p^\cE_{t_2}$, respectively.
@@
 \subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
-{\news As an intermediate step to consider polygon shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
+{\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
 For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
@@
 \subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint} 
-For reachability constraints with respect to a convex polygon, the first step is to keep all segments that defines the hyperplane outside the reachability ellipsoid.
+For reachability constraints with respect to a convex polygon, the first step is to keep all segments that define the hyperplane outside the reachability ellipsoid.
 Similar to \eqref{equ:ProjectPoint}, we define
@@
 
-We employ the \new{attack-proof MAPF(APMAPF)} solver \cite{wardega2019resilience} on a 8 by 8 grid world with similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
-This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with additional task function targeting the map exploration task.
+We employ the \new{attack-proof MAPF(APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
 Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions.
@@
 {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space.
-In this cases, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids.
+In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids.
 Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated.
-For instance, in this scenario, we deploy a security camera as additional checkpoint to observe agent 3 at time $8$ to ensure security.}
+For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}
 
@@
   \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.45\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
-  \caption{{\news Trajectory design of a map exploration task forthree-robot system based on result in grid world result~\Cref{fig:Grid-example-application}.
-Zone 1 is obstacle, Zone 2 and Zone 3 are safe zones.
-\Cref{fig:SecurityBreak} shows the unsecured trajectory design in continuous world optimized with respect to a map exploration task where Zone 1 and 2 are considered together as one obstacle.
-A potential path that could break the security by entering region 1 is highlighted in dashline.
-\Cref{fig:ReachabilitySimulation} shows the secured trajectory with the incorporation of co-observation and reachability constraints.}}
+  \caption{{\news Trajectory design of a map exploration task for a three-robot system based on the grid world result~\cref{fig:Grid-example-application}.
+Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
+(\ref{fig:SecurityBreak}) The unsecured trajectory design in continuous world, optimized with respect to a map exploration task with Zone 1 and 2 considered together as one obstacle.
+A potential path that could break the security by entering region 1 is highlighted as the red dashline.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation and reachability constraints.}}
   \label{fig:example-application}
@@
 \subsubsection{Limitations}\label{sec:reachability-discussion}
-Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.{\news However, two primary challenges need to be addressed.
+Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.
+{\news However, two primary challenges need to be addressed.
 Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths.
@@
 These robots focus on co-observations either within their respective sub-teams, or when necessary, deviate and join another sub-team to provide necessary co-observations.
-The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation} that the resulting MRS plan meet the security in \cref{rmk:revised-security} while minimizing the number of additional robots required.
+The objective of this problem is to formulate a strategy for this new co-observation strategy, named \emph{cross-trajectory co-observation}, such that the resulting MRS plan meets the security in \cref{rmk:revised-security} while minimizing the number of additional robots required.
 
@@
 The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
-It representes either the first or last instance where a robot is co-observed by a teammates, and serves as a point where the robot can leave or join a new team.
+It represents either the first or last instance where a robot is co-observed by a teammate, and serves as a point where the robot can leave or join a new team.
 % at which a robot is co-observed by its teammates, and where it can leave or join a new team. 
@@
     \item[Checkpoints $V_p$] where additional robots are required for security through co-observation.
-    \item[Tranectory edges $E_t$] representing the original planned path of the primary robot.
-    \item[Connection vertices $V_c$] representing non-checkpoint locations linked via $E_c$.
-    \item[Cross-trajectory edges $E_c$] representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support, at least one endpoint be a checkpoint.
+    \item[Trajectory edges $E_t$] represent the original planned path of the primary robot.
+    \item[Connection vertices $V_c$] represent non-checkpoint locations linked via $E_c$.
+    \item[Cross-trajectory edges $E_c$] represent feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support, at least one endpoint be a checkpoint.
   \end{description}
@@
 We assume that the planned trajectory for each sub-team has a robot operating on it.
-The co-observation planning problem is then transformed into a network multi-flow problem by modelling the additional robots as flows traveling through $G$.
+The co-observation planning problem is then transformed into a network multi-flow problem by modeling the additional robots as flows traveling through $G$.
 These flows either follow the planned trajectory via trajectory edges $E_t$ or switch teams via cross-trajectory edges $E_c$ to ensure valid and secured paths.
@@
 
-This section presents the two components of our approach: constructing the checkpoint graph based on unsecured multi-robot trajectories, and the formulation and solution of the network multi-flow problem.
+This section presents the two components of our approach: constructing the checkpoint graph based on unsecured multi-robot trajectories and the formulation and solution of the network multi-flow problem.
 
@@
 As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree.
-We assume that the generated paths can be travelled in both directions (this is used later in our analysis).
+We assume that the generated paths can be traveled in both directions (this is used later in our analysis).
 Key function from \rrtstar{} is used during constructions of the checkpoint graph, specifically
@@
 
-Our objective here is to ascertain the existence of feasible paths instead of optimize specific tasks.
-While the ADMM based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
+Our objective here is to ascertain the existence of feasible paths instead of optimizing specific tasks.
+While the ADMM-based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
 
@@
 \subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
-To enable co-observation cross different sub-team at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories, allowing robots deviate from one sub-team to perform co-observation with a different sub-team.
+To enable co-observation across different sub-teams at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories, allowing robots to deviate from one sub-team to perform co-observation with a different sub-team.
 %\begin{remark}
@@
   \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0.2cm, clip, valign=c]{security_graph}}
-  \caption{{\news (\ref{fig:two-edges}) Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
+  \caption{{\news (\ref{fig:two-edges}) The latest departure node $q^{d}_{b}$ found for $v_{r1}$ and the earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
 (\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}}
@@
 \new{We group $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
-For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing corresponding segment of the planned trajectory.
+For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing the corresponding segment of the planned trajectory.
 Examples are shown in \cref{fig:security-graph-generate}.
@@
 We assume that $n_p$ robots are dedicated (one in each sub-team) to follow the reference trajectory (named \emph{reference robots}).
-The goal is to plan the routes of the $n-n_p$ additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations, and potentially minimize the number of cross-trajectory robots needed.
+The goal is to plan the routes of the $n-n_p$ additional \emph{cross-trajectory robots} dedicated to cross-trajectory co-observations, and potentially minimizing the number of cross-trajectory robots needed.
 
@@
 Note that we assign fixed roles to robots for convenience in explaining the multi-flow formulation.
-In practice, after a cross-trajectory robot joins a team, it is considered interchangable, and could switch roles with the reference robot of that trajectory.
+In practice, after a cross-trajectory robot joins a team, it is considered interchangable and could switch roles with the reference robot of that trajectory.
 % (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
@@
 {\news To formulate the problem as a network multi-flow problem, we augment the checkpoint graph to a flow graph.
-A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node is added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$.
+A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node are added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$.
 Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v^{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v^{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}
@@
         & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1, \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
-        & f^k_{ij} \in \{0,1\} \,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
+        & f^k_{ij} \in \{0,1\} ,  \forall (ij)\in E ,\label{eq:SingleFLowCapacity}
      \end{align}
@@
 
-The first term in the cost \eqref{eq:flow-cost} represents the total number of robot used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
+The first term in the cost \eqref{eq:flow-cost} represents the total number of robots used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
 {\news The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
 The flow coverage constraint \eqref{eq:FlowCoverage} ensures that all checkpoints $ \{V^{s}_{p}\}$ have been visited and can support a co-observation.
-The checkpoint graph $G$ is acyclic, placing this problem in complexity class $P$; thus, it can be solved in polynominal time \cite{1702662}.
+The checkpoint graph $G$ is acyclic, placing this problem in complexity class $P$; thus, it can be solved in polynomial time \cite{1702662}.
 }
@@
 It is possible for the resulting flows to have a subset of flows $F_{e} \in F$ that is empty, i.e.
-$f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$; these flow will not increase the cost and can be discarded from the solution.
+$f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$; these flows will not increase the cost and can be discarded from the solution.
 
@@
 An increase in robots generally enhances security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.
-In order to identify the minimum number of robots necessary, we propose an iterative approach in which we start with $\cK=1$ and gradually increase it until $F$ contains an empty flow, indicating the point where further additions of robots do not improve performance.
+To identify the minimum number of robots necessary, we propose an iterative approach in which we start with $\cK=1$ and gradually increase it until $F$ contains an empty flow, indicating the point where further additions of robots do not improve performance.
 
@@
   \centering
-  \subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.47\linewidth, trim = 4cm 2cm 4cm 2cm,valign=c]{old_result}}
-  \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 4cm 1cm 4cm 1cm,valign=c]{old_result_graph.png}}
-  \caption{\Cref{fig:previous_result_plan} showcase an unsecured 4-robot map exploration task.
-The cross-trajectory co-observation plan is shown as dotted arrows on top of the original plan in \Cref{fig:previous_result_plan}.
-The checkpoint graph and resulting flows are shown in \Cref{fig:previous_result_graph}.}
+  \subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.47\linewidth, trim = 2cm 1cm 1cm 1cm,clip,valign=b]{old_result_v2}}
+  \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
+  \caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as dotted arrows on top of the original plan in \cref{fig:previous_result_plan}.
+(\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}
   \label{fig:3-team-ctco}
@@
 The problem shows no solution for $\cK\leq 2$.
-For cases $\cK=3$, problem return the optimal result as shown in \Cref{fig:Cross-trajectory-result}.
+For cases $\cK=3$, the problem returns the optimal result as shown in \Cref{fig:Cross-trajectory-result}.
 If we further increase $\cK>3$, we do not get a better result; instead, the planner will return four flows with the rest $\cK-3$ flows empty.
 
-We then test the proposed method for a 4-team and 7-team case with result shown in \cref{fig:Cross-trajectory-result}, where four trajectories are provided for a map exploration task with no security related constraints (co-observation schedule and reachability).
-We have a $10m\times10m$ task space, three forbidden regions (rectangle regions in \Cref{fig:Result-plan}) and robots with a max velocity of $0.5m/dt$.
+We then test the proposed method for 4-team and 7-team cases with results shown in \cref{fig:Cross-trajectory-result}, where four trajectories are provided for a map exploration task with no security-related constraints (co-observation schedule and reachability).
+We have a $10m\times10m$ task space, three forbidden regions (rectangle regions in \Cref{fig:Result-plan}), and robots with a max velocity of $0.5m/dt$.
 
@@
   %\subfloat[Unsecured plan\label{fig:unsecured-plan}]{\includegraphics[width=0.31\linewidth, trim = 3cm 2cm 3cm 2cm, clip,valign=c]{SecurityBreak}}
-  \subfloat[4-agent co-observation plan\label{fig:Result-plan}]{\includegraphics[width=0.47\linewidth,trim = 4cm 2cm 4cm 2cm, clip,valign=c]{Traj_result}}
+  \subfloat[4-agent case\label{fig:Result-plan}]{\includegraphics[width=0.47\linewidth,trim = 3.5cm 2cm 1.5cm 0cm, clip,valign=c]{Traj_result_v2}}
   %\subfloat[Graph flow result\label{fig:result-graph}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{Graph_result}}
-  \subfloat[7-agent co-observation plan\label{fig:Result-plan-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 2cm 4cm 2cm, clip,valign=c]{7-team-plan.png}}
+  \subfloat[7-agent case\label{fig:Result-plan-7-team}]{\includegraphics[width=0.47\linewidth,trim = 3.5cm 2cm 1.5cm 0cm, clip,valign=c]{7-team-plan_v2.png}}
   %\subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
-  \caption{Cross-trajectory co-observation result of a 4 sub-teams task (\Cref{fig:Result-plan}) and a 7 sub-teams task \Cref{fig:Result-plan-7-team}}\label{fig:Cross-trajectory-result}
+  \caption{\new{(\ref{fig:Result-plan}) Cross-trajectory co-observation result of a 4 sub-teams task.
+(\ref{fig:Result-plan-7-team}) Cross-trajectory co-observation result of a 7 sub-teams task.}}\label{fig:Cross-trajectory-result}
 \end{figure}
@@
 We establish a mutual observation schedule to ensure that any deviations into forbidden regions break the schedule, triggering detection.
-Co-observation requirements and reachability analysis are incorporated into the trajectory planning phase, formulated as constraints for the optimal problem.
+Co-observation requirements and reachability analysis are incorporated into the trajectory planning phase, and formulated as constraints for the optimal problem.
 In scenarios where a secured plan is infeasible or enhanced task performance is necessary, we propose using redundant robots for cross-trajectory co-observations, offering the same security guarantees against plan-deviation attacks.
@@
 \begin{definition}
-  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
+  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as the zero-level set of the quadratic function
   \begin{equation}\label{equ:standard-ellipse}

### 2024-12-08 response.tex
Finish refinine paper, working on response

@@
 These have been carefully incorporated into the revised manuscript, resulting in a clearer, more informative, and more readable version.
-All reviewer comments have been thoroughly addressed, and the corresponding changes have been highlighted in \new{blue} for ease of reference.
-Our detailed responses to the reviewers' comments are outlined below:
+We acknowledge the reviewers' concerns regarding grammatical errors, unclear definitions, and poorly formatted figures, which were noted as obstacles to evaluating the paper's technical contributions.
+In this revision, we have thoroughly addressed these issues by eliminating grammatical errors, refining definitions and notations for clarity, and replotting the figures to enhance readability.
+All reviewer comments have been carefully addressed, and the corresponding changes have been highlighted in \new{blue} for ease of reference.
+Our detailed responses to the reviewers' comments, provided in a 1:1 correspondence, are outlined below.
 \vspace{0.2cm}

### 2024-12-08 paper.tex
Finish refinine paper, working on response

@@
 
-A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}.
+A preliminary version of the paper is presented in \cite{yang2020multi,yang2021multi}.
 Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accommodate for more flexible objectives.
@@
   \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
-  \caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as dotted arrows on top of the original plan in \cref{fig:previous_result_plan}.
+  \caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as arrows on top of the original plan in \cref{fig:previous_result_plan}.
 (\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}

### 2024-12-08 response.tex
writting response

@@
 %% Language and font encodings
+\input{preamble/common}
 \usepackage[english]{babel}
@@
 \usepackage[colorinlistoftodos]{todonotes}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{indentfirst}
-\usepackage{graphicx}
-\usepackage{subfigure}
+% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
+% \usepackage{indentfirst}
+% \usepackage{graphicx}
+% \usepackage{subfigure}
 \usepackage{float}
@@
 
-\section*{Response to the Editor} 
-\begin{cmt*}{}{}
-Editor Comments.
-\end{cmt*}
-
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-
-Your response.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 1
@@
 %%%%%%%%%%%%% Comment 1.1
-\begin{cmt}{}{}
+\begin{cmt*}{}{}
 
-Comments 1.1
+	This paper proposes a multi-agent mobile robot planning algorithm that
+	is robust agains attackers that would compromise the agents by
+	directing them to unsafe regions. This is achieved by incorporating 1)
+	co-observation constraints so that the agents could watch over each
+	other, 2) reachability constraints so that the region the agents could
+	potentially enter does no overlap with unsafe regions, and 3) sub-team
+	planning algorithm to improve robustness by adding more number of
+	agents.
 
+	The proposed method is interesting, but I think the writing must be
+	improved significantly to secure the clarity, and there are a lot of
+	grammar mistakes that need to be fixed. To me, it appears that the
+	draft may have been prepared somewhat hastily, which is not considerate
+	of the reviewers' time.
+
+\end{cmt*}
+\vspace{0.1cm}
+\noindent
+\underline{\textbf{Response:}}
+\vspace{0.2cm}
+We are grateful for your thoughtful comments and for expressing interest in our proposed method.
+We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism.
+In the revised version, we have been extra careful to address all grammar issues and have implemented thorough proofreading to minimize similar mistakes in future submissions.
+We greatly appreciate your patience and constructive feedback, which have been invaluable in improving the quality of our manuscript.
+
+\vspace{0.3cm}
+
+%%%%%%%%%%%%% Comment 1.0
+\begin{cmt}{}{}        %% use * when do not need enumerate
+	It seems like Example 1 is introduced as an example to help
+	readers understand the formulation (1) in details. However, it is still
+	vague, and it doesn't easily connect to Figure 3b.
 \end{cmt}
@@
 
-Your Response 1.1
-
-\vspace{0.3cm}
-
-%%%%%%%%%%%%% Comment 1.0
-\begin{cmt*}{}{}        %% use * when do not need enumerate
-
-Comments
-
-\end{cmt*}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-
-Your Response
-
+\begin{example}\label{example:map_exploration}
+	\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see Fig.
+2a).
+The space is modeled as grid points, each with an associated value.
+The goal is to find paths that minimize uncertainty in reconstructing the field.
+Each grid point $j$ is associated with a Kalman Filter (KF) [28] to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot.
+The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in [6]).}
+\end{example}
+\begin{figure}[h]
+	\centering
+	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
+	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+	\caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
+  \end{figure}
 \vspace{0.3cm}
@@
 \begin{cmt}{}{}
-
-Comments 1.2
-
+	Personally, I think to much space is dedicated to the details of how
+	reachability constraints are implemented in the ADMM formulation (Sec.
+	D, E, F, G, H). Although they are important details, I think this part
+	can be condensed more, and some of the details can be deferred to the
+	Appendix, so that some space can be dedicated more to improve the
+	clarity of the other sections.
 \end{cmt}
@@
 \vspace{0.2cm}
-
-Your Response 1.2
 

### 2024-12-08 paper.tex
writting response

@@
 maximum surveillance coverage, minimal energy cost).
-In contrast to our work in \Cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}.
+In contrast to our work in \cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}.
 Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity and to incorporate more complex non-convex constraints.
@@
 This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem.
-%In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
+%In contrast with such approach, our research in \cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
 % \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}
@@
 {\news The rest of this paper is organized as follows.
-\Cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and the security constraints.
-\Cref{sec:cross-trajectory} introduces the enhanced security planning algorithm through cross-trajectory co-observation.
-\Cref{sec:summary} concludes this article.
+\cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and the security constraints.
+\cref{sec:cross-trajectory} introduces the enhanced security planning algorithm through cross-trajectory co-observation.
+\cref{sec:summary} concludes this article.
 
@@
 \begin{example}\label{example:map_exploration}
-\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\Cref{fig:illustration}).
+\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}).
 The space is modeled as grid points, each with an associated value.
@@
 However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
-We allow $\vz = D(\vq)$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy in general ADMM formulation), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ to allow for an easier projection step in \Cref{eq:z-update}.
-In summary, we transform \Cref{eq:general-problem} into
+We allow $\vz = D(\vq)$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy in general ADMM formulation), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ to allow for an easier projection step in \cref{eq:z-update}.
+In summary, we transform \cref{eq:general-problem} into
 \begin{equation}\label{eq:ADMMSetConstraint_modified}
@@
 
-We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for security constraints including co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:ellipsoid-point}-\Cref{eq:region_ellipsoid_constraint}).
-The latter is based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
+We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for security constraints including co-observation security constraints (\cref{sec:co-observation-constraint}), and reachability constraints (\cref{sec:ellipsoid-point}-\cref{eq:region_ellipsoid_constraint}).
+The latter is based on the definition of \emph{ellipse-region-constraint} (\cref{sec:reachability}).
 Formulation of traditional path planning constraints like velocity constraints and convex obstacle constraints can be found in \cite{yang2020multi}, thus are omitted in this paper.
@@
 This constraint is represented as a relative distance requirement between the two robots at a specific time instant, ensuring they are within a defined radius to inspect each other or exchange data.
-%Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \Cref{sec:reachability}, do not intersect with any forbidden regions.
+%Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \cref{sec:reachability}, do not intersect with any forbidden regions.
 
@@
 
-{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
-\Cref{def:secured-plan} can then be restated as follows:
+{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
+\cref{def:secured-plan} can then be restated as follows:
 \begin{definition}\label{rmk:revised-security}
@@
 \newcommand{\oFE}{o}
-{\news To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration).
+{\news To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \cref{fig:EllipseConstraintExample} for an illustration).
 From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
@@
   \begin{proof}
-  See \Cref{proof:Ellipse2PointDiff}.
+  See \cref{proof:Ellipse2PointDiff}.
   \end{proof}
@@
   \begin{proof}
-  See \Cref{proof:dpi_ne_dt}.
+  See \cref{proof:dpi_ne_dt}.
   \end{proof}
@@
 %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}).
-%We apply the new security constraints on the map exploration problem shown in \Cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed.
+%We apply the new security constraints on the map exploration problem shown in \cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed.
 The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}.
@@
 % It's important to note that additional checkpoints (e.g., stationary security cameras) need to be incorporated to generate an attack-proof solution.
-Further solutions to avoid these checkpoints are discussed in \Cref{sec:cross-trajectory}.
+Further solutions to avoid these checkpoints are discussed in \cref{sec:cross-trajectory}.
 
@@
 stationary security camera) need to be incorporated in order to generated an attack-proof solution.
-Additional solutions to avoid these checkpoints will be discussed in \Cref{sec:cross-trajectory}.
+Additional solutions to avoid these checkpoints will be discussed in \cref{sec:cross-trajectory}.
 %The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}.
@@
 Our objective here is to ascertain the existence of feasible paths instead of optimizing specific tasks.
-While the ADMM-based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
+While the ADMM-based solver \cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
 
@@
 The path of a robot $k$ all starts from $v^{+}$ and ends at $v^{-}$, and are represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
-The planning problem can be formulated as a vertex path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \Cref{rmk:revised-security}).
+The planning problem can be formulated as a vertex path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \cref{rmk:revised-security}).
 %Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
@@
 
-We first test the proposed method for the example application in \Cref{fig:example-application,fig:ReachabilitySimulation}, using the same setup in \Cref{sec:ADMM-simulation}.
-Using the parameters $w_{c}=10$, $w_{t}=1$ and $\rho = 0.01$, the result returns a total of $\cK=3$ surveillance robots with cross-trajectory plan shown in \Cref{fig:3-team-ctco}.
-%In \Cref{fig:previous_result_grap}, each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
-The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph \Cref{fig:previous_result_graph}, where each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
-The planning result in the workspace is shown in \Cref{fig:previous_result_plan} as dash-dotted arrows with the same color used for each flow in \Cref{fig:previous_result_graph}.
-Compared with the result in \Cref{fig:ReachabilitySimulation}, it is easy to see that there is a significant improvement in map coverage in \Cref{fig:previous_result_plan}.
+We first test the proposed method for the example application in \cref{fig:example-application,fig:ReachabilitySimulation}, using the same setup in \cref{sec:ADMM-simulation}.
+Using the parameters $w_{c}=10$, $w_{t}=1$ and $\rho = 0.01$, the result returns a total of $\cK=3$ surveillance robots with cross-trajectory plan shown in \cref{fig:3-team-ctco}.
+%In \cref{fig:previous_result_grap}, each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
+The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph \cref{fig:previous_result_graph}, where each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
+The planning result in the workspace is shown in \cref{fig:previous_result_plan} as dash-dotted arrows with the same color used for each flow in \cref{fig:previous_result_graph}.
+Compared with the result in \cref{fig:ReachabilitySimulation}, it is easy to see that there is a significant improvement in map coverage in \cref{fig:previous_result_plan}.
 At the same time, unsecured deviations to the forbidden regions of robots are secured through cross-trajectory observations.
@@
 The problem shows no solution for $\cK\leq 2$.
-For cases $\cK=3$, the problem returns the optimal result as shown in \Cref{fig:Cross-trajectory-result}.
+For cases $\cK=3$, the problem returns the optimal result as shown in \cref{fig:Cross-trajectory-result}.
 If we further increase $\cK>3$, we do not get a better result; instead, the planner will return four flows with the rest $\cK-3$ flows empty.
@@
 We then test the proposed method for 4-team and 7-team cases with results shown in \cref{fig:Cross-trajectory-result}, where four trajectories are provided for a map exploration task with no security-related constraints (co-observation schedule and reachability).
-We have a $10m\times10m$ task space, three forbidden regions (rectangle regions in \Cref{fig:Result-plan}), and robots with a max velocity of $0.5m/dt$.
+We have a $10m\times10m$ task space, three forbidden regions (rectangle regions in \cref{fig:Result-plan}), and robots with a max velocity of $0.5m/dt$.
 
@@
 \subsection{Householder rotations}\label{sec:householder}
-\new{We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \Cref{sec:reachability,sec:ellipse-region-constraint}.
+\new{We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \cref{sec:reachability,sec:ellipse-region-constraint}.
 This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}.

### 2024-12-09 response.tex
finish response reviewer 1

@@
 % \usepackage[colorlinks=true, allcolors=blue]{hyperref}
-% \usepackage{indentfirst}
-% \usepackage{graphicx}
+\usepackage{indentfirst}
+\usepackage{graphicx}
 % \usepackage{subfigure}
@@
 \usepackage{url}
+\usepackage{xcolor}
+\pagenumbering{arabic}
 
@@
 \newtheorem{example}{Example}
-
+\newcommand{\re}{\tcblower \underline{\textbf{Response:}}}
+\newcommand{\rv}{{\Large{\underline{\textbf{Revision:}}}}\quad}
 \usepackage[export]{adjustbox} 
@@
 	of the reviewers' time.
-
-\end{cmt*}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-We are grateful for your thoughtful comments and for expressing interest in our proposed method.
+	\tcblower
+	\underline{\textbf{Response:}} We are grateful for your thoughtful comments and for expressing interest in our proposed method.
 We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism.
@@
 
-\vspace{0.3cm}
-
+\end{cmt*}
+\vspace{0.1cm}
 %%%%%%%%%%%%% Comment 1.0
@@
 	vague, and it doesn't easily connect to Figure 3b.
+	\tcblower
+	\underline{\textbf{Response:}} Example 1 has been revised to improve clarity, with additional illustrative content and an updated figure added to better showcase the example application and its relevance to the proposed approach.
 \end{cmt}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-
+\rv
 \begin{example}\label{example:map_exploration}
-	\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see Fig.
-2a).
-The space is modeled as grid points, each with an associated value.
-The goal is to find paths that minimize uncertainty in reconstructing the field.
-Each grid point $j$ is associated with a Kalman Filter (KF) [28] to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot.
-The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in [6]).}
+\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}).
+The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) [28].
+The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$.
+Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot.
+The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in [6]).
+}
 \end{example}
-\begin{figure}[h]
+\setcounter{figure}{1}
+\begin{figure}[H]
 	\centering
-	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
-	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
-	\caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
+	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4\linewidth,valign=c]{illustration figure_1}} 
+	\subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4\linewidth,valign=c]{SecurityBreak_v2}}
+	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
+	\caption{\new{(2a) Illustration of a 3 robot map exploration task case.
+(2b) The unsecured trajectory design optimized for a map exploration task.
+Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
 \end{figure}
-\vspace{0.3cm}
+{\news In the absence of further security requirements, the robots are expected to spread out and follow a boustrophedon pattern, efficiently exploring as much of the task space as possible (as illustrated in Fig.2b).
+This exploration strategy optimizes coverage and minimizes reconstruction uncertainty across the field.
+}
 
@@
 	clarity of the other sections.
+	\tcblower
+	\underline{\textbf{Response:}} As suggested, we have condensed this section and moved the “Transformation to Canonical Frame” part into the appendix to streamline the main text and improve readability.
+We believe that the remaining details on the implementation of the reachability constraints are essential and provide critical context for understanding the proposed method.
+We appreciate your suggestion, which has helped us enhance the balance and clarity of the manuscript.
 \end{cmt}
-\vspace{0.1cm}
+\rv
+\renewcommand\thesubsection{D}
+ \subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
+{\news	\newcommand{\oFE}{o}
+ To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see Fig.3a for an illustration).
+From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
+The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
+\setcounter{equation}{9}
+\begin{equation}\label{eq:transformations}
+  q=R\Eframe{q}+\oFE,\quad
+  \Eframe{q}=R\transpose(q-\oFE).
+\end{equation}
+where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see Appendix B for details).
+To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e.
+$H(q_1,q_2)$.
+More details on (10) are given in Appendix A.
+  Reachability constraints are formulated with respect to different types of forbidden regions a point, a plane, a segment, and a convex polygon.}
+\renewcommand\thesubsection{F}
+\subsection{Plane-ellipsoid reachability constraint}\label{sec:ellipsoide-plane}
+\new{For a hyperplane shaped forbidden region $\mathcal{L}(q) = \{q\in\mathbb{R}^m: \vn\transpose q = d\}$ (Fig.3c), the reachability constraint is $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.}
+%%
+\renewcommand\thesubsection{G}
+\def\sZ{\mathcal{Z}}
+\subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
+{\news  
+The reachability constraints for a convex polygon is treated as a union of reachability constraints for aeach indivisual segments that define the hyperplane. We define
+\setcounter{constraint}{3}
+\setcounter{equation}{29}
+\begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
+\begin{align}
+D(\vq) &= \bmat{D_{seg1}(\vq)\\D_{seg2}(\vq)\\ \vdots} \label{eq:region_ellipsoid_constraint}\\
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
+   \Pi_\sZ(\vz) & = 0, 
+\end{align}
+\end{constraint}
+where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region. 
+For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
+\begin{equation}
+\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
+\end{equation}
+When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
+red region in Fig.
+3d), the constraint is a plane-ellipse constraint in Section II-F.
+Otherwise (i.e.
+brown region in Fig.
+3d), the constraint is a point-ellipse constraint in Section II-F.
+
+\begin{constraint}[Line-segment-ellipsoid reachability constraint]
+\begin{align}
+D_{seg}(\vq) &=  \begin{cases}
+D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
+D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
+D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
+\end{cases} \label{eq:segment_ellipsoid_constraint}\\
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{seg}(\vq)} = 0 \},\\
+   \Pi_\sZ(\vz) & = 0, 
+\end{align}
+\end{constraint}
+where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function (11) respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint (22).
+with respect to frame $\Eframe {\cL}$.
+This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e.
+keep foci waypoints outside the region, introduced in [6]) to prevent cases where the ellipse is a subset of the region.
+}
+
+\vspace{0.2cm}
+%%%%%%%%%%%%% Comment 1.3
+\begin{cmt}{}{}
+	The word “checkpoint” appears abruptly in page 6 without concrete
+	definition, although it seems like it is an important component of the
+	formulation, and an important design choice for the results. For
+	example, in the way Figure 3 is presented, I don't get a good idea why
+	the checkpoint location is there in (c). 
+	\re 
 	\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
+ For the feedback reguarding the term "checkpoint", the original intent of “checkpoint” in Section 2 was to illustrate the limitations of the method proposed, specifically to show that even if APMAPF yields a valid solution, transforming this solution to a continuous domain may still need additional security measure to guarantee security.
+To address the concern, we have replaced the term “checkpoints” with “key locations” in Section 2 to avoid confusion.
+Additionally, we have added a formal definition of “checkpoints” and the “checkpoint graph” later in Section 3 to provide a clear and precise explanation of these concepts.
+These updates ensure that the term is used consistently and that its role in the methodology is explicitly defined.
+\end{cmt}
+\rv
+\renewcommand\thesubsection{H}
+\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
+We employ the \new{attack-proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a).
+This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
+Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions.
+Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions.
+{\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space.
+In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids.
+Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated.
+For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}
+
+The simulation result, shown in Fig.4b, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3.
+Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots.
+The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable.
+All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.
+
+1) Limitations:
+Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.
+{\news However, two primary challenges need to be addressed.
+Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths.
+For example, agent 3 in~Fig.4b requires additional security measures to create secured reachability areas.
+Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~Fig.2b and Fig.4b.
+The introduction of security constraints resulted in the top left corner remaining unexplored by any robots.
+This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments.
+These challenges are further addressed in Section III, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}
 
@@
 
-%%%%%%%%%%%%% Comment 1.3
 \begin{cmt}{}{}
+	Similarly, how the
+	trajectories are broken down to multiple ellipsoid components are not
+	clear, is it a design choice to make the constraints less conservative
+	than setting a single ellipsoid with the start and goal point?
+	\re 
+	The reachability ellipsoids are designed to work in conjunction with the co-observation technique.
+Instead of using a single ellipsoid defined by the start and goal points, the trajectory is divided into smaller ellipsoids based on co-observation times.
+This approach ensures that the constraints are aligned with the co-observation schedule, reducing conservativeness while maintaining security guarantees.
+We also make modification to Definition 4 (Remark 1 in the original manuscript) to make this more clear.
+\end{cmt}
+\rv
+{\news \setcounter{definition}{3}
+ \begin{definition}\label{rmk:revised-security}
+	A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
+\end{definition}}
 
-Comments 1.3
+\vspace{0.3cm}
+\begin{cmt}{}{}
+	Similarly, in page 7, “key locations” and “checkpoint graph” are
+	mentioned without clear explanations what they are.
+	\re  
+	In Section III, we add additional definition to 'checkpoint' and 'checkpoint graph'
+\end{cmt}
+\rv
 
+{\news
+Our strategy is based on the following concept:
+\setcounter{definition}{5}
+\setcounter{remark}{1}
+\begin{definition}
+The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$.
+It represents either the first or last instance where a robot is co-observed by a teammate, and serves as a point where the robot can leave or join a new team.
+% at which a robot is co-observed by its teammates, and where it can leave or join a new team. 
+\end{definition}
+For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. %, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding location and time for checkpoint $v_{pi}$.
+To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
+\begin{remark}\label{rmk:checkpoints}
+  A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
+  \end{remark}
+}
+{\news 
+\begin{definition}
+  The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where $V = (\union_p V_p) \union V_c$ is the set of verticies representing waypoints on the planned trajectory and $E = E_{t} \union E_{c}$ is the set of edges representing feasible paths connecting $V$.
+The components of the checkpoint graph are defined as follows:
+  \begin{description}
+    \item[Checkpoints $V_p$] where additional robots are required for security through co-observation.
+    \item[Trajectory edges $E_t$] represent the original planned path of the primary robot.
+    \item[Connection vertices $V_c$] represent non-checkpoint locations linked via $E_c$.
+    \item[Cross-trajectory edges $E_c$] represent feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support, at least one endpoint be a checkpoint.
+  \end{description}
+\end{definition}}
+\vspace{0.3cm}
+\begin{cmt}{}{}
+	The plots are not reader-friendly at all. In all figures, trajectory
+	lines are too thin. The legend text is too small. In figure 2, there is
+	no number scale for (b) and I am even not sure if this corresponds to
+	the same scenario as (a) and (c). In Figure 5, the color of the
+	sub-team robots seem like not matching with the main robots.
+	\re We have re-plotted the figures to make them more reader-friendly by thickening trajectory lines, enlarging legend text, and ensuring consistent coloring between sub-team robots and main robots in Figure 7 and Figure 8  (Figure 5 and 6 in original manuscript).
+
+	For Figure 2, we appreciate the comment regarding the lack of a number scale especially on (b,c,d).
+The intention of these figures are to illustrate the geometric relationships between ellipsoids and different shapes, as well as the transformation of coordinates.
+To maintain focus on these aspects, we chose to omit the number scale and believe that it is not essential for conveying the intended concept.
+\end{cmt}
+\rv
+\setcounter{figure}{1}
+\begin{figure}[H]
+	\centering
+	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4	\linewidth,valign=c]{illustration figure_1}} 
+	\subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4	\linewidth,valign=c]{SecurityBreak_v2}}
+	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
+	\caption{\new{(2a) Illustration of a 3 robot map exploration task case.
+(2b) The unsecured trajectory design optimized for a map exploration task.
+Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
+  \end{figure}
+\setcounter{figure}{3}
+  \begin{figure}[H]
+	\centering
+	% \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.4	\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth,valign=c]{Grid_world}}
+	% \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4	\linewidth,valign=c]{SecurityBreak_v2}}
+	\subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
+	\caption{{\news Trajectory design a three-robot system based on the grid world result.
+Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
+	\label{fig:example-application}
+  \end{figure}
+  \setcounter{figure}{6}
+  \begin{figure}[H]
+	\centering
+	\subfloat[Cross-trajectory co-observation plan \label{fig:previous_result_plan}]{\includegraphics[width=0.4\linewidth, trim = 2cm 1cm 1cm 1cm,clip,valign=b]{old_result_v2}}
+	\subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.4\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
+	\caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as arrows on top of the original plan in \cref{fig:previous_result_plan}.
+(\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}
+	\label{fig:3-team-ctco}
+  \end{figure}
+
+  \begin{figure}[H]
+	\centering
+	%\subfloat[Unsecured plan\label{fig:unsecured-plan}]{\includegraphics[width=0.31\linewidth, trim = 3cm 2cm 3cm 2cm, clip,valign=c]{SecurityBreak}}
+	\subfloat[4-agent case\label{fig:Result-plan}]{\includegraphics[width=0.4\linewidth,trim = 1cm 1cm 1.5cm 0cm, clip,valign=c]{Traj_result_v3.png}}
+	%\subfloat[Graph flow result\label{fig:result-graph}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{Graph_result}}
+	\subfloat[7-agent case\label{fig:Result-plan-7-team}]{\includegraphics[width=0.4\linewidth,trim = 3.5cm 2cm 1.5cm 0cm, clip,valign=c]{7-team-plan_v2.png}}
+	%\subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
+	\caption{\new{(\ref{fig:Result-plan}) Cross-trajectory co-observation result of a 4 sub-teams task.
+(\ref{fig:Result-plan-7-team}) Cross-trajectory co-observation result of a 7 sub-teams task.}}\label{fig:Cross-trajectory-result}
+  \end{figure}
+\vspace{0.2cm}
+
+\begin{cmt}{}{}
+	The author assumes “Zone 1” is tolerable and Zone 2 and 3 are hard
+constraints, but what if the environment is the opposite? Do you get
+infeasible solution? It is very skeptical that the author is making
+deliberate assumptions to make the example work in a special case.
+\re We acknowledge the limitation of the method proposed in Section II, as it relies on the specific setup, and a safe solution is not always guaranteed to exist.
+This limitation is explicitly discussed in the manuscript.
+The chosen result is deliberate, not to make the example work in a special case, but to illustrate that even when APMAPF finds a solution in the grid world, such a plan may fail to guarantee security when transformed into the continuous domain, requiring further manual adjustments.
+In the revised version, we have further emphasized these limitations and the challenges they aim to address in the simulation results.
+Corre
 \end{cmt}
 \vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
+\rv
+\renewcommand\thesubsection{H}
+\subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
+We employ the \new{attack-proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a).
+This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
+Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions.
+Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions.
+{\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space.
+In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids.
+Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated.
+For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}
 
-Your Response 1.3
+The simulation result, shown in Fig.4b, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3.
+Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots.
+The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable.
+All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.
 
-\vspace{0.3cm}
+1) Limitations:
+Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.
+{\news However, two primary challenges need to be addressed.
+Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths.
+For example, agent 3 in~Fig.4b requires additional security measures to create secured reachability areas.
+Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~Fig.2b and Fig.4b.
+The introduction of security constraints resulted in the top left corner remaining unexplored by any robots.
+This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments.
+These challenges are further addressed in Section III, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}
 
+\begin{cmt}{}{}
+	p 8 - A heuristic approach is provided (Algorithm 1); Is it
+	almost impossible for the reader to decipher this algorithm without any
+	explanations in words.
+\re	We have replaced the algorithm with a more detailed and understandable word-based explanation to improve readability and make the approach easier to follow.
+\end{cmt}
+\rv {\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
+Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
+$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$.
+Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$.
+Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$.
+Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$.
+Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process.
+The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$.
+A toy example is shown in \cref{fig:checkpoint-generate}.
+}
+
+\begin{cmt}{}{}
+	Similar to the comment above, it will be good to introduce what the
+“network multi-flow problem” is.
+\re 
+We have add additional content to introduce the what the "network multi-flow problem" in our setup.
+\end{cmt}
+\rv \new{We assume that the planned trajectory for each sub-team has a robot operating on it.
+The co-observation planning problem is then transformed into a network multi-flow problem by modeling the additional robots as flows traveling through $G$.
+These flows either follow the planned trajectory via trajectory edges $E_t$ or switch teams via cross-trajectory edges $E_c$ to ensure valid and secured paths.
+Additionally, they are required to visit every checkpoint $V_p$ to meet the security requirements introduced in~\ref{rmk:checkpoints}.
+This formulation reduces the co-observation problem to finding valid flow patterns in $G$.
+The problem is then formulated into linear objectives and constraints, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
+}
+
+\begin{cmt}{}{}
+	p3 - “rotation derived from a modifie version of Householder
+transformations [25].” ; At least a brief introduction of
+Householder transformations (in words) must be included for readers who
+are not familiar with it.
+\re A brief introduction of Householder transformation is added.
+\end{cmt}
+\rv \new{the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see Appendix B for details).}
+
+\begin{cmt}{}{}
+This reachability ellipsoid is an over approximation of the exact
+reachability region in Definition 3.”; A proof or at least a
+reference to the proof should be provided.
+\re While we believe that a formal proof is not necessary for this context, we have added additional content to make the approximation more intuitive.
+This includes a clearer explanation of how the reachability ellipsoid relates to the exact reachability region.
+These additions aim to enhance the reader's understanding without requiring formal proof.
+\end{cmt}
+\rv {\news
+\begin{definition}\label{sec:ellipsoidal definition}
+Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
+\end{definition}
+
+For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):
+\begin{definition}\label{def:Reachability}
+	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
+\end{definition}
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+\begin{cmt}{}{}
+	Other grammar related comments.
+	\re We have carefully reviewed and corrected all listed grammar mistakes, as well as others that were not explicitly mentioned. 
+\end{cmt}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 2

### 2024-12-09 paper.tex
finish response reviewer 1

@@
 \end{equation}
-
 To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.
@@
 \begin{example}\label{example:map_exploration}
-\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}).
+\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}).
+The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}.
+The KF estimates uncertainty at each point through its covariance $P_j$ updated based on the measurements taken by robots along the trajectory $\vq$.
+Measurement quality, modeled by a Gaussian radial basis function, decreases with distance from the robot.
+The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}).
+}
+\end{example}
+\begin{figure}
+  \centering
+  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,valign=c]{illustration figure_1}} 
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
+(\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task.
+Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
+\end{figure}
+
+% To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.
+
+% \begin{example}\label{example:map_exploration}
+% \new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}).
 The space is modeled as grid points, each with an associated value.
@@
 The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}
-
-% Robots are tasked to navigate, collecting sensory data of an unknown task space to map a slowly-varying field, denoted as $\vx$, (see Figure~\ref{fig:SecurityBreak}).
-The map comprises points of interest arranged on a grid, each associated with a slowly-changing value.
-Our goal is to find paths that minimize uncertainty and effectively reconstruct the field.
-We associate a Kalman Filter (KF)~(cf.
-\cite{anderson2012optimal}) to each point $j$, and use it to track the uncertainty through its estimated covariance $P_j$.
-The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality.
-The optimization objective $\varPhi(\vq)$ is written as the maximum uncertainty $\max_j P_{j}$ (detailed formulation can be found in \cite{yang2020multi}).
-\end{example}
-\begin{figure}
-  \centering
-  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
-  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
-  \caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
-\end{figure}
+% \end{example}
+% \begin{figure}
+%   \centering
+%   \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
+%   \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+%   \caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
+% \end{figure}
 
@@
 
-To incorporate the security against malicious deviations (through co-observation and reachability analysis) as constraints in the optimal trajectory planning problem, we define the security as:
+{\news In the absence of further security requirements, the robots are expected to spread out and follow a boustrophedon pattern, efficiently exploring as much of the task space as possible (as illustrated in~\cref{fig:SecurityBreak}).
+This exploration strategy optimizes coverage and minimizes reconstruction uncertainty across the field.
+}To incorporate the security against malicious deviations (through co-observation and reachability analysis) as constraints in the optimal trajectory planning problem, we define the security as:
 \begin{definition}\label{def:secured-plan}
@@
   \end{equation}
-\subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
-{\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
-For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
-\begin{equation}
-\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
-\end{equation}
-When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
+% \subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
+% {\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
+% For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
+% \begin{equation}
+% \bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
+% \end{equation}
+% When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
 red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}.
@@
 
-\begin{constraint}[Line-segment-ellipsoid reachability constraint]
-\begin{align}
-D(\vq) &=  \begin{cases}
-D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
-D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
-D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
-\end{cases} \label{eq:segment_ellipsoid_constraint}\\
-  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
-   \Pi_\sZ(\vz) & = 0, 
-\end{align}
-\end{constraint}
-where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}.
+% \begin{constraint}[Line-segment-ellipsoid reachability constraint]
+% \begin{align}
+% D(\vq) &=  \begin{cases}
+% D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
+% D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
+% D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
+% \end{cases} \label{eq:segment_ellipsoid_constraint}\\
+%   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
+%    \Pi_\sZ(\vz) & = 0, 
+% \end{align}
+% \end{constraint}
+% where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}.
 with respect to frame $\Eframe {\cL}$.
-
 \subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}
-For reachability constraints with respect to a convex polygon, the first step is to keep all segments that define the hyperplane outside the reachability ellipsoid.
-Similar to \eqref{equ:ProjectPoint}, we define
+{\news  
+The reachability constraints for a convex polygon is treated as a union of reachability constraints for aeach indivisual segments that define the hyperplane. We define
 \begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
@@
 where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region. 
+For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
+\begin{equation}
+\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
+\end{equation}
+When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
+red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}.
+Otherwise (i.e.
+brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.
+
+\begin{constraint}[Line-segment-ellipsoid reachability constraint]
+\begin{align}
+D_{seg}(\vq) &=  \begin{cases}
+D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
+D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
+D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
+\end{cases} \label{eq:segment_ellipsoid_constraint}\\
+  \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D_{seg}(\vq)} = 0 \},\\
+   \Pi_\sZ(\vz) & = 0, 
+\end{align}
+\end{constraint}
+where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}.
+with respect to frame $\Eframe {\cL}$.
 This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e.
 keep foci waypoints outside the region, introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
-
+}
 \subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
-
-We test the newly introduced security constraints with~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}.
-The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$.
 %All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent.
@@
   % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
-  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.45\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
-  \caption{{\news Trajectory design of a map exploration task for a three-robot system based on the grid world result~\cref{fig:Grid-example-application}.
+  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth,valign=c]{Grid_world}}
+  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
+  \caption{{\news Trajectory design a three-robot system based on the grid world result.
 Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
-(\ref{fig:SecurityBreak}) The unsecured trajectory design in continuous world, optimized with respect to a map exploration task with Zone 1 and 2 considered together as one obstacle.
-A potential path that could break the security by entering region 1 is highlighted as the red dashline.
-(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation and reachability constraints.}}
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
   \label{fig:example-application}
@@
   %\subfloat[Unsecured plan\label{fig:unsecured-plan}]{\includegraphics[width=0.31\linewidth, trim = 3cm 2cm 3cm 2cm, clip,valign=c]{SecurityBreak}}
-  \subfloat[4-agent case\label{fig:Result-plan}]{\includegraphics[width=0.47\linewidth,trim = 3.5cm 2cm 1.5cm 0cm, clip,valign=c]{Traj_result_v2}}
+  \subfloat[4-agent case\label{fig:Result-plan}]{\includegraphics[width=0.47\linewidth,trim = 1cm 1cm 1.5cm 0cm, clip,valign=c]{Traj_result_v3.png}}
   %\subfloat[Graph flow result\label{fig:result-graph}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{Graph_result}}

### 2024-12-09 response.tex
update

@@
 \newcommand{\re}{\tcblower \underline{\textbf{Response:}}}
-\newcommand{\rv}{{\Large{\underline{\textbf{Revision:}}}}\quad}
+\newcommand{\rv}{{\large{\underline{\textbf{Revision:}}}}\quad}
 \usepackage[export]{adjustbox} 
@@
 %%%%%%%%%%%%% Comment 2.1
+\begin{cmt*}{}{}
+	This paper proposed a novel multi-robot optimal planning algorithm that
+	integrated mutual observations and introduced reachability constraints
+	for enhanced security, which ensures that, even with adversarial
+	movements, compromised robots cannot breach forbidden regions without
+	missing scheduled co-observations. The contribution of this paper is
+	hard evaluate due to the organization. 
+	\re We sincerely thank the reviewer for their valuable comments and feedback.
+We acknowledge the concern regarding the organization of the manuscript, which may have made it challenging to fully evaluate the contributions.
+In the revised version, we have carefully restructured the manuscript to improve its organization and readability, ensuring that the key contributions are presented more clearly and effectively.
+We greatly appreciate your valuable feedback, which has been instrumental in enhancing the quality of our work.
+\end{cmt*}
+%%%%%%%%%%%%% Comment 2.1
 \begin{cmt}{}{}
-
-Comments 2.1
-
+The dimension of p is erroneously defined;
+\re After carefully reviewing the manuscript, we believe the reviewer might have meant the dimension of $q$ rather than $p$.
+In the revised version, we have corrected the definition of $q$ to ensure clarity and accuracy.
+Thank you for bringing this to our attention.
 \end{cmt}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-
-Your Response 2.1
-
-\vspace{0.3cm}
-
-%%%%%%%%%%%%% Comment 2.2
-\begin{cmt}{}{}
-
-Comments 2.2
-
-\end{cmt}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-
-Your Response 2.2
-
-\vspace{0.3cm}
+\rv {\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
+For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
+}
 
@@
 \begin{cmt}{}{}
-
-Comments 2.3
+There are many grammar errors, please check it carefully
+\re We have carefully reviewed and corrected all identified grammar issues, as well as others not explicitly mentioned.
+The revised manuscript has undergone thorough proofreading to ensure clarity and grammatical accuracy.
 
 \end{cmt}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
-
-Your Response 2.3
-
-\vspace{0.3cm}
 
@@
 \begin{cmt}{}{}
+In Definition 1, is reasonable to say ``any potential deviations''?
+\re We believe that this phrase is resonable and essential to the definition and intention of security against plan-deviation attacks.
+The definition is designed to ensure that the trajectory plan accounts for all possible paths a compromised robot might take toward forbidden regions.
+By explicitly requiring that any such deviation results in the robot missing its next co-observation, the definition provides a rigorous and comprehensive security guarantee.
+As such, the phrase "any potential deviations" accurately reflects the intended scope of the definition.
+\end{cmt}
 
-Comments 2.4
+\begin{cmt}{}{}
+	In the definition of $U$, what does ``,'' mean?
+	\re  We are not entirely sure what the specific concern or issue is in this context.
+However, if the reviewer is referring to $u'$ , it was intended to denote the vector $u$ before normalization.
+To avoid any potential confusion, we have revised the notation in the updated manuscript.
+We appreciate your feedback and have taken steps to ensure clarity in this definition.
+\end{cmt}
+\setcounter{definition}{8}
+\setcounter{equation}{41}
+\rv {\news \begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
+	% \begin{equation}
+	%   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
+	% \end{equation}
+  the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
+	\begin{equation}\label{eq:H definition}
+	  H(\nu_1,\nu_2) = 2 u u\transpose-I.
+	\end{equation}
+  \end{definition}}
+\begin{cmt}{}{}
+	How to solve (9a)?
+	\re  In practical applications, Eq.4a (originally 9a) is solved iteratively using a nonlinear optimization solver, such as \emph{fmincon}.
+Additionally, the derivatives of the constraint projection functions, as derived later in the manuscript, are specifically utilized to solve the optimization problem more efficiently and quickly.
+These derivatives enhance the solver's performance by providing necessary gradient information, improving convergence speed.
+We have clarified these points in the revised manuscript to provide further insight into the solution process.
+\end{cmt}
+\rv {\news
+\setcounter{remark}{0}
+\begin{remark}
+In practical application, (4a) is solved iteratively via a nonlinear optimization solver like \emph{fmincon}.
+The gradients of the constraint functions, derived later, is used to enhance solver efficiency and accuracy.
+Meanwhile, (4b) and (4c) have closed form solutions.
+\end{remark}
+}
+\begin{cmt}{}{}
+	How to define $d_{\max}$ in (14)?
+	\re $d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.
+\end{cmt}
+\setcounter{constraint}{0}
+\rv \begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
+	\begin{align}
+	D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:coobservation_constraint}\\
+	  \sZ &= \{\vz \mid \norm{\vz} \leq d_{max} \},\\
+	   \Pi_\sZ(z) & = \begin{cases}
+	d_{max}\frac{\vz}{\norm{\vz}} &\text{if } \norm{\vz} > d_{max},\\
+	\vz	& otherwise,
+	\end{cases}
+	\end{align}
+	where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.}
+	\end{constraint}
 
+\begin{cmt}{}{}
+	In Definition 4, it is unclear that $\mathcal E$ is an ellipsoid. There is no definition of the function $d(\cdot,\cdot)$;
+	\re In the revised manuscript, we have added additional explanations to clarify that $\cE$ is an ellipsoid and to explicitly define the function $d(\cdot,\cdot)$ to avoid confusion and ensure clarity.
 \end{cmt}
-\vspace{0.1cm}
-\noindent
-\underline{\textbf{Response:}}
-\vspace{0.2cm}
+\rv {\news \setcounter{definition}{1}
+\begin{definition}\label{sec:ellipsoidal definition}
+Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
+\end{definition}
 
-Your Response 2.4
-
-\vspace{0.3cm}
-
+For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):
+\begin{definition}\label{def:Reachability}
+	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
+\end{definition}
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
 \end{document}

### 2024-12-09 paper.tex
update

@@
 \begin{remark}
-In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver like \emph{fmincon}, while \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
+In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver like \emph{fmincon}.
+The gradients of the constraint functions, derived later, is used to enhance solver efficiency and accuracy.
+Meanwhile, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
 \end{remark}
@@
 \begin{definition}\label{def:Reachability}
-	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
+	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
 \end{definition}
@@
 }
-
 \subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}

### 2024-12-10 response.tex
Finished

@@
 \newtheorem{example}{Example}
-\newcommand{\re}{\tcblower \underline{\textbf{Response:}}}
+\newcommand{\re}{\tcblower \underline{\textbf{Response:}}\quad}
 \newcommand{\rv}{{\large{\underline{\textbf{Revision:}}}}\quad}
@@
 \end{figure}
-{\news In the absence of further security requirements, the robots are expected to spread out and follow a boustrophedon pattern, efficiently exploring as much of the task space as possible (as illustrated in Fig.2b).
-This exploration strategy optimizes coverage and minimizes reconstruction uncertainty across the field.
-}
+{\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
+To address potential threats, we adopt the \emph{physical masquerade attacks} framework from [2], where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection.
+The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
+These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan.
+The corresponding security requirement can then be formally defined as:}
+\begin{definition}\label{def:secured-plan}
+  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\end{definition}
 
@@
 \setcounter{constraint}{0}
+\setcounter{equation}{6}
 \rv \begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
@@
 This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+
+\begin{cmt}{}{}
+	It is unclear about how to ensure the security. Where is the attack?
+	\re We have added a detailed description of the attacker model in the revised manuscript, outlining how a compromised robot attempts to gain unauthorized access while masquerading as legitimate.
+The mechanisms for ensuring security are formally described in Definition 1 and further extended in Definition 4 and Remark 2, which outline the requirements and constraints necessary to detect and mitigate such attacks effectively.
+\end{cmt}
+\rv {\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
+To address potential threats, we adopt the \emph{physical masquerade attacks} framework from [2], where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection.
+The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
+These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan.
+The corresponding security requirement can then be formally defined as:}
+\setcounter{definition}{0}
+\begin{definition}\label{def:secured-plan}
+  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\end{definition}
+\setcounter{definition}{3}
+\setcounter{remark}{1}
+
+{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
+\cref{def:secured-plan} can then be restated as follows:
+\begin{definition}\label{rmk:revised-security}
+  A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
+\end{definition}
+}
+
+{\news To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions.
+This requirement can be formally stated as:
+\begin{remark}\label{rmk:checkpoints}
+  A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
+  \end{remark}
+}
+\begin{cmt}{}{}
+	Please check the reference format carefully.
+	\re Thank you for pointing this out. We have carefully reviewed and revised the reference format in the manuscript to ensure consistency and compliance with the journal's guidelines.
+\end{cmt}
+\newpage
+\section{Response to reviewer 3} 
+\begin{cmt}{}
+	Please check the grammar and typos, here are some within the first two pages:
+	\dots
+	I stop marking these typos after page 2, but please do a careful proof-read of your own paper. 
+	\re  We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism.
+In the revised version, we have been extra careful to address all grammar issues and have implemented thorough proofreading to minimize similar mistakes in future submissions.
+We greatly appreciate your patience and constructive feedback, which have been invaluable in improving the quality of our manuscript.
+\end{cmt}
+\begin{cmt}{}{}
+	Some definitions and symbols are not clearly explained:
+	1) First paragraph of Sec 2: the dimension of $q$ should be $n_p*m*T$
+	right? Further, how is it aggregated? In what order?	
+	\re In the revised manuscript, we have clarified that the dimension of $q$ have been clearified and have further explained the aggregation process.
+\end{cmt}
+\rv {\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
+For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
+}
+\begin{cmt}{}{}
+	Def 2: what is $\hat v_F$ and $\hat v_\epsilon$? Also $v_F$ and $v_e$ are defined later, so not proper to use here. 
+	\re We acknowledge that in Definition 2 (Definition 9 in the revised manuscript) $\hat v_F$ and $\hat v_\epsilon$ were typographical errors and have been corrected in the revised manuscript.
+Additionally, the terms $v_F$ and $v_e$ have been modified to ensure proper introduction and to avoid confusion.
+\end{cmt}
+\setcounter{definition}{8}
+\setcounter{equation}{41}
+\rv 
+{\news 
+\begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
+	% \begin{equation}
+	%   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
+	% \end{equation}
+  the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
+	\begin{equation}\label{eq:H definition}
+	  H(\nu_1,\nu_2) = 2 u u\transpose-I.
+	\end{equation}
+  \end{definition}}
+
+  \begin{cmt}{}{}
+	3) What is the difference between lowercase letters and bold-type
+lowercase letters? If bold-type denotes vectors, then why $x(t)$ in
+eq(2), u, v's in eq (3) not in bold-type?  
+\re We apologize for the confusion regarding the notation.
+To address this, we have added additional clarification in the revised manuscript.
+Specifically, we use non-bold symbols to denote single-agent states (e.g.
+$q_{ij}$) and scalars, while bold symbols represent aggregated states of a single robot or multiple robots (e.g., $\vq$).
+This distinction has been made explicit to avoid further ambiguity.
+  \end{cmt}
+  \rv {\news 
+  \noindent\myparagraph{Notation} 
+  In this paper, we use non-bold symbols like to denote single-agent states (e.g.
+$q_{ij}$) and scalers, while bold symbols represent aggregated states of single robot and multiple robots (e.g.
+$\vq$).
+}
+
+  \begin{cmt}{}{}
+3)	Def 3: the 'workspace' is not specified before. The function
+d(q1,q2) is not defined. Further, this def is confusing, do you want to
+say that the reachability region is the union of all trajectory states,
+such that starting from q(t1) = q1, you are able to reach q(t2) = q2
+while satisfying the speed constraints?
+
+4) Def 4: what is $v_{maq}$? Why is the ellipsoid an
+over-approximation of reachability region? 
+\re Thank you for pointing out the issues on Definition 3 (Definition 2 in the new manuscript).
+In the revised manuscript, we have modified the term 'workspace' for clarity, refined the definition to avoid confusion, and added a detailed description of the function $ d(q_1, q_2)$, which represents the Euclidean distance between $q_1$  and  $q_2$ .
+These changes aim to ensure the definition accurately conveys that the reachability region is the union of all trajectory states satisfying the specified conditions.
+
+As for Defnintion 4 (Definition 3 in the new manuscript), we acknowledge that the term $v_{maq}$ as a typographical error, and it has been corrected to $v_{max}$ in the revised manuscript.
+Additionally, we have provided a more detailed explanation to clarify why the ellipsoid is an over-approximation of the reachability region.
+Specifically, it represents the set of points $q'$ whose sum of distances two foci $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid.
+  \end{cmt}
+  \setcounter{definition}{1}
+  \rv {\news
+  \begin{definition}\label{sec:ellipsoidal definition}
+  Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$.
+The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
+  \end{definition}
+
+  For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):
+  \begin{definition}\label{def:Reachability}
+	  The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
+  \end{definition}
+  This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+
+  \begin{cmt}{}{}
+	 Fig 3: legends are too small. 
+	\re We acknowledge that the legends and other aspects of the figures in the original manuscript were not clear.
+In the revised manuscript, we have addressed these issues by replotting the figures, including Figure 3, to ensure readability and clarity.
+  \end{cmt}
+  \rv \setcounter{figure}{1}
+  \begin{figure}[H]
+	  \centering
+	  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4\linewidth,valign=c]{illustration figure_1}} 
+	  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4\linewidth,valign=c]{SecurityBreak_v2}}
+	  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
+	  \caption{\new{(2a) Illustration of a 3 robot map exploration task case.
+(2b) The unsecured trajectory design optimized for a map exploration task.
+Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
+  \end{figure}
+  \setcounter{figure}{3}
+  \begin{figure}[H]
+	\centering
+	% \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.4	\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth,valign=c]{Grid_world}}
+	% \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4	\linewidth,valign=c]{SecurityBreak_v2}}
+	\subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
+	\caption{{\news Trajectory design a three-robot system based on the grid world result.
+Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
+	\label{fig:example-application}
+  \end{figure}
+  \begin{cmt}{}{}
+	4. The idea of the reachability ellipse seems very similar to another
+idea called 'safe flight corridor' from
+ "Liu, Sikang, et al. "Planning dynamically feasible trajectories for
+quadrotors using safe flight corridors in 3-d complex environments."
+IEEE Robotics and Automation Letters 2.3 (2017): 1688-1695." 
+What is this essential difference between these two methods? 
+\re Thank you for highlighting the potential similarity between the reachability ellipse and the Safe Flight Corridor (SFC) method.
+Our approach differs fundamentally in its purpose and application.
+Unlike the ellipsoids in IRIS and SFC, which are designed to approximate collision-free spaces, the reachability region in our method explicitly maps all reachable states given several known states (and regardless of collision) and is tailored to address security concerns.
+
+In the revised manuscript, we have included more detailed content to clarify this distinction and provide a comprehensive explanation of the differences between our approach and SFC.
+  \end{cmt}
+  \rv {\news Ellipsoids are also used in other path-planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) [24],[25] and the Safe Flight Corridor (SFC) [26],[27].
+Differing from the reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximating the safe collision-free space rather than addressing security applications.}
+
+  {\news\noindent [24] R.
+Deits and R.
+Tedrake, “Computing large convex regions of obstacle- free space through semidefinite programming,” in Algorithmic Founda- tions of Robotics XI: Selected Contributions of the Eleventh International Workshop on the Algorithmic Foundations of Robotics.
+Springer, 2015, pp.
+109–124.
+
+  \noindent[25] A.
+Ray, A.
+Pierson, and D.
+Rus, “Free-space ellipsoid graphs for multi- agent target monitoring,” in 2022 International Conference on Robotics and Automation (ICRA).
+IEEE, 2022, pp.
+6860–6866.
+
+  \noindent[26] S.
+Liu, M.
+Watterson, K.
+Mohta, K.
+Sun, S.
+Bhattacharya, C.
+J.
+Taylor, and V.
+Kumar, “Planning dynamically feasible trajectories for quadrotors using safe flight corridors in 3-d complex environments,” IEEE Robotics and Automation Letters, vol.
+2, no.
+3, pp.
+1688–1695, 2017.
+
+  \noindent[27] D. Fan, Q. Liu, C. Zhao, K. Guo, Z. Yang, X. Yu, and L. Guo, “Flying in narrow spaces: Prioritizing safety with disturbance-aware control,” IEEE Robotics and Automation Letters, 2024.
+  }
 \end{document}

### 2024-12-10 paper.tex
Finished

@@
   \centering
-  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,valign=c]{illustration figure_1}} 
-  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v2}}
   % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
@@
 
-% To give a concrete example of the cost $\varPhi$ and the set $\Omega$, we introduce a representative application that will be used for all the simulations throughout the paper.
-
-% \begin{example}\label{example:map_exploration}
-% \new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}).
-The space is modeled as grid points, each with an associated value.
-The goal is to find paths that minimize uncertainty in reconstructing the field.
-Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot.
-The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}
-% \end{example}
-% \begin{figure}
-%   \centering
-%   \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
-%   \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
-%   \caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
-% \end{figure}
-
-% \begin{definition}\label{def:secured-plan}
-%   A multi-robot trajectory plan is secure again plan-deviation attacks if it ensures that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
-% \end{definition}
-
-{\news In the absence of further security requirements, the robots are expected to spread out and follow a boustrophedon pattern, efficiently exploring as much of the task space as possible (as illustrated in~\cref{fig:SecurityBreak}).
-This exploration strategy optimizes coverage and minimizes reconstruction uncertainty across the field.
-}To incorporate the security against malicious deviations (through co-observation and reachability analysis) as constraints in the optimal trajectory planning problem, we define the security as:
+{\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
+To address potential threats, we adopt the \emph{physical masquerade attacks} framework from~\cite{wardega2019resilience}, where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection.
+The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
+These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan.
+The corresponding security requirement can then be formally defined as:}
 \begin{definition}\label{def:secured-plan}
@@
   % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth,valign=c]{Grid_world}}
+  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
   % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
-  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
+  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
   \caption{{\news Trajectory design a three-robot system based on the grid world result.

### 2024-12-12 response.tex
last notes

@@
 	The reachability ellipsoids are designed to work in conjunction with the co-observation technique.
-Instead of using a single ellipsoid defined by the start and goal points, the trajectory is divided into smaller ellipsoids based on co-observation times.
+Instead of using a single ellipsoid defined by the start and goal points, the ellipsoid are defined by smaller ellipsoids between two consecutive co-observation times.
 This approach ensures that the constraints are aligned with the co-observation schedule, reducing conservativeness while maintaining security guarantees.
@@
 In the revised version, we have further emphasized these limitations and the challenges they aim to address in the simulation results.
-Corre
 \end{cmt}
@@
 	explanations in words.
-\re	We have replaced the algorithm with a more detailed and understandable word-based explanation to improve readability and make the approach easier to follow.
+\re	We have replaced the algorithm with more detailed and understandable prose to improve readability and make the approach easier to follow.
 \end{cmt}

### 2024-12-12 paper.tex
last notes

@@
 Multi-robot systems (MRS) have found wide applications in various fields.
-While offering numerous advantages, the distributed nature and dependence on network communication render the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
-This paper addresses a specific scenario in which robots are compromised by attackers and directed to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
-Such countering deliberate deviations, termed \emph{plan-deviation attacks}, are identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}.
-As a security measure, we utilized the onboard sensing capabilities of the robots to perform inter-robot co-observations and check for unusual behavior.
-These mutual observation establish a co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.
-
-A preliminary version of the paper is presented in \cite{yang2020multi,yang2021multi}.
-Extending the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)}-based trajectory optimization solver to accommodate for more flexible objectives.
-In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
+Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
+This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+{\news A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
+These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}
+
+A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}.
+That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives.
+However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance.
+As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}
+In this paper, we incorporate an additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
 This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
 We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
-We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.
-
-However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance.
-As an extension of the previous works \cite{yang2020multi,yang2021multi}, we also address the feasibility and optimality challenges.
+We present a mathematical formulation of the reachability regions \new{as spatio-temporal constraints} compatible with the solver in \cite{yang2020multi}.
+ we also address the feasibility and optimality challenges.
 For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.
@@
 \begin{example}\label{example:map_exploration}
-\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}).
+\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}).
 The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}.
@@
 
-{\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
-To address potential threats, we adopt the \emph{physical masquerade attacks} framework from~\cite{wardega2019resilience}, where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection.
+{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimizing coverage, and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
+However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as properly functioning agent, attempts to gain access to unauthorized locations without detection.
 The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
-These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan.
+These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan.
 The corresponding security requirement can then be formally defined as:}
@@
 \begin{remark}
-In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver like \emph{fmincon}.
-The gradients of the constraint functions, derived later, is used to enhance solver efficiency and accuracy.
-Meanwhile, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
+In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon} \rtron{Add ref}.
+The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation).
+At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
 \end{remark}
@@
 
-We employ the \new{attack-proof MAPF(APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
 This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
@@
   % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
+  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
   % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
-  \subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
+  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,trim =2cm 1.8cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
   \caption{{\news Trajectory design a three-robot system based on the grid world result.
 Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
-(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective.
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective.
 (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
@@
 
-{\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
+{\news \rtron{Use enumerate} We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
 Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.

### 2024-12-12 paper.tex
Finish main paper

@@
 Multi-robot systems (MRS) have found wide applications in various fields.
-Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
-This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+\new{Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.} This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
 {\news A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
@@
 As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}
-In this paper, we incorporate an additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
+
+In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature.
 This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots.
@@
 We present a mathematical formulation of the reachability regions \new{as spatio-temporal constraints} compatible with the solver in \cite{yang2020multi}.
- we also address the feasibility and optimality challenges.
-For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.
-These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
+
+\new{Furthermore, we address the feasibility and optimality challenges.
+For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
 The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another.
@@
 	\centering
-    \subfloat[Plan-deviation attack\label{fig:example-plan-dev}]{\includegraphics[width = 0.32\linewidth]{plan-deviation}}
-    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.32\linewidth]{co-observ}}
-    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.32\linewidth]{cross-traj}}
+    \subfloat[Plan-deviation attack\label{fig:example-plan-dev}]{\includegraphics[width = 0.32\linewidth]{plan-deviation-v2}}
+    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.32\linewidth]{co-observ-v2}}
+    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.32\linewidth]{cross-traj-v2}}
 
@@
 \begin{remark}
-In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon} \rtron{Add ref}.
+In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon}~\cite{MATLAB:fmincon}.
 The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation).
@@
     \centering
-    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}}
-    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}}
-
-    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth, trim = 0.3cm 1cm 0.3cm 1cm, clip]{Ellipse2line_V2}}
-    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth,trim = 0cm 1cm 0.3cm 0.5cm, clip]{Ellipse2safezone_V2}}
+    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth]{Reachability-v2}}
+    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth]{Ellipse2point-v2}}
+
+    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth]{Ellipse2line-v3}}
+    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth]{Ellipse2safezone-v3}}
 
@@
   % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
-  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,trim =2cm 1.8cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
+  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
   \caption{{\news Trajectory design a three-robot system based on the grid world result.
@@
 (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective.
-(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.
+Attack attempts into forbidden region (red dashed line) will cause team 1 miss next scheduled co-observation.}}
   \label{fig:example-application}
@@
 In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
-A heuristic approach is provided to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose).
-%with a toy example shown in Figure \ref{fig:checkpoint-generate}.
-
-{\news \rtron{Use enumerate} We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
+{\news We use a heuristic approach (~\cref{alg:graph}) to locate the checkpoints on given trajectories.
+\cref{alg:graph} is applied independently to each sub-team to generate their initial checkpoints.” While an optimal solution would likely be NP-hard, this approach works well enough for our purpose.} %with a toy example shown in Figure \ref{fig:checkpoint-generate}.
+
+% {\news
+%   \begin{enumerate}
+%   \item Initialization: Add the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, where $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
+%   \item Forward search: Find the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})$ does not overlap with any of the forbidden areas $F$.
+Once found, add $(q_{p}(t_{1}),t_1)$ to $V_{p}$.
+%   \item Backward search: Find the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\}$ such that the reachability ellipsoid $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3})$ does not overlap with any of the forbidden areas $F$.
+Once found, add $(q_{p}(t_{3}),t_3)$ to $V_{p}$.
+%   \item Update indices: $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$.
+%   \item Repeat the process until: $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$
+% \end{enumerate}}
+
+  \begin{algorithm}\label{alg:graph}
+  \caption{Checkpoint Graph Initialization for Team $\cI_p$}
+  {\news \begin{algorithmic}[1]
+  \State \textbf{Initialization:} Add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$, where $t_{0} = 0$ and $t_{2} = T$, as \emph{start} and \emph{end vertices}.
+  \While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_{2}$}
+      \State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_{2}\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$.
+Then add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
+      \State \textbf{Backward Search:} Find the smallest $t_{3}\in\{t_{1}, \dots, t_{2}-1\}$ such that $
+      \mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Then add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
+      \State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_{2} \leftarrow t_{3}$.
+  \EndWhile
+  \end{algorithmic}}
+  \end{algorithm}
+% {\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
 Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
@@
 	\centering
-    \subfloat[]{\includegraphics[width=0.45\linewidth,trim = 1.7cm 2cm 1cm 2.7cm, clip,valign=c]{SC_gen_1}}
-    \subfloat[]{\includegraphics[width=0.45\linewidth,trim = 1.7cm 2cm 1cm 2.7cm, clip,valign=c]{SC_gen_2}}
+    \subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_1-v2}}
+    \subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_2-v2}}
     \caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
@@
     \centering
-  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0cm, clip, valign=c]{two_edges}}
-  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0.2cm, clip, valign=c]{security_graph}}
+  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,valign=c]{two_edges-v2}}
+  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,valign=c]{security_graph-v2}}
   \caption{{\news (\ref{fig:two-edges}) The latest departure node $q^{d}_{b}$ found for $v_{r1}$ and the earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.

### 2024-12-12 paper.tex
update figure

@@
   \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
-  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v2}}
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
   % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}

### 2024-12-12 paper.tex
fix gramma errors

@@
 A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}.
-That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives.
+That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration space, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives.
 However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance.
@@
 \new{Furthermore, we address the feasibility and optimality challenges.
-For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
+For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and form them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
 The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another.
@@
 
-\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such area.
-Optimization-based approaches are customizable to a varity of constraints (e.g.
+\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such areas.
+Optimization-based approaches are customizable to a variety of constraints (e.g.
 speed limit, avoiding obstacles) and task specifications (e.g.
@@
 Geometric methods like zonotopes and ellipsoids are commonly used to enclose reachability sets compactly \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}.
-For online safety assessments against cyber attacks, \cite{kwon2017reachability} computed reachable CPS states under attacks and compared them with a safe region based on state estimation.
+For online safety assessments against cyber attacks, \cite{kwon2017reachability} compute reachable CPS states under attacks and compared them with a safe region based on state estimation.
 By incorporating an additional security measure that provides two secured states, the reachability region in our work is over-approximated using ellipsoids.
@@
 \noindent\myparagraph{Notation} 
-In this paper, we use non-bold symbols like to denote single-agent states (e.g.
-$q_{ij}$) and scalers, while bold symbols represent aggregated states of single robot and multiple robots (e.g.
-$\vq$).
-}
+In this paper, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, and bold symbols to represent aggregated states of single robot and multiple robots (e.g. $\vq$). }
 
@@
 
-{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimizing coverage, and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
-However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as properly functioning agent, attempts to gain access to unauthorized locations without detection.
+{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}).
+However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection.
 The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
@@
 In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon}~\cite{MATLAB:fmincon}.
-The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation).
+The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numerical differentiation).
 At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
@@
 \end{align}
-where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.}
+where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the security can be ensured through co-observation.}
 \end{constraint}
@@
 We then use the ellipsoids to introduce various reachability constraints with respect to other geometric entities, such as points, lines, line segments, and polygons.
-These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning presented in \cref{chapter:ADMM review}.
+These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning is presented in \cref{chapter:ADMM review}.
 }
@@
 
-    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robot are expected at given time $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period.
+    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robots are expected at given times $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period.
 The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
@@
     (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projects point $p_{L}$ outside the ellipse to $p_{t}$.
-    (\ref{fig:Ellipse-to-safezone}) For convec-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
+    (\ref{fig:Ellipse-to-safezone}) For convex-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
     \label{fig:Reachability_full}
@@
 where $d_{\cE t} = \sqrt{ n_\cE\transpose Q^{-1} n_\cE}$; intuitively, $d_{\cE t}$ can be treated as a distance between the tangent plane $\cL_1^\cE$ (or $\cL_2^\cE$) and the origin (i.e., the center of the ellipse $\cE$).
-The concept of \emph{tangent interpolation point}s is introduced to characterize the relationship between the plane and the ellipsoid.
+The concept of \emph{tangent interpolation point}s are introduced to characterize the relationship between the plane and the ellipsoid.
 
@@
 {\news  
-The reachability constraints for a convex polygon is treated as a union of reachability constraints for aeach indivisual segments that define the hyperplane. We define
+The reachability constraints for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
 \begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
@@
 \end{constraint}
-where $D_{seg}$ are the constraint functions for all line segments used to define the convex polygon region. 
+where $D_{seg}$ are the constraint functions for all line segments that define the convex polygon region. 
 For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:
@@
 Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated.
-For instance, in this scenario, we deploy a security camera as additional security measure to observe agent 3 at time $8$ to ensure security.}
+For instance, in this scenario, we deploy a security camera as an additional security measure to observe agent 3 at time $8$ to ensure security.}
 
@@
   \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
-  \caption{{\news Trajectory design a three-robot system based on the grid world result.
+  \caption{{\news Trajectory design of a three-robot system based on the grid world result.
 Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
@@
 (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.
-Attack attempts into forbidden region (red dashed line) will cause team 1 miss next scheduled co-observation.}}
+Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
   \label{fig:example-application}
@@
 \begin{definition}
-  The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where $V = (\union_p V_p) \union V_c$ is the set of verticies representing waypoints on the planned trajectory and $E = E_{t} \union E_{c}$ is the set of edges representing feasible paths connecting $V$.
+  The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where $V = (\union_p V_p) \union V_c$ is the set of vertices representing waypoints on the planned trajectory and $E = E_{t} \union E_{c}$ is the set of edges representing feasible paths connecting $V$.
 The components of the checkpoint graph are defined as follows:
@@
 To find edges between different nominal trajectories, we use the \rrtstar{}~\cite{karaman2010incremental} algorithm to find paths from a waypoint on one trajectory to multiple destination points (i.e., reference trajectories of other sub-teams, in our method).
-As a optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree.
+As an optimal path planning algorithm, \rrtstar{} returns the shortest paths between an initial location and points in the free configuration space, organized as a tree.
 We assume that the generated paths can be traveled in both directions (this is used later in our analysis).
-Key function from \rrtstar{} is used during constructions of the checkpoint graph, specifically
+Key function from \rrtstar{} is used during the construction of the checkpoint graph, specifically
 {\news\begin{description}
@@
 
-Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$.
+Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ corresponds to a security checkpoint $\union_p V_p$.
 The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur {\news while switching trajectories}.
@@
 Note that we assign fixed roles to robots for convenience in explaining the multi-flow formulation.
-In practice, after a cross-trajectory robot joins a team, it is considered interchangable and could switch roles with the reference robot of that trajectory.
+In practice, after a cross-trajectory robot joins a team, it is considered interchangeable and could switch roles with the reference robot of that trajectory.
 % (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
@@
 Technically, we can always create a trivial schedule that involves only co-observations between members of the same team; this, however, would make the solution more vulnerable in the case where multiple agents are compromised in the same team.
-While in this paper we explicitly consider only the single attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
+In this paper we explicitly consider only the single-attacker scenario, multi-attacks can be potentially handled by taking advantage of the \emph{decentralized blocklist protocol} introduced in \cite{wardega2023byzantine}.
 For this reason, we setup the methods presented below to always prefer \emph{cross-trajectory co-observation} when feasible.
@@
 
-With the formulation, the planning problem is written as an optimization problem, where the optimization cost balances between the co-observation performance and total number of flows (cross-trajectory robots) needed:
+With the formulation, the planning problem is written as an optimization problem, where the optimization cost balances between the co-observation performance and the total number of flows (cross-trajectory robots) needed:
  \begin{subequations} \label{eq:flow-coverage-problem}
@@
 \subsection{Co-observation performance}
-The network flow problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
+The network flow problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follow the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
 %Additionally, for a fixed number of robots $\cK \geq N_{p}$,
@@
 \begin{remark} 
-The value of row $\rho$ is upper bounded such that the second term for each single flow in \eqref{eq:flow-cost} is always smaller than one, i.e., $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}\leq 1$.
+The value of row $\rho$ is upper-bounded such that the second term for each single flow in \eqref{eq:flow-cost} is always smaller than one, i.e., $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}\leq 1$.
 Otherwise, the iteration continues indefinitely as adding additional flow introduce a negative term $\sum_{(+i)\in E} f^{k}_{+i} - \rho\sum_{(ij)\in E} w_{ij} f^k_{ij} = 1- \rho\sum_{(ij)\in E} w_{ij} f^k_{ij}<0$ which always makes the cost \eqref{eq:flow-cost} smaller.

### 2024-12-12 response.tex
Finished

@@
 \begin{example}\label{example:map_exploration}
-\new{Robots are tasked with navigating an unknown task space to collecte sensory data to reconstruct a field (as illustrated in~\cref{fig:illustration}).
+\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}).
 The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) [28].
@@
 \end{example}
+
 \setcounter{figure}{1}
@@
 	\centering
-	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4\linewidth,valign=c]{illustration figure_1}} 
-	\subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4\linewidth,valign=c]{SecurityBreak_v2}}
-	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
-	\caption{\new{(2a) Illustration of a 3 robot map exploration task case.
-(2b) The unsecured trajectory design optimized for a map exploration task.
+  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
+  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
+(\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task.
 Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
 \end{figure}
-{\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
+{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}).
+However, we consider the possibility of threats following the \emph{physical masquerade attack} model [2], where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection.
+The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
+These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan.
+The corresponding security requirement can then be formally defined as:}
+\begin{definition}\label{def:secured-plan}
+  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+\end{definition}
+
+% {\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
 To address potential threats, we adopt the \emph{physical masquerade attacks} framework from [2], where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection.
@@
 The corresponding security requirement can then be formally defined as:}
-\begin{definition}\label{def:secured-plan}
-  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
-\end{definition}
+% \begin{definition}\label{def:secured-plan}
+%   A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+% \end{definition}
 
@@
 	\tcblower
-	\underline{\textbf{Response:}} As suggested, we have condensed this section and moved the “Transformation to Canonical Frame” part into the appendix to streamline the main text and improve readability.
+	\underline{\textbf{Response:}} As suggested, we have condensed this section and moved part of the “Transformation to Canonical Frame” section into the appendix to streamline the main text and improve readability.
 We believe that the remaining details on the implementation of the reachability constraints are essential and provide critical context for understanding the proposed method.
@@
 {\news  
-The reachability constraints for a convex polygon is treated as a union of reachability constraints for aeach indivisual segments that define the hyperplane. We define
+The reachability constraint for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
 \setcounter{constraint}{3}
@@
 	\noindent
- For the feedback reguarding the term "checkpoint", the original intent of “checkpoint” in Section 2 was to illustrate the limitations of the method proposed, specifically to show that even if APMAPF yields a valid solution, transforming this solution to a continuous domain may still need additional security measure to guarantee security.
+ For the feedback regarding the term "checkpoint", the original intent of “checkpoint” in Section 2 was to illustrate the limitations of the method proposed, specifically to show that even if APMAPF yields a valid solution, transforming this solution to a continuous domain may still need additional security measure to guarantee security.
 To address the concern, we have replaced the term “checkpoints” with “key locations” in Section 2 to avoid confusion.
@@
 \subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
-We employ the \new{attack-proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a).
+We employ the \new{Attack-Proof MAPF(APMAPF)} solver [2] on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.4a).
 This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
@@
 	\centering
-	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4	\linewidth,valign=c]{illustration figure_1}} 
-	\subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4	\linewidth,valign=c]{SecurityBreak_v2}}
-	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
-	\caption{\new{(2a) Illustration of a 3 robot map exploration task case.
-(2b) The unsecured trajectory design optimized for a map exploration task.
+	\subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+	\subfloat[Continuous world trajectory\label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
+	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+	\caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
+(\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task.
 Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
   \end{figure}
-\setcounter{figure}{3}
   \begin{figure}[H]
     \centering
-	% \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.4	\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth,valign=c]{Grid_world}}
-	% \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4	\linewidth,valign=c]{SecurityBreak_v2}}
-	\subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
-	\caption{{\news Trajectory design a three-robot system based on the grid world result.
+    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth]{Reachability-v2}}
+    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth]{Ellipse2point-v2}}
+
+    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth]{Ellipse2line-v3}}
+    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth]{Ellipse2safezone-v3}}
+
+    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robots are expected at given times $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period.
+The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
+    (\ref{fig:Ellipse-to-point}) For point-ellipsoid constraint, $q_{avoid}$ is projected to the areas outside the ellipsoid to $q_{p}$. 
+    (\ref{fig:Ellipse-to-plane}) For plane-ellipsoid constraint, the projection is simplified to the point-ellipse constraint that projects point $p_{L}$ outside the ellipse to $p_{t}$.
+    (\ref{fig:Ellipse-to-safezone}) For convex-polygon-ellipsoid constraint, the projection is either a plane-ellipse constraint $D_{1}$ (for the red region) or a point-ellipse constraint $D_{2}$ (for the brown region).}
+    \label{fig:Reachability_full}
+  \end{figure}
+  \begin{figure}[H]
+	\centering
+  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+  \subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
+  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  \subfloat[Secured result. \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
+  \caption{{\news Trajectory design of a three-robot system based on the grid world result.
 Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
-(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective.
-(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.
+Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
   \label{fig:example-application}
@@
 	explanations in words.
-\re	We have replaced the algorithm with more detailed and understandable prose to improve readability and make the approach easier to follow.
+\re	We have re-written the algorithm with more detailed and add illustration figure to improve readability and make the approach easier to follow.
 \end{cmt}
-\rv {\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
-Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
-$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$.
-Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$.
-Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$.
-Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$.
-Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process.
-The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$.
-A toy example is shown in \cref{fig:checkpoint-generate}.
-}
+\rv  
+\begin{algorithm}
+	\caption{Checkpoint Graph Initialization for Team $\cI_p$}\label{alg:graph}
+	{\news \begin{algorithmic}[1]
+	\State \textbf{Initialization:} Set $t_{0} \leftarrow 0$ and $t_{2} \leftarrow T$, and add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$ as \emph{start} and \emph{end vertices}.
+	\While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_{2}$}
+		\State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_{2}\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$.
+Once found, add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
+		\State \textbf{Backward Search:} Find the smallest $t_{3}\in\{t_{1}, \dots, t_{2}-1\}$ such that $
+		\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Once found, add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
+		\State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_{2} \leftarrow t_{3}$.
+	\EndWhile
+	\end{algorithmic}}
+	\end{algorithm}
+	\setcounter{figure}{4}
+	\begin{figure}[H]
+		\centering
+		\subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_1-v2}}
+		\subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_2-v2}}
+		\caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
+	\end{figure}
 
@@
 \re 
-We have add additional content to introduce the what the "network multi-flow problem" in our setup.
+We have added additional content to introduce what the "network multi-flow problem" in our setup.
 \end{cmt}
-\rv \new{We assume that the planned trajectory for each sub-team has a robot operating on it.
+\rv 
+\textbf{In Section III.A, we make the following modification}
+
+\new{We assume that the planned trajectory for each sub-team has a robot operating on it.
 The co-observation planning problem is then transformed into a network multi-flow problem by modeling the additional robots as flows traveling through $G$.
@@
 \end{cmt}
-\rv \new{the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see Appendix B for details).}
+\rv \textbf{In Section II.D we modified:}
+
+\new{the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see Appendix B for details).}
 
@@
 \end{cmt}
+\setcounter{definition}{1}
 \rv {\news
@@
 \end{definition}
-This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
 \begin{cmt}{}{}
@@
 \end{cmt}
-\rv {\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
+\rv \textbf{In Section II, first paragraph, we modified}
+
+{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
 For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
@@
 In Definition 1, is reasonable to say ``any potential deviations''?
-\re We believe that this phrase is resonable and essential to the definition and intention of security against plan-deviation attacks.
+\re We believe that this phrase is reasonable and essential to the definition and intention of security against plan-deviation attacks.
 The definition is designed to ensure that the trajectory plan accounts for all possible paths a compromised robot might take toward forbidden regions.
@@
 \begin{remark}
-In practical application, (4a) is solved iteratively via a nonlinear optimization solver like \emph{fmincon}.
-The gradients of the constraint functions, derived later, is used to enhance solver efficiency and accuracy.
-Meanwhile, (4b) and (4c) have closed form solutions.
+In practical application, (4a) is solved iteratively via a nonlinear optimization solver such as \emph{fmincon} [30].
+The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numerical differentiation).
+At the same time, (4b) and (4c) have closed form solutions.
 \end{remark}
+[30] The MathWorks, Inc., MATLAB Optimization Toolbox, The Math- Works, Inc., Natick, Massachusetts, 2024, version R2024b, https://www. mathworks.com/products/optimization.html.
 }
@@
 \end{definition}
-This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
 
@@
 The mechanisms for ensuring security are formally described in Definition 1 and further extended in Definition 4 and Remark 2, which outline the requirements and constraints necessary to detect and mitigate such attacks effectively.
+We also add potential attacks to the unsecured and secured result figures.
 \end{cmt}
-\rv {\news Ideally, robots are expected to spread out in a boustrophedon pattern to efficiently explore the task space, optimizing coverage and minimizing reconstruction uncertainty (\cref{fig:SecurityBreak}).
-To address potential threats, we adopt the \emph{physical masquerade attacks} framework from [2], where a compromised insider (robot) masquerading as a properly functioning robot, attempting to gain access to unauthorized locations without detection.
+\rv 
+\textbf{In Section I, Introduction, Paragraph 1, we revised}
+
+{\news A countermeasure to these \emph{plan-deviation attacks} [2]–[4] is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
+These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}
+
+\textbf{In Section II, after Example 1 we revised:}
+\setcounter{figure}{1}
+\begin{figure}[H]
+	\centering
+  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
+  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
+(\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task.
+Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
+\end{figure}
+{\news 
+Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}).
+However, we consider the possibility of threats following the \emph{physical masquerade attack} model [2], where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection.
 The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE).
-These malicious deviations remain undetected as long as the self-reports from uncompromised robots align with the motion plan.
+These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan.
 The corresponding security requirement can then be formally defined as:}
@@
 
+\textbf{In section II.C:}
+
 {\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
@@
 }
+\setcounter{figure}{3}
+\begin{figure}[H]
+	\centering
+  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+  \subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
+  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  \subfloat[Secured result. \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
+  \caption{{\news Trajectory design of a three-robot system based on the grid world result.
+Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.
+Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
+  \label{fig:example-application}
+  \end{figure}
+
+\textbf{In Section III.A:}
 
@@
 }
+
 \begin{cmt}{}{}
@@
 \end{cmt}
-\rv {\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
+\rv \textbf{In Section II, we modified:}
+
+{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
 For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
@@
   \noindent\myparagraph{Notation} 
-  In this paper, we use non-bold symbols like to denote single-agent states (e.g.
-$q_{ij}$) and scalers, while bold symbols represent aggregated states of single robot and multiple robots (e.g.
-$\vq$).
-}
+  In this paper, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, and bold symbols to represent aggregated states of single robot and multiple robots (e.g. $\vq$). }
 
@@
 Additionally, we have provided a more detailed explanation to clarify why the ellipsoid is an over-approximation of the reachability region.
-Specifically, it represents the set of points $q'$ whose sum of distances two foci $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid.
+Specifically, it represents the set of points $q'$ whose sum of distances two foci $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid.
   \end{cmt}
@@
   \end{definition}
-  This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+  This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
 
@@
 	\centering
-	  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.4\linewidth,valign=c]{illustration figure_1}} 
-	  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4\linewidth,valign=c]{SecurityBreak_v2}}
-	  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth]{Grid_world}}
-	  \caption{\new{(2a) Illustration of a 3 robot map exploration task case.
-(2b) The unsecured trajectory design optimized for a map exploration task.
+	\subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+	\subfloat[Continuous world trajectory\label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
+	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
+	\caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
+(\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task.
 Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
@@
 	\centering
-	% \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.4	\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.4	\linewidth,valign=c]{Grid_world}}
-	% \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.4	\linewidth,valign=c]{SecurityBreak_v2}}
-	\subfloat[Securd result \label{fig:ReachabilitySimulation}]{\includegraphics[width=0.52\linewidth,trim =2cm 1.5cm 2cm 1cm, clip,valign=c]{FinalResult}}
-	\caption{{\news Trajectory design a three-robot system based on the grid world result.
+	% \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
+	\subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
+	% \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+	\subfloat[Secured result. \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
+	\caption{{\news Trajectory design of a three-robot system based on the grid world result.
 Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
-(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in 8$\times$8 grid-world without map exploring objective.
-(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
+(\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective.
+(\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.
+Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
 	\label{fig:example-application}

### 2024-12-12 paper.tex
Finished

@@
 
-    \caption{{\news \ref{fig:example-plan-dev} The attacker deviates the red robot into a forbidden region.\ref{fig:example-co-observation} Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
-\ref{fig:example-cross-traj} The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
+    \caption{{\news (\ref{fig:example-plan-dev}) The attacker deviates the red robot into a forbidden region.(\ref{fig:example-co-observation}) Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
+(\ref{fig:example-cross-traj}) The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
 \end{figure}
@@
   \centering
-  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+  \subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
   \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
@@
 \end{definition}
-This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
  \begin{figure}
@@
 {\news  
-The reachability constraints for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
+The reachability constraint for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
 \begin{constraint}[Convex-polygon-ellipsoid reachability constraint]\label{constraint:polygon-ellipsoid}
@@
 \end{constraint}
-where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}.
-with respect to frame $\Eframe {\cL}$.
+where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint} with respect to frame $\Eframe {\cL}$.
 This constraint needs to be supplemented with a convex obstacle constraint for the polygon (i.e.
@@
 
-We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}).
+We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (\cref{fig:Grid-example-application}).
 This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
@@
   % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
+  \subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
   % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
@@
 \subsubsection{Limitations}\label{sec:reachability-discussion}
-Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.
+Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of MRS.
 {\news However, two primary challenges need to be addressed.
@@
 The introduction of security constraints resulted in the top left corner remaining unexplored by any robots.
-This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments.
-These challenges are further addressed in \cref{sec:cross-trajectory}, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}
+This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of MRS deployments.
+These challenges are further addressed in \cref{sec:cross-trajectory}, ensuring the effective integration of reachability and co-observation in securing MRS.}
 
@@
 In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
-{\news We use a heuristic approach (~\cref{alg:graph}) to locate the checkpoints on given trajectories.
+{\news We use a heuristic approach (\cref{alg:graph}) to locate the checkpoints on given trajectories.
 \cref{alg:graph} is applied independently to each sub-team to generate their initial checkpoints.” While an optimal solution would likely be NP-hard, this approach works well enough for our purpose.} %with a toy example shown in Figure \ref{fig:checkpoint-generate}.
@@
 
-  \begin{algorithm}\label{alg:graph}
-  \caption{Checkpoint Graph Initialization for Team $\cI_p$}
+\begin{algorithm}
+	\caption{Checkpoint Graph Initialization for Team $\cI_p$}\label{alg:graph}
 	{\news \begin{algorithmic}[1]
-  \State \textbf{Initialization:} Add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$, where $t_{0} = 0$ and $t_{2} = T$, as \emph{start} and \emph{end vertices}.
+	\State \textbf{Initialization:} Set $t_{0} \leftarrow 0$ and $t_{2} \leftarrow T$, and add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$ as \emph{start} and \emph{end vertices}.
 	\While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_{2}$}
 		\State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_{2}\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$.
-Then add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
+Once found, add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
 		\State \textbf{Backward Search:} Find the smallest $t_{3}\in\{t_{1}, \dots, t_{2}-1\}$ such that $
-      \mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Then add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
+		\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Once found, add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
 		\State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_{2} \leftarrow t_{3}$.
@@
 
-    Thus equation \eqref{equ:dPi_dt} could be written as:
+    Thus, equation \eqref{equ:dPi_dt} could be written as:
     \begin{multline}

### 2025-05-31 response_2.tex
Accepted version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Paper Response Letter. 
% LaTeX Template
% Version 1.0 (20/07/2023)
% 
% This template refers to the toolbox tutorial (in Chinese):
% https://liam.page/2016/07/22/using-the-tcolorbox-package-to-create-a-new-theorem-environment/
% Please refer to the tutorial for your customization. 
% 
% Template license: Creative Commons CC BY 4.0
%
% Author: Yuhan Xie
% Contact email: yhxie0107@gmail.com
% Any revision advice is welcome!
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}
%% Language and font encodings
\input{preamble/common}
\usepackage[english]{babel}
\usepackage{times} % make the section title in Times New Roman

\usepackage{booktabs}
\usepackage{tabu}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=2.5cm,bottom=2cm,left=1.7cm,right=1.7cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{indentfirst}
\usepackage{graphicx}
% \usepackage{subfigure}
\usepackage{float}
\usepackage{threeparttable} 
\usepackage{multirow}
\usepackage{url}
\usepackage{xcolor}
\pagenumbering{arabic}

\usepackage[most]{tcolorbox}
\newcommand{\rrtstar}{$\texttt{RRT}^\texttt{*}$}
\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}

\newtheorem{constraint}{ADMM constraint}
\newtheorem{example}{Example}
\newcommand{\re}{\tcblower \underline{\textbf{Response:}}\quad}
\newcommand{\rv}{{\large{\underline{\textbf{Revision:}}}}\quad}
\usepackage[export]{adjustbox} 
\usepackage[capitalise]{cleveref}
\usepackage{xcolor}
\newcommand{\new}[1]{\textcolor{blue}{#1}}
\newcommand{\news}{\color{blue}}
\graphicspath{{Figs/}}

\begin{document}

\newtcbtheorem[auto counter, number within = section]{cmt}{Comment}{
	colbacktitle = black!60!white, colframe = black!60!white,
	colback = black!5!white,
	fonttitle=\bfseries,%fontupper=\itshape,
}{t}

\noindent
Dear Editor and Reviewers:

\vspace{0.2cm}
\noindent
We would like to express our sincere gratitude to the Editor-in-Chief, Associate Editor, and anonymous reviewers for their time and constructive feedback throughout the review process. Following the acceptance of our manuscript, we have carefully addressed the remaining minor issues related to typos, formatting, and clarity. All necessary corrections have been made, and the updated changes are highlighted in \new{blue} for clarity. We appreciate the opportunity to further improve the manuscript and are confident that these refinements contribute to a more polished and readable final version.

\vspace{0.2cm}
\noindent
Yours sincerely,

\noindent
Ziqi Yang, Roberto Tron

\vspace{1cm}
\begin{cmt*}{}{}
Some minor formatting adjustments have been made to ensure that the overall content remains within the page limit. These changes are purely presentational and do not affect the technical content of the paper.
\end{cmt*}
\rv 
\textbf{Appendix B}
\setcounter{proposition}{2}
\begin{proposition}\label{prop:HProperty}
 {\news The matrix $H$ has the following properties:
  \begin{enumerate}
  \item\label{it:rotation} It is a rotation, i.e. (a) $H\transpose H=I$; (b) $\det(H)=1$
  % \begin{enumerate}
  %   \item\label{it:orthonormality} $H\transpose H=I$;
  %   \item\label{it:determinant} $\det(H)=1$.
  %   \end{enumerate}
  \item\label{it:transformation} $\nu_2=H \nu_1$.
  \end{enumerate}}
\end{proposition}
\begin{proof}
 {\news For subclaim~\ref{it:rotation}a,  since $u\transpose u=1$:
  \begin{equation}
    H\transpose H=H^2=4uu\transpose u u\transpose - 4uu\transpose +I^2=I.
  \end{equation}}
\end{proof}
\newpage
\section{Response to reviewer 1}
\begin{cmt*}{}{}
We thank the reviewer for their time and constructive feedback during the review process. We are pleased that no further comments were raised and appreciate their role in helping improve the quality of the manuscript.
\end{cmt*}
\vspace{0.2cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 1
\section{Response to reviewer 2} 
\begin{cmt*}{}{}
We sincerely thank the reviewer for their constructive comments during the initial review, which significantly contributed to improving the quality of this paper. We also appreciate the reviewer’s acknowledgment of the improvements made in the previous revision. In this final round, we have carefully addressed the additional comments raised and made the necessary corrections in the manuscript. Our detailed responses are provided below.
\end{cmt*}
\vspace{0.1cm}
%%%%%%%%%%%%% Comment 1.0
\begin{cmt}{}{}        %% use * when do not need enumerate
1. There still are some typos, eg.,

   a) in Fig 4, the legend is Region 1 and Region 2, but in the text,
you use Zone1 and Zone2.

   b) Sec 2D, first paragraph, $q^{\epsilon} \in F^{\epsilon}$?
	\re All typos mentioned have been fixed.
\end{cmt}
\rv 
\textbf{Section II.D}

\newcommand{\oFE}{o}
To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \cref{fig:EllipseConstraintExample} for an illustration). 
From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
The full transformation from coordinates \new{$q^\cE\in\cF_\cE$} to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):\setcounter{figure}{3}
\begin{figure}[h]
  \centering
  \subfloat[Grid world result\label{fig:Grid-example-application}]{\includegraphics[height = 0.3\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.3\linewidth,valign=t]{FinalResult-v2}}
  \caption{ Trajectory design of a three-robot system based on the grid world result. \new{Region} 1 is an obstacle, \new{region} 2 and \new{region} 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints. Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}
  \label{fig:example-application}
\end{figure}

\textbf{Section II.H}

The simulation result, shown in Fig.~\ref{fig:ReachabilitySimulation}, displays reachability regions as black ellipsoids, demonstrating empty intersections with \new{region} 2 and 3. Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots. The intersections between obstacles and ellipsoids, as observed between agent 3 and \new{region} 1, are deemed tolerable. All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks. 
\begin{cmt}{}{}
	2. In algorithm 1, what is the reason for using $t_0 + 1$ and $t_2 - 1$?

	3. In Fig 5, no explanation is made in the caption
\re The algorithm aims to find the furthest waypoint such that the reachability region between waypoint at $t_0$ and a later waypoint that does not intersect with any forbidden region. Since evaluating the reachability region between the same waypoint (e.g., $t_0$ to $t_0$) is not meaningful, we exclude such cases and begin the search from $t_0 +1$ The same logic applies in the reverse direction, where we stop at $t_2 -1$ instead of including $t_2$. For better readability, we reorder the sequence of the variables ($v_0$ to $v_3$) and add additional indicator in the illustration figure (Fig.5).
\end{cmt}
\rv
\setcounter{figure}{4}
\begin{algorithm}
	\caption{Checkpoint Graph Initialization for Team $\cI_p$}\label{alg:graph}
  \begin{algorithmic}[1]
	{\news \State \textbf{Initialization:} Set $t_{0} \leftarrow 0$ and $t_{3} \leftarrow T$, and add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_3),t_3)$ to $V_{p}$ as \emph{start} and \emph{end vertices}.
	\While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_3),t_{0},t_3) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_3$}
		\State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_3\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$. Once found, add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
		\State \textbf{Backward Search:} Find the smallest $t_2\in\{t_{1}, \dots, t_3-1\}$ such that $
		\mathcal{E}(q_{p}(t_3),q_{p}(t_2), t_3,t_2) \cap F = \emptyset.$ Once found, add $(q_{p}(t_2),t_2)$ to $V_{p}$.
		\State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_3 \leftarrow t_2$.
	\EndWhile}
	\end{algorithmic}
	\end{algorithm}
\begin{figure}[h]
	\centering
    \subfloat{\includegraphics[width=0.47\linewidth,valign=c]{SC_gen_1_v3}}
    \subfloat{\includegraphics[width=0.47\linewidth,valign=c]{SC_gen_2_v3}}
    \caption{\news Example of \cref{alg:graph}. Start at both ends, each trajectory finds the largest reachability region avoiding forbidden areas, then repeats the process on remaining segments to build secure checkpoints.}\label{fig:checkpoint-generate}
\end{figure}

\end{document}

### 2025-05-31 paper.tex
Accepted version

@@
 We address security challenges in multi-robot systems (MRS) where adversaries may take control of compromised robots to gain unauthorized physical access to forbidden regions.
-We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces {\news \emph{reachability constraints} and \emph{co-observations} between robots to enhance security}.
+We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability constraints} and \emph{co-observations} between robots to enhance security.
 Our formulation can guarantee that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations.
-\new{We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation.
+We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation.
 Furthermore, to enhance system resilience and tackle feasibility challenges, we introduce the notion of \emph{sub-teams}; these cohesive units replace individual robots along each trajectory; we plan \emph{cross-trajectory co-observation} that use redundant robots to switch between different trajectories, securing multiple sub-teams without requiring modifications to the plans.
 We formulate cross-trajectories plans by solving a \emph{network-flow vertex path coverage problem} on the \emph{checkpoint graph} generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks.
-We demonstrate the effectiveness and robustness of our proposed algorithm through simulations, which significantly strengthen the security of multi-robot systems in the face of adversarial threats.}
+We demonstrate the effectiveness and robustness of our proposed algorithm through simulations, which significantly strengthen the security of multi-robot systems in the face of adversarial threats.
 \end{abstract}
@@
 Multi-robot systems (MRS) have found wide applications in various fields.
-\new{Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.} This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
-{\news A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
-These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}
+Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.
+This paper addresses a specific scenario in which robots are compromised by physically masquerading attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.
+A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
+These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.
 
 A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}.
-That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration space, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives.
+That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration space, and incorporated the co-observation planning as constraints in the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives.
 However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance.
-As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}
+As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.
 
@@
 We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint.
-We present a mathematical formulation of the reachability regions \new{as spatio-temporal constraints} compatible with the solver in \cite{yang2020multi}.
-
-\new{Furthermore, we address the feasibility and optimality challenges.
-For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and form them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
+We present a mathematical formulation of the reachability regions as spatio-temporal constraints compatible with the solver in \cite{yang2020multi}.
+
+Furthermore, we address the feasibility and optimality challenges.
+For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and form them into \emph{sub-teams} with the original ones.
+These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams.
 The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another.
 This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events.
-The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.
+The cross-trajectory co-observation problem is transformed as a Multi-Agent Pathfinding (MAPF) problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.
 
@@
 
-    \caption{{\news (\ref{fig:example-plan-dev}) The attacker deviates the red robot into a forbidden region.(\ref{fig:example-co-observation}) Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
-(\ref{fig:example-cross-traj}) The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}}
+    \caption{ (\ref{fig:example-plan-dev}) The attacker deviates the red robot into a forbidden region.(\ref{fig:example-co-observation}) Red and blue robots are scheduled to co-observe each other during the task, resulting in a new secured trajectory (solid lines) replacing the optimal ones (dashed line).
+(\ref{fig:example-cross-traj}) The blue team sends one robot to observe the red team (solid blue line) while having the rest of the robots follow the optimal trajectory.}\label{fig:cross-traj-comparison-set}
 \end{figure}
@@
 This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem.
-%In contrast with such approach, our research in \cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
-% \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}
-
-% Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}.
-One typical approach involves computing an over-approximation of the reachable space for checking safety properities.
-Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric representation, such as zonotopes and ellipsoids, as a compact enclosure of the reachability sets.
-In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.
-\new{Reachability analysis is essential for security and safety verification in cyber-physical systems (CPSs) \cite{gueguen2009safety, ding2020secure}, often involving an over-approximation of reachable space to verify safety properties.
+
+Reachability analysis is essential for security and safety verification in cyber-physical systems (CPSs) \cite{gueguen2009safety, ding2020secure}, often involving an over-approximation of reachable space to verify safety properties.
 Geometric methods like zonotopes and ellipsoids are commonly used to enclose reachability sets compactly \cite{kurzhanski2000ellipsoidal, lakhal2019interval, maiga2015comprehensive}.
@@
 Ellipsoids are also used in other path-planning methods like Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}.
-Differing from the reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximating the safe collision-free space rather than addressing security applications.}
+Differing from the reachability region that requires mapping all reachable states given several known states, the ellipsoids of IRIS and SFC focus on approximating the safe collision-free space rather than addressing security applications.
 
@@
 
-{\news The rest of this paper is organized as follows.
+The rest of this paper is organized as follows.
 \cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and the security constraints.
@@
 \noindent\myparagraph{Notation} 
-In this paper, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, and bold symbols to represent aggregated states of single robot and multiple robots (e.g. $\vq$). }
+In this paper, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, and bold symbols to represent aggregated states of single robot and multiple robots (e.g. $\vq$).
 
@@
 We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions.
-{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
+We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon.
 For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation.
-}
-\new{The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraints and the security constraints (co-observation schedule, reachability analysis).} Formally:
+The overall goal is to minimize or maximize an objective function $\varPhi(\vq):\real{n m T} \to \real{}$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraints and the security constraints (co-observation schedule, reachability analysis).
+Formally:
 \begin{equation}\label{eq:general-problem}
@@
 \begin{example}\label{example:map_exploration}
-\new{Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}).
+Robots are tasked with navigating an unknown task space to collect sensory data and reconstruct a field (as illustrated in~\cref{fig:illustration}).
 The task space is modeled as a grid, where each grid point has an associated value tracked by a Kalman Filter (KF) \cite{anderson2012optimal}.
@@
 The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty in reconstructing the field (detailed in \cite{yang2020multi}).
-}
 \end{example}
@@
   \centering
-  \subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
+  \subfloat[Map exploration task\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
   \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
-  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
-  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
+  \caption{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case.
 (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task.
-Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
+Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}
 \end{figure}
 
-{\news Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}).
+ Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}).
 However, we consider the possibility of threats following the \emph{physical masquerade attack} model \cite{wardega2019resilience}, where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection.
@@
 These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan.
-The corresponding security requirement can then be formally defined as:}
+The corresponding security requirement can then be formally defined as:
 \begin{definition}\label{def:secured-plan}
-  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
+  A multi-robot trajectory plan is secured against plan-deviation attacks if it ensures that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots.
 \end{definition}
@@
 \subsubsection{Differentials}
-\new{We define the differential of a map $f(x):\real{d_1}\to\real{d_2}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{d_1\times d_2}$ such that}
+We define the differential of a map $f(x):\real{d_1}\to\real{d_2}$ at a point $x_0$ as the unique matrix $\partial_x f \in\real{d_1\times d_2}$ such that
 \begin{equation}\label{equ:dt_to_dx}
@@
 For brevity, we will use $\dot f$ for $\dert f$ and $\partial_x f$ for $\frac{\partial f}{\partial x}$.
-%The differentials $\partial_x f$ is derived through \eqref{equ:dt_to_dx} having $\dot f$ divided by $\dot x$.
-
-\new{With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{d_1 \times d_3}\to\real{d_2}$.
-Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.}
+
+With a slight abuse of notation, we use the same notation $\partial_xf$ for the differential of a matrix-valued function with scalar arguments $f:\real{d_1 \times d_3}\to\real{d_2}$.
+Note that in this case \eqref{equ:dt_to_dx} is still formally correct, although the RHS needs to be interpreted as applying $\partial_x f$ as a linear operator to $\dot{x}$.
 
@@
 More specifically, we rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$ and include it in the objective function (details can be found in \cite{yang2020multi}). 
-%In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$.
-However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
 We allow $\vz = D(\vq)$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy in general ADMM formulation), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ to allow for an easier projection step in \cref{eq:z-update}.
@@
 $D_i(\vq)$ is chosen such that the new constraint set~$\cZ_i$ becomes simple to compute which is illustrated in later sections.
-% and the function~$D_i(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.
 
@@
 after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
-{\news
 \begin{remark}
@@
 \end{remark}
-}
-% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}
 
@@
 
-% \subsection{Velocity constraints}\label{sec:velocity-constraint}
-% We constraint for the movement of each agent by a maximum velocity defined as the distance in any direction over a single discrete time step.
-The function $D(\vq)$ returns the velocity vectors for the $i$-th agent at each time step $j$, and constrain its result to a sphere.
-% \begin{constraint}[Velocity constraint]
-% \begin{align}
-%      D_{ij}(\vq) &= q_{ij}-q_{i(j-1)}, \quad j\in\{1,\ldots, T\},\\
-% \label{eq:velocity_constraint}
-%    \sZ_{ij} &=\bigl\{\vz \mid \norm{\vz} \leq v_{max}\bigr\},\\
-%    \Pi_{\sZ_{ij}}(\vz)&=\begin{cases}
-%    v_{\max}\frac{\vz}{\norm{\vz}} \textrm{ if } \norm{\vz}>v_{\max},\\
-%    \vz\textrm{ otherwise.}
-%    \end{cases}
-% \end{align}
-% \end{constraint}
-
-% \subsection{Convex polygonal obstacles collision constraints} \label{sec:obstacle-constraint}
-% We use convex polygons $\cP$ to model regions  that cannot be entered by agents (solid obstacles and forbidden regions).
-$\cP$ is defined using a collection of $l$ hyperplanes $n_{k}\transpose q = m_{k}$, where $n_k$ is the normal vector pointing toward the outside of the obstacle and $m_k$ is the scalar offset defining the $k$-th hyperplane.We define the function $D(\vq)$ to return the maximum distance from $q_{ij}$ to all hyperplane boundaries of region $\cP$, and  constraint $z$ to be a non-negative scalar.
-This constraint is applied to all $q_{ij} \in \vq$.
-
-% Non-convex obstacles can be handled by a union of (possibly overlapping) convex obstacles.
-And by using outward-pointing normals for $n_k$, this method can also serve to constrain the robots within a designated workspace region.
-% \begin{constraint}[Obstacle constraint]
-% \begin{align}
-%      	D(q_{ij}) &= \max_{k=1,\dots,l} (d_{k}(q_{ij},\cP)),\\
-% \label{eq:obstacle_constraint}
-%   \sZ &= \{z \mid z \geq 0 \},\\
-%    \Pi_\sZ(z) & = \begin{cases}
-%    0 & \textrm{if} \quad z < 0,\\
-%    z  & \textrm{otherwise.}
-%    \end{cases} \label{eq:zoneConstraintProjection}
-% \end{align}
-% where $d_{k}(q_{ij},\cP)= p_{ij}\transpose n_k - m_k$ returns the distance between a single waypoint $q_{ij}$ and the $k$th hyperplane .
-% \end{constraint}
-% %The motivating idea for \eqref{eq:obstacle_constraint} and \eqref{eq:zoneConstraintProjection} is to identify waypoints within a specific region and project them to the closest boundary.
-
-% \subsection{Waypoints with flexible deadlines}\label{sec:waypoint-constraint}
-% Security-related constraints often necessitate that a robot reaches a specified location at a particular time.
-We assume that robot $i$ is tasked with reaching a given point $p$ within a radius of $d_{max}$ at some time instant $j$ within a predefined time window $[t_1,t_2]$, leading to the following:
-
-% \begin{constraint}[Waypoint constraint]
-% \begin{align}
-%      	D(\vq) &= \min_{j\in\{t_1,\dots,t_2-1\}}\bigl(\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})\bigr),\\
-% \label{eq:waypoint_constraint}
-%   \sZ &= \{z \mid z < z_{max} \},\\
-%    \Pi_\sZ(z) & = \min(z, d_{max}),
-% \end{align}
-% where $\dist(p,\overrightarrow{q_{ij}q_{i(j+1)}})$ returns the distance between the fixed point $p$ and the segment $\overrightarrow{q_{ij}q_{i(j+1)}}$.
-% \end{constraint}
-
-% This function returns the smallest distance between $(p,q_{ij})$ and $(p,q_{i(j+1)})$ if the projection of the point $p$ does not lie on the line segment~$\overrightarrow{q_{ij}q_{i(j+1)}}$; as a consequence, this constraint does not need to be satisfied exactly at one of the points on the discretized trajectory, but it can also be satisfied ``en route'' on the segment between them.
-
 \subsection{Co-observation schedule constraint}\label{sec:co-observation-constraint}
@@
 This constraint is represented as a relative distance requirement between the two robots at a specific time instant, ensuring they are within a defined radius to inspect each other or exchange data.
-%Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \cref{sec:reachability}, do not intersect with any forbidden regions.
-
-%The co-observation constraints is used to guarantee that, at time required by the schedule, two robots should get close enough with each other to observe each other's behavior.
-This constraint is modeled as a relative distance constraint between two robots at some time instant $j$ (i.e., to require two agents see each other within a certain radius to inspect each other, or to exchange data).
-The location of the co-observation should make sure that the ellipsoidal reachability region between each co-observation, considered in later sections \ref{sec:reachability}, has an empty intersection with all forbidden regions.
-
-% We write the function for the constraint as:
 \begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
@@
 \end{align}
-where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the security can be ensured through co-observation.}
+where $a,b$ are the indices of the pair of agents required for a mutual inspection, $d_{max}$ is the maximum distance between a pair of robots that the security can be ensured through co-observation.
 \end{constraint}
@@
 
-\new{In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory.
+In this section, we define \emph{ellipsoidal reachability regions} with respect to a pair of locations along a trajectory.
 We then use the ellipsoids to introduce various reachability constraints with respect to other geometric entities, such as points, lines, line segments, and polygons.
 These constraints, combined with the co-observation constraint~\ref{constraint:coobservation}, form the basis of the secured ADMM planning is presented in \cref{chapter:ADMM review}.
-}
-% In this section, we define \emph{ellipsoidal reachability regions} based on pairs of co-observation locations on a trajectory, and a transformation of such region in axis-aligned form.
-Different types of reachability constraints (between an ellipsoid and different geometric entities such as a point, line, line segment, and polygon) alongside their projections, and differentials are introduced in subsequent sections.
-Together with the co-observation constraint~\ref{constraint:coobservation}, these will be used in the ADMM formulation of \cref{chapter:ADMM review} to provide security for all observed and unobservered periods.
-%The reachability region is defined as the set of locations $q(t)$ that a robot can reach between two given fixed positions:
-{\news
+
 \begin{definition}\label{sec:ellipsoidal definition}
@@
 The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
-	% The \emph{reachability region} for two waypoints $q(t_1)=q_1$, $q(t_2)=q_2$ is defined as the sets of points $q'$ in the \new{free configuration space} such that there exist a \rtronhl{this $q$ should be probably $q_{dev}$ or something similar, to distinguish it from the planned $q$}{trajectory $q(t)$ where $q(t')=q'$, $t_1\leq t' \leq t_2$ and $q(t)$ satisfies the velocity constraint $d(q(t),q(t+1))\leq v_{max}$}\rtron{, where $d(\cdot,\cdot)$ represents the distance between two points}.
 \end{definition}
 
-For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
+For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):·
 \begin{definition}\label{def:Reachability}
@@
 \end{definition}
-This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
+This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. 
  \begin{figure}
@@
 
-    \caption{\news (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robots are expected at given times $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period.
+    \caption{ (\ref{fig:EllipseConstraintExample}) The black line is the planned trajectory, $q_1$ and $q_2$ are two co-observed locations where the robots are expected at given times $t_1$ and $t_2$, dashed lines show a possible trajectory of a compromised robot during the unobserved period.
 The axis of global frame $\cF$ and canonical frame $\cF_{\cE}$ are shown as $x_{\cF}, y_{\cF}$ and $x_{\cE}, y_{\cE}$ respectively.
@@
 
-{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
+  The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$.
 \cref{def:secured-plan} can then be restated as follows:
@@
 \end{definition}
-}
+
 \subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
 \newcommand{\oFE}{o}
-{\news To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \cref{fig:EllipseConstraintExample} for an illustration).
+To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \cref{fig:EllipseConstraintExample} for an illustration).
 From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
-The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
+The full transformation from coordinates \new{$q^\cE\in\cF_\cE$} to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
 \begin{equation}\label{eq:transformations}
@@
 More details on \eqref{eq:transformations} are given in \cref{apx:transformation}.
-  % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
-  % \begin{align}
-  %   \nu_\cF &= \frac{q_2-q_1}{\norm{q_2-q_1}}, & \nu_\cE&=[1,0,0]^T;
-  % \end{align}
-  % \new{see Fig.\ref{fig:EllipseConstraintExample} for an illustration.
-Note that $\nu_{\cF}$ is a function of $q_1,q_2$ while $\nu_\cE$ is constant.
-From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation} (see \cref{sec:householder}), while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:}
-  % \begin{align} 
-  %   R&=H(\nu_\cF(q_1,q_2),\nu_\cE), &o&=\frac{1}{2}(q_1+q_2).
-  % \end{align}
-
-  Reachability constraints are formulated with respect to different types of forbidden regions a point, a plane, a segment, and a convex polygon.}
-  % We are now ready to formulate constraints based on reachability ellipsoids against different types of forbidden regions: a point, a plane, a segment, and a convex polygon which is is done by defining $D(q)$, its differential $\partial_qD(q)$, the set $\zeta$ and the projection $\Pi_\zeta$.
+
+  Reachability constraints are formulated with respect to different types of forbidden regions a point, a plane, a segment, and a convex polygon.
 
 \subsection{Point-ellipsoid reachability constraint}\label{sec:ellipsoid-point}
-% As shown in Fig.\ref{fig:Ellipse-to-point}, we consider a forbidden region in the shape of a single point $q_{avoid}$.
-The goal is to design the trajectory $q(t)$ such that $q_{avoid}\notin\mathcal{E}(q_1,q_2)$.
-This constraint can be written as,
-{\news For a forbidden region in the shape of a single point $q_{avoid}$ (\cref{fig:Ellipse-to-point}), the constraint is written as:}
+ For a forbidden region in the shape of a single point $q_{avoid}$ (\cref{fig:Ellipse-to-point}), the constraint is written as:
 \begin{constraint}[Point-ellipsoid reachability constraint]
@@
  Detailed methods for computing $s$ can be found in \cite{yang2021multi,yang2020multi,eberly}.
-
-  %The point to project, $q_{avoid}$, can be likewise expressed in $\cF_\cE$ as $\Eframe{q}_{avoid} =  H (\Fframe q_{avoid}-o)$.
-We now turn our attention to the problem of projecting $\Eframe{q}_{avoid}$ on the zero level set of $E^\cE$ (i.e., the reachability ellipsoid in the canonical frame).
-The derivations below are loosely inspired by \cite{eberly}.
-
-  %Let $q^\cE_p$ be the point on the surface of the ellipsoid, i.e., $\Eframe E(q^\cE_p) = 0$, corresponding to the projection of the point $q^\cE_{avoid}$.
-Using Lagrange multipliers applied to the constrained optimization problem \eqref{eq:ellipse-point-projection} (after transforming it in the canonical frame), one can show that the vector from a point to its projection, $q^\cE_{avoid}- q^\cE_p$, must be collinear with the gradient of $\Eframe \cE$, i.e.
- % \begin{equation}
- %   q^\cE_p- q^\cE_{avoid} = s \partial_q \Eframe E(q^\cE_p)\transpose = s Q q^\cE_p
-  %\end{equation}
-  %for some scale $s\in\real{}$;
- % thus $q^\cE_p$ can be written as:
 
@@
 
-\new{For a hyperplane shaped forbidden region $\mathcal{L}(q) = \{q\in\mathbb{R}^m: \vn\transpose q = d\}$ (\cref{fig:Ellipse-to-plane}), the reachability constraint is $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
-When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.}
-% Intuitively, $d_\cE$ can be thought as a distance between the the plane $\cL$ and the origin (i.e., the center of $\cE$).
+For a hyperplane shaped forbidden region $\mathcal{L}(q) = \{q\in\mathbb{R}^m: \vn\transpose q = d\}$ (\cref{fig:Ellipse-to-plane}), the reachability constraint is $\mathcal{L} \cap \mathcal{E}(q_1,q_2,a) = \emptyset$.
+When transformed into the canonical frame, the hyperplane can be written as $\Eframe \cL(\Eframe{q}) = \{  \Eframe{q}\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe{q} = d_{\cE}\}$, with $\vn_\cE = H(q_1,q_2)\vn, \quad d_\cE =-\vn\transpose o + d$.
 
@@
 \begin{definition}
- {\news The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ between the plane $\cL$ and the ellipsoid $\cE$ is defined on the plane by } 
+  The \emph{tangent interpolation point} $p^\cE_{\cL} \in \mathcal{L}$ between the plane $\cL$ and the ellipsoid $\cE$ is defined on the plane by 
     \begin{equation}\label{equ:ProjectPoint}
@@
   \end{equation}
-% \subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
-% {\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
-% For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
-% \begin{equation}
-% \bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
-% \end{equation}
-% When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e.
-red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}.
-Otherwise (i.e.
-brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.
-
-% \begin{constraint}[Line-segment-ellipsoid reachability constraint]
-% \begin{align}
-% D(\vq) &=  \begin{cases}
-% D_{p_{1}}(\vq) & (\Eframe{p_1}-\Eframe{p_2})\transpose (\Eframe{p_{\cL}}-\Eframe{p_2})<0\\
-% D_{p_{2}}(\vq) & (\Eframe{p_2}-\Eframe{p_1})\transpose (\Eframe{p_{\cL}} -\Eframe{p_1})<0\\
-% D_\Eframe{p_{\cL}}(\vq) & \textrm{otherwise}
-% \end{cases} \label{eq:segment_ellipsoid_constraint}\\
-%   \sZ &= \{\vq\in\mathbb{R}^{nm}:\norm{D(\vq)} = 0 \},\\
-%    \Pi_\sZ(\vz) & = 0, 
-% \end{align}
-% \end{constraint}
-% where $D_{p_{1}}$ and $D_{p_{2}}$ are the point-ellipsoid constraint projection function~\eqref{eq:point_ellipsoid_constraint} with respect to $\Eframe{p_{1}}$ and $\Eframe{p_{2}}$, and $D_\Eframe{p_{\cL}}$ is the plane-ellipsoid constraint~\eqref{eq:plane_ellipsoid_constraint}.
-with respect to frame $\Eframe {\cL}$.
 \subsection{Convex-polygon-ellipse reachability constraint}\label{sec:ellipse-region-constraint}  
-{\news  
 The reachability constraint for a convex polygon is treated as a union of reachability constraints for each individual segments that define the hyperplane. We define
@@
 keep foci waypoints outside the region, introduced in \cite{yang2020multi}) to prevent cases where the ellipse is a subset of the region.
-}
+
 \subsection{Secured planning results and limitation}\label{sec:ADMM-simulation}
-%All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent.
-%robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}).
-%We apply the new security constraints on the map exploration problem shown in \cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed.
-The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}.
-The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.
-
-We employ the \new{Attack-Proof MAPF (APMAPF)} solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (\cref{fig:Grid-example-application}).
+
+We employ the Attack-Proof MAPF (APMAPF) solver \cite{wardega2019resilience} on an 8 by 8 grid world with a similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (\cref{fig:Grid-example-application}).
 This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with an additional task function targeting the map exploration task.
@@
 Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions.
-{\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space.
+It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space.
 In this case, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids.
 Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated.
-For instance, in this scenario, we deploy a security camera as an additional security measure to observe agent 3 at time $8$ to ensure security.}
-
-The simulation result, shown in Fig.~\ref{fig:ReachabilitySimulation}, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3.
+For instance, in this scenario, we deploy a security camera as an additional security measure to observe agent 3 at time $8$ to ensure security.
+
+The simulation result, shown in Fig.~\ref{fig:ReachabilitySimulation}, displays reachability regions as black ellipsoids, demonstrating empty intersections with \new{region} 2 and 3.
 Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots.
-The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable.
+The intersections between obstacles and ellipsoids, as observed between agent 3 and \new{region} 1, are deemed tolerable.
 All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.
 
-%As depicted in Fig.\ref{fig:Grid-example-application}, no explicit tasks are assigned besides the start and goal locations.
-Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18.
-This result serves as the initial trajectory input for the ADMM solver.
-Considering this schedule, reachability for all agents in-between scheduled co-observations is constrained and kept away from the forbidden regions.
-% It's important to note that additional checkpoints (e.g., stationary security cameras) need to be incorporated to generate an attack-proof solution.
-Further solutions to avoid these checkpoints are discussed in \cref{sec:cross-trajectory}.
-
-%We utilize the APMAPF solver introduced in \cite{wardega2019resilience} to generate a MAPF plan with co-observation schedule on a grid-world application (Fig.\ref{fig:Grid-example-application}) and transform the result to a continuous configuration space, under the map exploration tasks.
-All robots have the task of collecting sensor information on the underlying vector field, with agent 3 having an additional task to visit the \emph{checkpoint} at time $8$.
-Assuming that the sensors on the robots return data with higher accuracy for locations closer to the agent, the robots should ideally perform a boustrophedon pattern (like the unconstraint result in Figure~\ref{fig:SecurityBreak}).
-We first set up an co-observation schedules considering two forbidden regions using the APMAPF algorithm, and add reachability constraints ensure a empty intersection between all robots' reachability regions between co-observations and forbidden regions.
-
-%As shown in Fig.\ref{fig:Grid-example-application}, no task has been assigned to the agent besides the start and goal location.
-Agent 1 and 2 need to meet at time 8 and 14, whereas agent 2 and 3 need to meet at time 18.
-This result is also used as the initial trajectory input for the ADMM solver.
-
-%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained.
-Notice that additional checkpoint (i.e.
-stationary security camera) need to be incorporated in order to generated an attack-proof solution.
-Additional solutions to avoid these checkpoints will be discussed in \cref{sec:cross-trajectory}.
-%The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}.
-The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3.
-Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles.
-Therefore, the intersections between obstacles and ellipsoids, i.e.
-the case here between agent 3 and zone 1, are tolerable.
-All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task.
 \begin{figure}
   \centering
-  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
-  \subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
-  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
+  \subfloat[Grid world result\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
   \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
-  \caption{{\news Trajectory design of a three-robot system based on the grid world result.
-Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions.
+  \caption{ Trajectory design of a three-robot system based on the grid world result.
+\new{Region} 1 is an obstacle, \new{region} 2 and \new{region} 3 are forbidden regions.
 (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective.
 (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.
-Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
+Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}
   \label{fig:example-application}
@@
 
-% \begin{figure}
-% \begin{center}
-%   \includegraphics[width=0.6\linewidth,trim =1cm 1.5cm 1cm 1.5cm, clip]{FinalResult}
-%   \caption{Securd result using co-observation and reachability constraints.}
-% \label{fig:ReachabilitySimulation}
-% \end{center}  
-% \end{figure}
-
-% \begin{figure}[htbp]
-% \centering
-% %\subfloat[Unsecured optimal trajectory\label{fig:SecurityBreak}]{\includegraphics[width=0.47\linewidth, trim =1cm 2cm 1cm 2cm, clip]{SecurityBreak}}
-% \subfloat[Secured trajectory\label{fig:ReachabilitySimulation}]{\includegraphics[width=0.6\linewidth]{FinalResult}}
-
-% \caption{ is the securd result with co-observation and reachability constraints.}
-% \label{fig:2_ADMM_result}
-% \end{figure}
-
 \subsubsection{Limitations}\label{sec:reachability-discussion}
 Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of MRS.
-{\news However, two primary challenges need to be addressed.
+However, two primary challenges need to be addressed.
 Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths.
@@
 This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of MRS deployments.
-These challenges are further addressed in \cref{sec:cross-trajectory}, ensuring the effective integration of reachability and co-observation in securing MRS.}
-
-%Our solution shows that planning with reachability and co-observation is a promising approach to enhance the security of multi-agent systems.
-However, two main challenges have been identified in \cite{wardega2023hola}.
-Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other.
-In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path.
-Agent 3 in the Figure \ref{fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas.
-Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \ref{fig:SecurityBreak} and \ref{fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots.
-This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems.
-These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
+These challenges are further addressed in \cref{sec:cross-trajectory}, ensuring the effective integration of reachability and co-observation in securing MRS.
 
@@
 
-{\news
 Our strategy is based on the following concept:
@@
 It represents either the first or last instance where a robot is co-observed by a teammate, and serves as a point where the robot can leave or join a new team.
-% at which a robot is co-observed by its teammates, and where it can leave or join a new team. 
 \end{definition}
-For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. %, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding location and time for checkpoint $v_{pi}$.
+For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. 
 To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
@@
   \end{remark}
-}
-{\news 
+
 \begin{definition}
@@
 The problem is then formulated into linear objectives and constraints, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
-}
 
@@
 Key function from \rrtstar{} is used during the construction of the checkpoint graph, specifically
-{\news\begin{description}
+\begin{description}
 \item[$\texttt{Cost}(v)$] This function returns a total travel distance to the unique path from the initial position to $v$. 
-\end{description}}
+\end{description}
 
@@
 In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
-{\news We use a heuristic approach (\cref{alg:graph}) to locate the checkpoints on given trajectories.
-\cref{alg:graph} is applied independently to each sub-team to generate their initial checkpoints.” While an optimal solution would likely be NP-hard, this approach works well enough for our purpose.} %with a toy example shown in Figure \ref{fig:checkpoint-generate}.
-
-% {\news
-%   \begin{enumerate}
-%   \item Initialization: Add the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, where $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
-%   \item Forward search: Find the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})$ does not overlap with any of the forbidden areas $F$.
-Once found, add $(q_{p}(t_{1}),t_1)$ to $V_{p}$.
-%   \item Backward search: Find the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\}$ such that the reachability ellipsoid $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3})$ does not overlap with any of the forbidden areas $F$.
-Once found, add $(q_{p}(t_{3}),t_3)$ to $V_{p}$.
-%   \item Update indices: $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$.
-%   \item Repeat the process until: $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$
-% \end{enumerate}}
+We use a heuristic approach (\cref{alg:graph}) to locate the checkpoints on given trajectories.
+\cref{alg:graph} is applied independently to each sub-team to generate their initial checkpoints.” While an optimal solution would likely be NP-hard, this approach works well enough for our purpose.
 
@@
 	\caption{Checkpoint Graph Initialization for Team $\cI_p$}\label{alg:graph}
-	{\news \begin{algorithmic}[1]
-	\State \textbf{Initialization:} Set $t_{0} \leftarrow 0$ and $t_{2} \leftarrow T$, and add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$ as \emph{start} and \emph{end vertices}.
-	\While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_{2}$}
-		\State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_{2}\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$.
+  \begin{algorithmic}[1]
+	{\news \State \textbf{Initialization:} Set $t_{0} \leftarrow 0$ and $t_{3} \leftarrow T$, and add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_3),t_3)$ to $V_{p}$ as \emph{start} and \emph{end vertices}.
+	\While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_3),t_{0},t_3) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_3$}
+		\State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_3\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$.
 Once found, add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
-		\State \textbf{Backward Search:} Find the smallest $t_{3}\in\{t_{1}, \dots, t_{2}-1\}$ such that $
-		\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Once found, add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
-		\State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_{2} \leftarrow t_{3}$.
-	\EndWhile
-	\end{algorithmic}}
+		\State \textbf{Backward Search:} Find the smallest $t_2\in\{t_{1}, \dots, t_3-1\}$ such that $
+		\mathcal{E}(q_{p}(t_3),q_{p}(t_2), t_3,t_2) \cap F = \emptyset.$ Once found, add $(q_{p}(t_2),t_2)$ to $V_{p}$.
+		\State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_3 \leftarrow t_2$.
+	\EndWhile}
+	\end{algorithmic}
 	\end{algorithm}
-% {\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
-Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e.
-$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$.
-Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$.
-Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$.
-Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$.
-Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process.
-The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$.
-A toy example is shown in \cref{fig:checkpoint-generate}.
-}
-
-\begin{figure}
+\begin{figure}[h]
 	\centering
-    \subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_1-v2}}
-    \subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_2-v2}}
-    \caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
+    \subfloat{\includegraphics[width=0.47\linewidth,valign=c]{SC_gen_1_v3}}
+    \subfloat{\includegraphics[width=0.47\linewidth,valign=c]{SC_gen_2_v3}}
+    \caption{\news Example of \cref{alg:graph}.
+Start at both ends, each trajectory finds the largest reachability region avoiding forbidden areas, then repeats the process on remaining segments to build secure checkpoints.}\label{fig:checkpoint-generate}
 \end{figure}
-
-% \begin{algorithm}
-%   \caption{Secure Checkpoint Generation for a Sub-Team $p$}\label{alg:checkpoint-gen}
-%   \begin{algorithmic}
-%   \State $v_{p0} \gets (q_{p}(0),0)$; $v_{pT} \gets (q_{p}(T),T)$
-%   \State $V_{p} = \{v_{p0}, v_{pT}\}$
-%   \State $t_0 \gets 0$; $t_1 \gets T$
-%   \While {$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}),t_{0},t_{1}) \intersect F \neq \emptyset$ or $t_1 - t_0 > 1$}
-%     \State $i \gets 1$; $j\gets 1$
-%     \While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{0}+i),t_{0},t_0+i) \intersect F = \emptyset$ and $t_0+i > t_1$}
-%       \State $v_{pf} \gets (q_{p}(t_0+i),t_0+i)$
-%       \State $i \gets i+1$
-%     \EndWhile
-%     \State $V_{p}\gets V_{p}\union v_{pf}$
-%     \While{$\mathcal{E}(q_{p}(t_{1}-j),q_{p}(t_{1}),t_{1}-j,t_{1}) \intersect F = \emptyset$ and $t_0+i \geq t_1-j$}
-%     \State $v_{pb} \gets (q_{p}(t_1-j),t_1-j)$
-%     \State $j \gets j+1$
-%     \EndWhile
-%     \If {$t_0+i \neq t_1-j$}
-%     \State $V_{p}\gets V_{p}\union v_{pb}$
-%     \EndIf
-%   \EndWhile
-%   \end{algorithmic}
-%   \rtron{It is probably better to substitute this with a description in words. If you want to keep the pseudocode, move it to the appendix.}
-%   \end{algorithm}
-
-% \begin{figure}
-% 	\centering
-%     \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_1}}
-%     \subfloat[]{\includegraphics[width=0.45\linewidth]{SC_gen_2}}
-%     \caption{Checkpoint generation example}\label{fig:checkpoint-generate}
-% \end{figure}
 
@@
 To enable co-observation across different sub-teams at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories, allowing robots to deviate from one sub-team to perform co-observation with a different sub-team.
-%\begin{remark}
 
 Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ corresponds to a security checkpoint $\union_p V_p$.
-The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur {\news while switching trajectories}.
-%\end{remark}
+The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur  while switching trajectories.
 
@@
   \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,valign=c]{security_graph-v2}}
-  \caption{{\news (\ref{fig:two-edges}) The latest departure node $q^{d}_{b}$ found for $v_{r1}$ and the earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
-(\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}}
+  \caption{ (\ref{fig:two-edges}) The latest departure node $q^{d}_{b}$ found for $v_{r1}$ and the earliest arrival node $q^{a}_{b}$ found for $v_{r3}$.
+(\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}
 \end{figure}
 
-%We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone through \rrtstar{} (ignoring, for the moment, any timing constraint).
-Then, we prune these trees by considering time constraints (that consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints) and ellipsoidal reachability constraints.
-
 We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone (ignoring, for the moment, any timing constraint). 
-More precisely, \new{for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on the reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.}
+More precisely, for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on the reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.
 Then, to prune these trees, we consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints.
@@
 For each trajectory $r\neq p$, we define the \emph{earliest arrival node} from $v_p$ to $v_{ea} = (q_{r}(t^{a}_r),t^{a}_r)$ as the arrival node characterized by the minimum $t^{a}_r$ discovered.
-%$t^{a}_r$ is designated as the \emph{earliest arrival time}.
 
@@
 For each trajectory $r\neq p$, we define the \emph{latest departure node} $v_{ld}=(q_{r}(t^{d}_r),t^{d}_r)$ as the departure node characterized by the maximum $t^{d}_r$ discovered.
-% $t^{d}_r$ is designated as the \emph{latest departure time}.
 \end{description}
-% For each $v_{p} \in V_{p}$, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$.
-Examples are shown in \cref{fig:two-edges}.
-{\news The set $V_c$ contains all the \emph{latest departure} and \emph{earliest arrival} nodes (if they are not identified as checkpoints already); the corresponding paths are added as cross-trajectory edges $E_q$.
-A toy example is shown in \cref{fig:two-edges}.}
+
+The set $V_c$ contains all the \emph{latest departure} and \emph{earliest arrival} nodes (if they are not identified as checkpoints already); the corresponding paths are added as cross-trajectory edges $E_q$.
+A toy example is shown in \cref{fig:two-edges}.
 
 \subsubsection{In-trajectory edges}\label{sec:Graph-intro}
-\new{We group $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
+We group $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$.
 For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing the corresponding segment of the planned trajectory.
 Examples are shown in \cref{fig:security-graph-generate}.
-}
-
-%For convenience, we use $|V_{q}|$ and $|E_{q}|$ to denote the cardinality of the sets $V_{q}$ and $E_{q}$
 
@@
 In practice, after a cross-trajectory robot joins a team, it is considered interchangeable and could switch roles with the reference robot of that trajectory.
-% (i.e., the original reference robot might serve as a cross-trajectory robot in a later cross-trajectory co-observation).
 \end{remark}
 
-{\news To formulate the problem as a network multi-flow problem, we augment the checkpoint graph to a flow graph.
+To formulate the problem as a network multi-flow problem, we augment the checkpoint graph to a flow graph.
 A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node are added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$.
-Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v^{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v^{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}
-
-%The goal is to find paths in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
+Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v^{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v^{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).
+
 The path of a robot $k$ all starts from $v^{+}$ and ends at $v^{-}$, and are represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$.
 The planning problem can be formulated as a vertex path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \cref{rmk:revised-security}).
-%Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.
 
@@
 The first term in the cost \eqref{eq:flow-cost} represents the total number of robots used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms.
-{\news The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
+ The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$).
 The flow coverage constraint \eqref{eq:FlowCoverage} ensures that all checkpoints $ \{V^{s}_{p}\}$ have been visited and can support a co-observation.
 The checkpoint graph $G$ is acyclic, placing this problem in complexity class $P$; thus, it can be solved in polynomial time \cite{1702662}.
-}
 
@@
 The network flow problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follow the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).
-%Additionally, for a fixed number of robots $\cK \geq N_{p}$,
 It is possible for the resulting flows to have a subset of flows $F_{e} \in F$ that is empty, i.e.
@@
   \subfloat[Checkpoint graph and result flows \label{fig:previous_result_graph}]{\includegraphics[width=0.47\linewidth, trim = 10cm 3cm 7cm 3cm,clip,valign=b]{old_result_graph_v2}}
-  \caption{\new{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as arrows on top of the original plan in \cref{fig:previous_result_plan}.
-(\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}}
+  \caption{(\ref{fig:previous_result_plan}) The cross-trajectory co-observation plan is shown as arrows on top of the original plan in \cref{fig:previous_result_plan}.
+(\ref{fig:previous_result_graph}) The checkpoint graph and resulting flows highlighted.}
   \label{fig:3-team-ctco}
@@
 Using the parameters $w_{c}=10$, $w_{t}=1$ and $\rho = 0.01$, the result returns a total of $\cK=3$ surveillance robots with cross-trajectory plan shown in \cref{fig:3-team-ctco}.
-%In \cref{fig:previous_result_grap}, each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
 The flows derived from the solution of the optimization problem \eqref{eq:flow-coverage-problem} are highlighted in the graph \cref{fig:previous_result_graph}, where each horizontal line represents the original trajectory of a sub-team and the number on each vertex $v_{i}$ represents the corresponding time $t_{i}$.
@@
   \centering
-  %\subfloat[Unsecured plan\label{fig:unsecured-plan}]{\includegraphics[width=0.31\linewidth, trim = 3cm 2cm 3cm 2cm, clip,valign=c]{SecurityBreak}}
   \subfloat[4-agent case\label{fig:Result-plan}]{\includegraphics[width=0.47\linewidth,trim = 1cm 1cm 1.5cm 0cm, clip,valign=c]{Traj_result_v3.png}}
-  %\subfloat[Graph flow result\label{fig:result-graph}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{Graph_result}}
   \subfloat[7-agent case\label{fig:Result-plan-7-team}]{\includegraphics[width=0.47\linewidth,trim = 3.5cm 2cm 1.5cm 0cm, clip,valign=c]{7-team-plan_v2.png}}
-  %\subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
-  \caption{\new{(\ref{fig:Result-plan}) Cross-trajectory co-observation result of a 4 sub-teams task.
-(\ref{fig:Result-plan-7-team}) Cross-trajectory co-observation result of a 7 sub-teams task.}}\label{fig:Cross-trajectory-result}
+  \caption{(\ref{fig:Result-plan}) Cross-trajectory co-observation result of a 4 sub-teams task.
+(\ref{fig:Result-plan-7-team}) Cross-trajectory co-observation result of a 7 sub-teams task.}\label{fig:Cross-trajectory-result}
 \end{figure}
-
-% \begin{figure}
-%   \centering
-%    \subfloat[Cross-trajectory co-observation plan\label{fig:Result-plan-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 2cm 4cm 2cm, clip,valign=c]{7-team-plan.png}}
-%   \subfloat[Graph flow result\label{fig:result-graph-7-team}]{\includegraphics[width=0.47\linewidth,trim = 4cm 0cm 4cm 0cm, clip,valign=c]{7-team-graph.png}}
-%   \caption{Cross-trajectory co-observation result of a 7 sub-teams task.}\label{fig:Cross-trajectory-result-7}
-% \end{figure}
 
@@
 
-%This paper introduces security measures to protect Multi-Robot Systems (MRS) from plan-deviation attacks by setting up mutual obversation schedule to guarangee that any deviations into forbidden regions will break the schedule and trigger detection.
-We incorporate the co-observation requirements and reachability analysis into the trajectory planning phase and formulate them as constraints for the optimal problem.
-In scenarios where a secured plan is infeasible or better task performance is needed, we propose the use of redundant robots for cross-trajectory co-observations, providing the same security guarantees against plan-deviation attacks.
-However, given the time-sensitive nature of co-observation and the need for close proximity, collision avoidance during co-observation planning becomes crucial.
-Future work will focus on integrating collision avoidance into the planning phase.
-Additionally, dynamic assignment of duties within sub-teams will be explored, making it more challenging for attackers to plan and execute successful attacks.
-
-%In this paper, we provide methods to enhance the security of a MRS against plan-deviation attacks.
-First, by introducing co-observation schedule and keeping reachability region during unobserved periods away from the forbidden regions, we provide an secured trajectory optimized for certain scenarios with guarantees that any deviations to forbidden regions will for sure break the schedule and get detected.
-Additionally, for scenarios that requires better task performance or when a secured plan is not feasible, we introduce redundant robots to performs cross-trajectory co-observations that can provide any unsecured MRS trajectories with the same security guarantee.
-
-%As co-observation is time-sensitive and requires robots to be in close proximity, it is important to consider the possible collision during co-observation planning.
-The main future work will focus on including collision avoidance in the planning phase.
-Additionally, the assignment of the duties within the sub-team can performed dynamically, making it more difficult for attackers to successfully plan and execute attacks.
-This makes realtime task assignment and control another topic worth looking into.
-
 \appendix
-{\news
 \subsection{Transformation of a reachability ellipsoid to canonical frame}\label{apx:transformation}
@@
 \subsection{Householder rotations}\label{sec:householder}
-\new{We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \cref{sec:reachability,sec:ellipse-region-constraint}.
+We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \cref{sec:reachability,sec:ellipse-region-constraint}.
 This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}.
-% With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection). 
 We call our version of the operator a \emph{Householder rotation}.
-In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.}
+In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.
 \begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
-  % \begin{equation}
-  %   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
-  % \end{equation}
 the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
@@
 \begin{proposition}\label{prop:HProperty}
-  The matrix $H$ has the following properties:
+ {\news The matrix $H$ has the following properties:
   \begin{enumerate}
-  \item It is a rotation, i.e.
-    \begin{enumerate}
-    \item\label{it:orthonormality} $H\transpose H=I$;
-    \item\label{it:determinant} $\det(H)=1$.
-    \end{enumerate}
+  \item\label{it:rotation} It is a rotation, i.e. (a) $H\transpose H=I$; (b) $\det(H)=1$
+  % \begin{enumerate}
+  %   \item\label{it:orthonormality} $H\transpose H=I$;
+  %   \item\label{it:determinant} $\det(H)=1$.
+  %   \end{enumerate}
   \item\label{it:transformation} $\nu_2=H \nu_1$.
-  \end{enumerate}
+  \end{enumerate}}
 \end{proposition}
 \begin{proof}
-  For subclaim~\ref{it:orthonormality}:
-  \begin{equation}
-    H\transpose H=H^2=4uu\transpose u u\transpose - 4uu\transpose +I^2=I,
-  \end{equation}
-  since $u\transpose u=1$.
-
-  For subclaim~\ref{it:determinant}, let $U=\bmat{u & u^\bot_{1} & u^\bot_{2}}$, where $u^\bot_{1},u^\bot_{2}$ are two orthonormal vectors such that $I=UU\transpose=uu\transpose + u^\bot_{1}(u^\bot_{1})\transpose+u^\bot_{2}(u^\bot_{2})\transpose$; then, substituting $I$ in \eqref{eq:H definition}, we have that the eigenvalue decomposition of $H$ is given by
+ {\news For subclaim~\ref{it:rotation}a,  since $u\transpose u=1$:
+  \begin{equation}
+    H\transpose H=H^2=4uu\transpose u u\transpose - 4uu\transpose +I^2=I.
+  \end{equation}}
+
+  For subclaim~\ref{it:rotation}b, let $U=\bmat{u & u^\bot_{1} & u^\bot_{2}}$, where $u^\bot_{1},u^\bot_{2}$ are two orthonormal vectors such that $I=UU\transpose=uu\transpose + u^\bot_{1}(u^\bot_{1})\transpose+u^\bot_{2}(u^\bot_{2})\transpose$; then, substituting $I$ in \eqref{eq:H definition}, we have that the eigenvalue decomposition of $H$ is given by
   \begin{equation}
@@
 \end{equation}
-such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. %One can verify by direct computation the following property:
-%\begin{equation}\label{eq:asymmetric to cross}
-%  wv\transpose-vw\transpose=\cross{\cross{v}w}.
-%\end{equation}
+such that $[v]_\times w=v\times w$ for any $w\in\real{3}$. 
 \begin{proposition}\label{prop:Hderivitive}
@@
   \end{proof}
-}
+
   \subsection{Proof of proposition \ref{prop:Ellipse2PointDiff}}\label{proof:Ellipse2PointDiff}
